### 2019-09-13 theme.tex
adds section documents

\section{Theme}

\Huge{Saving the World One Atom at a Time}\\

There are many challenges facing the world today. Some of these have been designated existential threats to humanity. As students, these obstacles may appear insurmountable. The ANS Student Conference is a marvelous opportunity to inspire optimism for the future as researchers, professionals, and others students, gather to showcase critical advances in technology. Whether the problem is solving the world's energy needs, developing technology to take us to the stars, or curing cancer, nuclear, plasma, and radiological engineering will be at the center of those endeavors. Our goal is to inspire and motivate students in these fields to tackle these grand challenge problems. Students will hear from visionary speakers and leaders of the nuclear science community. They will leave with renewed hope for the future and the knowledge that their efforts are saving the world, one atom at a time.\\
The University of Illinois at Urbana-Champaign would honored to host the ANS Student Conference in 2021 and to share the innovative and galvanizing environment of our great campus.

### 2019-09-13 theme.tex
adds some images

@@
 As students, these obstacles may appear insurmountable.
-The ANS Student Conference is a marvelous opportunity to inspire optimism for the future as researchers, professionals, and others students, gather to showcase critical advances in technology.
-Whether the problem is solving the world's energy needs, developing technology to take us to the stars, or curing cancer, nuclear, plasma, and radiological engineering will be at the center of those endeavors.
-Our goal is to inspire and motivate students in these fields to tackle these grand challenge problems.
+The ANS Student Conference is a marvelous opportunity to inspire optimism for the future as researchers, professionals, and students, gather to showcase critical advances in technology.
+Nuclear, plasma, and radiological engineering will be central to endeavors like solving the world's energy needs, developing technology that will take us to the stars, treating cancer, and many others.
+Our goal is to inspire and motivate students in these fields to tackle grand challenge problems.
 Students will hear from visionary speakers and leaders of the nuclear science community.

### 2019-09-13 main.tex
updates main file

\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{{./images/}}

\begin{document}

\begin{titlepage}
   \begin{center}
       \vspace*{1cm}

       \textbf{Saving the World One Atom at a Time}

       \vspace{0.5cm}
       Nuclear, Plasma, and Radiological Engineering

       \vspace{1.5cm}

       \textbf{Presented by ANS at the University of Illinois Urbana-Champaign}

       \vfill
       \vspace{0.8cm}

       \includegraphics[width=0.4\textwidth]{ans_sc_logo2.png}
   \end{center}
\end{titlepage}

\input{letter}
\input{theme}
\input{uiuc}
\input{conflog}
\input{proglog}
\input{management}
\input{budget}

\end{document}

### 2019-09-13 uiuc.tex
adds info about uiuc

\section{Urbana-Champaign and UIUC}

\subsection{About Urbana-Champaign}
Champaign-Urbana (CU) is a close-knit community filled with music, culture, and food. While Campustown, the neighborhood immediately surrounding campus,  is an important part of the atmosphere, there is plenty to do off campus. Relax in one of the outdoor restaurants downtown or walking through the various gardens and parks around town. The culture in Champaign is very rich as a result of many annual festivals such as the CU Pride Parade, the Ellnora guitar festival, and the Pygmalion festival. The Krannert Center for the Performing Arts is also a world-renowned theater that has hosted groups from all genres like the New York Philharmonic, the Russian National Ballet, and Sonny Rollins.

\subsubsection{Accessibility}
Myriad festivals and sporting events on campus draw many people to Champaign-Urbana at varying times of the year, which means hotels are not hard to find. A large number of these hotels are located around downtown Champaign and the Eastern side of campus, making transportation easy. There is also a small airport, Willard Airport, just 20 minutes from campus that regularly has flights to and from the Chicago O’Hare and Dallas Ft Worth airports. Finally, there are several reliable bus services that make frequent trips from Champaign-Urbana to O’Hare and the Chicagoland area.

\subsubsection{Weather}
With an average high temperature of 65℉ and an average low temperature of 40℉, April in Champaign is a gorgeous month of dwindling winter weather as summer begins to round the corner. Holding a conference during this time would be the perfect way to showcase our beautiful city.

\subsubsection{About the University of Illinois}
Founded in 1867, the University of Illinois at Urbana-Champaign (UIUC) has cultivated a long history of significant scientific discoveries and contributions. The theory of superconductivity, the invention of the transistor, the discovery of archaea, the fourth domain of life, and the first web browser are just some of the many breakthroughs from UIUC. Established in 1876, the famous Morrow Plots became the first research crop field at a university and is still used today. Attendees will also be familiar with Blue Waters, one of the world’s fastest supercomputers. 
The UIUC Grainger College of Engineering has had sixteen Nobel Laureates in physics. Including John Bardeen, the only scientist to ever win the award twice. It also offers 15 different majors to more than 9,100 undergraduate and 3,400 graduate students. Of its twelve ranked majors, nine are ranked among the top 10 in the nation, and six of which remain ranked among the top 5 in their degree. Overall, the College of Engineering in Urbana-Champaign ranks sixth among the nation’s best undergraduate engineering programs. With more than 250 degrees for undergraduates and graduates and a multitude of first-class research facilities and resource, UIUC gives its 45,000 students the ability to succeed.\\
Today, the University of Illinois at Urbana-Champaign attracts visitors from throughout the state by offering a variety of valuable public attractions. UIUC maintains four public museums: the Spurlock Museum, containing 54,000 cultural artifacts from around the world; the Illinois Natural History Survey, possessing more than 9.5 million biologic specimens in its collection; the Sousa Archives and Center for American Music, providing shows and education to students and the public; and the Krannert Art Museum, providing fine arts events and education. More than 470,000 square feet of recreational space is occupied by other facilities including an ice arena, climbing wall, swimming pools, parks, sports fields, parks, and outdoor adventure venues. In the fall, football, volleyball, and Marching Illini fans tailgate and spectate at Memorial Stadium or Huff Hall. During the winter and spring, our Illini support many teams, including the basketball teams at the newly remodelled State Farm Center. Throughout the year, the university supports 21 different sports teams and finds ways for Illini to enjoy friendly competition whether they participate, cheer, or simply watch the events.

\subsubsecton{UIUC ANS Student Chapter (ANS-UIUC)}
The ANS-UIUC maintains and develops a cohesive community of students in nuclear engineering. It also engages in education and outreach programs to teach members of the surrounding community about nuclear science. Membership is currently around 70-80 students and has been steadily growing. The chapter works to host events catering to nuclear, plasma, and radiological concentrations. It also makes professional development a large part of member involvement. Below is an outline of the ways ANS-UIUC participates in activism, outreach, and professional development.

\begin{figure}
	\centering
	\includegraphics[width=9cm]{ans_uiuc_group.jpg}
\end{figure}

### 2019-09-13 uiuc.tex
adds image and info about uiuc

@@
-\section{Urbana-Champaign and UIUC}
+\section*{Urbana-Champaign and UIUC}
 
-\subsection{About Urbana-Champaign}
+\subsection*{About Urbana-Champaign}
 Champaign-Urbana (CU) is a close-knit community filled with music, culture, and food.
@@
 
-\subsubsection{Accessibility}
+\subsubsection*{Accessibility}
 Myriad festivals and sporting events on campus draw many people to Champaign-Urbana at varying times of the year, which means hotels are not hard to find.
@@
 
-\subsubsection{Weather}
+\subsubsection*{Weather}
 With an average high temperature of 65℉ and an average low temperature of 40℉, April in Champaign is a gorgeous month of dwindling winter weather as summer begins to round the corner.
@@
 
-\subsubsection{About the University of Illinois}
+\subsection*{About the University of Illinois}
 Founded in 1867, the University of Illinois at Urbana-Champaign (UIUC) has cultivated a long history of significant scientific discoveries and contributions.
@@
 Today, the University of Illinois at Urbana-Champaign attracts visitors from throughout the state by offering a variety of valuable public attractions.
-UIUC maintains four public museums: the Spurlock Museum, containing 54,000 cultural artifacts from around the world; the Illinois Natural History Survey, possessing more than 9.5 million biologic specimens in its collection; the Sousa Archives and Center for American Music, providing shows and education to students and the public; and the Krannert Art Museum, providing fine arts events and education.
+UIUC maintains four public museums: the Spurlock Museum, containing 54,000 cultural artifacts from around the world; the Illinois Natural History Survey, has more than 9.5 million biologic specimens in its collection; the Sousa Archives and Center for American Music, provides shows and education to students and the public; and the Krannert Art Museum, offers fine arts and education.
 More than 470,000 square feet of recreational space is occupied by other facilities including an ice arena, climbing wall, swimming pools, parks, sports fields, parks, and outdoor adventure venues.
-In the fall, football, volleyball, and Marching Illini fans tailgate and spectate at Memorial Stadium or Huff Hall.
-During the winter and spring, our Illini support many teams, including the basketball teams at the newly remodelled State Farm Center.
-Throughout the year, the university supports 21 different sports teams and finds ways for Illini to enjoy friendly competition whether they participate, cheer, or simply watch the events.
 
-\subsubsecton{UIUC ANS Student Chapter (ANS-UIUC)}
+\subsecton{UIUC ANS Student Chapter (ANS-UIUC)}
 The ANS-UIUC maintains and develops a cohesive community of students in nuclear engineering.
@@
 It also makes professional development a large part of member involvement.
-Below is an outline of the ways ANS-UIUC participates in activism, outreach, and professional development.
+ANS-UIUC has historically been one of the best represented institutions at the annual student conference and is a tradition this chapter is eager to uphold.
 
-\begin{figure}
+% Group picture from the 2019 kick off barbeque.
+\begin{figure}[H]
 	\centering
@@
 \end{figure}
+
+% Picture of attendees to the 2019 ANS Student Conference
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=9cm]{ans_conf_19.jpg}
+\end{figure}

### 2019-09-14 proglog.tex
update program logistics (proglog.tex)

\section{Program Logistics}

% Request review from Katy Huff
\subsection{Potential Speakers}

### 2019-09-15 draft.tex
adds word documents and a draft file

\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{float}
\graphicspath{{./images/}}

\begin{document}

\begin{titlepage}
   \begin{center}
       \vspace*{1cm}

       \textbf{Saving the World One Atom at a Time}

       \vspace{0.5cm}
       Nuclear, Plasma, and Radiological Engineering

       \vspace{1.5cm}

       \textbf{Presented by ANS at the University of Illinois Urbana-Champaign}

       \vfill
       \vspace{0.8cm}

       \includegraphics[width=0.4\textwidth]{ans_sc_logo2.png}
   \end{center}
\end{titlepage}

\section{Theme}
$\Huge{Saving the World One Atom at a Time}$\\
There are many challenges facing the world today and some have been designated existential threats to humanity. Young people today will witness the growing toll of anthropogenic climate change. As students, obstacles at the scale of the world climate crisis appear daunting and overwhelming. We believe that many solutions will come from the nuclear sciences. The ANS student conference is an opportunity for students and professionals to come together and share advances in critical technology and research, dedicated to solving these problems. Whether the problem is solving the world’s energy needs, developing technology that will take us to the stars, or curing cancer, nuclear, plasma, and radiological engineering will be at the center of those endeavors. Our goal is to inspire and motivate students in nuclear, plasma, and radiological engineering fields to tackle big problems. Saving the world one atom at a time reflects the fact that nuclear science is a powerful force in dealing with grand challenge problems. This theme also honors the individual, atomic, contributions from students, researchers, and professionals, in the field of nuclear engineering, that are essential to progress. This conference is about science and it is about the people that make the science possible. Students will hear from visionary speakers and leaders of the nuclear science community and come away with optimism for the future; knowing that they are saving the world one atom at a time.\\
The University of Illinois at Urbana-Champaign chapter of ANS would be honored to host the 2021 student conference. We hope to create an atmosphere that will galvanize students and professionals for the exciting future of nuclear engineering

\section{Letter from the Chairs}

\section{About UIUC}
\section{Conference Logistics}
\section{Program Logistics}
\section{Conference Management}
\section{Conference Budget}

\end{document}

### 2019-09-15 draft.tex
adds stuff to draft

@@
 \usepackage{graphicx}
+\usepackage{eso-pic}
+\usepackage{soul}
+% \usepackage{background}
 \usepackage{float}
+\usepackage[top=2cm, bottom=2cm, outer=2cm, inner=2cm]{geometry}
+\setcounter{tocdepth}{3}
+\setcounter{secnumdepth}{3}
+
 \graphicspath{{./images/}}
+
+% \backgroundsetup{
+% scale=1,
+% angle=-90,
+% opacity=.4,  %% adjust
+% contents={\includegraphics[width=\paperwidth,height=\paperheight]{earth1.png}}
+% }
 
@@
 \begin{titlepage}
+\AddToShipoutPictureBG*{\includegraphics[angle=90, width=\paperwidth,height=\paperheight]{earth1.png}};
+
    \begin{center}
+
        \vspace*{1cm}
@@
 
-       \includegraphics[width=0.4\textwidth]{ans_sc_logo2.png}
+       \includegraphics[width=0.4\textwidth]{ans_sc_logo3.png}
    \end{center}
@@
 
+\clearpage
+\tableofcontents
+\newpage
+
+% ===============================================================================================
+% ===============================================================================================
+% ============================================THEME==============================================
+% ===============================================================================================
+% ===============================================================================================
 \section{Theme}
-$\Huge{Saving the World One Atom at a Time}$\\
+\subsection{Letter from the chairs}
 There are many challenges facing the world today and some have been designated existential threats to humanity.
@@
 
+\newpage
 \section{Letter from the Chairs}
 
-\section{About UIUC}
+% ===============================================================================================
+% ===============================================================================================
+% ========================================About UIUC=============================================
+% ===============================================================================================
+% ===============================================================================================
+
+\newpage
+\section{Champaign-Urbana and UIUC}
+\subsection*{About Champaign-Urbana}
+Champaign-Urbana (CU) is a close-knit community filled with music, culture, and food.
+While Campustown, the neighborhood immediately surrounding campus,  is an important part of the atmosphere, there is plenty to do off campus.
+Relax in one of the outdoor restaurants downtown or walking through the various gardens and parks around town.
+The culture in Champaign is very rich as a result of many annual festivals such as the CU Pride Parade, the Ellnora guitar festival, and the Pygmalion festival.
+The Krannert Center for the Performing Arts is also a world-renowned theater that has hosted groups from all genres like the New York Philharmonic, the Russian National Ballet, and Sonny Rollins.
+
+\subsubsection*{Accessibility}
+Myriad festivals and sporting events on campus draw many people to Champaign-Urbana at varying times of the year, which means hotels are not hard to find.
+A large number of these hotels are located around downtown Champaign and the Eastern side of campus, making transportation easy.
+There is also a small airport, Willard Airport, just 20 minutes from campus that regularly has flights to and from the Chicago O’Hare and Dallas Ft Worth airports.
+Finally, there are several reliable bus services that make frequent trips from Champaign-Urbana to O’Hare and the Chicagoland area.
+
+\subsubsection*{Weather}
+With an average high temperature of 65$^\circ$F and an average low temperature of 40$^\circ$F , April in Champaign is a gorgeous month of dwindling winter weather as summer begins to round the corner.
+Hlding a conference during this time would be the perfect way to showcase our beautiful city.
+
+\subsection*{About the University of Illinois}
+Founded in 1867, the University of Illinois at Urbana-Champaign (UIUC) has cultivated a long history of significant scientific discoveries and contributions.
+The theory of superconductivity, the invention of the transistor, the discovery of archaea, the fourth domain of life, and the first web browser are just some of the many breakthroughs from UIUC.
+Established in 1876, the famous Morrow Plots became the first research crop field at a university and is still used today.
+Attendees will also be familiar with Blue Waters, one of the world’s fastest supercomputers.
+The UIUC Grainger College of Engineering has had sixteen Nobel Laureates in physics.
+Including John Bardeen, the only scientist to ever win the award twice.
+It also offers 15 different majors to more than 9,100 undergraduate and 3,400 graduate students.
+Of its twelve ranked majors, nine are ranked among the top 10 in the nation, and six of which remain ranked among the top 5 in their degree.
+Overall, the College of Engineering in Urbana-Champaign ranks sixth among the nation’s best undergraduate engineering programs.
+With more than 250 degrees for undergraduates and graduates and a multitude of first-class research facilities and resource, UIUC gives its 45,000 students the ability to succeed.\\
+Today, the University of Illinois at Urbana-Champaign attracts visitors from throughout the state by offering a variety of valuable public attractions.
+UIUC maintains four public museums: the Spurlock Museum, containing 54,000 cultural artifacts from around the world; the Illinois Natural History Survey, has more than 9.5 million biologic specimens in its collection; the Sousa Archives and Center for American Music, provides shows and education to students and the public; and the Krannert Art Museum, offers fine arts and education.
+More than 470,000 square feet of recreational space is occupied by other facilities including an ice arena, climbing wall, swimming pools, parks, sports fields, parks, and outdoor adventure venues.
+
+\subsection*{UIUC ANS Student Chapter (ANS-UIUC)}
+The ANS-UIUC maintains and develops a cohesive community of students in nuclear engineering.
+It also engages in education and outreach programs to teach members of the surrounding community about nuclear science.
+Membership is currently around 70-80 students and has been steadily growing.
+The chapter works to host events catering to nuclear, plasma, and radiological concentrations.
+It also makes professional development a large part of member involvement.
+ANS-UIUC has historically been one of the best represented institutions at the annual student conference and is a tradition this chapter is eager to uphold.
+
+% Group picture from the 2019 kick off barbeque.
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=12cm]{ans_uiuc_group.jpg}
+  \caption{Members of ANS-UIUC at the 2019 Kick Off Barbeque.}
+\end{figure}
+
+% Picture of attendees to the 2019 ANS Student Conference
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=12cm]{ans_conf_19.jpg}
+  \caption{Members of ANS-UIUC at the 2019 Student Conference at VCU.}
+\end{figure}
+% ===============================================================================================
+% ===============================================================================================
+% =====================================Conference Logistics======================================
+% ===============================================================================================
+% ===============================================================================================
+
+\newpage
 \section{Conference Logistics}
+
+% ===============================================================================================
+% ===============================================================================================
+% ======================================Program Logistics========================================
+% ===============================================================================================
+% ===============================================================================================
+\newpage
 \section{Program Logistics}
+
+% ===============================================================================================
+% ===============================================================================================
+% ====================================Conference Management======================================
+% ===============================================================================================
+% ===============================================================================================
+\newpage
 \section{Conference Management}
+
+% ===============================================================================================
+% ===============================================================================================
+% ======================================Conference Budget========================================
+% ===============================================================================================
+% ===============================================================================================
+
+\newpage
 \section{Conference Budget}

### 2019-09-15 draft.tex
made changes to the draft

@@
 \setcounter{tocdepth}{3}
-\setcounter{secnumdepth}{3}
+% \setcounter{secnumdepth}{3}
 
@@
 
-       \textbf{Saving the World One Atom at a Time}
+       \Huge\textbf{Saving the World One Atom at a Time}
 
@@
 The University of Illinois at Urbana-Champaign chapter of ANS would be honored to host the 2021 student conference.
-We hope to create an atmosphere that will galvanize students and professionals for the exciting future of nuclear engineering
-
-\newpage
-\section{Letter from the Chairs}
+We hope to create an atmosphere that will galvanize students and professionals for the exciting future of nuclear engineering.
 
@@
 \section{Champaign-Urbana and UIUC}
-\subsection*{About Champaign-Urbana}
+\subsection{About Champaign-Urbana}
 Champaign-Urbana (CU) is a close-knit community filled with music, culture, and food.
@@
 
-\subsubsection*{Accessibility}
+\subsubsection{Accessibility}
 Myriad festivals and sporting events on campus draw many people to Champaign-Urbana at varying times of the year, which means hotels are not hard to find.
@@
 
-\subsubsection*{Weather}
+\subsubsection{Weather}
 With an average high temperature of 65$^\circ$F and an average low temperature of 40$^\circ$F , April in Champaign is a gorgeous month of dwindling winter weather as summer begins to round the corner.
@@
 
-\subsection*{About the University of Illinois}
+\subsection{About the University of Illinois}
 Founded in 1867, the University of Illinois at Urbana-Champaign (UIUC) has cultivated a long history of significant scientific discoveries and contributions.
@@
 
-\subsection*{UIUC ANS Student Chapter (ANS-UIUC)}
-The ANS-UIUC maintains and develops a cohesive community of students in nuclear engineering.
+\subsection{UIUC ANS Student Chapter (ANS-UIUC)}
+The ANS-UIUC maintains and develops a cohesive community of students in nuclear, plasma, and radiological engineering (NPRE).
 It also engages in education and outreach programs to teach members of the surrounding community about nuclear science.
@@
 \end{figure}
+
+\subsection{Research at UIUC}
+Faculty in NPRE conduct research in many areas of interest to the nuclear science community.
+Students are highly encouraged to participate and make their own atomic contributions that will someday save the world.
+
+\subsubsection{Nuclear Power}
+Words
+
+\subsubsection{Plasma Physics and Fusion Science}
+Words
+
+\subsubsection{Radiological Science}
+Words
+
+\subsubsection{Reliability and Risk Analysis}
+
+\subsubsection{Materials Science}
 % ===============================================================================================

### 2019-09-15 draft.tex
adds info about conference logistics

@@
 \usepackage{soul}
+\usepackage{xcolor}
 % \usepackage{background}
@@
 
-       \Huge\textbf{Saving the World One Atom at a Time}
+       \Huge\color{white}\textbf{Saving the World One Atom at a Time}
 
@@
 
-       \textbf{Presented by ANS at the University of Illinois Urbana-Champaign}
+       \Large\textbf{Presented by ANS at the University of Illinois Urbana-Champaign}
 
@@
 \clearpage
+\newpage
+
+[Letter from the Chairs goes here!]
+
+\newpage
 \tableofcontents
@@
 % ===============================================================================================
-\section{Theme}
-\subsection{Letter from the chairs}
+\section{Saving the World One Atom at a Time}
 There are many challenges facing the world today and some have been designated existential threats to humanity.
@@
 \subsubsection{Nuclear Power}
-Words
+The Department of Nuclear, Plasma, and Radiological Engineering at Illinois is well known for its pioneering research in the area of reactor power engineering.
+Graduates have gone on to leadership positions in industry, national laboratories, and academia.
+Research in the Nuclear Power concentration covers all aspects of power generation using nuclear energy on land, underwater (submarine), and in space.
+It is inherently interdisciplinary and relies on several branches of physics and engineering for design and analysis of large complex systems.
+These include aspects of reactor physics, reactor thermal-hydraulics, reactor safety, reliability and risk, instrumentation and control, training and education, human factors engineering, reactor materials, nonproliferation, and more.
+Safety starndards and maintenance for existing reactors and new reactor designs are also explored by faculty in the department.
+Cross-cutting areas of research include multi-physics and multi-scale modeling and simulation, high performance computing, reliability and risk, validation and verification, and uncertainty analysis.
+Recently, the University of Illinois declared a plan to be completely carbon-neutral by 2050.
+Nuclear power is the perfect candidate to help UIUC attain its energy goals.
+Together, the University and the NPRE department are saving the world one atom at at time.
 
 \subsubsection{Plasma Physics and Fusion Science}
-Words
+The research theme of Fusion and Plasma Physics in the NPRE department has a long history of work in the area of magnetic and inertial nuclear fusion as well as plasma engineering.
+NPRE is now one of the leading departments in plasma-material interactions with its Center for Plasma-Materials Interactions established by Prof.
+David Ruzic.
+Furthermore, in the past few years, three new faculty members have been added to this area including: Prof.
+Davide Curelli and Prof.
+Daniel Andruzcyk.
+There are five research themes that spans the work in fusion and plasma physics: fusion materials, plasma-material interface (PMI) diagnostics, plasma-edge and PMI modeling, plasma nanosynthesis, and plasma sources and processing.
+The Hybrid Illinois Device for Research and Application (right) marks the newest addition to the team at CPMI.
+This device finished construction and achieved first plasma during the spring of 2016
 
 \subsubsection{Radiological Science}
-Words
+Radiological engineering at UIUC strives to discover novel applications for ionizing radiation in biomedical research, homeland security, and nuclear safeguards.
+We have developed various gamma-ray, x-ray and neutron detectors, imaging devices, and novel algorithms for analyzing the data from these systems.
+These algorithms range from the use of so-called "big data" techniques applied to large sensor networks to advanced radiological imaging methods and image processing techniques for biomedical research.
+We work with physicists, biologist, chemists, material scientists, statisticians, and physicians around the world, to develop advanced diagnostic imaging and radiation-induced therapeutic approaches to address some of the most critical health care-related issues, such as cancer, cardiac diseases, diabetes and neurodegenerative disorders.
+We also work with organizations like the Departments of Defense, Energy, and Homeland Security and the International Atomic Energy Agency to deploy our research around the world to detect and identify the illicit movement of nuclear and radiological materials.
 
 \subsubsection{Reliability and Risk Analysis}
+Risk analysis represents the pinnacle of interdisciplinary research and education.
+Following the Three Mile Island disaster in 1979, Probabilistic Risk Assessment (PRA) has become a key pillar of the risk-informed nuclear regulatory framework, and is now a requirement for every nuclear power plant in the United States.
+Enhancing the prevention of catastrophic technological accidents and the protection of the environment requires advancement in multidisciplinary PRA.
+It demands the development of a common vocabulary within diverse engineering and social science domains in order to address risks emerging from the interface of social and technical systems.
 
 \subsubsection{Materials Science}
+
+\subsubsection{NPRE Research Groups and Laboratories}
+\begin{itemize}
+  \item \textbf{Advanced Reactors and Fuel Cycles (ARFC)} - \textit{Dr. Katy Huff}\\
+  The ARFC group seeks to advance the safety and sustainability of nuclear energy production through improved reactor designs, fuel cycle strategies, and waste management techniques.
+In the area of advanced reactors, our work focuses on extending current simulation tools with features essential to advanced reactor multiphysics.
+In the context of the broader nuclear fuel cycle, the ARFC group emphasizes modeling, simulation, and analysis of the global nuclear fuel cycle, with an emphasis on sustainability.
+A crosscutting theme of our research is an emphasis on advancing methods and software for computational nuclear engineering.
+Accordingly, the Advanced Reactors and Fuel Cycles group is proud to be affiliated with the University of Illinois National Center for Supercomputing Applications and its Blue Waters computing facility.
+  \item \textbf{Virtual Education and Research Laboratory (VERL)} - \textit{Dr. Rizwan Uddin}\\
+  The VERL group focuses on the development of innovative numerical methods and their implementation on high performance computing machines.
+Research efforts center on problems in nuclear engineering, with emphasis on thermal-hydraulics and reactor physics.
+
+  \item \textbf{Analysis of Reactor Transients and Stability (ARTS)} - \textit{Dr. Tomasz Kozlowski}\\
+  The ARTS group performs deterministic safety analysis by developing and validating advanced methods to accurately determine reactor safety margins and reactor behavior.
+By performing high-fidelity numerical predictions of the reactor behavior in abnormal transient scenarios of safety significance, our work supports the nuclear reactor safety analysis, and increases the fidelity of primary system simulation.
+This approach is at the heart of nuclear power’s excellent safety record – always striving to improve current tools and methods.
+
+  \item \textbf{Center for Plasma-Material Interactions (CPMI)} - \textit{Dr. David Ruzic}\\
+  The primary objective of CPMI is the study of plasma-material interactions relevant to fusion, semiconductor manufacturing, and plasma processing through a combination of experimental and computational means.
+CPMI has facilities for the study of fusion materials, High Power Impulse Magnetron Sputtering (HiPIMS), liquid metals, Extreme Ultraviolet Lithography (EUVL),  laser-material interactions, and more.
+Projects are supported by both government and commercial partners to further the application and knowledge of plasma physics.
+The facility recently finished the construction of the HIDRA fusion device, which is a stellarator-tokamak machine hybrid machine used to study plasma-materials interactions.
+HIDRA is currently run by Dr.
+Daniel Andruczyk.
+
+  \item \textbf{Materials Science} - \textit{Dr. James F. Stubbins}\\
+  The group investigates a wide variety of topics within the realm of materials research including mechanical properties, microstructural evaluations, plus radiation damage investigations, and modeling.
+Materials such as copper alloys nickel-based alloys, stainless steels, ferritic steels, and silicon-carbide composites are studied using a variety of analytical techniques electron microscopy and spectroscopy.
+
+  \item \textbf{Non-Equilibrium Matter Laboratory} - \textit{Dr. Yang Zhang}\\
+  This laboratory focuses on the study of non-equilibrium matter, with particular emphasis on liquids and soft matter, using integrated neutron and synchrotron light experimental probes and atomistic modeling and simulation.
+The structure and dynamics of these systems are either inherently complex or driven away from equilibrium by extreme conditions.
+In particular, our current interests include a range of fundamental and technical problems involving slow phenomena and rare events, such as: materials far from equilibrium and in extreme environments; extreme properties of liquids; and glassy or jammed soft matters.
+
+  \item \textbf{Radiation Imaging Group} - \textit{Dr. Ling Jian Meng}\\
+  Research is on developing radiation sensor and systems for visualizing the distribution of radioactivity in surrounding objects, patients, and small lab animals etc.
+Current emphasis includes (a) developing novel radiation sensors for detecting X-ray, gamma rays and neutrons, and (b) developing nuclear techniques for detecting and imaging a tiny amount radiolabeled molecules inside small lab animals.
+
+  \item \textbf{Socio-Technical Risk Analysis (SoTeRiA)} - \textit{Dr. Zahra Mohaghegh}\\
+  The Socio-Technical Risk Analysis (SoTeRiA) Laboratory is evolving Probabilistic Risk Assessment (PRA) by explicitly incorporating the underlying science of accident causation into risk scenarios.
+SoTeRiA laboratory has pioneered two key areas of theoretical and methodological innovations: (1) spatio-temporal causal modeling of social and physical failure mechanisms in PRA, and (2) the fusion of big data analytics with PRA.
+The Lab’s current projects include: Fire PRA; Location-specific Loss- Of-Coolant Accident (LOCA) Frequency Estimations; Risk-Informed Resolution of Generic Safety Issue 191; Human and Organizational Influences on System Risk; Risk-Informed Regulation; and Risk-Informed Emergency Preparedness, Planning and Response.
+
+  \item \textbf{Laboratory: High Temperature Environmental Exposure Lab} - \textit{Dr. Brent Heuser}\\
+  A simultaneous thermal analyzer with combined thermogravimetric and differential scanning calorimetry function is housed in this laboratory.
+The response of LWR fuel cladding materials in high temperature steam environments for improved accident tolerance is currently of interest.
+
+  \item \textbf{Laboratory: Nuclear Materials Fabrication and Studies Lab} - \textit{Dr. Brent Heuser}\\
+  The Radiation Detection and Imaging Lab focuses on developing non-invasive imaging technology for use in preclinical medical research.
+Many of our current endeavors focus on developing semiconductor Single Photon Emission Computed Tomography (SPECT) and Positron Emission Tomography (PET).
+These works challenge the current state of the art for spatial resolution and system sensitivity.
+The use of highly pixelated CdTe detectors has driven our work to break into a spatial resolution on the order of 300 microns for both PET and SPECT.
+Our work in SPECT has also challenged the limits of aperture sensitivity through the engineering of the compound-eye aperture.
+\end{itemize}
 % ===============================================================================================
@@
 \section{Conference Logistics}
+
+\subsection{Date Selection}
+We are aware that there is no perfect date in which everyone who wants to attend the conference can do so.
+However, our hope is to accommodate as many students as possible with a proposed date of either: Thursday April 8th - Saturday April 10th or Thursday April 15th - April 17th, 2021.
+Two dates are proposed because the Mom's association that runs Mom's Weekend, one of the largest events of the year, has not announced their 2021 dates yet.
+Mom's weekend is typically held the first weekend of April which conflicts with Easter in 2021.
+This consensus was reached after looking up any holidays, scheduled spring breaks, final exams, and other miscellaneous conflict dates for 42 schools with active ANS student sections.
+Based on these findings, there are no major conflicts with any of the schools for these dates.
+These factors were considered in order to maximize the possible number of attendees that can benefit from the conference.
+A handful of schools did not have an academic calendar available for the 2021 Spring semester, so data was based on their listed 2020 dates.
+These date selections avoid conflicting with large event weekends such as Mom's Weekend, dates pending, and the Illini Marathon.
+If, for some reason, an issue arises with our proposed dates, our back-up date is Thursday April 1st - Saturday April 3rd.
+This is unfortunately the same weekend as Easter Sunday.
+However, we prioritized avoid final exams, and UIUC’s Mom’s Weekend.
+Please see the appendix for the full conflicts calendar.
+
+\subsection{Conference Facilities}
+\begin{itemize}
+  \item \textbf{The Illini Union}\\
+  \item \textbf{NCSA}
+  \item \textbf{Engineering Hall}
+  \item \textbf{The I-Hotel}
+  \item \textbf{}
+\end{itemize}
+
+\subsection{Facilities Contingency Plan}
+Words
 

### 2019-09-15 main.tex
adds image and info about uiuc
adds info about conference logistics

@@
 \usepackage{graphicx}
+\usepackage{eso-pic}
+\usepackage{soul}
+\usepackage{xcolor}
+% \usepackage{background}
+\usepackage{float}
+\usepackage[top=2cm, bottom=2cm, outer=2cm, inner=2cm]{geometry}
+\setcounter{tocdepth}{3}
+% \setcounter{secnumdepth}{3}
+
 \graphicspath{{./images/}}
+
+% \backgroundsetup{
+% scale=1,
+% angle=-90,
+% opacity=.4,  %% adjust
+% contents={\includegraphics[width=\paperwidth,height=\paperheight]{earth1.png}}
+% }
 
@@
 \begin{titlepage}
+\AddToShipoutPictureBG*{\includegraphics[angle=90, width=\paperwidth,height=\paperheight]{earth1.png}};
+
    \begin{center}
+
        \vspace*{1cm}
 
-       \textbf{Saving the World One Atom at a Time}
+       \Huge\color{white}\textbf{Saving the World One Atom at a Time}
 
@@
 
+\clearpage
+\newpage
+
+[Letter from the Chairs goes here!]
 \input{letter}
+
+\newpage
+\tableofcontents
+\newpage
+
 \input{theme}

### 2019-09-16 draft.tex
adds conference facilities
add tikz

@@
 \graphicspath{{./images/}}
+
+% Creates the flow chart for conference management
+\usepackage{tikz}
+\usetikzlibrary{shapes.geometric, arrows}
+
+\tikzstyle{chair} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=blue!30]
+\tikzstyle{director} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=green!30]
+\tikzstyle{coordinator} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=red!30]
+\tikzstyle{arrow} = [thick,->,>=stealth]
 
@@
   \item \textbf{The Illini Union}\\
-  \item \textbf{NCSA}
-  \item \textbf{Engineering Hall}
-  \item \textbf{The I-Hotel}
-  \item \textbf{}
+  \item \textbf{National Center for Supercomputing Applications (NCSA)}\\
+  \item \textbf{Engineering Hall}\\
+  \item \textbf{The I-Hotel}\\
+  \item \textbf{}\\
 \end{itemize}
@@
 
+\begin{tikzpicture}[node distance = 2cm]
+
+  \node (gen chair) [chair] {General Co-Chair};
+  \node (tech chair) [chair] {Technical Co-Chair};
+  \node (fin dir) [director] {Financial Director};
+  \node (pub dir) [director] {Communications Director};
+  \node (reg coord) [coordinator] {Registration Coordinator};
+  % \node (gen chair) [chair] {General Co-Chair};
+  % \node (gen chair) [chair] {General Co-Chair};
+  % \node (gen chair) [chair] {General Co-Chair};
+  % \node (gen chair) [chair] {General Co-Chair};
+  % \node (gen chair) [chair] {General Co-Chair};
+
+\end{tikzpicture}
+
 % ===============================================================================================

### 2019-09-16 uiuc.tex
fixes makefile and fixes theme.tex uiuc.tex

@@
-\section*{Urbana-Champaign and UIUC}
+\section{Urbana-Champaign and UIUC}
 
-\subsection*{About Urbana-Champaign}
+\subsection{About Urbana-Champaign}
 Champaign-Urbana (CU) is a close-knit community filled with music, culture, and food.
@@
 
-\subsubsection*{Weather}
-With an average high temperature of 65℉ and an average low temperature of 40℉, April in Champaign is a gorgeous month of dwindling winter weather as summer begins to round the corner.
+\subsubsection{Weather}
+With an average high temperature of 65$^{\circ}$ and an average low temperature of 40$^{\circ}$, April in Champaign is a gorgeous month of dwindling winter weather as summer begins to round the corner.
 Holding a conference during this time would be the perfect way to showcase our beautiful city.
 
-\subsection*{About the University of Illinois}
+\subsection{About the University of Illinois}
 Founded in 1867, the University of Illinois at Urbana-Champaign (UIUC) has cultivated a long history of significant scientific discoveries and contributions.
@@
 
-\subsecton{UIUC ANS Student Chapter (ANS-UIUC)}
+\subsection{UIUC ANS Student Chapter (ANS-UIUC)}
 The ANS-UIUC maintains and develops a cohesive community of students in nuclear engineering.

### 2019-09-18 main.tex

@@
-\documentclass[12pt, letterpaper]{article}
+\documentclass[11pt, letterpaper]{article}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{xcolor}
+
+\usepackage{gfsdidot} % Use the GFS Didot font: http://www.tug.dk/FontCatalogue/gfsdidot/
+\usepackage{microtype} % Improves typography
+
+\usepackage{fancyhdr}
+% \usepackage{pagecounting}
+% \usepackage[dvips]{color}
+
+\newcommand{\illinoislogo}{\includegraphics[height=0.5in]{images/illinoislogo.png}}
+\newcommand{\anslogo}{\hspace{-4mm}\includegraphics[height=0.5in]{images/ansuiuc.png}}
+\newcommand{\anssite}{ans.npre.illinois.edu}
 % \usepackage{background}
@@
 % \setcounter{secnumdepth}{3}
+\usepackage{environ}
+\NewEnviron{letter}{%
+  \input{structure}
+  \opening
+  \closing
+}
 
@@
 
-% \backgroundsetup{
-% scale=1,
-% angle=-90,
-% opacity=.4,  %% adjust
-% contents={\includegraphics[width=\paperwidth,height=\paperheight]{earth1.png}}
-% }
+% Creates the flow chart for conference management
+\usepackage{tikz}
+\usetikzlibrary{shapes.geometric, arrows}
+
+\tikzstyle{chair} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=blue!30]
+\tikzstyle{director} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=orange!30]
+\tikzstyle{coordinator} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=white!30]
+\tikzstyle{arrow} = [thick,->,>=stealth]
 
@@
 
+\pagestyle{fancy}
+\lhead{\anslogo}
+\rhead{\illinoislogo}
+
 [Letter from the Chairs goes here!]

### 2019-09-18 theme.tex
fixes makefile and fixes theme.tex uiuc.tex

@@
-\section{Theme}
-
-\Huge{Saving the World One Atom at a Time}\\
-
-There are many challenges facing the world today.
-Some of these have been designated existential threats to humanity.
-As students, these obstacles may appear insurmountable.
-The ANS Student Conference is a marvelous opportunity to inspire optimism for the future as researchers, professionals, and students, gather to showcase critical advances in technology.
-Nuclear, plasma, and radiological engineering will be central to endeavors like solving the world's energy needs, developing technology that will take us to the stars, treating cancer, and many others.
-Our goal is to inspire and motivate students in these fields to tackle grand challenge problems.
-Students will hear from visionary speakers and leaders of the nuclear science community.
-They will leave with renewed hope for the future and the knowledge that their efforts are saving the world, one atom at a time.\\
-The University of Illinois at Urbana-Champaign would honored to host the ANS Student Conference in 2021 and to share the innovative and galvanizing environment of our great campus.
+\section{Saving the World One Atom at a Time}
+There are many challenges facing the world today and some have been designated existential threats to humanity.
+Young people today will witness the growing toll of anthropogenic climate change.
+As students, obstacles at the scale of the world climate crisis appear daunting and overwhelming.
+We believe that many solutions will come from the nuclear sciences.
+The ANS student conference is an opportunity for students and professionals to come together and share advances in critical technology and research, dedicated to solving these problems.
+Whether the problem is solving the world’s energy needs, developing technology that will take us to the stars, or curing cancer, nuclear, plasma, and radiological engineering will be at the center of those endeavors.
+Our goal is to inspire and motivate students in nuclear, plasma, and radiological engineering fields to tackle big problems.
+Saving the world one atom at a time reflects the fact that nuclear science is a powerful force in dealing with grand challenge problems.
+This theme also honors the individual, atomic, contributions from students, researchers, and professionals, in the field of nuclear engineering, that are essential to progress.
+This conference is about science and it is about the people that make the science possible.
+Students will hear from visionary speakers and leaders of the nuclear science community and come away with optimism for the future; knowing that they are saving the world one atom at a time.\\
+The University of Illinois at Urbana-Champaign chapter of ANS would be honored to host the 2021 student conference.
+We hope to create an atmosphere that will galvanize students and professionals for the exciting future of nuclear engineering.

### 2019-09-20 management.tex
modifies the Makefile

\section{Conference Management}

Executive Board Candidates:

Program Coordinator:
\begin{enumerate}
\item Brady Moran
\end{enumerate}

Media Coordinator
\begin{enumerate}
\item Nathan Ryan
\end{enumerate}

Registration Coordinator
\begin{enumerate}
\item Jasmine (?)
\end{enumerate}

### 2019-09-20 proglog.tex
adds images and information about speakers

@@
 \subsection{Potential Speakers}
+
+\subsubsection{Rachel Slaybaugh, UC Berkeley}
+\begin{wrapfigure}{r}{0.5\textwidth}
+	\begin{center}
+		\includegraphics[width=0.48\textwidth,scale=0.2]{slaybaugh.jpg}
+	\end{center}
+\end{wrapfigure}
+Prof.
+Slaybaugh's research is based in numerical methods for neutron transport with an emphasis on supercomputing.
+She applies these methods to reactor design, shielding, and nuclear security and nonproliferation.
+Slaybaugh was a key founder of the nuclear innovation bootcamp, which seeks to train students and professionals in skills essential to innovation in nuclear energy while executing team projects.
+Finally, Slaybaugh has served as a Program Director at ARPA-E, developing and running their first fission energy programs.
+Advanced Research Projects Agency-Energy (ARPA-E) invests in research for ways to generate, use, and store energy.
+These projects have the potential to radically improve economic prosperity in the U.S.
+and environmental wellbeing.
+Due to her endeavors in teaching and sharing nuclear innovation, we believe that Slaybaugh's goals are aligned with the goals of this conference and would make her an excellent addition to the program.
+Slaybaugh has much to offer the conference with her vision and leadership.
+\subsubsection{Suzanne Hobbs Baker}
+\begin{wrapfigure}{r}{0.5\textwidth}
+	\begin{center}
+		\includegraphics[scale=0.75]{hobbsbaker.jpeg}
+	\end{center}
+\end{wrapfigure}
+Talking about nuclear energy, specifically with the general public, is one of Suzanne Hobbs Baker's key goals.
+Baker has a strong track record as a nuclear science communicator.
+In 2008 she founded a nonprofit organization aimed at reaching women, minorities, and young people with critical information about climate change and nuclear energy.
+She currently works as the creative director for Fast Path to Zero Initiatve at the University of Michigan and as a Nuclear security fellow with Third Way Energy.
+Baker's work in empowering minorities and students to solve the world climate crisis with nuclear energy, as well as her skill in creative science communication, ensures that Baker has a lot to offer the student conference.
+Celebrating the people behind the science is one of the key goals of this conference and an area in which Baker has a lot of experience.
+\vfill
+\subsubsection{Todd Allen, UW Madison}
+\begin{wrapfigure}{r}{0.5\textwidth}
+	\begin{center}
+		\includegraphics[scale=0.75,width=0.48\textwidth]{allen.jpeg}
+	\end{center}
+\end{wrapfigure}
+His first post-Ph.D.
+position was as a staff scientist at Argonne National Laboratory.
+While at Argonne, he joined the leadership team tasked with developing the Generation IV Roadmap, the document that framed the resurgence of the nuclear research programs early in the 21st Century.Following Argonne, he joined the faculty at the University of Wisconsin.
+While there, he split his time between establishing a premier material science program at the university and supporting the Idaho National Laboratory.
+At INL, he led the transition of the Advanced Test Reactor into a national user facility.
+He also ran a six-institution Energy Frontier Research Center focused on answering fundamental questions about heat transfer in nuclear fuel.
+From 2013-2016, he helped lead the Idaho National Laboratory as the Deputy Laboratory Director for Science $\&$ Technology, including being an important contributor to the development of the Gateway for Accelerated Innovation in Nuclear (GAIN) initiative announced at the White House in November 2015.
+Since 2016 he has been a Visiting Senior Fellow with Clean Energy Program at Third Way, a Washington, DC based think tank.
+His role in formulating the roadmap for Generation IV reactors and his leadership indicate that he would make a great speaker at the conference.
+\subsubsection{Rita Baranwal, DOE Nuclear Energy}
+\subsubsection{Jim Conca, Forbes}
+\subsubsection{Fatima Ebrahimi, Princeton}
+
+\subsection{Panels}

### 2019-09-20 theme.tex
adds images and information about speakers

@@
 \section{Saving the World One Atom at a Time}
+
+The future is nuclear.\\
 There are many challenges facing the world today and some have been designated existential threats to humanity.
@@
 The University of Illinois at Urbana-Champaign chapter of ANS would be honored to host the 2021 student conference.
-We hope to create an atmosphere that will galvanize students and professionals for the exciting future of nuclear engineering.
+We hope to create an atmosphere that will galvanize students and professionals for the exciting future of nuclear engineering.\\
+
+Goals of the conference
+\begin{enumerate}
+	\item Celebrate the people behind the science
+	\item Inspire young students to take on grand challenge problems
+	\item Help students and professionals develop a strong network of like-minded people. 
+\end{enumerate}

### 2019-09-20 proglog.tex
adds images and speaker info

@@
 \subsubsection{Rachel Slaybaugh, UC Berkeley}
-\begin{wrapfigure}{r}{0.5\textwidth}
-	\begin{center}
-		\includegraphics[width=0.48\textwidth,scale=0.2]{slaybaugh.jpg}
-	\end{center}
-\end{wrapfigure}
+% \begin{wrapfigure}{r}{0.5\textwidth}
+% 	\begin{center}
+% 		\includegraphics[width=0.48\textwidth,scale=0.2]{slaybaugh.jpg}
+% 	\end{center}
+% \end{wrapfigure}
 Prof.
@@
 Slaybaugh has much to offer the conference with her vision and leadership.
+
 \subsubsection{Suzanne Hobbs Baker}
-\begin{wrapfigure}{r}{0.5\textwidth}
-	\begin{center}
-		\includegraphics[scale=0.75]{hobbsbaker.jpeg}
-	\end{center}
-\end{wrapfigure}
+% \begin{wrapfigure}{r}{0.5\textwidth}
+% 	\begin{center}
+% 		\includegraphics[scale=0.75]{hobbsbaker.jpeg}
+% 	\end{center}
+% \end{wrapfigure}
 Talking about nuclear energy, specifically with the general public, is one of Suzanne Hobbs Baker's key goals.
@@
 Celebrating the people behind the science is one of the key goals of this conference and an area in which Baker has a lot of experience.
-\vfill
+
 \subsubsection{Todd Allen, UW Madison}
-\begin{wrapfigure}{r}{0.5\textwidth}
-	\begin{center}
-		\includegraphics[scale=0.75,width=0.48\textwidth]{allen.jpeg}
-	\end{center}
-\end{wrapfigure}
+% \begin{wrapfigure}{r}{0.5\textwidth}
+% 	\begin{center}
+% 		\includegraphics[scale=0.75,width=0.48\textwidth]{allen.jpeg}
+% 	\end{center}
+% \end{wrapfigure}
 His first post-Ph.D.
@@
 His role in formulating the roadmap for Generation IV reactors and his leadership indicate that he would make a great speaker at the conference.
+
 \subsubsection{Rita Baranwal, DOE Nuclear Energy}
+Dr.
+Rita Baranwal serves as the Assistant Secretary for the Office of Nuclear Energy in the U.S.
+Department of Energy (DOE).
+Dr.
+Baranwal leads the office’s efforts to promote research and development (R$\&$D) on existing and advanced nuclear technologies that sustain the existing U.S.
+fleet of nuclear reactors, enable the deployment of advanced nuclear energy systems, and enhance the U.S.A.'s global commercial nuclear energy competitiveness.
+Prior to her current role, Dr.
+Baranwal directed the Gateway for Accelerated Innovation in Nuclear (GAIN) initiative at Idaho National Laboratory.
+She was responsible for providing the nuclear industry and other stakeholders access to DOE's state-of-the-art R$\&$D expertise, capabilities, and infrastructure to achieve faster and cost-effective development, demonstration, and ultimate deployment of innovative nuclear energy technologies.
+Under her leadership, GAIN positively impacted over 120 companies.
+Baranwal is a clear choice of speaker to discuss the ways to improve nuclear legislation and how companies can rapidly develop new nuclear technology.
+
 \subsubsection{Jim Conca, Forbes}
+Jim Conca has been a scientist in the field of the earth and environmental sciences for 33 years, specializing in geologic disposal of nuclear waste, energy-related research, planetary surface processes, radiobiology and shielding for space colonies, subsurface transport and environmental clean-up of heavy metals.
+He is a Trustee of the Herbert M.
+Parker Foundation, Adjunct at WSU, an Affiliate Scientist at LANL and consult on strategic planning for the DOE, EPA/State environmental agencies, and industry including companies that own nuclear, hydro, wind farms, large solar arrays, coal and gas plants.
+He also writes for Forbes magazine about nuclear issues, energy, and the environment.
+Conca has a strong vision for the future and is not shy about coming up with ideas to solve grand challenge problems.
+In addition to his experience and ambition, he is an excellent science communicator to scientists and non-scientists alike.
+Together, these factors make him an ideal speaker at the conference.
+
 \subsubsection{Fatima Ebrahimi, Princeton}
+Fatima Ebrahimi is a Research Physicist at the PPPL Theory Department
+and an Affiliated Research Scholar at the Department of Astrophysical
+Sciences, Princeton University.
+She has many years of experience in theoretical and global computational extended magnetohydrodynamics (MHD) with wide applications to laboratory fusion and astrophysical plasmas.
+Her main research interests are MHD
+stability in fusion plasmas, momentum transport, dynamos, and magnetic reconnection in laboratory fusion and astrophysical plasmas.
+She has written many papers over a wide range of topics and peer-reviewed journals.
+She is an elected executive committee member
+of the APS Topical Group in Plasma Astrophysics (GPAP), 2018-2021, and program committee member for U.S.
+Magnetic Fusion Research (MFR) Strategic Directions, 2017-2018.
+Dr.
+Ebrahimi is a great choice to have as a speaker on the future of fusion energy.
+
+\subsubsection{Brian Jurczyk, CEO Starfire Industries}
+Brian holds a dual PhD/MBA degree with background in aerospace, nuclear, plasma and radiological engineering and technology commercialization.
+As CEO, Brian works to find creative win-win solutions with commercial and industrial partners for particularly challenging applications - at all stages of value creation from basic IP development through early-stage manufacturing.
+In 2012-13, Brian received the Innovation Celebration "Entrepreneurial Excellence in Management Award," was named to Central Illinois Business' "40-under-40" and has served as Chairperson of the Champaign-Urbana CEO Roundtable.
+As a professional leader in plasma and radiological engineering, Jurczyk would be a great speaker to have at the conference on topics related to the future of plasma engineering and professional development.
 

### 2019-09-20 conflog.tex
adds workshops and panels

\section{Conference Logistics}

\subsection{Date Selection}
Primary date selection\\
Rationale for date selection\\
Graphical calendar of date selection and conflicts\\
\subsection{Conference Facilities}
Conference facilities\\
\subsection{Conference Contingency Plan}
\subsection{Hotels and Accomodations}
\subsection{Travel and Transportation}

### 2019-09-20 proglog.tex
adds workshops and panels

@@
-\section{Program Logistics}
+\section{Conference Program}
 
@@
 
-\subsection{Panels}
+\subsection{Saving the World Panel Series}
+Technical and non-technical panels encourage interaction between students and professionals at the conference.
+Each panel is designed to address one or more of the stated goals for the conference.
+They also serve as a way for students and professionals to learn more about relevant issues, find inspiration for their next project, and feel encouraged for the future of the nuclear field.\\
+
+$\Large\textbf{Technical Panels}$
+
+\subsubsection{Critical Conversations: Microreactors}
+
+\subsubsection{Applications for Fusion and Plasma}
+
+\subsubsection{Nuclear Policy and Legislation}
+Nuclear energy is one of the most heavily regulated fields in the United States.
+This panel aims to enlighten attendees about how legislation is written and how non-scientist government officials might better understand the potential of nuclear energy.
+This panel will allow attendees to learn who is working in this area and develop a network of people devoted to issues of nuclear policy.
+Rita Baranwal would be an excellent speaker on this panel because of her work for the DOE.\\
+
+$\Large\textbf{Non-Technical Panels}$
+
+\subsubsection{Science is People: Conducting Inclusive Research}
+Research and technology that will help us solve the grand challenge problems of the world must also reflect the diverse needs of the people that live in it.
+Everyone comes to nuclear engineering from a variety of backgrounds, identities, abilities, and experiences.
+Saving the World One Atom at a Time means making atomic contributions.
+Finding ways to encourage and include even one more person in the endeavor of nuclear science is an important kind of atomic contribution.
+This panel works toward the goal of celebrating the people behind the science.
+It also serves to inspire students and
+
+\subsubsection{Talking To Non-Scientists}
+It has been shown that when members of the general public are given more scientific evidence they are less likely to shift their beliefs.
+While this finding is surprising to members of the scientific community, people who value data and evidence, it can be difficult to find ways to effectively communicate your research to the public.
+Attendees will learn how other scientists effectively communicate their results.
+No longer discouraged by potential resistance from the public, students will steel their resolve for working on ambitious projects that can save the world.
+Suzanne Hobbs Baker would be a great choice for this panel, as well as members of The Story Collider; a non-profit organization devoted to helping scientists tell stories
+
+\subsubsection{How to Host a Conference}
+
+\subsection{Workshops}
+
+\subsubsection{Scientific Storytelling}
+Science is people.
+The Story Collider is a non-profit organization whose mission is to honor the people and stories behind the science and teach scientists to use these stories to their advantage.
+From their website:
+\begin{quote}
+	We know that storytelling is not typically taught during scientific training, and is sometimes explicitly discouraged.
+There are many reasons why.
+But like it or not, stories are how people understand the world, and they weave together fact and emotion.
+Compared to other forms of communication, these narratives can be more successful in:
+	\begin{itemize}
+		\item generating interest and engagement with a topic,
+		\item improving comprehension, and
+		\item influencing real-world beliefs, even among skeptical audiences.
+	\end{itemize}
+\end{quote}

### 2019-09-20 theme.tex
adds workshops and panels

@@
 \section{Saving the World One Atom at a Time}
-
 The future is nuclear.\\

### 2019-09-20 proglog.tex
adds several section outlines and workshops

@@
 \subsubsection{Critical Conversations: Microreactors}
+This panel explores the benefits of microreactors in general. It will also explore the idea of universities as potential markets for microreactors. Microreactors are exactly what they sound like,
 
@@
 No longer discouraged by potential resistance from the public, students will steel their resolve for working on ambitious projects that can save the world.
-Suzanne Hobbs Baker would be a great choice for this panel, as well as members of The Story Collider; a non-profit organization devoted to helping scientists tell stories
+Suzanne Hobbs Baker would be a great choice for this panel, as well as members of The Story Collider; a non-profit organization devoted to helping scientists tell stories that
 
 \subsubsection{How to Host a Conference}
+This panel is devoted to sharing the experience of this conference's planning committee with students from other schools that may want to host their own student conference.
+This panel is for students by students.
+We will discuss our process from writing a successful proposal to executing a successful conference.
 
@@
 \end{quote}
+
+\subsubsection{MOOSE Workshop}
+The Multiphysics Object Oriented Simulation Environment is an open source framework for finite element modeling, developed and maintained by Idaho National Laboratory.
+MOOSE is a powerful framework that enables users to couple several different physics codes together under a single API.
+Many research groups at UIUC use this framework for simulating reactors and materials.
+The Idaho National Laboratory MOOSE team gives many workshops a year to train future user-developers of the framework.
+We will invite this team to give a half-day MOOSE workshop at the conference.
+The workshop will take place in NCSA room 1030.
+
+\subsubsection{PyNE and PyRK Workshop}
+Python for Nuclear Engineering (PyNE) and Python for Reactor Kinetics (PyRK) are two open source packages with computational tools for nuclear science and engineering.
+The PyNE toolkit provides both a Python and a C++ API for common computational pre- and post-processing tasks in nuclear engineering.
+PyRK offers point kinetics implementation for nuclear reactors.
+This workshop will provide a hands-on tutorial for attendees to begin using PyNE and make use of its capabilities for their curriculum and research work.
+The Advanced Reactors and Fuel Cycles (ARFC) research group at UIUC and its collaborators will provide instructors.
+This workshop, alpha-tested at the University of Wisconsin will be aimed at students who can provid their own laptops and have a desire to improve their nuclear computational skills.
+The workshop will be approximately two hours of instruction at NCSA room 1030.
+
+\subsubsection{Scientific Writing Workshop}
+
+\subsubsection{LaTeX Workshop}

### 2019-09-20 proglog.tex
added workshop information

@@
 
+\subsubsection{Building Your Network}
+The AAAS conducts workshops that teach early career scientists and students how to develop a professional network that will benefit them in the future.
+They hold regular workshops about strategic networking, making new contacts, and getting the most out of a conference.
+We will invite them to conduct a workshop where attendees can come away with skills to maximize their experience at the ANS Student Conference.
+
 \subsubsection{MOOSE Workshop}
@@
 The workshop will be approximately two hours of instruction at NCSA room 1030.
-
-\subsubsection{Scientific Writing Workshop}
-
-\subsubsection{LaTeX Workshop}

### 2019-09-21 main.tex
adds images and information about speakers
adds images and speaker info
adds several section outlines and workshops
adds conference management and research info

@@
-\documentclass[11pt, letterpaper]{article}
+\documentclass[10pt, letterpaper]{article}
 \usepackage[utf8]{inputenc}
 \usepackage{graphicx}
+\usepackage{wrapfig}
 \usepackage{eso-pic}
@@
 \usepackage{xcolor}
-
+\usepackage{tabularx}
 \usepackage{gfsdidot} % Use the GFS Didot font: http://www.tug.dk/FontCatalogue/gfsdidot/
@@
 \usepackage{float}
-\usepackage[top=2cm, bottom=2cm, outer=2cm, inner=2cm]{geometry}
+\usepackage[top=2cm, bottom=2.75cm, outer=2cm, inner=2cm]{geometry}
 \setcounter{tocdepth}{3}
@@
 % Creates the flow chart for conference management
+\usepackage{varwidth}
 \usepackage{tikz}
+\usetikzlibrary{trees}
 \usetikzlibrary{shapes.geometric, arrows}
 
-\tikzstyle{chair} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=blue!30]
-\tikzstyle{director} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=orange!30]
-\tikzstyle{coordinator} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=white!30]
+\tikzstyle{chair} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,thick, fill=blue!50, execute at begin node={\begin{varwidth}{3cm}},execute at end node={\end{varwidth}}]
+\tikzstyle{director} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=orange!70, execute at begin node={\begin{varwidth}{3cm}},execute at end node={\end{varwidth}}]
+\tikzstyle{coordinator} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=white!30, execute at begin node={\begin{varwidth}{3cm}},execute at end node={\end{varwidth}}]
 \tikzstyle{arrow} = [thick,->,>=stealth]
@@
 \begin{document}
-
+% ======================================================================================================
+% DO NOT EDIT THIS SECTION
+% ======================================================================================================
 \begin{titlepage}
@@
 
-       \vspace*{1cm}
+       \vspace*{0.25cm}
 
@@
 
-       \vspace{0.5cm}
+       \vspace{0.3cm}
        Nuclear, Plasma, and Radiological Engineering
 
-       \vspace{1.5cm}
+       \vfill
+       \vspace{7.5cm}
+
+       \includegraphics[width=0.4\textwidth]{ans_sc_logo3.png}
+
+       \vspace{1cm}
 
@@
 
-       \vfill
-       \vspace{0.8cm}
-
-       \includegraphics[width=0.4\textwidth]{ans_sc_logo3.png}
    \end{center}
 \end{titlepage}
+% ======================================================================================================
+% ======================================================================================================
+% ======================================================================================================
 
@@
 
-[Letter from the Chairs goes here!]
 \input{letter}
@@
 \input{theme}
+\newpage
 \input{uiuc}
+\newpage
 \input{conflog}
+\newpage
 \input{proglog}
+\newpage
 \input{management}
+\newpage
 \input{budget}

### 2019-09-21 management.tex
adds several section outlines and workshops
adds conference management and research info

@@
 
-Executive Board Candidates:
+% ===============================================
+% This is the hierarchy breakdown
+% ===============================================
+\begin{center}
+	\begin{tikzpicture}[
+		chair/.style={rectangle, text centered, draw,fill=blue!20, execute at begin node={\begin{varwidth}{9em}},
+   		execute at end node={\end{varwidth}}},
+   		committee/.style={rectangle,draw,fill=green!40, text centered, execute at begin node={\begin{varwidth}{7em}},
+   		execute at end node={\end{varwidth}}},
+   		coordinator/.style={rectangle,draw,fill=red!30, text centered, execute at begin node={\begin{varwidth}{7em}},
+   		execute at end node={\end{varwidth}}},
+		grandchild/.style={grow=down,xshift=1em,anchor=west,
+		edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)}, execute at begin node={\begin{varwidth}{8em}},
+   		execute at end node={\end{varwidth}}},
+		first/.style={level distance=12ex},
+		second/.style={level distance=24ex},
+		third/.style={level distance=36ex},
+		level 1/.style={sibling distance=11em}]
+	    % Parents
+	    \coordinate
+	      child[grow=left] {node[chair,anchor=east]{General Co-Chair \\ (Sam Dotson)}}
+	      child[grow=right] {node[chair,anchor=west]{Technical Co-Chair\\ (Jeremy Mettler)}}
+	      child[grow=down,level distance=3ex]
+	    [edge from parent fork down]
+	    % Children and grandchildren
+	    child{node[committee] {Non-Technical Subcommittee}
+	      child[grandchild,first] {node[chair]{Logistics Chair}}
+	      child[grandchild,second] {node[coordinator]{Hotels and Transportation}}
+	      child[grandchild,third] {node[coordinator] {Hospitality and Catering}}}
+	    child {node[committee] {Communications Subcommittee}
+	      child[grandchild, first] {node[chair] {Publications Chair}}
+	      child[grandchild, second] {node[coordinator]{Media}}
+	      child[grandchild, third] {node[coordinator] {Program}}}
+	    child{node[committee] {Financial Subcommittee}
+	      child[grandchild,first] {node[chair]{Financial Chair}}
+	      child[grandchild,second] {node[coordinator]{Registration}}
+	      child[grandchild,third] {node[coordinator]{Sponsorship}}}
+	    child {node[committee]{Technical Subcommittee}
+	      child[grandchild,first] {node[chair]{Sessions Chair}}
+	      child[grandchild,second] {node[coordinator]{Workshops}}
+	      child[grandchild,third] {node[coordinator]{Career Fair}}};
+	\end{tikzpicture}
+\end{center}
+% ===============================================
+% ===============================================
+% ===============================================
 
-Program Coordinator:
+\subsection{Position Responsibilities}
+The general and technical chairs are responsible for setting up major milestones and 
+ensuring that those milestones are met. Together they oversee all four subcommittees but 
+are each primarily in charge of two. They will serve as the primary contacts between subcommittee
+chairs and the faculty as well as professionals. The two co-chairs have the final word on all 
+conference decisions.
+
+\begin{itemize}
+	\item $\large\textbf{\textit{General Co-Chair}}$\\
+	In addition to the responsibilities outlined above, the General Co-Chair primarily oversees the
+	Non-technical and Publications Subcommittees. Works with the Technical Co-Chair to plan full committee
+	meetings and completes any remaining tasks to ensure that milestones are met.
+	\item $\large\textbf{\textit{Technical Co-Chair}}$\\
+	In addition to the responsibilities outlined above, the Technical Co-Chair primarily oversees the
+	Technical and Financial Subcommittees. Works with the General Co-Chair to plan full committee
+	meetings and completes any remaining tasks to ensure that milestones are met.
+	\item $\textbf{Non-Technical Subcommittee}$\\
+	The Non-Technical Subcommittee oversees, arranges, and executes all actions related to hospitality, transportation, special events, and non-technical workshops and panels.
+This committee keeps the theme of the conference in mind when organizing all events.
+They ensure that the conference runs smoothly.
+	\begin{itemize}
+		\item[$\circ$] $\textbf{Logistics Chair (Gavin Davis?)}$\\
+		The Logistics Chair is in charge of planning all tours and non-technical workshops and panels. Organizes speakers during dinners
+		Also responsible for keeping track of subcommittee and reporting to the General and Technical Co-Chairs.
+		\item[$\circ$] $\textbf{Hotels and Transportation Coordinator}$\\
+		Coordinates with ANS National to negotiate room rates and room blocks for hotels. Reserves busses for the 
+		necessary times and events. Works with the Hospitality and Catering Coordinator and the Logistics Chair.
+		\item[$\circ$] $\textbf{Hospitality and Catering Coordinator}$\\
+		Responsible for planning and organizing all catered meals for the conference.
+that includes contacting the catering services, reserving the venues where meals are held, and making sure the venues are staffed.
+	\end{itemize}
+	\item $\textbf{Financial Subcommittee}$\\
+	The Financial Subcommittee oversees, arranges, and executes all actions related to banking, sponsorship, registration, reimbursement, budgeting, and monetary exchanges.
+This committee works closely with the General and Technical Co-Chairs.
+	\begin{itemize}
+		\item[$\circ$] $\textbf{Financial Chair}$\\
+		Sets the budget for the whole committee and ensures that the committee does not exceed the budget.
+Manages the ANS Student Committee account and collects receipts.
+Updates and maintains the budget as required.
+Keeps track of subcommittee progress and reports to the General and Technical Co-Chairs.
+		\item[$\circ$] $\textbf{Registration Coordinator (Jasmine Dinari?)}$
+		Handles the registration for professional and student attendees. Communicates the number of attendees to the Program Coordinator. 
+		\item[$\circ$] $\textbf{Sponsorship Coordinator}$\\
+		Assists the Financial Chair with matters involving sponsorship as well as working closely with the registration coordinator and the General and Technical Co-Chairs.
+	\end{itemize}
+	\item $\textbf{Technical Subcommittee}$\\
+	The Technical Subcommittee works with the Technical Co-Chair to process student abstracts and set up 
+	technical workshops, panels and sessions. 
+	\begin{itemize}
+		\item[$\circ$] $\textbf{Sessions Chair (Gwen Chee?)}$\\
+		Responsible for organizing presentation, poster sessions, and technical
+		panels. Also responsible for ensuring that judges understand the judging criteria, and organizes the award ceremony.
+		Keeps track of subcommittee progress and reports to the General and Technical Co-chairs.
+		\item[$\circ$] $\textbf{Workshops Coordinator (Zach Jeckell?)}$\\
+		Organizes workshops locations, times, staffing, costs, supplies, student enrollment
+		and any other tasks required to have successful workshops. Also assists the Sessions Chair when needed.
+		\item[$\circ$] $\textbf{Career Fair Coordinator (Rierson Johnson?)}$\\
+		Oversees staffing and support for the career fair as well as working with the Sponsorship
+		Coordinator to ensure a successful career fair. Also assists the Sessions Chair when needed.
+	\end{itemize}
+	\item $\textbf{Communications Subcommittee}$
+	The Communications Subcommittee is in charge of public relations and communicating status updates with attendees.
+	\begin{itemize}
+		\item[$\circ$] $\textbf{Publications Chair (Nate Reid?)}$\\
+		The Publications Chair is primarily responsible for publishing and organizing the student abstracts, as well as 
+		helping the media coordinator maintain a social media presence. 
+		\item[$\circ$] $\textbf{Media Coordinator (Nathan Ryan?)}$\\
+		The Media Coordinator is reponsible for designing the conference website, constantly updating social media presence,
+		and obtains information from other members of the planning committee for the website. 
+		\item[$\circ$] $\textbf{Program Coordinator (Brady Moran?)}$\\
+		The Program Coordinator is in charge of setting the program for the conference, minimizing event overlap, and coordinating
+		with the Publications Chair and Media Coordinator.
+	\end{itemize}
+\end{itemize}
+
+\subsection{Planning Committee Biographies}
+[All committee members must plan on attending the upcoming student conference!]
+
+\subsection{Conflict Resolution}
+
+Committee members should hold professionalism at the forefront of their composure in order to avoid and resolve issues amicably without the involvement of higher powers.
+As such, members are encouraged to settle conflicts without invoking this protocol.
+If an issue arises that immediately presents itself as overwhelming, the scope of the issue exceeds an individual’s ability to handle it, or the issue imposes certain implications that jeopardizes the mission of the planning committee, members should not hesitate to refer to this section.
+In the event of a conflict between members of the planning committee, a document for decision-making and
+conflict resolution has been drafted and approved by the general committee. All General Committee members
+are expected to abide by the resolution. Key points of the resolution are as follows:
 \begin{enumerate}
-\item Brady Moran
+	\item Subcommittees are encouraged to operate as autonomous and democratic as possible; however, the General
+	Co-Chairs reserve the rights to make all final decisions. If the Co-Chairs cannot agree, the faculty advisor will be involved.
+	\item Conflicts between committee members are to be resolved outside of the committee. Should this begin to
+	affect the work of these members, the General Co-Chairs may intervene.
+	\item Any cases of misconduct or negligence will be handled by the General Co-Chairs as necessary.
+	\item For extreme cases of misconduct or negligence, separate steps for the removal and replacement of a
+	member are outlined for general members, Subcommittee Chairs, and General Co-Chairs. These include
+	a discussion with the offending member, consultation of the Faculty Advisor, and a hearing with the
+	General Committee to decide if removal is necessary.
 \end{enumerate}
 
-Media Coordinator
-\begin{enumerate}
-\item Nathan Ryan
-\end{enumerate}
+\subsection{Staffing Requirements}
 
-Registration Coordinator
-\begin{enumerate}
-\item Jasmine (?)
-\end{enumerate}
+% ===============================================
+% Milestones
+% ===============================================
+\subsection{Milestones}
+
+\begin{center}
+	\begin{tabular*}{\textwidth}{c | @{\extracolsep{\fill}}c @{\extracolsep{\fill}} c}
+\hline\hline
+Deadline & Task & Responsibility\\
+\hline\hline
+
+&November&\\
+\hline\hline
+& & \\
+\hline\hline
+&December&\\
+\hline\hline
+12/14/19& Some task needs to be done& General Co-Chair \\
+\hline\hline
+&$\textbf{2020}$&\\
+\hline\hline
+&January&\\
+\hline\hline
+& & \\
+\hline\hline
+&February&\\
+\hline\hline
+& & \\
+\hline\hline
+&March&\\
+\hline\hline
+& & \\
+\hline\hline
+&April&\\
+\hline\hline
+& & \\
+\hline\hline
+&May&\\
+\hline\hline
+& & \\
+\hline\hline
+&June&\\
+\hline\hline
+& & \\
+\hline\hline
+&July&\\
+\hline\hline
+& & \\
+\hline\hline
+&August&\\
+\hline\hline
+& & \\
+\hline\hline
+&September&\\
+\hline\hline
+& & \\
+\hline\hline
+&October&\\
+\hline\hline
+& & \\
+\hline\hline
+&November&\\
+\hline\hline
+& & \\
+\hline\hline
+&December&\\
+\hline\hline
+& & \\
+\hline\hline
+&$\textbf{2021}$&\\
+\hline\hline
+&January&\\
+\hline\hline
+& & \\
+\hline\hline
+&February&\\
+\hline\hline
+& & \\
+\hline\hline
+&March&\\
+\hline\hline
+& & \\
+\hline\hline
+&April&\\
+\hline\hline
+\end{tabular*}
+\end{center}

### 2019-09-21 uiuc.tex
adds conference management and research info

@@
 	\includegraphics[width=9cm]{ans_uiuc_group.jpg}
+	\caption{Members of ANS-UIUC at the 2019 Kick Off Barbeque.}
 \end{figure}
@@
 	\includegraphics[width=9cm]{ans_conf_19.jpg}
+	\caption{Members of ANS-UIUC at the 2019 Student Conference at VCU.}
 \end{figure}
+
+\subsection{Research at UIUC}
+Faculty in NPRE conduct research in many areas of interest to the nuclear science community.
+Students are highly encouraged to participate and make their own atomic contributions that will someday save the world.
+
+\subsubsection{Nuclear Power}
+The Department of Nuclear, Plasma, and Radiological Engineering at Illinois is well known for its pioneering research in the area of reactor power engineering.
+Graduates have gone on to leadership positions in industry, national laboratories, and academia.
+Research in the Nuclear Power concentration covers all aspects of power generation using nuclear energy on land, underwater (submarine), and in space.
+It is inherently interdisciplinary and relies on several branches of physics and engineering for design and analysis of large complex systems.
+These include aspects of reactor physics, reactor thermal-hydraulics, reactor safety, reliability and risk, instrumentation and control, training and education, human factors engineering, reactor materials, nonproliferation, and more.
+Safety starndards and maintenance for existing reactors and new reactor designs are also explored by faculty in the department.
+Cross-cutting areas of research include multi-physics and multi-scale modeling and simulation, high performance computing, reliability and risk, validation and verification, and uncertainty analysis.
+Recently, the University of Illinois declared a plan to be completely carbon-neutral by 2050.
+Nuclear power is the perfect candidate to help UIUC attain its energy goals.
+Together, the University and the NPRE department are saving the world one atom at at time.
+
+\subsubsection{Plasma Physics and Fusion Science}
+The research theme of Fusion and Plasma Physics in the NPRE department has a long history of work in the area of magnetic and inertial nuclear fusion as well as plasma engineering.
+NPRE is now one of the leading departments in plasma-material interactions with its Center for Plasma-Materials Interactions established by Prof.
+David Ruzic.
+Furthermore, in the past few years, three new faculty members have been added to this area including: Prof.
+Davide Curelli and Prof.
+Daniel Andruzcyk.
+There are five research themes that spans the work in fusion and plasma physics: fusion materials, plasma-material interface (PMI) diagnostics, plasma-edge and PMI modeling, plasma nanosynthesis, and plasma sources and processing.
+The Hybrid Illinois Device for Research and Application (right) marks the newest addition to the team at CPMI.
+This device finished construction and achieved first plasma during the spring of 2016
+
+\subsubsection{Radiological Science}
+Radiological engineering at UIUC strives to discover novel applications for ionizing radiation in biomedical research, homeland security, and nuclear safeguards.
+We have developed various gamma-ray, x-ray and neutron detectors, imaging devices, and novel algorithms for analyzing the data from these systems.
+These algorithms range from the use of so-called "big data" techniques applied to large sensor networks to advanced radiological imaging methods and image processing techniques for biomedical research.
+We work with physicists, biologist, chemists, material scientists, statisticians, and physicians around the world, to develop advanced diagnostic imaging and radiation-induced therapeutic approaches to address some of the most critical health care-related issues, such as cancer, cardiac diseases, diabetes and neurodegenerative disorders.
+We also work with organizations like the Departments of Defense, Energy, and Homeland Security and the International Atomic Energy Agency to deploy our research around the world to detect and identify the illicit movement of nuclear and radiological materials.
+
+\subsubsection{Reliability and Risk Analysis}
+Risk analysis represents the pinnacle of interdisciplinary research and education.
+Following the Three Mile Island disaster in 1979, Probabilistic Risk Assessment (PRA) has become a key pillar of the risk-informed nuclear regulatory framework, and is now a requirement for every nuclear power plant in the United States.
+Enhancing the prevention of catastrophic technological accidents and the protection of the environment requires advancement in multidisciplinary PRA.
+It demands the development of a common vocabulary within diverse engineering and social science domains in order to address risks emerging from the interface of social and technical systems.
+
+\subsubsection{Materials Science}
+
+\subsubsection{NPRE Research Groups and Laboratories}
+\begin{itemize}
+  \item \textbf{Advanced Reactors and Fuel Cycles (ARFC)} - \textit{Dr. Katy Huff}\\
+  The ARFC group seeks to advance the safety and sustainability of nuclear energy production through improved reactor designs, fuel cycle strategies, and waste management techniques.
+In the area of advanced reactors, our work focuses on extending current simulation tools with features essential to advanced reactor multiphysics.
+In the context of the broader nuclear fuel cycle, the ARFC group emphasizes modeling, simulation, and analysis of the global nuclear fuel cycle, with an emphasis on sustainability.
+A crosscutting theme of our research is an emphasis on advancing methods and software for computational nuclear engineering.
+Accordingly, the Advanced Reactors and Fuel Cycles group is proud to be affiliated with the University of Illinois National Center for Supercomputing Applications and its Blue Waters computing facility.
+  \item \textbf{Virtual Education and Research Laboratory (VERL)} - \textit{Dr. Rizwan Uddin}\\
+  The VERL group focuses on the development of innovative numerical methods and their implementation on high performance computing machines.
+Research efforts center on problems in nuclear engineering, with emphasis on thermal-hydraulics and reactor physics.
+
+  \item \textbf{Analysis of Reactor Transients and Stability (ARTS)} - \textit{Dr. Tomasz Kozlowski}\\
+  The ARTS group performs deterministic safety analysis by developing and validating advanced methods to accurately determine reactor safety margins and reactor behavior.
+By performing high-fidelity numerical predictions of the reactor behavior in abnormal transient scenarios of safety significance, our work supports the nuclear reactor safety analysis, and increases the fidelity of primary system simulation.
+This approach is at the heart of nuclear power’s excellent safety record – always striving to improve current tools and methods.
+
+  \item \textbf{Center for Plasma-Material Interactions (CPMI)} - \textit{Dr. David Ruzic}\\
+  The primary objective of CPMI is the study of plasma-material interactions relevant to fusion, semiconductor manufacturing, and plasma processing through a combination of experimental and computational means.
+CPMI has facilities for the study of fusion materials, High Power Impulse Magnetron Sputtering (HiPIMS), liquid metals, Extreme Ultraviolet Lithography (EUVL),  laser-material interactions, and more.
+Projects are supported by both government and commercial partners to further the application and knowledge of plasma physics.
+The facility recently finished the construction of the HIDRA fusion device, which is a stellarator-tokamak machine hybrid machine used to study plasma-materials interactions.
+HIDRA is currently run by Dr.
+Daniel Andruczyk.
+
+  \item \textbf{Materials Science} - \textit{Dr. James F. Stubbins}\\
+  The group investigates a wide variety of topics within the realm of materials research including mechanical properties, microstructural evaluations, plus radiation damage investigations, and modeling.
+Materials such as copper alloys nickel-based alloys, stainless steels, ferritic steels, and silicon-carbide composites are studied using a variety of analytical techniques electron microscopy and spectroscopy.
+
+  \item \textbf{Non-Equilibrium Matter Laboratory} - \textit{Dr. Yang Zhang}\\
+  This laboratory focuses on the study of non-equilibrium matter, with particular emphasis on liquids and soft matter, using integrated neutron and synchrotron light experimental probes and atomistic modeling and simulation.
+The structure and dynamics of these systems are either inherently complex or driven away from equilibrium by extreme conditions.
+In particular, our current interests include a range of fundamental and technical problems involving slow phenomena and rare events, such as: materials far from equilibrium and in extreme environments; extreme properties of liquids; and glassy or jammed soft matters.
+
+  \item \textbf{Radiation Imaging Group} - \textit{Dr. Ling Jian Meng}\\
+  Research is on developing radiation sensor and systems for visualizing the distribution of radioactivity in surrounding objects, patients, and small lab animals etc.
+Current emphasis includes (a) developing novel radiation sensors for detecting X-ray, gamma rays and neutrons, and (b) developing nuclear techniques for detecting and imaging a tiny amount radiolabeled molecules inside small lab animals.
+
+  \item \textbf{Socio-Technical Risk Analysis (SoTeRiA)} - \textit{Dr. Zahra Mohaghegh}\\
+  The Socio-Technical Risk Analysis (SoTeRiA) Laboratory is evolving Probabilistic Risk Assessment (PRA) by explicitly incorporating the underlying science of accident causation into risk scenarios.
+SoTeRiA laboratory has pioneered two key areas of theoretical and methodological innovations: (1) spatio-temporal causal modeling of social and physical failure mechanisms in PRA, and (2) the fusion of big data analytics with PRA.
+The Lab’s current projects include: Fire PRA; Location-specific Loss- Of-Coolant Accident (LOCA) Frequency Estimations; Risk-Informed Resolution of Generic Safety Issue 191; Human and Organizational Influences on System Risk; Risk-Informed Regulation; and Risk-Informed Emergency Preparedness, Planning and Response.
+
+  \item \textbf{Laboratory: High Temperature Environmental Exposure Lab} - \textit{Dr. Brent Heuser}\\
+  A simultaneous thermal analyzer with combined thermogravimetric and differential scanning calorimetry function is housed in this laboratory.
+The response of LWR fuel cladding materials in high temperature steam environments for improved accident tolerance is currently of interest.
+
+  \item \textbf{Laboratory: Nuclear Materials Fabrication and Studies Lab} - \textit{Dr. Brent Heuser}\\
+  The Radiation Detection and Imaging Lab focuses on developing non-invasive imaging technology for use in preclinical medical research.
+Many of our current endeavors focus on developing semiconductor Single Photon Emission Computed Tomography (SPECT) and Positron Emission Tomography (PET).
+These works challenge the current state of the art for spatial resolution and system sensitivity.
+The use of highly pixelated CdTe detectors has driven our work to break into a spatial resolution on the order of 300 microns for both PET and SPECT.
+Our work in SPECT has also challenged the limits of aperture sensitivity through the engineering of the compound-eye aperture.
+\end{itemize}

### 2019-09-21 management.tex
adds milestones

@@
 \subsection{Staffing Requirements}
+Staffing for room breakdowns and setups, registration, socials, workshops, tours, etc.
+will be supplied by either UIUC ANS members or students of the NPRE department.
+While it is likely that members of our student chapter will voluntarily fill all the staffing requirements of conference hosted events.
+If not, we will rely on other student organizations for support including, but not limited to: ACDIS and WIE.
+Participating in conference events on a staff level is a beneficial experience for any undergraduate who wants to become more familiar with ANS or support their ANS Chapter.
+Throughout the conference, interacting with registering students, driving groups to tour a scientific facility, and turning rooms for technical sessions provide plentiful opportunities for volunteers to interact with myriad members on a number of levels.
+Thus, it will be an overall positive experience for the volunteers.
+Quantitative needs are outlined in Appendix G.
 
@@
 \begin{center}
-	\begin{tabular*}{\textwidth}{c | @{\extracolsep{\fill}}c @{\extracolsep{\fill}} c}
+\begin{longtable}{c |  c  c}
 \hline\hline
@@
 \hline\hline
-& & \\
+& Announcement of 2021 Conference & \\
+& Update milestones with lessons learned &\\
+& Notify department of selection & Co-Chairs\\
+& Confirm Conference Committee & Co-Chairs\\
+& Finalize Conference Date & Co-Chairs\\
+& Confirm Conference Reservations & Non-Technical\\
+& Contact ANS National for support with hotel negotiations& Co-Chairs and Non-Technical\\
+& Set up banking through Busey Bank and ANS National& Financial\\
 \hline\hline
@@
 \hline\hline
-12/14/19& Some task needs to be done& General Co-Chair \\
+&Finalize Facilities Reservations& Non-Technical\\
+&Finalize Logo Design& Communications\\
+&Begin Designing Website and Social Media& Communications\\
 \hline\hline
@@
 \hline\hline
-& & \\
+& Finalize meeting schedule& Co-Chairs\\
+&&\\
 \hline\hline
@@
 \hline\hline
-& & \\
+& Launch social media plan& Communications\\
+& Finalize list of potential speakers& Non-Technical\\
+& Finalize technical topics& Technical\\
 \hline\hline
@@
 \hline\hline
-& & \\
+& Contact Speakers and Presenters& Non-Technical and Technical\\
 \hline\hline
@@
 \hline\hline
-& & \\
+& Attend Student Conference at NC State& All\\
+& Request lessons learned from NC State& Co-Chairs\\
+& Create sponsor letters and contact & General Co-Chair\\
+& Prepare tour opportunities& Non-Technical\\
 \hline\hline
@@
 \hline\hline
-& & \\
+& Confirm tours and costs& Non-Technical\\
+& Submit Progress Report to SSC& \\
+& Create a Call for Papers & Technical and Communications\\
 \hline\hline
@@
 \hline\hline
-& & \\
+& Send Delegates to National Conference& Co-Chairs, All\\
 \hline\hline
@@
 \hline\hline
-& & \\
+& Confirm with all speakers and presenters& \\
+& Report on sponsorship& Financial\\
+& Reassess budget& Financial\\
 \hline\hline
@@
 \hline\hline
-& & \\
+& Update with sponsors& Financial\\
+& Submit second progress to SSC& Co-Chairs\\
 \hline\hline
@@
 \hline\hline
-& & \\
+& Updates on conference deadlines& Financial\\
+& Order gift bags& Non-Technical\\
 \hline\hline
@@
 \hline\hline
-& & \\
+& Confirm hotel blocks and contracts& Non-Technical\\
+& Registration Opens& Financial\\
+& Create and test online paper submission& Technical\\
 \hline\hline
@@
 \hline\hline
-& & \\
+& Attend Winter Conference 2020& Co-Chairs, All\\
+& Finalize marketing material& Communications\\
+& Report from winter conference & Co-Chairs\\
 \hline\hline
@@
 \hline\hline
-& & \\
+& Update website & Communications \\
+& Third progress report to SSC& Co-Chairs\\
+& Send out call for papers& Communications\\
 \hline\hline
@@
 \hline\hline
-& & \\
+& Confirm all judges, panelists, and speakers& Technical\\
+& First paper deadline -- send to reviewers & Technical\\
+& Recruit student volunteers& All\\
+& Finalize tours& Non-Technical\\
+& Finalize conference transportation& Non-Technical\\
 \hline\hline
@@
 \hline\hline
-& & \\
+& Finalize program& Communications\\
+& Order gift bag items & Financial and Non-Technical\\
+& Final Paper Deadline& Technical\\
+& Finalize App& Communications\\
+& Finalize budget& Financial\\
+& Extended Paper Deadline& \\
 \hline\hline
@@
 \hline\hline
-& & \\
+& Print Programs& Communications\\
+& Finalize Awards& Technical\\
+& Finalize Staff Schedule& Non-Technical\\
+& Prepare gift bags, print tags, and banners& Non-Technical\\
+& Final progress report to SSC& Co-Chairs\\
 \hline\hline
 &April&\\
+& Host ANS Student Conference 2021 & \\
+& Return seed money& Financial\\
+& Process Student Reimbursements& Financial\\
+& Finalize financial report& Financial\\
+& Submit conference report& Co-Chairs\\
 \hline\hline
-\end{tabular*}
+\end{longtable}
 \end{center}

### 2019-09-21 conflog.tex
adds sam bio

@@
+% ===============================================================================================
+% ===============================================================================================
+% =====================================Conference Logistics======================================
+% ===============================================================================================
+% ===============================================================================================
+
 \section{Conference Logistics}
@@
 Graphical calendar of date selection and conflicts\\
+
+We are aware that there is no perfect date in which everyone who wants to attend the conference can do so.
+However, our hope is to accommodate as many students as possible with a proposed date of either: Thursday April 8th - Saturday April 10th or Thursday April 15th - April 17th, 2021.
+Two dates are proposed because the Mom's association that runs Mom's Weekend, one of the largest events of the year, has not announced their 2021 dates yet.
+Mom's weekend is typically held the first weekend of April which conflicts with Easter in 2021.
+This consensus was reached after looking up any holidays, scheduled spring breaks, final exams, and other miscellaneous conflict dates for 42 schools with active ANS student sections.
+Based on these findings, there are no major conflicts with any of the schools for these dates.
+These factors were considered in order to maximize the possible number of attendees that can benefit from the conference.
+A handful of schools did not have an academic calendar available for the 2021 Spring semester, so data was based on their listed 2020 dates.
+These date selections avoid conflicting with large event weekends such as Mom's Weekend, dates pending, and the Illini Marathon.
+If, for some reason, an issue arises with our proposed dates, our back-up date is Thursday April 1st - Saturday April 3rd.
+This is unfortunately the same weekend as Easter Sunday.
+However, we prioritized avoid final exams, and UIUC’s Mom’s Weekend.
+Please see the appendix for the full conflicts calendar.
+
 \subsection{Conference Facilities}
-Conference facilities\\
+\begin{itemize}
+  \item \textbf{The Illini Union}\\
+  \item \textbf{National Center for Supercomputing Applications (NCSA)}\\
+  \item \textbf{Engineering Hall}\\
+  \item \textbf{The I-Hotel}\\
+  \item \textbf{}\\
+\end{itemize}
 \subsection{Conference Contingency Plan}

### 2019-09-21 management.tex
adds sam bio

@@
 
+\newpage
 \subsection{Planning Committee Biographies}
+
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{L}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[width=0.3\textwidth]{dotsons2.jpg}
+	\end{center}
+\end{wrapfigure}
+$\textbf{General Co-Chair - Sam Dotson}$\\
+Sam graduated with a B.S.
+in Physics from UIUC in 2019.
+He attended his first ANS student conference in April 2019 and was so inspired by his experience that he decided to pursue graduate work in nuclear engineering rather than physics.
+Now he does research on machine learning applications and computational reactor physics with Dr.
+Kathryn Huff in the ARFC group.
+Hosting a student conference that will inspire others the way he was inspired is one of his top priorities this year.
+He has experience planning activities for student organizations such as Guidance for Physics Students (GPS) and has experience fundraising for the College of Lake County (CLC).
+He helped set a record amount of donations at the 2016 CLC Foundation Gala, where he was an invited speaker and volunteer.
+He will be attending the ANS National conference in November 2019, as well as the ANS Student Conference 2020 at North Carolina State University.\\
+
+$\textbf{Technical Co-Chair - Jeremy Mettler}$\\
+
 [All committee members must plan on attending the upcoming student conference!]
@@
 &April&\\
+\hline\hline
 & Host ANS Student Conference 2021 & \\

### 2019-09-22 proglog.tex
adds two new speakers and a panel

@@
 
-\subsubsection{Fatima Ebrahimi, Princeton}
-Fatima Ebrahimi is a Research Physicist at the PPPL Theory Department
-and an Affiliated Research Scholar at the Department of Astrophysical
-Sciences, Princeton University.
-She has many years of experience in theoretical and global computational extended magnetohydrodynamics (MHD) with wide applications to laboratory fusion and astrophysical plasmas.
-Her main research interests are MHD
-stability in fusion plasmas, momentum transport, dynamos, and magnetic reconnection in laboratory fusion and astrophysical plasmas.
-She has written many papers over a wide range of topics and peer-reviewed journals.
-She is an elected executive committee member
-of the APS Topical Group in Plasma Astrophysics (GPAP), 2018-2021, and program committee member for U.S.
-Magnetic Fusion Research (MFR) Strategic Directions, 2017-2018.
-Dr.
-Ebrahimi is a great choice to have as a speaker on the future of fusion energy.
-
 \subsubsection{Brian Jurczyk, CEO Starfire Industries}
@@
 As a professional leader in plasma and radiological engineering, Jurczyk would be a great speaker to have at the conference on topics related to the future of plasma engineering and professional development.
+
+\subsubsection{Ross Radel, CEO Phoenix, LLC}
+Ross is the CEO and a Board of Directors member of Phoenix.
+He holds a MS and a PhD in Nuclear Engineering from the University of Wisconsin-Madison.
+He previously worked as the Senior Member of the Technical Staff at Sandia National Laboratories.
+Ross has extensive experience with nuclear reactors and advanced power conversion systems that are directly applicable to Phoenix’s core technologies.
+His previous research at the University of Wisconsin focused on high-flux neutron generation for detecting clandestine material, specifically highly enriched uranium.
+The mission of Radel's company, Phoenix, is to transform nuclear technology to better our world.
+This mission statement reflects our mission in hosting the student conference well.
+We believe Dr.
+Radel would be a great speaker for the future of nuclear technology.
+
+\subsubsection{Greg Piefer, CEO SHINE}
+Dr.
+Piefer is the founder and CEO of SHINE Medical Technologies.
+The mission of SHINE is to lead the world in safe, clean, and affordable production of medical tracers and treatment elements.
+He holds a PhD in nuclear engineering, and BS degrees in physics and electrical and computer engineering from the University of Wisconsin–Madison.
+Greg has received numerous awards and honors including the prestigious UW-Madison Early Career award, is the primary inventor on multiple patents and author or co-author of numerous publications, and serves on the boards of several profit and non-profit entities.
+His passion is the growth of technology companies that take scientific advancement to commercialization, providing the opportunity to serve and better humanity.
+Piefer's goals are perfectly attuned to the goals of this conference and he would be an excellent speaker on the powerful applications of radiological engineering.
 
@@
 
-\subsubsection{Applications for Fusion and Plasma}
+\subsubsection{Applications for Plasma Processing}
+
+\subsubsection{Fusion: Materials for the Future}
 

### 2019-09-22 proglog.tex
add plasma panels

@@
 \subsubsection{Critical Conversations: Microreactors}
-This panel explores the benefits of microreactors in general. It will also explore the idea of universities as potential markets for microreactors. Microreactors are exactly what they sound like,
+Microreactors are a growing area of nuclear research and the first installations have been projected for some time in the mid 2020s.
+They are capable of generating 1-50 MWth, which can be used directly or converted to electricity.
+These relatively portable reactors are capable of powering remote areas and towns with little infrastructure.
+UIUC has stated that it aims to be carbon neutral by 2050.
+The University is exploring the possibility of constructing a microreactor on campus for research and power generation, a first of its kind, in pursuit of its decarbonization goals.
+This panel will discuss the benefits and applications for microreactors around the world and also talk specifically about the potential market for microreactors on universities.
+We have a several groups on campus researching, simulating, and modelling microreactors.
+Faculty leading these groups would be excellent speakers on this panel.
 
 \subsubsection{Applications for Plasma Processing}
+Plasma processing has become a staple in many fields of advanced manufacturing.
+Without plasma, modern conveniences such as smartphones and powerful computer technology would not be possible.
+In this panel, representatives from companies at the cutting-edge of plasma processing research will discuss how plasmas continue to revolutionize contemporary industry.
+Potential panelists include Brian Jurczyk, CEO of Starfire Industries, and Phi Nguyen, former Vice President and Director of Engineering at Intel Corp.
 
 \subsubsection{Fusion: Materials for the Future}
+Nuclear fusion has the potential to serve as the ultimate clean energy source, capable of supplying the world’s energy needs for millennia.
+Harnessing this immensely powerful energy resource requires further innovation in a variety of scientific disciplines.
+One of the largest remaining obstacles to fusion energy is the unprecedented strain placed on the materials from which fusion reactors are built.
+This panel will focus on the latest advancements in plasma facing components research and could feature panelists such as Professor David Ruzic, director of the UIUC Center for Plasma-Material Interactions, and Dr.
+Lauren Garrison, Weinberg Fellow at ORNL.
 
@@
 This panel will allow attendees to learn who is working in this area and develop a network of people devoted to issues of nuclear policy.
-Rita Baranwal would be an excellent speaker on this panel because of her work for the DOE.\\
+Rita Baranwal would be an excellent speaker on this panel because of her work for the DOE.
+
+\subsubsection{Radiological Techonology for a Healthier and Safer Future}
+From the production of medical isotopes to nuclear verification, radiological engineering will play an important role in the future of health, security, and more.
+This panel will illuminate some of those applications and show attendees what could be possible with radiological technology.
+Speakers may include Greg Piefer from SHINE and Ross Radel from Phoenix.\\
 

### 2019-09-22 theme.tex
modifies theme

@@
 The ANS student conference is an opportunity for students and professionals to come together and share advances in critical technology and research, dedicated to solving these problems.
-Whether the problem is solving the world’s energy needs, developing technology that will take us to the stars, or curing cancer, nuclear, plasma, and radiological engineering will be at the center of those endeavors.
-Our goal is to inspire and motivate students in nuclear, plasma, and radiological engineering fields to tackle big problems.
+Nuclear, plasma, and radiological engineering will be central to many endeavors.
+Whether the goal is solving the world’s energy needs, developing technology that will take us to the stars, or curing cancer.
+By hosting this conference, we hope to inspire and motivate students in nuclear, plasma, and radiological engineering fields to tackle big problems.
 Saving the world one atom at a time reflects the fact that nuclear science is a powerful force in dealing with grand challenge problems.
-This theme also honors the individual, atomic, contributions from students, researchers, and professionals, in the field of nuclear engineering, that are essential to progress.
-This conference is about science and it is about the people that make the science possible.
+This theme also honors the individual, atomic, contributions from students, researchers, and professionals that are essential to progress.
+This conference is about science and it is about the people that make science possible.
 Students will hear from visionary speakers and leaders of the nuclear science community and come away with optimism for the future; knowing that they are saving the world one atom at a time.\\

### 2019-09-22 conflog.tex
adds transportation info

@@
   \item \textbf{National Center for Supercomputing Applications (NCSA)}\\
-  \item \textbf{Engineering Hall}\\
+  \item \textbf{Beckman Institute}\\
   \item \textbf{The I-Hotel}\\
@@
 \end{itemize}
+
 \subsection{Conference Contingency Plan}
 \subsection{Hotels and Accomodations}
+
+$\Large\textbf{Illini Union}$\\
+
+$\Large\textbf{Marriott TowneSuites}$\\
+
+$\Large\textbf{Hyatt}$\\
+
 \subsection{Travel and Transportation}
+
+\subsubsection{Getting to Champaign}
+The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport.
+There is also a small airport located just 20 minutes outside of campus.
+Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus several times per day.
+Below are the round-trip, non-stop, airfare costs for the first weekend of April.
+\begin{center}
+	\begin{tabular}{lcc}
+		\hline\hline
+		\textbf{School} & \textbf{Departure City} & \textbf{Airfare to O'Hare (ORD)*}\\
+		\hline\hline
+		University of Florida & Orlando (ORL) & $\$$ 236\\
+		Texas A$\&$M & College Station (CLL)& $\$$ 393\\
+		Penn State University & State College (SCE) & $\$$ 349\\
+		MIT & Boston (BOS) & $\$$ 217\\
+		UNLV & Las Vegas (LAS) & $\$$ 308\\
+		Georgia Tech & Atlanta (ATL) & $\$$ 175\\
+		University of Michigan & Detroit (DTW) & $\$$ 240\\
+		Oregon State University & Portland (PDX) & $\$$ 355\\
+		RPI & Albany (ALB) & $\$$ 504\\
+		UC Berkley & Oakland (OAK) & $\$$ 674\\
+		UC Irvine & Orange County (SNA) & $\$$ 439\\
+		US Naval Academy & Baltimore (BWI)& $\$$ 383\\
+		University of Marlyand & Baltimore (BWI) & $\$$ 383\\
+		University of Missouri-Columbia & St. Louis (STL) & $\$$ 168\\
+		University of Nevada & Reno (RNO) & $\$$ 374\\
+		University of New Mexico & Albuqurque (ABQ) & $\$$ 477\\
+		NC State  University & Raleigh (RDU) & $\$$ 195\\
+		University of Pittsburgh& Pittsburgh (PIT) & $\$$ 271\\
+		Clemson University & Greenville (GSP) & $\$$ 295\\
+		SC State University & Columbia (CAE) & $\$$ 365\\
+		University of South Carolina & Columbia (CAE) & $\$$ 365\\
+		Brigham Young University & Salt Lake City (SLC) & $\$$ 441\\
+		U. Wisconsin-Madison & Madison (MSN) & $\$$ 229\\
+		Colorado School of Mines & Denver (DEN)& $\$$ 223\\
+		University of  Tennessee-Knoxville & Knoxville (TYS) & $\$$ 279\\
+		Virginia Commonwealth University & Richmond (RIC) & $\$$ 326 \\
+		Iowa State University & Des Moines (DSM) & $\$$ 199 \\
+		University of Iowa & Cedar Rapids (CID) & $\$$ 249 \\
+	\end{tabular}	
+\end{center}
+\textbf{*}\textit{These fares are predicted to go down around February and March.}\\
+
+Due to the central location of UIUC, driving might be a good option for some schools and individuals. Below are the approximate driving times from several universities. 
+\begin{center}
+	\begin{tabular}{l r}
+	\hline\hline
+	\textbf{School}& \textbf{Drive Time}\\
+	\hline\hline
+	U. Tennessee Knoxville & 7 h 13 min\\
+	University of Michigan & 5 h 24 min\\
+	Clemson University & 10 h 5 min\\
+	U. Missouri-Columbia & 4 h 18 min\\
+	Georgia Tech University & 8 h 54 min \\
+	University of Pittsburgh & 7 h 19 min\\
+	U. Wisconsin-Madison & 3 h 53 min \\
+	Penn State University & 9 h 17 min\\
+	University of South Carolina& 10 h 44 min\\
+	Iowa State University & 5 h 24 min \\
+	University of Iowa & 3 h 34 min\\
+	Vanderbilt University & 5 h 18 min\\
+	\end{tabular}
+\end{center}

### 2019-09-22 management.tex
adds transportation info

@@
 \begin{enumerate}
-	\item Subcommittees are encouraged to operate as autonomous and democratic as possible; however, the General
-	Co-Chairs reserve the rights to make all final decisions. If the Co-Chairs cannot agree, the faculty advisor will be involved.
-	\item Conflicts between committee members are to be resolved outside of the committee. Should this begin to
-	affect the work of these members, the General Co-Chairs may intervene.
-	\item Any cases of misconduct or negligence will be handled by the General Co-Chairs as necessary.
+	\item Subcommittees are encouraged to resolve conflicts internally and as democratically as possible.
+If an independent resolution cannot be reached, the Co-Chairs should be involved.
+The Co-Chairs have the final word on all decisions.
+If the Co-Chairs are unable to agree on a solution, the faculty advisor will be involved.
+	\item Conflicts between individual committee members are to be resolved outside of the committee. Should such a conflict jeopradize the mission of the conference the Co-Chairs will be involved. 
+	\item Any cases of misconduct or negligence will be handled appropriately by the Co-Chairs.
 	\item For extreme cases of misconduct or negligence, separate steps for the removal and replacement of a
-	member are outlined for general members, Subcommittee Chairs, and General Co-Chairs. These include
+	member are outlined for general members, Subcommittee Chairs, and Co-Chairs. These include
 	a discussion with the offending member, consultation of the Faculty Advisor, and a hearing with the

### 2019-09-23 conflog.tex
adds hotel info and jeremy bio

@@
 \subsection{Date Selection}
-Primary date selection\\
-Rationale for date selection\\
-Graphical calendar of date selection and conflicts\\
 
-We are aware that there is no perfect date in which everyone who wants to attend the conference can do so.
-However, our hope is to accommodate as many students as possible with a proposed date of either: Thursday April 8th - Saturday April 10th or Thursday April 15th - April 17th, 2021.
-Two dates are proposed because the Mom's association that runs Mom's Weekend, one of the largest events of the year, has not announced their 2021 dates yet.
-Mom's weekend is typically held the first weekend of April which conflicts with Easter in 2021.
-This consensus was reached after looking up any holidays, scheduled spring breaks, final exams, and other miscellaneous conflict dates for 42 schools with active ANS student sections.
-Based on these findings, there are no major conflicts with any of the schools for these dates.
-These factors were considered in order to maximize the possible number of attendees that can benefit from the conference.
-A handful of schools did not have an academic calendar available for the 2021 Spring semester, so data was based on their listed 2020 dates.
-These date selections avoid conflicting with large event weekends such as Mom's Weekend, dates pending, and the Illini Marathon.
-If, for some reason, an issue arises with our proposed dates, our back-up date is Thursday April 1st - Saturday April 3rd.
-This is unfortunately the same weekend as Easter Sunday.
-However, we prioritized avoid final exams, and UIUC’s Mom’s Weekend.
-Please see the appendix for the full conflicts calendar.
+We propose the conference be held on the following dates: 
+\begin{enumerate}
+	\item Thursday, April 8$^{th}$ - Sunday, April 11$^{th}$ 
+	\item Thursday, April 15$^{th}$ - Sunday, April 18$^{th}$
+\end{enumerate}
+We believe either of these dates would serve as an appropriate first choice because they avoid major conflict dates like finals and spring break for most schools.
+Additionally, mid-April offers pleasant mild weather in Champaign.
+The reason for proposing two weekends to host the conference is due to the UIUC tradition of hosting Mom's Weekend on or near the first weekend in April.
+The Illinois Mom's Association has not yet announced their 2021 dates but to avoid potential conflict, we suggest two dates.
+In the event that both of these dates are unavailable our backup date is
+\begin{itemize}
+	\item Thursday, April 1$^{st}$ - Sunday, April 4$^{th}$.  
+\end{itemize}
+This is a backup date because Easter falls on that Sunday.
+In general, this should be avoided.
+In this case we found that holding the conference at the end of April would conflict with finals for students and holding it earlier in March would conflict with several spring breaks as well as having potentially poorer weather.
+A detailed conflict schedule is listed in Appendix A.
 
 \subsection{Conference Facilities}
-\begin{itemize}
-  \item \textbf{The Illini Union}\\
-  \item \textbf{National Center for Supercomputing Applications (NCSA)}\\
-  \item \textbf{Beckman Institute}\\
-  \item \textbf{The I-Hotel}\\
-  \item \textbf{}\\
-\end{itemize}
+
+\textbf{The Illini Union}\\
+
+% \begin{figure}[h!]
+% 	\includegraphics[width=\textwidth]{illini-union.png}
+% 	\caption{Illini Student Union}
+% \end{figure}
+
+The Illini Union is capable of hosting the entire technical program.
+Keeping the conference contained in one convenient location while being within easy access of the rest of the campus.
+Technical sessions will be held in a combination of rooms on the second, third, and fourth floors of The Union.
+Each of these rooms has at least enough capacity for 42 people and A/V capability.
+There will also be rooms available to have panels and workshops during the course of the technical program.
+The Illini Rooms A and B will be a combined space for the career fair and Illini Room C will host the poster sessions.
+We will keep the space open to allow the poster sessions and career fairs to share attendance and encourage networking.
+A detailed list of room capacities and floor plans are located in Appendix D: Building Layout.
 
 \subsection{Conference Contingency Plan}
+In the event that the Union has reduced availability during the conference we have the ability to host technical sessions and workshops at a combination of buildings: The National Center for Supercomputing Applications (NCSA) and Beckman Institute.
+These two buildings have large capacity rooms and small capacity rooms.
+As these buildings are UIUC property, the cost of renting them are significantly reduced compared to a private facility.
+Additionally, these two buildings are adjacent to one another and are at most a 10 minute walk from either the Union or Marriott TowneSuites.
+See Fig.\ref{fig:conf-map} for a map of the proposed conference facilities.\\
+
+\textbf{National Center for Supercomputing Applications (NCSA)}\\
+NCSA is a hub of transdisciplinary research and digital scholarship where University of Illinois faculty, staff, and students, and collaborators from around the globe, unite to address research grand challenges for the benefit of science and society.\\
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.8\textwidth]{ncsa_front.jpg}
+	\caption{NCSA}
+	\label{fig:ncsa}
+\end{figure}
+
+\textbf{Beckman Institute}
+The Beckman Institute for Advanced Science and Technology at the University of Illinois is an interdisciplinary research institute devoted to leading-edge research in the physical sciences, computation, engineering, biology, behavior, cognition, and neuroscience.\\
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.6\textwidth]{beckman.jpg}
+	\caption{Beckman Institute}
+	\label{fig:beckman}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\textwidth]{campus_map.png}
+	\caption{Map of conference facilities and hotels}
+	\label{fig:conf-map}
+\end{figure}
+
 \subsection{Hotels and Accomodations}
+We are fortunate to have our primary hotel, the Union, be the same as our primary conference venue.
+While the Union has many rooms available it does not have enough capacity to hold every attendee of the conference.
+Thus, we have listed two hotels that are on campus and can house the majority of attendees plus a third hotel where professionals and overflow attendees can stay.
 
-$\Large\textbf{Illini Union}$\\
+$\textbf{Illini Union}$\\
+This is the primary hotel for all student attendees and invited speakers.Commuting to the conference will be as easy as taking the elevator downstairs because the Illini Union is where the primary conference activities will be held.
+The Union is also a five-minute walk from Green Street, the campus hub of dining and social activities.
+Guests have access to Wi-Fi and, upon request, guest passes to the university recreational facilities.
+Breakfast is provided in the form vouchers for any of the hotel restaurant options inside the Union.
+Hosting technical sessions, workshops, and plenaries in the Union will help us negotiate a lower room rate.\\
 
-$\Large\textbf{Marriott TowneSuites}$\\
+$\textbf{Marriott TowneSuites}$\\
+Rooms at the Marriott resemble a studio apartment with an open floor plan, refrigerator, stove, microwave, dishes, and dining area.
+Many rooms are equipped with pull-out couches, allowing 5 students to share a queen double room if desired.
+The hotel offers internet access for a maximum of 3 devices per room.
+The hotel is located on Green Street and the Illini Union a mere five-minute walk away.
+For $\$$7 a day, guests may park in a parking garage with 8ft clearance.
 
-$\Large\textbf{Hyatt}$\\
+% \begin{figure}[H]
+% \centering
+% \begin{subfigure}{0.5\linewidth}
+% 	\includegraphics[width=0.4\textwidth]{marriott_room1.jpeg}		
+% \end{subfigure}
+% \end{figure}
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}[b]{0.5\linewidth}
+		\centering
+		\includegraphics[width=0.5\textwidth]{marriott_room1.jpeg}
+		\caption{Marriott queen double}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.5\textwidth]{marriott_room2.jpeg}
+		\caption{Marriott king single}
+	\end{subfigure}
+\end{figure}
 
+$\textbf{Hyatt}$\\
+The Hyatt is a gorgeous hotel located in the heart of downtown Champaign, surrounded by local restaurants and vibrant a nightlife.
+It is just a short busride away from the main conference activities.
+Parking is also available for added accessibility.
+This is a great place for professionals to stay and enjoy.
+Wifi is included with every room.
+Joining the Hyatt rewards program is free and comes with the added benefit of free breakfast every morning.
+
+\newpage
 \subsection{Travel and Transportation}
@@
 Below are the round-trip, non-stop, airfare costs for the first weekend of April.
+Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip.
 \begin{center}
@@
 \end{center}
+
+\subsubsection{Getting to the Conference}
+The primary location for all conference events is the Illini Union.
+This is also the primary hotel for conference attendees.
+The secondary hotel, Marriott TowneSuites is merely a five minute walk from the Union.

### 2019-09-23 management.tex
adds hotel info and jeremy bio

@@
 		\vspace{-\baselineskip}
-		\includegraphics[width=0.3\textwidth]{dotsons2.jpg}
+		\includegraphics[height=15\baselineskip]{dotsons2.jpg}
 	\end{center}
@@
 
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{R}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{mettlerj.jpg}
+	\end{center}
+\end{wrapfigure}
 $\textbf{Technical Co-Chair - Jeremy Mettler}$\\
+Jeremy graduated with a B.S.
+in Nuclear, Plasma, and Radiological Engineering from UIUC in 2018, and is now attending as a 2nd-year graduate student studying plasma science under Dr.
+David Ruzic.
+He has been heavily involved in the UIUC student chapter of ANS since his freshman year, serving on the executive board for three years as External Vice President and President.
+Jeremy has attended the past five ANS Student Conferences, which serve as an inspiration for his involvement in this proposal process.
+He is dedicated to making sure that future generations of students are able to have the same amazing experiences through ANS as he had, especially at the ANS Student Conference.
+Outside of ANS, he has held a summer internship at Oak Ridge National Lab, and is currently focusing his research towards combined laser-plasma systems for materials processing.\\
 

### 2019-09-23 proglog.tex
adds hotel info and jeremy bio

@@
 The workshop will be approximately two hours of instruction at NCSA room 1030.
+
+% =========================================================================================
+% =========================================================================================
+% =========================================================================================
+% Technical and Non-Technical Tours
+% =========================================================================================
+% =========================================================================================
+% =========================================================================================
+
+\subsection{Tours}
+
+\subsubsection{Technical Tours}
+Out of the 61 commercially operating nuclear power plants and 99 nuclear reactors in the U.S., Illinois is home to six nuclear power stations and eleven active reactors.
+Being located in a state with numerous power plants, as well as being surrounded by locations of interest to a variety of nuclear-related disciplines, the touring opportunities at the University of Illinois mirror the diversity of UIUC’s Nuclear Plasma and Radiological Engineering program.\\
+
+\textbf{Argonne National Laboratory}\\
+Located in Lemont, Illinois, Argonne works closely with universities, industry, and other national labs to help make an impact on the atomic, human, and global scale.
+With 14 research divisions, five national scientific user facilities, and hundreds of research partners, attendees of this tour will be exposed to the diverse areas of research in nuclear science.
+Argonne is two-and-a-half-hour drive away.
+Bus transportation will be provided.
+On the tour, students will be guided around the site’s scientific and engineering facilities.\\
+
+\textbf{Clinton Power Station}\\
+Located about 35 miles away from Champaign, the Clinton Power Station is an Exelon owned nuclear power plant that started operating at full power on September 15th, 1987.
+They currently serve over one million customers and operate 94.9$\%$ of the time.
+The tour will be held on Thursday morning and bus transportation will be provided.
+Attendees will be guided by a Clinton employee.
+The tour will include the control-room simulator that operator trainees use, and a chance to learn more about the site’s innovative safety, operation, and engineering practices.\\
+
+\textbf{Starfire Industries LLC}\\
+Starfire Industries is located at the south end of campus and works with federal organizations such as DARPA, Homeland Security, NASA, and others.
+They offer services in areas like neutron radiography, fabrication, and prototyping.
+Students will be able to get to the site by using the MTD busses that run continuously throughout the day and will be free to all conference attendees.
+Here, students will be able to learn more about Starfire products such as the IMPULSE pulsed power module, plasma sources, thin film systems, nGen neutron generators, neutron detectors, and the PICTORIS neutron radiography system.
+Starfire’s collaboration with government agencies and propensity for solving big problems related to plasma engineering make them a great place to learn about plasma processing applications.\\
+
+\textbf{National Center for Supercomputing Applications (NCSA)}\\
+Also located on campus is NCSA, which houses Blue Waters, one of the most powerful supercomputers in the world.
+The NCSA is within walking distance from all conference hotels.
+During the tour, attendees will tour the machine room and witness some of the beautiful results it produces.
+Supercomputers like Blue Waters are important for solving computationally challenging problems and creating robust simulations for a variety of phenomena.\\
+
+\subsubsection{Non-Technical Tours}
+
+Brewery tours are staple social event and tour at the ANS Student Conference.
+Champaign-Urbana has several popular local breweries that give tours and tastings at their facilities.
+Due to this, we will be able to expand the number of attendees that can go on these tours over previous conferences.
+These will require sign up before the conference and we expect spots to fill up quickly.\\
+
+\textbf{Riggs Brewery Tour}\\
+For 21+ attendees, two tours of a local brewery will be included in our tours list Thursday afternoon from 3-5pm.
+Find out how Riggs makes their beer and taste test it along the way.
+Each tour will last approximately one hour and accommodates up to 20 people per tour.
+Riggs is located in east Urbana.
+Transportation to and from the brewery will be provided.
+\\
+
+\textbf{Triptych Brewery Tour}\\
+For 21+ attendees, Triptych offers two tours that run around 1.5 hours for roughly 30 people each that includes several beer tastings throughout.
+Tours will be from 2-5pm on Thursday afternoon.
+Triptych is located in Savoy, IL, just 15 minutes from campus.
+Transportation to and from the brewery will be provided.\\
+
+\textbf{University Tour}\\
+Attendees will be able to take a tour of the UIUC campus.
+They will start at the Talbot Laboratory where the department of Nuclear Plasma and Radiological Engineering is located.
+Here, students will get to see the Virtual Education and Research Laboratory to see how virtual reality technology can be adapted and applied to educational methods.
+There are also many other historical artifacts on display for participants to see.
+Afterwards, students will be led to various noteworthy locations unique to UIUC.\\

### 2019-09-23 uiuc.tex
updated about UIUC, in progress

@@
-\section{Urbana-Champaign and UIUC}
+\section{East-central Illinois: The cities of Champaign and Urbana}
 
-\subsection{About Urbana-Champaign}
-Champaign-Urbana (CU) is a close-knit community filled with music, culture, and food.
+\subsection{Champaign-Urbana in a Nutshell}
+%Champaign-Urbana (CU) is a close-knit community filled with music, culture, and food.
 While Campustown, the neighborhood immediately surrounding campus,  is an important part of the atmosphere, there is plenty to do off campus.
@@
 The Krannert Center for the Performing Arts is also a world-renowned theater that has hosted groups from all genres like the New York Philharmonic, the Russian National Ballet, and Sonny Rollins.
+
+Champaign-Urbana (CU), or colloquially known as Chambana, is home to the flagship campus of the University of Illinois system, the University of Illinois at Urbana-Champaign (UIUC).
+Since its foundations in the mid 19th century, it has flourished into the cultural hub of the midwest that it is today.
+CU houses many landmarks and districts, and it showcases both community and nationwide events annually.
+It is home to the Historic Virginia Theater, host to Ebertfest in honor of the late film critic and UIUC alumnus Roger Ebert.
+The Krannert Center for the Performing Arts is located on U of I campus, which is known for its four first-class venues, including the Foellinger Great Hall - one of the most acoustically perfect performance spaces in the world, attracting world famous artists and ensembles to perform there every year.
+Other notable events that attract many people to the twin cities are the Pygmalion Music Festival, the Urbana Sweetcorn Festival, and the Illinois Marathon.
+
+CU is an industrial base to several major companies.
+This encompasses offices for Abbott Laboratories, Archer Daniels Midland (ADM), Caterpillar, John Deere, The Dow Chemical Company (TDCC), IBM, and State Farm.
+Other top employers in CU include Kraft Heinz, Carle Foundation Hospital, Jimmy John's, and high technology employer Wolfram Research.
+Carle has notably been affiliated with the creation of the first college in CU in over 60 years, the Carle Illinois College of Medicine -  ``the world's first engineering-based college of medicine".
+Research Park at the University of Illinois serves as a technology hub for several research and development ventures, where there are more than 120 companies employing 2,100 students and professionals in high-technology careers.
+Over 70 startup companies work in commercializing technology in Research Park.
 
@@
 
+\subsubsection{Accommodations}
+Information about facility/hotel space/capacity goes here - reference UNLV 2012, UPenn 2014, UW 2016
+
 \subsubsection{Weather}
@@
 
-\subsection{About the University of Illinois}
+\subsection{University of Illinois at Urbana-Champaign: Learning \& Labor}
 Founded in 1867, the University of Illinois at Urbana-Champaign (UIUC) has cultivated a long history of significant scientific discoveries and contributions.

### 2019-09-23 uiuc.tex
updates about illinois section

@@
 
-Champaign-Urbana (CU), or colloquially known as Chambana, is home to the flagship campus of the University of Illinois system, the University of Illinois at Urbana-Champaign (UIUC).
-Since its foundations in the mid 19th century, it has flourished into the cultural hub of the midwest that it is today.
-CU houses many landmarks and districts, and it showcases both community and nationwide events annually.
-It is home to the Historic Virginia Theater, host to Ebertfest in honor of the late film critic and UIUC alumnus Roger Ebert.
+Champaign-Urbana (CU), known colloquially as Chambana, is home to the state's flagship campus the University of Illinois at Urbana-Champaign (UIUC).
+Since its founding in the mid 19th century, it has grown into the flourishing cultural hub of the midwest that it is today.
+CU houses many landmarks and districts and showcases both local and national events annually.
+It is home to the Historic Virginia Theater, host of Ebertfest in honor of the late film critic and UIUC alumnus Roger Ebert.
 The Krannert Center for the Performing Arts is located on U of I campus, which is known for its four first-class venues, including the Foellinger Great Hall - one of the most acoustically perfect performance spaces in the world, attracting world famous artists and ensembles to perform there every year.
-Other notable events that attract many people to the twin cities are the Pygmalion Music Festival, the Urbana Sweetcorn Festival, and the Illinois Marathon.
+Other notable events that attract many people to the twin cities are the Pygmalion Music Festival, the Urbana Sweetcorn Festival, and the Illini Marathon.
 
-CU is an industrial base to several major companies.
-This encompasses offices for Abbott Laboratories, Archer Daniels Midland (ADM), Caterpillar, John Deere, The Dow Chemical Company (TDCC), IBM, and State Farm.
-Other top employers in CU include Kraft Heinz, Carle Foundation Hospital, Jimmy John's, and high technology employer Wolfram Research.
+CU is an industrial base to several major companies including Abbott Laboratories, Archer Daniels Midland (ADM), Caterpillar, John Deere, The Dow Chemical Company (TDCC), IBM, and State Farm.
+Other top employers in CU include Kraft Heinz, Carle Foundation Hospital, and Wolfram Research.
 Carle has notably been affiliated with the creation of the first college in CU in over 60 years, the Carle Illinois College of Medicine -  ``the world's first engineering-based college of medicine".
 Research Park at the University of Illinois serves as a technology hub for several research and development ventures, where there are more than 120 companies employing 2,100 students and professionals in high-technology careers.
-Over 70 startup companies work in commercializing technology in Research Park.
+
+Illinois relies heavily on nuclear power to supply its energy needs with 52$\%$ of electricity generated by nuclear plants.
+UIUC also bears a long tradition of nuclear power research and was home to the TRIGA nuclear reactor for almost 40 years.
+During this time researchers at UIUC made contributed to the knowledge store of nuclear reactor kinetics, isotope production, fission fragment physics, and much more.
+Now, UIUC is exploring ways to use nuclear power to accelerate its decarbonization efforts.
+We hope to continue the nuclear tradition by hosting the ANS Student Conference in 2021.
 
@@
 Finally, there are several reliable bus services that make frequent trips from Champaign-Urbana to O’Hare and the Chicagoland area.
-
-\subsubsection{Accommodations}
-Information about facility/hotel space/capacity goes here - reference UNLV 2012, UPenn 2014, UW 2016
 

### 2019-09-23 socials.tex
added socials

\section*{Socials}

\subsection*{Illini Union Rec Room Lockout}
The Illini Union Rec Room is located in the basement of the Union building. A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at the Krannert Center for Performing Arts, only a short walk away through the University of Illinois main quad! This space can accompany up to 150 people, with extra tables outside of the Rec Room for socializing, playing board games, or having a late night snack or coffee with professionals or students from other universities.

% Illini Union Rec Room Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{union_recroom1.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{union_recroom2.png}
	\end{subfigure}		
\end{figure}

\subsection*{77 Club at Memorial Stadium}
Memorial Stadium is not only home to the Fighting Illini football team, but also to exquisite event space overlooking Zuppke Field. The sixth level of Memorial Stadium is home of the magnificent 77 Club, which honors Illini great, the "Galloping Ghost" Red Grange. This 5,020 square foot space is located midfield and features an outdoor patio area overlooking the city of Champaign, for a combined total space of 9,740 square feet. This event will take place following dinner at I Hotel Conference Center, and is just a short and scenic walk away past the State Farm Center (formerly the historic Assembly Hall). Tables will be set up around a stage featuring live music and a dance floor and drinks will be served. This is the perfect event to incorporate a little bit of Illinois history with music, dancing, and socializing!

% 77 Club Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.7\linewidth]{77club1.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{77club2.png}
	\end{subfigure}		
\end{figure}

\subsection*{Pour Bros. Taproom in Downtown Champaign}
Welcome to Illinois' first pour-your-own taprooms. Pour Bros. Taproom is located in the heart of the historic downtown Champaign area and features 28 pour-your-own taps: beers, ciders, meads and wine\ldots all poured by you, one ounce at a time. Socialize over the vintage games Pour Bros has to offer: skeeball, bubble hockey, steel tip darts, DAGZ and more! If you are feeling more on the leisurely side, Pour Bros features live music in a spacious and comfortable seating area for you to get your networking on.

% Pour Bros Picture
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.5\linewidth]{pour_bros2.png}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{pour_bros1.png}
	\end{subfigure}		
\end{figure}

\subsection*{Under 21 Social: University of Illinois Ice Arena}
For students under the drinking age that cannot attend the Pour Bros. Taproom social event, the University of Illinois Ice Arena is another option that is only a brief walking distance from the Union. It was built in 1931 and offers a unique option for skating get-togethers from broomball and hockey to group skating parties. The Ice Arena is a 55,000 square foot facility and is the only one in Champaign-Urbana. The dimensions of the rink are 192' by 115' with a 1,200 seat arena surrounding. There are four public locker rooms, four party areas, and two Zambonis in the facility. The Center Ice Cafe offers hot chocolate, coffee, smoothies, fountain drinks, and more to quench your thirst.  Snacks and concession items are also available.

% Ice Arena Picture
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{ice_arena.png}
\end{figure}

### 2019-09-23 management.tex
updates management, main

@@
 \subsection{Position Responsibilities}
-The general and technical chairs are responsible for setting up major milestones and 
-ensuring that those milestones are met. Together they oversee all four subcommittees but 
-are each primarily in charge of two. They will serve as the primary contacts between subcommittee
-chairs and the faculty as well as professionals. The two co-chairs have the final word on all 
-conference decisions.
+The three co-chairs are responsible for setting up major milestones and 
+ensuring that those milestones are met. Together they oversee all three subcommittees but 
+are each primarily in charge of one. They will serve as the primary contacts between subcommittee
+chairs and the faculty as well as professionals. The co-chairs have the final word on all 
+conference decisions. They serve as the face of the conference and
 
@@
 	In addition to the responsibilities outlined above, the General Co-Chair primarily oversees the
-	Non-technical and Publications Subcommittees. Works with the Technical Co-Chair to plan full committee
+	Non-technical Subcommittee and the Media Coordinator. He works with the Technical Co-Chair to plan full committee
 	meetings and completes any remaining tasks to ensure that milestones are met.
@@
 	In addition to the responsibilities outlined above, the Technical Co-Chair primarily oversees the
-	Technical and Financial Subcommittees. Works with the General Co-Chair to plan full committee
-	meetings and completes any remaining tasks to ensure that milestones are met.
+	Technical Subcommittee. Works with the General Co-Chair to plan full committee meetings and completes any remaining tasks to ensure that milestones are met.
+	\item $\large\textbf{\textit{Financial Co-Chair}}$\\
+	In addition to the responsibilities outlined above, the Financial Co-Chair primarily oversees the Financial Subcommittee.
+The Financial Co-Chair is also responsible for interacting with businesses, the university, and ANS National for sponsorship needs.
+He completes any remaining tasks to ensure that milestones are met.
+
 	\item $\textbf{Non-Technical Subcommittee}$\\
@@
 	\begin{itemize}
-		\item[$\circ$] $\textbf{Logistics Chair (Gavin Davis?)}$\\
-		The Logistics Chair is in charge of planning all tours and non-technical workshops and panels. Organizes speakers during dinners
-		Also responsible for keeping track of subcommittee and reporting to the General and Technical Co-Chairs.
+		\item[$\circ$] $\textbf{Logistics Chair}$\\
+		The Logistics Chair is in charge of planning all tours and non-technical workshops and panels.
+Organizes speakers during dinners.
+Recruits student volunteers to staff events and sessions during the conference.
+		Also responsible for keeping track of the subcommittee and reporting to the Co-Chairs.
 		\item[$\circ$] $\textbf{Hotels and Transportation Coordinator}$\\
@@
 that includes contacting the catering services, reserving the venues where meals are held, and making sure the venues are staffed.
+		\item[$\circ$]$\textbf{Tours Coordinator}$\\
+		The tours coordinator organizes tours and works with the transportation coordinator to ensure that transportation is available during the conference for these tours.
+		\item[$\circ$]$\textbf{Program Coordinator}$\\
+		The program coordinator creates programs for the conference, sets the conference schedule to minimize overlap between events and increase student involvement.
+Communicates with other coordinators and subcommittees about the schedule of events.
+Designs and purchases T-shirts for attendees.
+Arranges gift bags for attendees.
+Works with sponsorship coordinator to create gift bags.
 	\end{itemize}
@@
 	\begin{itemize}
-		\item[$\circ$] $\textbf{Financial Chair}$\\
-		Sets the budget for the whole committee and ensures that the committee does not exceed the budget.
-Manages the ANS Student Committee account and collects receipts.
-Updates and maintains the budget as required.
-Keeps track of subcommittee progress and reports to the General and Technical Co-Chairs.
-		\item[$\circ$] $\textbf{Registration Coordinator (Jasmine Dinari?)}$
+		\item[$\circ$] $\textbf{Account Coordinator}$\\
+		Manages the ANS Planning Committee account with Busey Bank and ANS National.
+The account coordinator is also responsible for keeping track of receipts, setting a budget for the committee, keeps track of all transactions,
+		\item[$\circ$] $\textbf{Registration Coordinator }$
 		Handles the registration for professional and student attendees. Communicates the number of attendees to the Program Coordinator. 
 		\item[$\circ$] $\textbf{Sponsorship Coordinator}$\\
-		Assists the Financial Chair with matters involving sponsorship as well as working closely with the registration coordinator and the General and Technical Co-Chairs.
+		Assists the Financial Co-Chair with matters involving sponsorship as well as working closely with the Registration and Account Coordinators and the General and Technical Co-Chairs.
+Works with the Program Coordinator on gift bag items and works with the Career Fair Coordinator.
 	\end{itemize}
@@
 	\begin{itemize}
-		\item[$\circ$] $\textbf{Sessions Chair (Gwen Chee?)}$\\
+		\item[$\circ$] $\textbf{Technical Subcommittee Chair}$\\
+		 Also responsible for ensuring that judges understand the judging criteria, and organizes the award ceremony.
+		Keeps track of subcommittee progress and reports to the General and Technical Co-chairs.
+		\item[$\circ$] $\textbf{Sessions Coordinator}$\\
 		Responsible for organizing presentation, poster sessions, and technical
-		panels. Also responsible for ensuring that judges understand the judging criteria, and organizes the award ceremony.
-		Keeps track of subcommittee progress and reports to the General and Technical Co-chairs.
-		\item[$\circ$] $\textbf{Workshops Coordinator (Zach Jeckell?)}$\\
+		panels. Makes sure that all rooms are properly set up with equipment to ensure smooth technical sessions.
+		\item[$\circ$] $\textbf{Workshops Coordinator}$\\
 		Organizes workshops locations, times, staffing, costs, supplies, student enrollment
 		and any other tasks required to have successful workshops. Also assists the Sessions Chair when needed.
-		\item[$\circ$] $\textbf{Career Fair Coordinator (Rierson Johnson?)}$\\
+		\item[$\circ$] $\textbf{Career Fair Coordinator}$\\
 		Oversees staffing and support for the career fair as well as working with the Sponsorship
@@
 	\end{itemize}
-	\item $\textbf{Communications Subcommittee}$
-	The Communications Subcommittee is in charge of public relations and communicating status updates with attendees.
-	\begin{itemize}
-		\item[$\circ$] $\textbf{Publications Chair (Nate Reid?)}$\\
-		The Publications Chair is primarily responsible for publishing and organizing the student abstracts, as well as 
-		helping the media coordinator maintain a social media presence. 
-		\item[$\circ$] $\textbf{Media Coordinator (Nathan Ryan?)}$\\
+	\item $\textbf{Media Coordinator}$\\
 		The Media Coordinator is reponsible for designing the conference website, constantly updating social media presence,
 		and obtains information from other members of the planning committee for the website. 
-		\item[$\circ$] $\textbf{Program Coordinator (Brady Moran?)}$\\
-		The Program Coordinator is in charge of setting the program for the conference, minimizing event overlap, and coordinating
-		with the Publications Chair and Media Coordinator.
-	\end{itemize}
 \end{itemize}
@@
 Outside of ANS, he has held a summer internship at Oak Ridge National Lab, and is currently focusing his research towards combined laser-plasma systems for materials processing.\\
+
+$\textbf{Financial Co-Chair}$\\\\
+
+$\textbf{Account Coordinator}$\\
+$\textbf{Registration Coordinator}$\\
+$\textbf{Sponsorship Coordinator}$\\
+
+$\textbf{Technical Subcommittee}$\\\\
+
+$\textbf{Technical Subcommittee Chair}$\\
+$\textbf{Sessions Coordinator}$\\
+$\textbf{Workshops Coordinator}$\\
+$\textbf{Career Fair Coordinator}$\\
+
+$\textbf{Non-Technical Subcommittee}$\\\\
+
+$\textbf{Logistics Chair}$\\
+$\textbf{Hotels and Transportation Coordinator}$\\
+$\textbf{Hospitality and Catering Coordinator}$\\
+$\textbf{Tours Coordinator}$\\
+$\textbf{Program Coordinator}$\\
+
+$\textbf{Media Coordinator}$\\
 

### 2019-09-24 management.tex
updates management

@@
 
-$\textbf{Account Coordinator}$\\
-$\textbf{Registration Coordinator}$\\
-$\textbf{Sponsorship Coordinator}$\\
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{R}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{stahlj.jpg}
+	\end{center}
+\end{wrapfigure}
+$\textbf{Account Coordinator - Jack Stahl}$\\
+
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{R}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{dinarij.jpg}
+	\end{center}
+\end{wrapfigure}
+$\textbf{Registration Coordinator - Jasmine Dinari}$\\
+
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{R}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{sheheej.jpg}
+	\end{center}
+\end{wrapfigure}
+$\textbf{Sponsorship Coordinator - James Shehee}$\\
 
@@
 
-$\textbf{Technical Subcommittee Chair}$\\
-$\textbf{Sessions Coordinator}$\\
-$\textbf{Workshops Coordinator}$\\
-$\textbf{Career Fair Coordinator}$\\
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{R}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{cheeg.jpg}
+	\end{center}
+\end{wrapfigure}
+$\textbf{Technical Subcommittee Chair- Gwen Chee}$\\
+
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{R}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{fairhurstr.jpg}
+	\end{center}
+\end{wrapfigure}
+$\textbf{Workshops Coordinator - Roberto Fairhurst}$\\
+Roberto graduated with a B.S.
+in Nuclear Engineering from Instituto Balseiro (Argentina) April 2018.
+He is now a 2nd-year graduate student at UIUC.
+He does research on computational multi-physics solvers applied to advanced reactors as part of the Advanced Reactors and Fuel Cycle group under the supervision of Dr.
+Kathryn Huff.
+He got experience in the organization of conferences during the planning and development of a technical workshop (TWOFCS19) that took place at UIUC in June 2019.
+His motivation for hosting a student conference is his passion for Nuclear Energy and his desire to transmit this passion to other students.
+He believes hosting the student conference at UIUC will help the field grow and thrive.
+This is also an opportunity to meet other people working in the field, share life experiences, and develop a stronger network.
+
+$\textbf{Sessions Coordinator - Zachary Jeckell}$\\
+$\textbf{Career Fair Coordinator - Greg Golba}$\\
 
@@
 
-$\textbf{Logistics Chair}$\\
-$\textbf{Hotels and Transportation Coordinator}$\\
-$\textbf{Hospitality and Catering Coordinator}$\\
-$\textbf{Tours Coordinator}$\\
-$\textbf{Program Coordinator}$\\
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{R}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{gaughann.JPG}
+	\end{center}
+\end{wrapfigure}
 
-$\textbf{Media Coordinator}$\\
+$\textbf{Logistics Chair - Natalie Gaughan}$\\
+Natalie earned her B.S.
+in Nuclear Engineering from the University of Wisconsin-Madison in 2017.
+She has completed internships at Argonne National Laboratory and the International Atomic Energy Agency.
+She is now a graduate student at UIUC intending to research radiological science and nuclear medicine.
+Natalie has attended two ANS student conferences in the past and knows how these conferences can be influential in students’ career development.
+She will be attending the upcoming ANS student conference in 2020 at NC State.
+
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{L}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{kdilan.jpg}
+	\end{center}
+\end{wrapfigure}
+$\textbf{Program Coordinator - Dilan Kurukulasuriya}$\\
+Dilan Kurukulasuriay is a second-year undergraduate student pursuing a B.S.
+in Nuclear, Plasma, and Radiological Engineering, along with a minor in Physics and Mathematics.
+He has been active in ANS at UIUC since the start of his freshman year, and he currently serves as the Outreach Chair on the Executive Board.
+Dilan has worked at the Center for Plasma-Material Interactions lab since the start of his freshman year on HIDRA, and he stayed on campus over the summer to continue to do so.
+Dilan attended the 2019 ANS Student Conference and it was the highlight of his freshman year of college.
+He is interested in fusion science research, specifically the materials interaction aspect.
+He also plans on attending the upcoming student conference at NC State in 2020.
+
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{R}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{davisg.jpg}
+	\end{center}
+\end{wrapfigure}
+$\textbf{Hotels and Transportation Coordinator - Gavin Davis}$\\
+
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{R}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{moranb.jpg}
+	\end{center}
+\end{wrapfigure}
+$\textbf{Hospitality and Catering Coordinator - Brady Moran}$\\
+
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{R}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{ballaa.jpg}
+	\end{center}
+\end{wrapfigure}
+$\textbf{Tours Coordinator - Anna Balla}$\\
+
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{L}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[width=0.3\textwidth]{ryann.jpg}
+	\end{center}
+\end{wrapfigure}
+$\textbf{Media Coordinator - Nathan Ryan}$\\
+Nathan is pursuing a B.S.
+in Physics from UIUC.
+He graduated in the top five of his high school class, while holding down a part time managerial position and running a research project at Argonne National Laboratory concurrent with his Sophomore through Senior years of Secondary Education.
+His first experience with Nuclear Physics was at the National Superconducting Cyclotron Laboratory where he worked with grad students on rare Cadmium isotopes.
+He has experience with building appealing website pages, as well as social media communications.
+He believes that an online presence for this event will supplement the success of an already great set of programs and individuals involved.
+He is excited to attend the upcoming ANS Student Conference at NC State in 2020.
 

### 2019-09-24 proglog.tex
moves socials to program logistics
adds speaker images

@@
 \subsubsection{Rachel Slaybaugh, UC Berkeley}
-% \begin{wrapfigure}{r}{0.5\textwidth}
-% 	\begin{center}
-% 		\includegraphics[width=0.48\textwidth,scale=0.2]{slaybaugh.jpg}
-% 	\end{center}
-% \end{wrapfigure}
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{L}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{speaker-0.jpg}
+	\end{center}
+\end{wrapfigure}
 Prof.
@@
 Due to her endeavors in teaching and sharing nuclear innovation, we believe that Slaybaugh's goals are aligned with the goals of this conference and would make her an excellent addition to the program.
-Slaybaugh has much to offer the conference with her vision and leadership.
+Slaybaugh has much to offer the conference with her vision and leadership.\\
 
 \subsubsection{Suzanne Hobbs Baker}
-% \begin{wrapfigure}{r}{0.5\textwidth}
-% 	\begin{center}
-% 		\includegraphics[scale=0.75]{hobbsbaker.jpeg}
-% 	\end{center}
-% \end{wrapfigure}
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{R}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{speaker-1.jpeg}
+	\end{center}
+\end{wrapfigure}
 Talking about nuclear energy, specifically with the general public, is one of Suzanne Hobbs Baker's key goals.
@@
 Baker's work in empowering minorities and students to solve the world climate crisis with nuclear energy, as well as her skill in creative science communication, ensures that Baker has a lot to offer the student conference.
-Celebrating the people behind the science is one of the key goals of this conference and an area in which Baker has a lot of experience.
+Celebrating the people behind the science is one of the key goals of this conference and an area in which Baker has a lot of experience.\\
 
+\vspace{0.5cm}
 \subsubsection{Todd Allen, UW Madison}
-% \begin{wrapfigure}{r}{0.5\textwidth}
-% 	\begin{center}
-% 		\includegraphics[scale=0.75,width=0.48\textwidth]{allen.jpeg}
-% 	\end{center}
-% \end{wrapfigure}
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{L}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{speaker-6.jpeg}
+	\end{center}
+\end{wrapfigure}
 His first post-Ph.D.
@@
 Since 2016 he has been a Visiting Senior Fellow with Clean Energy Program at Third Way, a Washington, DC based think tank.
-His role in formulating the roadmap for Generation IV reactors and his leadership indicate that he would make a great speaker at the conference.
+His role in formulating the roadmap for Generation IV reactors and his leadership indicate that he would make a great speaker at the conference.\\
 
 \subsubsection{Rita Baranwal, DOE Nuclear Energy}
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{R}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{speaker-5.jpg}
+	\end{center}
+\end{wrapfigure}
 Dr.
@@
 Under her leadership, GAIN positively impacted over 120 companies.
-Baranwal is a clear choice of speaker to discuss the ways to improve nuclear legislation and how companies can rapidly develop new nuclear technology.
+Baranwal is a clear choice of speaker to discuss the ways to improve nuclear legislation and how companies can rapidly develop new nuclear technology.\\
 
 \subsubsection{Jim Conca, Forbes}
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{L}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{speaker-3.jpeg}
+	\end{center}
+\end{wrapfigure}
 Jim Conca has been a scientist in the field of the earth and environmental sciences for 33 years, specializing in geologic disposal of nuclear waste, energy-related research, planetary surface processes, radiobiology and shielding for space colonies, subsurface transport and environmental clean-up of heavy metals.
@@
 In addition to his experience and ambition, he is an excellent science communicator to scientists and non-scientists alike.
-Together, these factors make him an ideal speaker at the conference.
+Together, these factors make him an ideal speaker at the conference.\\
 
 \subsubsection{Brian Jurczyk, CEO Starfire Industries}
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{R}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{speaker-4.jpg}
+	\end{center}
+\end{wrapfigure}
 Brian holds a dual PhD/MBA degree with background in aerospace, nuclear, plasma and radiological engineering and technology commercialization.
@@
 In 2012-13, Brian received the Innovation Celebration "Entrepreneurial Excellence in Management Award," was named to Central Illinois Business' "40-under-40" and has served as Chairperson of the Champaign-Urbana CEO Roundtable.
-As a professional leader in plasma and radiological engineering, Jurczyk would be a great speaker to have at the conference on topics related to the future of plasma engineering and professional development.
+As a professional leader in plasma and radiological engineering, Jurczyk would be a great speaker to have at the conference on topics related to the future of plasma engineering and professional development.\\
 
 \subsubsection{Ross Radel, CEO Phoenix, LLC}
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{L}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{radel.png}
+	\end{center}
+\end{wrapfigure}
 Ross is the CEO and a Board of Directors member of Phoenix.
@@
 We believe Dr.
-Radel would be a great speaker for the future of nuclear technology.
+Radel would be a great speaker for the future of nuclear technology.\\
 
 \subsubsection{Greg Piefer, CEO SHINE}
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{R}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{piefer.jpg}
+	\end{center}
+\end{wrapfigure}
 Dr.
@@
 His passion is the growth of technology companies that take scientific advancement to commercialization, providing the opportunity to serve and better humanity.
-Piefer's goals are perfectly attuned to the goals of this conference and he would be an excellent speaker on the powerful applications of radiological engineering.
+Piefer's goals are perfectly attuned to the goals of this conference and he would be an excellent speaker on the powerful applications of radiological engineering.\\
 
@@
 Afterwards, students will be led to various noteworthy locations unique to UIUC.\\
+
+\input{socials}

### 2019-09-25 liability.tex
adds liability

\section{Liability}
In the process of hosting a conference, especially a student conference, great care must be placed in assuring the protection of all involved parties, particularly ANS National and the hosting university,  should a concern for liability arise. The following sections outline such cases.

\subsection{Hotels}
The Marriott, Hampton, Illini Union, and I Hotel are not responsible for lost, stolen, or damaged items. Damages to their premise will be charged to those responsible. These terms are to be agreed upon contractually on a guest by guest basis as rooms become occupied. Hotels are covered through their own insurance policies.

\subsection{Transportation}

\subsubsection{Peoria Charter}
Peoria Charter is registered with the United Motorcoach Association, International Motorcoach Group, US Department of Transportation, the cities of Champaign-Urbana, and is fully insured in the State of Illinois. They also hold a certificate of registration from the University of Illinois board. Peoria Charter assumes responsibility for the safety of their passengers.

\subsubsection{UIUC Carpool}
While using UIUC rental shuttles, employees of the University with valid driver’s license will be drivers. The State of Illinois Self-Insured Motor Vehicle Liability Plan provides liability coverage to full-time, part-time, and student employees or student trustees operating a University motor vehicle in the course of their employment and in accordance with State of Illinois and University policies and procedures. The State of Illinois may accept liability to others harmed by a University employee's negligence, but occupants of University motor vehicles are not provided any medical payments. Any personal property belonging to drivers and/or occupants is the responsibility of those individuals. Neither the University nor the State of Illinois provides any insurance coverage for personal property.

\subsubsection{CU-MTD}
Though CU-MTD is the recommended mode of transportation while on campus, they are not affiliated with the conference. They are, however, liable for the safety of their passengers.

\subsection{Dining}
University Catering, and Round Barn assume all liability regarding foodborne illness derived from their respective events.

\subsubsection{Round Barn}
A $\$200$ non-refundable deposit is required for all functions to hold a room, and is due upon reservation. Security/damage deposits will be refunded 7 days after a scheduled event.

A finalized menu is required at least two weeks prior to the function. An accurate estimate of attendance must be submitted to the Round Barn seven days prior to an event.
Seventy-two hours prior to an event, the Round Barn must receive a final guaranteed attendance figure. This is what will be charged if the event falls under the final guaranteed attendance figure. If the final guaranteed attendance fall is under 90$\%$ of the previous seven-day estimate, the client will be charged for the difference at the rate of one-half the original per person rate.

Prices are subject to change without notice; however, pricing stated on a signed contract will be honored. Due to insurance regulations, it is forbidden to carry out any food or beverage provided by the Banquet Centre.

Cancellations of any function are required ninety days prior to the function or a penalty will be incurred.

\subsection{Bank Account and Expenses}
ANS claims liability for unpaid expenses with primary banking orchestrated through ANS National. All receipts will be managed by the Financial Chair It is thus imperative to save expenditure receipts and review all contracts involving the exchange of money carefully as to avoid unexpected expenses.

\subsection{Release of Information}
Since personal information - such as credit card numbers, addresses, and contact information - is necessarily gathered during registration, it is imperative that any and all leaks be avoided. ANS claims liability for leaks of secure information. Such information provided by attendees to secondary services do not fall under the liability of the conference.

\subsection{Disabilities}
UIUC is proudly a fully ADA compliant university. As such, all events hosted on campus will be compliant with ADA regulations. There can be no guarantee regarding the compliance of off-campus establishments.

\subsection{Alcohol}
During conference hosted or sponsored events at which alcohol is being served, only those at or above the age of 21 years who can produce a valid ID will be served. Establishments licensed to serve alcohol are liable for ensuring the age of their customers. Catering services reserve the right to deny service to those who cannot produce a valid form of ID regarding the sale of alcohol. Special care will be taken at events serving alcohol to ensure safe consumption and avoid cases of illness due to over-consumption, and to ensure individuals deemed too drunk will no longer be served and can return to their rooms safely.
Patrons of Champaign-Urbana bars must be 19 years old to enter. It is the responsibility of those establishments to verify the age of their customers before serving alcohol. ANS does not assume liability for underage consumption of alcohol.

### 2019-09-25 management.tex
updates management and proglog

@@
 $\textbf{Hospitality and Catering Coordinator - Brady Moran}$\\
+Brady a freshman in the Nuclear, Plasma, and Radiological Engineering program in the Plasma concentration.
+He is looking forward to putting his time and efforts toward ANS events throughout his years at UIUC.
+Last year, Brady planned a large tasting event, the Taste of Sauk Valley, which boasted 550 attendees, $\$$15,000 in revenue, and required him to coordinate 12 restaurants and various subcommittees.
+He is confident that this experience will help him make the Student Conference a great success.
+He will be attending the 2020 conference at NC State.
 

### 2019-09-25 proglog.tex
updates management and proglog

@@
 
-\subsubsection{Brian Jurczyk, CEO Starfire Industries}
+\subsubsection{Phi Nguyen, Former Vice President and Director of Engineering at Intel}
 \setlength\intextsep{0pt}
@@
 		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{speaker-4.jpg}
+		\includegraphics[height=15\baselineskip]{nguyenp.png}
 	\end{center}
 \end{wrapfigure}
-Brian holds a dual PhD/MBA degree with background in aerospace, nuclear, plasma and radiological engineering and technology commercialization.
-As CEO, Brian works to find creative win-win solutions with commercial and industrial partners for particularly challenging applications - at all stages of value creation from basic IP development through early-stage manufacturing.
-In 2012-13, Brian received the Innovation Celebration "Entrepreneurial Excellence in Management Award," was named to Central Illinois Business' "40-under-40" and has served as Chairperson of the Champaign-Urbana CEO Roundtable.
-As a professional leader in plasma and radiological engineering, Jurczyk would be a great speaker to have at the conference on topics related to the future of plasma engineering and professional development.\\
+Phi Nguyen, is a UIUC alumni from the NPRE department and went on to a major leadership role at the Intel corporation.
+Smartphones, computers, and other technology that most Americans take for granted everyday would not be possible without innovations from companies like Intel.
+Plasma processing plays a significant role in the production of key components of these devices.
+As the former Director of Engineering at Intel, Phi Nguyen is the perfect person to talk about how this important research helps solve big problems.
+
+\subsubsection{William Magwood?}
 

### 2019-09-25 liability.tex
updates liability

@@
 \subsection{Hotels}
-The Marriott, Hampton, Illini Union, and I Hotel are not responsible for lost, stolen, or damaged items.
+The Illini Union and the Garden Hotel in Urbana (soon to be the Radisson) are not responsible for lost, stolen, or damaged items.
 Damages to their premise will be charged to those responsible.
@@
 \subsection{Dining}
-University Catering, and Round Barn assume all liability regarding foodborne illness derived from their respective events.
+University Catering, Round Barn, and the Garden Hotel in Urbana (soon to be the Radisson) assume all liability regarding foodborne illness derived from their respective events.
 

### 2019-09-25 banking.tex
updates management

\subsection{Banking}

In order to properly handle all of the conference expenses, two accounts will be used. One account will be with the national ANS headquarters, and the second will be a local checking account through Busey Bank. Our student section currently holds a checking account with Busey Bank and has developed a working relationship with them. Similar to previous conferences, the national ANS account will be the primary account due to their previous experience in handling conference funds and their 501(c)(3) tax exemption status. Although an account with the national ANS organization is currently not maintained by the UIUC local chapter, should this bid be selected, the opening of an account would happen almost immediately. An established local checking account with Busey Bank allows for convenience when using them as a secondary account. The student section account has been maintained for a number of years, allowing for adequate knowledge of Busey’s policies and a stable relationship to be established with the local branch. A new account would be opened, such that the student chapter funds and the conference funds are completely separate and require different oversight. This account will be used for small expenses that can occur during the conference. Although the ANS-managed account could be used for such purposes, the presence of a local branch allows for more flexibility if a purchase becomes time sensitive. Should the additional Busey Bank account be unobtainable, an account would be established with Chase instead. If ANS National desires to manage all funds, accommodations will be made to consolidate the funds.

\subsubsection{Financial Oversight}
Financial integrity must be maintained when providing a conference of this size. To do so, diligent oversight will be practiced for all transactions related to the conference. Expense requests will be required for all transactions. These requests must carefully outline the reason for the purchase and the total cost. If the purchase is reoccuring, automation will be required at the time of request. These requests will require the approval of both conference chairs in addition to the financial director. Only the conference chairs and the financial director will have authority, assuming the previously mentioned permission, to complete transactions on the Busey Bank account. To ensure transparency, the financial director will update a public record containing all transactions.

### 2019-09-25 budget.tex
updates management

\section{Budget}

\subsection{Revenue}

\subsection{Expenses}

\subsection{Sponsorship Plan}

\input{banking}

\subsection{Financial Contingency}

\subsection{Cost of Attendance and Student Reimbursement}
The cost of attending the student conference, per student, varies among schools and is highly dependent on distance from UIUC and the preferred mode of travel. We will assume that minimizing cost is a priority for schools, thus number of persons per hotel room is double the number of beds.

### 2019-09-25 liability.tex
updates management

@@
 \subsection{Dining}
-University Catering, Round Barn, and the Garden Hotel in Urbana (soon to be the Radisson) assume all liability regarding foodborne illness derived from their respective events.
-
-\subsubsection{Round Barn}
-A $\$200$ non-refundable deposit is required for all functions to hold a room, and is due upon reservation. Security/damage deposits will be refunded 7 days after a scheduled event.
-
-A finalized menu is required at least two weeks prior to the function. An accurate estimate of attendance must be submitted to the Round Barn seven days prior to an event.
-Seventy-two hours prior to an event, the Round Barn must receive a final guaranteed attendance figure.
-This is what will be charged if the event falls under the final guaranteed attendance figure.
-If the final guaranteed attendance fall is under 90$\%$ of the previous seven-day estimate, the client will be charged for the difference at the rate of one-half the original per person rate.
-
-Prices are subject to change without notice; however, pricing stated on a signed contract will be honored.
-Due to insurance regulations, it is forbidden to carry out any food or beverage provided by the Banquet Centre.
-
-Cancellations of any function are required ninety days prior to the function or a penalty will be incurred.
+University Catering and the Garden Hotel in Urbana (soon to be the Radisson) assume all liability regarding foodborne illness derived from their respective events.
 

### 2019-09-25 main.tex
adds milestones
adds hotel info and jeremy bio
added socials
moves socials to program logistics
updates management and proglog
updates management

@@
 \usepackage{graphicx}
+\usepackage{subcaption}
 \usepackage{wrapfig}
@@
 \usepackage{xcolor}
+\usepackage[parfill]{parskip}
 \usepackage{tabularx}
+\usepackage{longtable}
 \usepackage{gfsdidot} % Use the GFS Didot font: http://www.tug.dk/FontCatalogue/gfsdidot/
 \usepackage{microtype} % Improves typography
-
+\usepackage[toc,page]{appendix} % creates an appendix
 \usepackage{fancyhdr}
@@
 
-\tikzstyle{chair} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,thick, fill=blue!50, execute at begin node={\begin{varwidth}{3cm}},execute at end node={\end{varwidth}}]
-\tikzstyle{director} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=orange!70, execute at begin node={\begin{varwidth}{3cm}},execute at end node={\end{varwidth}}]
-\tikzstyle{coordinator} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=white!30, execute at begin node={\begin{varwidth}{3cm}},execute at end node={\end{varwidth}}]
-\tikzstyle{arrow} = [thick,->,>=stealth]
+\tikzstyle{chair} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,thick, fill=blue!50, execute at begin node={\begin{varwidth}{2.5cm}},execute at end node={\end{varwidth}}]
+\tikzstyle{director} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=orange!70, execute at begin node={\begin{varwidth}{2.5cm}},execute at end node={\end{varwidth}}]
+\tikzstyle{coordinator} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=white!30, execute at begin node={\begin{varwidth}{2.5cm}},execute at end node={\end{varwidth}}]
+% \tikzstyle{arrow} = [thick,--,>=stealth]
 
@@
 \newpage
+\input{website}
+\newpage
 \input{budget}
+\newpage
+\input{liability}
+\newpage
+% Appendices
+\appendix
+\input{conflict}
+\input{judging}
+\input{schedule}
+\input{building}
+\input{locations}
+\input{staffreq}
+\input{facultyletter}
+\input{petition}
 

### 2019-09-25 management.tex
updates management

@@
 % ===============================================
+% \begin{center}
+% 	\begin{tikzpicture}[
+% 		chair/.style={rectangle, text centered, draw,fill=blue!20, execute at begin node={\begin{varwidth}{9em}},
+%    		execute at end node={\end{varwidth}}},
+%    		committee/.style={rectangle,draw,fill=green!40, text centered, execute at begin node={\begin{varwidth}{7em}},
+%    		execute at end node={\end{varwidth}}},
+%    		coordinator/.style={rectangle,draw,fill=red!30, text centered, execute at begin node={\begin{varwidth}{7em}},
+%    		execute at end node={\end{varwidth}}},
+% 		grandchild/.style={grow=down,xshift=1em,anchor=west,
+% 		edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)}, execute at begin node={\begin{varwidth}{8em}},
+%    		execute at end node={\end{varwidth}}},
+% 		first/.style={level distance=12ex},
+% 		second/.style={level distance=24ex},
+% 		third/.style={level distance=36ex},
+% 		level 1/.style={sibling distance=11em}]
+% 	    % Parents
+% 	    \coordinate
+% 	      child[grow=left] {node[chair,anchor=east]{General Co-Chair \\ (Sam Dotson)}}
+% 	      child[grow=right] {node[chair,anchor=west]{Technical Co-Chair\\ (Jeremy Mettler)}}
+% 	      child[grow=down,level distance=3ex]
+% 	    [edge from parent fork down]
+% 	    % Children and grandchildren
+% 	    child{node[committee] {Non-Technical Subcommittee}
+% 	      child[grandchild,first] {node[chair]{Logistics Chair}}
+% 	      child[grandchild,second] {node[coordinator]{Hotels and Transportation}}
+% 	      child[grandchild,third] {node[coordinator] {Hospitality and Catering}}}
+% 	    child {node[committee] {Communications Subcommittee}
+% 	      child[grandchild, first] {node[chair] {Publications Chair}}
+% 	      child[grandchild, second] {node[coordinator]{Media}}
+% 	      child[grandchild, third] {node[coordinator] {Program}}}
+% 	    child{node[committee] {Financial Subcommittee}
+% 	      child[grandchild,first] {node[chair]{Financial Chair}}
+% 	      child[grandchild,second] {node[coordinator]{Registration}}
+% 	      child[grandchild,third] {node[coordinator]{Sponsorship}}}
+% 	    child {node[committee]{Technical Subcommittee}
+% 	      child[grandchild,first] {node[chair]{Sessions Chair}}
+% 	      child[grandchild,second] {node[coordinator]{Workshops}}
+% 	      child[grandchild,third] {node[coordinator]{Career Fair}}};
+% 	\end{tikzpicture}
+% \end{center}
 \begin{center}
-	\begin{tikzpicture}[
-		chair/.style={rectangle, text centered, draw,fill=blue!20, execute at begin node={\begin{varwidth}{9em}},
-   		execute at end node={\end{varwidth}}},
-   		committee/.style={rectangle,draw,fill=green!40, text centered, execute at begin node={\begin{varwidth}{7em}},
-   		execute at end node={\end{varwidth}}},
-   		coordinator/.style={rectangle,draw,fill=red!30, text centered, execute at begin node={\begin{varwidth}{7em}},
-   		execute at end node={\end{varwidth}}},
-		grandchild/.style={grow=down,xshift=1em,anchor=west,
-		edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)}, execute at begin node={\begin{varwidth}{8em}},
-   		execute at end node={\end{varwidth}}},
-		first/.style={level distance=12ex},
-		second/.style={level distance=24ex},
-		third/.style={level distance=36ex},
-		level 1/.style={sibling distance=11em}]
-	    % Parents
-	    \coordinate
-	      child[grow=left] {node[chair,anchor=east]{General Co-Chair \\ (Sam Dotson)}}
-	      child[grow=right] {node[chair,anchor=west]{Technical Co-Chair\\ (Jeremy Mettler)}}
-	      child[grow=down,level distance=3ex]
-	    [edge from parent fork down]
-	    % Children and grandchildren
-	    child{node[committee] {Non-Technical Subcommittee}
-	      child[grandchild,first] {node[chair]{Logistics Chair}}
-	      child[grandchild,second] {node[coordinator]{Hotels and Transportation}}
-	      child[grandchild,third] {node[coordinator] {Hospitality and Catering}}}
-	    child {node[committee] {Communications Subcommittee}
-	      child[grandchild, first] {node[chair] {Publications Chair}}
-	      child[grandchild, second] {node[coordinator]{Media}}
-	      child[grandchild, third] {node[coordinator] {Program}}}
-	    child{node[committee] {Financial Subcommittee}
-	      child[grandchild,first] {node[chair]{Financial Chair}}
-	      child[grandchild,second] {node[coordinator]{Registration}}
-	      child[grandchild,third] {node[coordinator]{Sponsorship}}}
-	    child {node[committee]{Technical Subcommittee}
-	      child[grandchild,first] {node[chair]{Sessions Chair}}
-	      child[grandchild,second] {node[coordinator]{Workshops}}
-	      child[grandchild,third] {node[coordinator]{Career Fair}}};
+	\begin{tikzpicture}
+		\node (gen chair) [chair] {General Co-Chair (Sam Dotson)};
+		\node (tech chair) [chair, right of = gen chair, xshift = 5cm] {Technical Co-Chair (Jeremy Mettler)};
+		\node (div chair) [chair, left of = gen chair, xshift = -5cm] {Diversity Co-Chair (Nate Reid)};
+
+		\node (log chair) [director, below of = gen chair, xshift = -2.5cm, yshift = -2cm] {Logistics Chair (Natalie Gaughan)};
+		\node (med coord) [coordinator, below of = gen chair, xshift = 1cm, yshift = -4cm] {Media Coordinator (Nathan Ryan)};
+		\node (prog coord) [coordinator, below of = log chair, yshift = -2cm] {Program Coordinator (Dilan K.)};
+		\node (hat coord) [coordinator, below of = prog coord, yshift = -2cm] {Hotels and Transport (Gavin Davis)};
+		\node (hoa coord) [coordinator, below of = hat coord, yshift = -2cm] {Hospitality and Accomodations (Brady Moran)};
+		\node (tours coord) [coordinator, below of = hoa coord, yshift = -2cm] {Tours Coordinator (Anna Balla)};
+
+		\node (tsc chair) [director, below of = tech chair, xshift = 2cm, yshift = -2cm] {Technical Sub-Committee Chair (Gwen Chee)};
+		\node (work coord) [coordinator, below of = tsc chair, yshift = -2cm] {Workshops Coordinator (Roberto Fairhurst)};
+		\node (sesh coord) [coordinator, below of = work coord, yshift = -2cm] {Sessions Coordinator (Zach Jeckell)};
+		\node (cf coord) [coordinator, below of = sesh coord, yshift = -2cm] {Career Fair Coordinator (Greg Golba)};
+
+		\node (fin chair) [director, below of = tech chair, xshift = -2cm, yshift = -2cm] {Financial Chair (Jack Stahl)};
+		\node (spon coord) [coordinator, below of = fin chair, yshift = -2cm] {Sponsorships Coordinator (Jimmy Shehee)};
+		\node (reg coord) [coordinator, below of = spon coord, yshift = -2cm] {Registration Coordinator (Jasmine Dinari)};
+
+		\draw  (gen chair) -- (tech chair);
+		\draw  (gen chair) -- (div chair);
+		\draw  (gen chair) -- (log chair);
+		\draw  (log chair) -- (prog coord);
+		\draw  (prog coord) -- (hat coord);
+		\draw  (hat coord) -- (hoa coord);
+		\draw  (hoa coord) -- (tours coord);
+		\draw  (gen chair) -- (med coord);
+		\draw  (tech chair) -- (fin chair);
+		\draw  (gen chair) -- (fin chair);
+		\draw  (tech chair) -- (tsc chair);
+		\draw  (fin chair) -- (spon coord);
+		\draw  (spon coord) -- (reg coord);
+		\draw  (tsc chair) -- (work coord);
+		\draw  (work coord) -- (sesh coord);
+		\draw  (sesh coord) -- (cf coord);
+		\draw  (div chair) -- (log chair);
+
 	\end{tikzpicture}
 \end{center}
+
 % ===============================================
@@
 The three co-chairs are responsible for setting up major milestones and 
-ensuring that those milestones are met. Together they oversee all three subcommittees but 
-are each primarily in charge of one. They will serve as the primary contacts between subcommittee
-chairs and the faculty as well as professionals. The co-chairs have the final word on all 
-conference decisions. They serve as the face of the conference and
+ensuring that those milestones are met.
+Together they oversee all three subcommittees.
+They will serve as the primary contacts between subcommittee chairs and the faculty as well as professionals.
+The co-chairs have the final word on all conference decisions.
+They serve as the faces of the conference.
 
@@
 	Technical Subcommittee. Works with the General Co-Chair to plan full committee meetings and completes any remaining tasks to ensure that milestones are met.
-	\item $\large\textbf{\textit{Financial Co-Chair}}$\\
+	\item $\large\textbf{\textit{Diversity Co-Chair}}$\\
 	In addition to the responsibilities outlined above, the Financial Co-Chair primarily oversees the Financial Subcommittee.
@@
 	\begin{itemize}
-		\item[$\circ$] $\textbf{Account Coordinator}$\\
+		\item[$\circ$] $\textbf{Financial Chair}$\\
 		Manages the ANS Planning Committee account with Busey Bank and ANS National.

### 2019-09-25 management.tex
adds diversity chair

@@
 \section{Conference Management}
+
+The Conference Planning Committee is separated into three categories: Co-Chairs, Directors, Coordinators.
+The three co-chairs are responsible for setting up major milestones and ensuring that those milestones are met.
+Together they oversee all three subcommittees.
+They will serve as the primary contacts between subcommittee chairs and the faculty as well as professionals.
+The co-chairs have the final word on all conference decisions.
+They serve as the faces of the conference.
+In this proposal we have decided to add a novel Co-Chair position: Diversity Co-Chair.
+This addition reflects our goal of celebrating the people behind the science and make this conference experience accessible to as many people as possible.
+The Directors are in charge of specialized subcommittees and are responsible for making decisions in those areas.
+They must communicate with their subcommittees and with other directors to make sure there are no conflicting decisions.
+The coordinators work in an even more specialized area and help the directors by handling a single task.
 
@@
 \subsection{Position Responsibilities}
-The three co-chairs are responsible for setting up major milestones and 
-ensuring that those milestones are met.
-Together they oversee all three subcommittees.
-They will serve as the primary contacts between subcommittee chairs and the faculty as well as professionals.
-The co-chairs have the final word on all conference decisions.
-They serve as the faces of the conference.
 
@@
 	\item $\large\textbf{\textit{General Co-Chair}}$\\
-	In addition to the responsibilities outlined above, the General Co-Chair primarily oversees the
-	Non-technical Subcommittee and the Media Coordinator. He works with the Technical Co-Chair to plan full committee
-	meetings and completes any remaining tasks to ensure that milestones are met.
+	In addition to the responsibilities outlined above, the General Co-Chair oversees the
+	Non-technical Subcommittee, the Media Coordinator, and the Financial Subcommittee. He works with the Technical Co-Chair in talking to sponsors, companies, and planning full committee meetings. 
 	\item $\large\textbf{\textit{Technical Co-Chair}}$\\
@@
 	\item $\large\textbf{\textit{Diversity Co-Chair}}$\\
-	In addition to the responsibilities outlined above, the Financial Co-Chair primarily oversees the Financial Subcommittee.
-The Financial Co-Chair is also responsible for interacting with businesses, the university, and ANS National for sponsorship needs.
-He completes any remaining tasks to ensure that milestones are met.
+	In addition to the responsibilities outlined above, the Diversity Co-Chair is responsible for making sure the conference is as inclusive, diverse, and accessible as possible.
+This includes: contacting minority serving institutions to encourage their students to attend the conference, ensuring socials and dinners are accessible, verifies that the final list of speakers has adequate representation, and more.
+We believe the example set by UIUC will make this role a staple of future conferences.
 

### 2019-09-25 conflog.tex

@@
 	\centering
-	\includegraphics[width=0.6\textwidth]{beckman.jpg}
+	\includegraphics[width=0.8\textwidth]{beckman.jpg}
 	\caption{Beckman Institute}
@@
 
-\subsection{Hotels and Accomodations}
-We are fortunate to have our primary hotel, the Union, be the same as our primary conference venue.
-While the Union has many rooms available it does not have enough capacity to hold every attendee of the conference.
-Thus, we have listed two hotels that are on campus and can house the majority of attendees plus a third hotel where professionals and overflow attendees can stay.
+\subsection{Hotels and Accommodations}
+
+$\textbf{The Garden Hotel Urbana}$\\
+When selecting the primary hotel to accommodate students we considered the ability to host all students under one roof over proximity to the conference activities.
+The Garden Hotel Urbana (soon to be the Radisson) will be the primary hotel for all attendees.
+Since this hotel is just beyond walking distance from the main conference activities, regular transportation to and from the Union will be provided during peak commuting hours (8am-10am $\&$ 3pm-5pm).
+Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 8am to 6pm.
+This will also be the location of the opening ceremony dinner.\\
 
 $\textbf{Illini Union}$\\
-This is the primary hotel for all student attendees and invited speakers.Commuting to the conference will be as easy as taking the elevator downstairs because the Illini Union is where the primary conference activities will be held.
+This is the primary hotel for invited speakers and panelists.
+Commuting to the conference will be as easy as taking the elevator downstairs because the Illini Union is where the primary conference activities will be held.
 The Union is also a five-minute walk from Green Street, the campus hub of dining and social activities.
@@
 $\textbf{Marriott TowneSuites}$\\
-Rooms at the Marriott resemble a studio apartment with an open floor plan, refrigerator, stove, microwave, dishes, and dining area.
+In the event that attendance exceeds 600 people, we will have overflow rooms in the Marriott TowneSuites.
+Rooms at the Marriott resemble a studio apartment with an open floor plan, refrigerator, stove, microwave,dishes, and dining area.
 Many rooms are equipped with pull-out couches, allowing 5 students to share a queen double room if desired.
@@
 The hotel is located on Green Street and the Illini Union a mere five-minute walk away.
-For $\$$7 a day, guests may park in a parking garage with 8ft clearance.
-
-% \begin{figure}[H]
-% \centering
-% \begin{subfigure}{0.5\linewidth}
-% 	\includegraphics[width=0.4\textwidth]{marriott_room1.jpeg}		
-% \end{subfigure}
-% \end{figure}
+For $\$7$ a day, guests may park in a parking garage with 8ft clearance.\\
 \begin{figure}[H]
 	\centering
-	\begin{subfigure}[b]{0.5\linewidth}
+	\begin{subfigure}{0.5\textwidth}
 		\centering
-		\includegraphics[width=0.5\textwidth]{marriott_room1.jpeg}
-		\caption{Marriott queen double}
+		\includegraphics[width=0.9\linewidth]{marriott_room1.jpeg}
+	\end{subfigure}%
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{marriott_room2.jpeg}
 	\end{subfigure}
-	\begin{subfigure}[b]{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.5\textwidth]{marriott_room2.jpeg}
-		\caption{Marriott king single}
-	\end{subfigure}
+	\caption{Marriott Rooms: Left, a queen double. Right, a king single}		
 \end{figure}
 
-$\textbf{Hyatt}$\\
-The Hyatt is a gorgeous hotel located in the heart of downtown Champaign, surrounded by local restaurants and vibrant a nightlife.
-It is just a short busride away from the main conference activities.
-Parking is also available for added accessibility.
-This is a great place for professionals to stay and enjoy.
-Wifi is included with every room.
-Joining the Hyatt rewards program is free and comes with the added benefit of free breakfast every morning.
+UIUC is one of most well represented schools at past student conferences.
+Students from UIUC will be able to stay in their respective dorms and apartments to maximize the number of hotel rooms available to out of town guests.
+
+\begin{tabular}{cccccc}
+\hline\hline
+Hotel & Distance from the Union (mi) & Dates & Number of Rooms & Rates & Per Person\\
+\hline\hline
+Garden Urbana & 2.2  & 4/8-4/11 & 198 & 119 & $\$$29.75\\
+Illini Union & 0.0 & 4/8-4/11 & 35 & 134 & $\$$33.5\\
+\end{tabular}
 

### 2019-09-25 socials.tex
fixes quotation marks

@@
-\section*{Socials}
+\subsection{Socials}
 
-\subsection*{Illini Union Rec Room Lockout}
+\subsubsection{Illini Union Rec Room Lockout}
 The Illini Union Rec Room is located in the basement of the Union building.
@@
 
-\subsection*{77 Club at Memorial Stadium}
+\subsubsection{77 Club at Memorial Stadium}
 Memorial Stadium is not only home to the Fighting Illini football team, but also to exquisite event space overlooking Zuppke Field.
-The sixth level of Memorial Stadium is home of the magnificent 77 Club, which honors Illini great, the "Galloping Ghost" Red Grange.
+The sixth level of Memorial Stadium is home of the magnificent 77 Club, which honors Illini great, the ``Galloping Ghost'' Red Grange.
 This 5,020 square foot space is located midfield and features an outdoor patio area overlooking the city of Champaign, for a combined total space of 9,740 square feet.
@@
 
-\subsection*{Pour Bros. Taproom in Downtown Champaign}
+\subsubsection{Pour Bros. Taproom in Downtown Champaign}
 Welcome to Illinois' first pour-your-own taprooms.
@@
 
-\subsection*{Under 21 Social: University of Illinois Ice Arena}
+\subsubsection{Under 21 Social: University of Illinois Ice Arena}
 For students under the drinking age that cannot attend the Pour Bros.

### 2019-09-25 website.tex

\section{Website and Social Media}
\subsection{Website}
Shortly after the host is announced, ANS-UIUC will purchase a domain name and create a website in conjunction with ANS National. The website will be hosted using GitHub pages, a free hosting service for static websites. Since there is no cost, the website can be hosted indefinitely. This webhost was selected because several members of the chapter possess knowledge and experience in using it for serving collaborative, Jekyll-based, and static HTML websites. The domain name can be purchased for as little as one dollar for the first year, and a little less than $\$20$ to maintain annually. If we need to cut costs or decide that a domain name ending in ".github.io" is fine we can drop the purchased domain name. The website will include important dates, costs, calendars, schedules, maps, emergency contact information, as well as a direct link to the paper submission site for the conference. The mobile web app will store downloaded maps, emergency contact information, and calendars for offline use while providing access to all features of the website as well.

\subsection{Social Media}

### 2019-09-26 budget.tex
sync

@@
 \subsection{Revenue}
+Registration costs for the NC State Student Conference will be \$40 per student and \$250 per professional.
+With an anticipated attendance, we are expecting \$36,750.
+Sponsorship funds are estimated at \$182,250.
+This number does not take into account money typically provided by ANS National Divisions & Regional Sections.
+The ANS National provides seed monies that are to be reimbursed.
+
+Registration costs at the VCU conference will be \$35 per student and \$250 per professional.
+With our anticipated attendance, we are expecting \$40,750.
+We are estimating \$187,500 in sponsorship funds bringing our total revenue to \$228,250.
+This number does not take into account the money typically provided by ANS Sections and through the ANS National Seed money.
+We believe with our proximity to so many large nuclear companies, this sponsorship will be achieved.
+
+Complete sponsorship data from the 2014 and 2016 conferences was provided by the Penn State and Wisconsin Conference Co-Chairs.
+Overall sponsorship figures from 2015 were provided by the Texas A&M conference leadership.
+Each set of data was carefully analyzed by our sponsorship team in order to develop a reasonable sponsorship projection.
+As shown, we expect a total of 56 waived professional registrations.
+This correlates to the number of waived fees given in our expected tier sponsorship figures and also factors in discounts to speakers, panelists, and workshop instructors.
+
+Taking into account the revenues of past student conferences, we have estimated our sponsorship revenue to amount to \$175,500.
+Additionally, we have chosen to set our registration fees at \$35 for students and \$250 for professionals.
+Therefore, we expect \$53,250 from registration.
+In total, our revenue is expected to be \$228,750 which we believe is reasonable and conservative in light of past revenues.
+In addition, our estimates provide a difference with our expected expenditures.
+In this way, we are less likely to have to cut things from the budget or raise registration fees if our sponsorship goals are not met.
+-By setting the highest sponsorship level to be \$20,000 which is lower than in the past, we hope to attract three top sponsors to name the three conference dinners.
+This causes our overall revenue to be at a reasonable medium between Penn State and Texas A&M’s.
+-Lunch & learns have become very popular.
+Through advice from past chairs, we are requiring at least a \$10,000 contribution to host a lunch & learn so that we might attract more funding.
+Therefore, we anticipate that this might encourage otherwise \$5,000 or \$7,500 level sponsors to be \$10,000 sponsors.
+We hope to have more \$10,000 sponsors but then perhaps fewer \$5,000 sponsors.
+-ANS Divisions tend to donate \$1,000 to \$2,500.
+
+Matching this year’s conference at Texas A&M, early member registration fees at the UW-Madison conference will be \$35 per student and \$250 per professional.
+With a projected attendance of 500 students and 150 professionals, revenue from registration is projected to total \$55,000.
 
@@
 \subsection{Sponsorship Plan}
+The full cost of the conference will be covered through sponsorships from various entities.
+We will first reach out to local nuclear industries in North Carolina such as GE Hitachi in Wilmington (headquarters of their nuclear division), Duke Energy in Charlotte (headquarters) and Westinghouse Electric Company, to name a few.
+Next, companies that helped sponsor past ANS Conferences would be contacted in hopes of acquiring their continued support.
+And finally, we will seek sponsorship from the ANS itself and the NC State Engineering Department.
+To encourage large donations, we have set up different sponsorship packages.
+
+We plan to offer a variety of different sponsorship options that provide several levels of conference visibility.
+Through these incentives, sponsoring companies and organizations will be exposed to arguably the highest concentration of young talent available in the nuclear field.
+Our highest tier sponsors will get the most conference visibility by selecting one of our Elite Packages.
+These packages include the \$5000 Ally Package, the \$10,000 Advocate Package, the \$15,000 Leader Package, and lastly, the \$20,000 Champion Package.
+Incentives for each are outlined on the following page.
+In addition to Elite Packages, we’re offering three separate exhibitor packages.
+In this approach, we are offering a little something extra at each level.
+For those who are only interested in participating in the Career Fair, we have our Career Fair Basic package.
+For only \$1000 dollars more, sponsors will be provided additional incentives on top of hosting a career fair table.
+Lastly, we offer the Exhibitor Premier packages.
+With a limited availability, the Exhibitor Premier package offers the large additional incentive of hosting either the Friday or Saturday Lunch & Learns.
+Sponsors selecting this package will be interested to know that we are planning these Lunch & Learns in such a way we feel will maximize the number of attendees.
+This is done by creating little overlap between other conference activities and creating dining arrangements that make it most convenient for attendees to enter the Grand Ball Room where the Lunch & Learns are set to take place.
+For those who would like to contribute at any level below the exhibitor package levels, we have our Friends of Nuclear Contributor package.
+Any ANS Division who is a Friends of Nuclear Contributor will be offered two tables at the Divisions of ANS Policy Dinner.
+
+Upon the announcement that the 2016 ANS student conference is to be held in Madison, we will look towards meeting our revenue expectations through fundraising.
+Our first action will be to contact industry partners who have consistently supported past ANS conferences and our own ANS student section.
+Letters will be made detailing the conference’s plan and the great opportunity they have to get involved.
+Financial contributions will receive different incentives based on donation amount, detailed in Section 5.2.3.
+Two sources of support we already anticipate are from both the UW College of Engineering and the Engineering Physics department.
+We have spoken with one of the College of Engineering Deans and the Department Chair about our vision for the conference and their role in making this a reality.
+Beyond their written support (shown in Appendix G) they each are willing to sponsor at least \$2,000 towards the conference.
+In addition, the EP department is willing to help us reach out to our extensive alumni network for financial support of this conference.
+Conversations with previous conference hosts indicated the ANS divisions as another consistent source of support.
+Individual divisions give smaller donations, but as a whole they have consistently given \$36,000 in total to student conferences in recent years.
+As such, their contributions will also be recognized in our program and in lists of conference sponsors.
+In the past, local businesses have provided financial or other types of support for ANS student conferences.
+We will attempt to continue this trend and contact restaurants, for donations, either monetary or in the form of conference discounts.
+Due to the uncertain nature of these contributions, we have chosen to be safe and not include them in our revenue estimates.
 

### 2019-09-27 conflict.tex
add conflict calendars

\section{Appendix: Conflict Calendar}

\begin{figure}[H]
	\centering
	\textbf{March 2021}\par\medskip
	\includegraphics[width=\textwidth, height=9cm]{march-conflict.png}
	\caption{Potential Date Conflicts in March 2021}
\end{figure}

\vspace{1cm}

\begin{figure}[H]
	\centering
	\textbf{April 2021}\par\medskip
	\includegraphics[width=\textwidth, height=9cm]{april-conflict.png}
	\caption{Potential Date Conflicts in April 2021}
\end{figure}

### 2019-09-27 conflog.tex
adds air travel costs

@@
 
+\begin{center}
+   \begin{tabular}{lccc}
+    School & Departure City & O'Hare (ORD) &Willard (CMI) \\
+    \hline
+    University of California - Berkeley & San Francisco (SFO) & $\$$338 & $\$$436 \\
+    University of California - Irvine&Orange County (SNA)&$\$$394&$\$$436\\
+    Colorado School of Mines & Denver (DEN) & $\$$222 & $\$$328 \\
+    Three Rivers Community College & Hartford (BDL) & $\$$468 & $\$$327 \\ 
+    University of Florida & Gainesville (GNV)& $\$$377 & $\$$416 \\
+    Georgia Institute of Technology & Atlanta (ATL)& $\$$199 & $\$$291 \\
+    Southern Polytechnic State University & Atlanta (ATL) & $\$$199 & $\$$291 \\
+    Idaho State University & Idaho Falls (IDA) & $\$$501 & NA \\
+    Kansas State University & Manhattan (MHK) & $\$$336 & $\$$406 \\ 
+    Louisiana State University & Baton Roughe (BTR) & $\$$380 & $\$$329 \\
+    United States Naval Academy & Hanover (BWI) & $\$$210 & $\$$321 \\  
+    University of Maryland & Hanover (BWI)&$\$$210 &$\$$321 \\ 
+    Massachusetts Institute of Technology & Boston (BOS)&$\$$191 &$\$$325 \\ 
+    University of Massachusetts - Lowell &Boston (BOS) &$\$$191 &$\$$325 \\
+    University of Nevada - Las Vegas & Las Vegas (LAS)& $\$$262 &$\$$358 \\ 
+    University of New Mexico &Albuquerque (ABQ) &$\$$439 &$\$$358 \\ 
+    City College of New York &$\$$New York (JFK) &$\$$245 &$\$$325 \\
+    Excelsior College & Albany (ALB) &$\$$444 &$\$$327 \\ 
+    Rensselaer Polytechnic Institute & Albany (ALB)&$\$$444 &$\$$327 \\ 
+    United States Military Academy at West Point&New Windsor (SWF)&$\$$273 &$\$$357 \\ 
+    North Carolina State University &Morrisville (RDU) &$\$$180 &$\$$321 \\
+    Oregon State University &Portland (PDX) &$\$$314 &$\$$436 \\ 
+    Pennsylvania State University & Harrisburg (MDT)&$\$$397 & $\$$323 \\
+    University of Pittsburgh &Pittsburgh (PIT) &$\$$282 &$\$$293 \\ 
+    Clemson University&Greenville (GSP)&$\$$356&$\$$287\\
+    South Carolina State University&Columbia (CAE)&$\$$407 &$\$$564 \\ 
+    University of South Carolina&Columbia (CAE)&$\$$407&$\$$564\\
+    Chattanooga State Comunity College&Chattanooga (CHA)&$\$$334&$\$$316\\
+    University of Tennessee&Knoxville (TYS)&$\$$340&$\$$291\\
+    Texas A\&M University&College Station (CLL)&$\$$367&$\$$243\\
+    University of Texas - Arlington&Dallas (DFW)&$\$$197&$\$$303\\
+    University of Texas - Austin&Austin (AUS)&$\$$298&$\$$358\\
+    University of Texas - Permian Basin&Midland (MAF)&$\$$434&$\$$333\\
+    Utah State University&Salt Lake City (SLC)&$\$$298&$\$$358\\
+    University of Utah&Salt Lake City (SLC)&$\$$298&$\$$358\\
+    Virginia Commonwealth University&Richmond (RIC)&$\$$279&$\$$321\\
+    University of Washington&Seattle (SEA)&$\$$253&$\$$436\\
+    \hline
+    Average Lowest Cost for Air Travel&$\$$293&&
+
+    \end{tabular}
+
 Due to the central location of UIUC, driving might be a good option for some schools and individuals. Below are the approximate driving times from several universities. 

### 2019-09-27 uiuc.tex
updates section title
updates uiuc

@@
-\section{East-central Illinois: The cities of Champaign and Urbana}
+\section{Welcome to Illinois}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=\textwidth]{illinois-main.jpeg}
+\end{figure}
 
@@
 
-Champaign-Urbana (CU), known colloquially as Chambana, is home to the state's flagship campus the University of Illinois at Urbana-Champaign (UIUC).
-Since its founding in the mid 19th century, it has grown into the flourishing cultural hub of the midwest that it is today.
+Champaign-Urbana (CU), colloquially known as Chambana, is home to the state's flagship school, the University of Illinois at Urbana-Champaign (UIUC).
+Since its founding in the mid 19th century CU has grown into the flourishing cultural hub of the midwest it is today.
 CU houses many landmarks and districts and showcases both local and national events annually.
-It is home to the Historic Virginia Theater, host of Ebertfest in honor of the late film critic and UIUC alumnus Roger Ebert.
+It is home to the Historic Virginia Theater that hosts Ebertfest in honor of the late film critic and UIUC alumnus Roger Ebert.
 The Krannert Center for the Performing Arts is located on U of I campus, which is known for its four first-class venues, including the Foellinger Great Hall - one of the most acoustically perfect performance spaces in the world, attracting world famous artists and ensembles to perform there every year.
 Other notable events that attract many people to the twin cities are the Pygmalion Music Festival, the Urbana Sweetcorn Festival, and the Illini Marathon.
+
+\begin{wrapfigure}{r}{0.35\textwidth}
+  \begin{center}
+  \vspace{-\baselineskip}
+    \includegraphics[width=0.33\textwidth]{chm1.png}
+  \end{center}
+\end{wrapfigure}
 
@@
 Illinois relies heavily on nuclear power to supply its energy needs with 52$\%$ of electricity generated by nuclear plants.
+The first human controlled nuclear reaction, Chicago Pile One, happened in Illinois.
 UIUC also bears a long tradition of nuclear power research and was home to the TRIGA nuclear reactor for almost 40 years.
@@
 Now, UIUC is exploring ways to use nuclear power to accelerate its decarbonization efforts.
-We hope to continue the nuclear tradition by hosting the ANS Student Conference in 2021.
+This exploratory effort has the potential to position UIUC as the world leader in advanced carbon-free technologies.
+We hope to continue our excellent nuclear tradition by hosting the ANS Student Conference in 2021.
+\clearpage
 
-\subsubsection{Accessibility}
-Myriad festivals and sporting events on campus draw many people to Champaign-Urbana at varying times of the year, which means hotels are not hard to find.
+\subsubsection{Accessibility and Accomodation}
+Myriad festivals and sporting events on campus draw many people to Champaign-Urbana at various of the year, which means hotels are not hard to find.
 A large number of these hotels are located around downtown Champaign and the Eastern side of campus, making transportation easy.
-There is also a small airport, Willard Airport, just 20 minutes from campus that regularly has flights to and from the Chicago O’Hare and Dallas Ft Worth airports.
-Finally, there are several reliable bus services that make frequent trips from Champaign-Urbana to O’Hare and the Chicagoland area.
+Champaign-Urbana Mass Transit (CU-MTD) is a reliable public transportation service that sees millions of rides every year.
+All CU-MTD busses are wheelchair accessible.
+There is also a small airport, Willard Airport, just 20 minutes from campus that has regular flights to and from Chicago O’Hare and Dallas Fort Worth airports.
+Finally, Peoria Charter is a popular bus service with several daily trips between the UIUC campus and the Chicagoland area.
 
@@
 Founded in 1867, the University of Illinois at Urbana-Champaign (UIUC) has cultivated a long history of significant scientific discoveries and contributions.
-The theory of superconductivity, the invention of the transistor, the discovery of archaea, the fourth domain of life, and the first web browser are just some of the many breakthroughs from UIUC.
-Established in 1876, the famous Morrow Plots became the first research crop field at a university and is still used today.
-Attendees will also be familiar with Blue Waters, one of the world’s fastest supercomputers.
+The theory of superconductivity, the invention of the transistor, the discovery of archaea, the fourth domain of life, and the first web browser are just some of the many breakthroughs that came out of UIUC.
+The famous Morrow Plots, established in 1876, became the first research crop field at a university and is still used today.
+Attendees might also be familiar with Blue Waters, one of the world’s fastest supercomputers.
 The UIUC Grainger College of Engineering has had sixteen Nobel Laureates in physics.
@@
 Overall, the College of Engineering in Urbana-Champaign ranks sixth among the nation’s best undergraduate engineering programs.
-With more than 250 degrees for undergraduates and graduates and a multitude of first-class research facilities and resource, UIUC gives its 45,000 students the ability to succeed.\\
-Today, the University of Illinois at Urbana-Champaign attracts visitors from throughout the state by offering a variety of valuable public attractions.
-UIUC maintains four public museums: the Spurlock Museum, containing 54,000 cultural artifacts from around the world; the Illinois Natural History Survey, has more than 9.5 million biologic specimens in its collection; the Sousa Archives and Center for American Music, provides shows and education to students and the public; and the Krannert Art Museum, offers fine arts and education.
-More than 470,000 square feet of recreational space is occupied by other facilities including an ice arena, climbing wall, swimming pools, parks, sports fields, parks, and outdoor adventure venues.
+With more than 250 degrees for undergraduates and graduates and a multitude of first-class research facilities and resource, UIUC gives its 45,000 students the ability to succeed.
 
@@
 It also engages in education and outreach programs to teach members of the surrounding community about nuclear science.
+One of our most popular outreach programs is Engineering Open House (EOH), during which ANS won best exhibit.
+EOH is an annual event where members of the local community, from young children to senior adults, visit the engineering campus to learn more about STEM research.
+
+\begin{wrapfigure}{l}{0.5\textwidth}
+  \begin{center}
+  \vspace{-\baselineskip}
+    \includegraphics[width=0.48\textwidth]{eoh1.JPG}
+    \caption{Mouse Trap Chain Reaction at EOH 2019}
+  \end{center}
+\end{wrapfigure}
+
 Membership is currently around 70-80 students and has been steadily growing.
 The chapter works to host events catering to nuclear, plasma, and radiological concentrations.
-It also makes professional development a large part of member involvement.
+Professional development plays a crucial role in student development, and it is the biggest part of member involvement at UIUC.
+Events range from tours of various facilities to pizza with campus visitors.
+Some of the past tours have included Clinton Power Station, Oak Ridge National Laboratory, Analysis System (ANSYS) Inc, and Argonne National Laboratory.
 ANS-UIUC has historically been one of the best represented institutions at the annual student conference and is a tradition this chapter is eager to uphold.
 
-% Group picture from the 2019 kick off barbeque.
+\clearpage
+
 \begin{figure}[H]
   \centering
-	\includegraphics[width=9cm]{ans_uiuc_group.jpg}
-	\caption{Members of ANS-UIUC at the 2019 Kick Off Barbeque.}
-\end{figure}
-
-% Picture of attendees to the 2019 ANS Student Conference
-\begin{figure}[H]
+  \begin{subfigure}{0.5\textwidth}
     \centering
-	\includegraphics[width=9cm]{ans_conf_19.jpg}
-	\caption{Members of ANS-UIUC at the 2019 Student Conference at VCU.}
+    \includegraphics[width=8cm]{ans_uiuc_group.jpg}
+    \subcaption{ANS Barbeque 2019}
+  \end{subfigure}%
+  \begin{subfigure}{0.5\textwidth}
+    \centering
+    \includegraphics[width=8cm]{ans_conf_19.jpg}
+    \subcaption{ANS Student Conference 2019 at VCU}
+  \end{subfigure}   
 \end{figure}
@@
 \subsubsection{Plasma Physics and Fusion Science}
+\begin{wrapfigure}{r}{0.4\textwidth}
+  \begin{center}
+  \vspace{-\baselineskip}
+    \includegraphics[width=0.38\textwidth]{hidra.png}
+    \caption{HIDRA}
+  \end{center}
+\end{wrapfigure}
 The research theme of Fusion and Plasma Physics in the NPRE department has a long history of work in the area of magnetic and inertial nuclear fusion as well as plasma engineering.
@@
 The Hybrid Illinois Device for Research and Application (right) marks the newest addition to the team at CPMI.
-This device finished construction and achieved first plasma during the spring of 2016
+This device finished construction and achieved first plasma during the spring of 2016.
 

### 2019-09-27 conflog.tex
adds travel costs

--- 2019-09-25 conflog.tex
@@
 We believe either of these dates would serve as an appropriate first choice because they avoid major conflict dates like finals and spring break for most schools.
-Additionally, mid-April offers pleasant mild weather in Champaign.
+Additionally, mid-April offers pleasant, mild, weather in Champaign.
 The reason for proposing two weekends to host the conference is due to the UIUC tradition of hosting Mom's Weekend on or near the first weekend in April.
-The Illinois Mom's Association has not yet announced their 2021 dates but to avoid potential conflict, we suggest two dates.
+The Illinois Mom's Association has not yet announced their 2021 dates but, to avoid potential conflict, we suggest two dates.
 In the event that both of these dates are unavailable our backup date is
@@
 
-% \begin{figure}[h!]
-% 	\includegraphics[width=\textwidth]{illini-union.png}
-% 	\caption{Illini Student Union}
-% \end{figure}
+\begin{figure}[h]
+	\centering	
+	\includegraphics[scale=0.2]{illini-union.png}
+	\caption{Illini Student Union}
+\end{figure}
 
@@
 
-\begin{tabular}{cccccc}
+\begin{tabular}{lccccc}
 \hline\hline
-Hotel & Distance from the Union (mi) & Dates & Number of Rooms & Rates & Per Person\\
+\textbf{Hotel} & \textbf{Distance from the Union (mi)} & \textbf{Dates} & \textbf{Number of Rooms} & \textbf{Rates*} & \textbf{Per Person**}\\
 \hline\hline
@@
 Illini Union & 0.0 & 4/8-4/11 & 35 & 134 & $\$$33.5\\
+Marriott TowneSuites &0.25 & 4/8-4/11 & 95 & 189 & \$47.50\\ 
 \end{tabular}
+\textbf{*}\textit{Price for a queen double}
+\textbf{**}\textit{Assumes 4 people per room}
 
@@
 Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip.
+
 \begin{center}
-	\begin{tabular}{lcc}
+   \begin{tabular}{lccc}
    	\hline\hline
-		\textbf{School} & \textbf{Departure City} & \textbf{Airfare to O'Hare (ORD)*}\\
+    \textbf{School} & \textbf{Departure City} & \textbf{O'Hare (ORD)*} & \textbf{Willard (CMI)} \\
     \hline\hline
-		University of Florida & Orlando (ORL) & $\$$ 236\\
-		Texas A$\&$M & College Station (CLL)& $\$$ 393\\
-		Penn State University & State College (SCE) & $\$$ 349\\
-		MIT & Boston (BOS) & $\$$ 217\\
-		UNLV & Las Vegas (LAS) & $\$$ 308\\
-		Georgia Tech & Atlanta (ATL) & $\$$ 175\\
-		University of Michigan & Detroit (DTW) & $\$$ 240\\
-		Oregon State University & Portland (PDX) & $\$$ 355\\
-		RPI & Albany (ALB) & $\$$ 504\\
-		UC Berkley & Oakland (OAK) & $\$$ 674\\
-		UC Irvine & Orange County (SNA) & $\$$ 439\\
-		US Naval Academy & Baltimore (BWI)& $\$$ 383\\
-		University of Marlyand & Baltimore (BWI) & $\$$ 383\\
-		University of Missouri-Columbia & St. Louis (STL) & $\$$ 168\\
-		University of Nevada & Reno (RNO) & $\$$ 374\\
-		University of New Mexico & Albuqurque (ABQ) & $\$$ 477\\
-		NC State  University & Raleigh (RDU) & $\$$ 195\\
-		University of Pittsburgh& Pittsburgh (PIT) & $\$$ 271\\
-		Clemson University & Greenville (GSP) & $\$$ 295\\
-		SC State University & Columbia (CAE) & $\$$ 365\\
-		University of South Carolina & Columbia (CAE) & $\$$ 365\\
-		Brigham Young University & Salt Lake City (SLC) & $\$$ 441\\
-		U. Wisconsin-Madison & Madison (MSN) & $\$$ 229\\
-		Colorado School of Mines & Denver (DEN)& $\$$ 223\\
-		University of  Tennessee-Knoxville & Knoxville (TYS) & $\$$ 279\\
-		Virginia Commonwealth University & Richmond (RIC) & $\$$ 326 \\
-		Iowa State University & Des Moines (DSM) & $\$$ 199 \\
-		University of Iowa & Cedar Rapids (CID) & $\$$ 249 \\
+    University of California - Berkeley & San Francisco (SFO) & $\$$338 & $\$$436 \\
+    University of California - Irvine&Orange County (SNA)&$\$$394&$\$$436\\
+    Colorado School of Mines & Denver (DEN) & $\$$222 & $\$$328 \\
+    Three Rivers Community College & Hartford (BDL) & $\$$468 & $\$$327 \\ 
+    University of Florida & Gainesville (GNV)& $\$$377 & $\$$416 \\
+    Georgia Institute of Technology & Atlanta (ATL)& $\$$199 & $\$$291 \\
+    Southern Polytechnic State University & Atlanta (ATL) & $\$$199 & $\$$291 \\
+    Idaho State University & Idaho Falls (IDA) & $\$$501 & NA \\
+    Kansas State University & Manhattan (MHK) & $\$$336 & $\$$406 \\ 
+    Louisiana State University & Baton Roughe (BTR) & $\$$380 & $\$$329 \\
+    United States Naval Academy & Hanover (BWI) & $\$$210 & $\$$321 \\  
+    University of Maryland & Hanover (BWI)&$\$$210 &$\$$321 \\ 
+    Massachusetts Institute of Technology & Boston (BOS)&$\$$191 &$\$$325 \\ 
+    University of Massachusetts - Lowell &Boston (BOS) &$\$$191 &$\$$325 \\
+    University of Nevada - Las Vegas & Las Vegas (LAS)& $\$$262 &$\$$358 \\ 
+    University of New Mexico &Albuquerque (ABQ) &$\$$439 &$\$$358 \\ 
+    City College of New York &$\$$New York (JFK) &$\$$245 &$\$$325 \\
+    Excelsior College & Albany (ALB) &$\$$444 &$\$$327 \\ 
+    Rensselaer Polytechnic Institute & Albany (ALB)&$\$$444 &$\$$327 \\ 
+    United States Military Academy at West Point&New Windsor (SWF)&$\$$273 &$\$$357 \\ 
+    North Carolina State University &Morrisville (RDU) &$\$$180 &$\$$321 \\
+    Oregon State University &Portland (PDX) &$\$$314 &$\$$436 \\ 
+    Pennsylvania State University & Harrisburg (MDT)&$\$$397 & $\$$323 \\
+    University of Pittsburgh &Pittsburgh (PIT) &$\$$282 &$\$$293 \\ 
+    Clemson University&Greenville (GSP)&$\$$356&$\$$287\\
+    South Carolina State University&Columbia (CAE)&$\$$407 &$\$$564 \\ 
+    University of South Carolina&Columbia (CAE)&$\$$407&$\$$564\\
+    Chattanooga State Comunity College&Chattanooga (CHA)&$\$$334&$\$$316\\
+    University of Tennessee&Knoxville (TYS)&$\$$340&$\$$291\\
+    Texas A\&M University&College Station (CLL)&$\$$367&$\$$243\\
+    University of Texas - Arlington&Dallas (DFW)&$\$$197&$\$$303\\
+    University of Texas - Austin&Austin (AUS)&$\$$298&$\$$358\\
+    University of Texas - Permian Basin&Midland (MAF)&$\$$434&$\$$333\\
+    Utah State University&Salt Lake City (SLC)&$\$$298&$\$$358\\
+    University of Utah&Salt Lake City (SLC)&$\$$298&$\$$358\\
+    Virginia Commonwealth University&Richmond (RIC)&$\$$279&$\$$321\\
+    University of Washington&Seattle (SEA)&$\$$253&$\$$436\\
+    \hline
+    Average Lowest Cost for Air Travel**&$\$$293&&
     \end{tabular} 
 \end{center}
-\textbf{*}\textit{These fares are predicted to go down around February and March.}\\
+\textbf{*}\textit{A \$61 round-trip bus ticket through Peoria Charter was added to the cost.}\\
+\textbf{**}\textit{The average of the lowest price between O'Hare and Willard.}\\
 

### 2019-09-27 conflog.tex
add driving costs

--- 2019-09-27 conflog.tex
@@
 
+\begin{center}
+   \begin{tabular}{lcccc}
+   \hline\hline
+   School&Estimated Mileage (mi)&Driving Time (hrs)&Estimated Fuel  Cost&Estimated Fuel Cost per Person\\
+   \hline\hline
+    Purdue University&90&1.68&\$21.86&\$5.47\\
+    University of Cincinnati&233&\$56.60&\$14.15\\
+    Air Force Institute of Technology&250&3.97&\$60.73&\$15.18\\
+    University of Wisconsin&253&4.00&\$61.46&\$15.36\\
+    Missouri University of Science and Technology&279&4.35&\$67.77&\$16.94\\
+    University of Missouri - Columbia&291&4.48&\$70.69&\$17.67\\
+    Ohio State University&302&4.77&\$73.36&\$18.34\\
+    University of Michigan&345&5.27&\$83.81&\$20.95\\
+    Vanderbilt University&373&5.57&\$90.61&\$22.65\\
+    Iowa State University&378&5.73&\$91.82&\$22.96\\
+    \hline
+    Average&279&4.36&\$67.87&\$16.97
+
+    \end{tabular} 
+\end{center}
+
 \subsubsection{Getting to the Conference}

### 2019-09-27 budget.tex
adds comment
Expense Table
Remove Command
updates budget table
Budget Cuts Table

--- 2019-09-25 budget.tex
@@
 \subsection{Expenses}
+\hspace{-4cm}
+  \begin{tabular}{clcrccccr}
+    \hline\hline
+     & \multicolumn{1}{c}{Priority} & \multicolumn{1}{c}{Priority} & \multicolumn{1}{c}{Cost Per Unit} & \multicolumn{1}{c}{Thursday} & \multicolumn{1}{c}{Friday} & \multicolumn{1}{c}{Saturday} & \multicolumn{1}{c}{General} & \multicolumn{1}{c}{Total Cost} \\ \hline\hline
+     \multirow{10}{*}{\STAB{\rotatebox[origin=c]{90}{Facilities}}}
+     & Technical Session AV      & I                         & $\$$ 13.80                & 1                         & 6                        & 6                         & -                         & $\$$179.40               \\
+     & Technical Session Rooms   & I                         & $\$$ 0.00                 & -                         &  -                       &  -                        &  1                        & $\$$0.00                 \\
+     & Panel AV                  & I                         & $\$$ 17.80                & -                         &   2                      &   2                       &   -                       & $\$$71.20                \\
+     & Panel Rooms               & I                         & $\$$ 0.00                 & -                         &    -                     &    -                      &    1                      & $\$$0.00                 \\
+     & Workshop AV               & I                         & $\$$ 17.80                & 2                         &     -                    &     -                     &     -                     & $\$$35.60                \\
+     & Workshop Rooms            & I                         & $\$$ 0.00                 &  -                        &      -                   &      -                    &      1                    & $\$$0.00                 \\
+     & Dinner Room (Ihotel)      & I                         & $\$$ 4,000.00             &   -                       &       -                  &       1                   &       -                   & $\$$4,000.00             \\
+     & Dinner AV (Ihotel)        & I                         & $\$$ 0.00                 &    -                      &        -                 &        1                  &        -                  & $\$$0.00                 \\
+     & Dinner Room (Garden Hotel)& I                         & $\$$ 4,000.00             &     1                     &         1                &         -                 &         -                 & $\$$8,000.00             \\
+     & Dinner AV (Garden Hotel)  & I                         & $\$$ 0.00                 &      1                    &          1               &          -                &          -                & $\$$0.00                 \\ \hline
+     &                           &                           &                           &                           &\multicolumn{3}{r}{Facilities Subtotal:}     & $\$$12,286.20            \\ \hline\hline
+     \multirow{5}{*}{\STAB{\rotatebox[origin=c]{90}{Transport}}}
+     & Shuttles From Hotel       & I                         & $\$$ 1,000.00             & 2                         & 2                        & 2                         & -                         & $\$$6,000.00             \\
+     & Ihotel Dinner             & I                         & $\$$ 875.00               & -                         &  -                       &  4                        &  -                        & $\$$3,500.00             \\
+     & Brewery/Starfire Tours    & II                        & $\$$ 875.00               & 1                         &   -                      &   -                       &   -                       & $\$$875.00               \\
+     & Clinton Tour              & II                        & $\$$ 875.00               & 1                         &    -                     &    -                      &    -                      & $\$$875.00               \\
+     & Argonne Tour              & II                        & $\$$ 875.00               & 1                         &     -                    &     -                     &     -                     & $\$$875.00               \\ \hline
+     &                           &                           &                           &                           &\multicolumn{3}{r}{Transport Subtotal:}      & $\$$12,125.00            \\ \hline\hline
+     \multirow{5}{*}{\STAB{\rotatebox[origin=c]{90}{Food}}}
+     & Coffee/Tea                & III                       & $\$$ 1.95                 & -                         & 600                      & 600                       & -                         & $\$$2,486.25             \\
+     & Garden Hotel Dinners*     & II                        & $\$$ 36.50                & 600                       & 600                      &  -                        &  -                        & $\$$46,537.50            \\
+     & Ihotel Dinner             & II                        & $\$$ 27.50                & -                         &   -                      &   600                     &   -                       & $\$$17,531.25            \\
+     & Dinner Cash Bars          & III                       & $\$$ 336.00               & 1                         &    1                     &    1                      &    -                      & $\$$1,071.00             \\
+     & SSC Lunches               & II                        & $\$$ 16.50                & -                         &     -                    &     150                   &     -                     & $\$$2,629.69             \\ \hline
+     &                           &                           &                           &                           &\multicolumn{3}{r}{Food Subtotal:}           & $\$$70,255.69            \\ \hline\hline
+     \multirow{5}{*}{\STAB{\rotatebox[origin=c]{90}{Socials}}}
+     & Ice Skating               & III                       & $\$$ 240.00               & 2                         & -                        & -                         & -                         & $\$$480.00               \\
+     & Illini Rec Room           & III                       & $\$$ 490.00               &  -                        & 2                        &  -                        &  -                        & $\$$982.00               \\
+     & Memorial Stadium Club 77  & III                       & $\$$ 2,000.00             & -                         &   -                      &   1                       &   -                       & $\$$2,000.00             \\
+     & Club 77 Tab               & IV                        & $\$$ 3,000.00             & -                         &    -                     &    1                      &    -                      & $\$$3,000.00             \\
+     & Guido's Tab               & IV                        & $\$$ 3,000.00             & -                         &     1                    &     -                     &     -                     & $\$$3,000.00             \\ \hline
+     &                           &                           &                           &                           &\multicolumn{3}{r}{Socials Subtotal:}        & $\$$9,462.00             \\ \hline\hline
+     \multirow{7}{*}{\STAB{\rotatebox[origin=c]{90}{Miscellaneous}}}
+     & Conference Programs       & I                         & $\$$ 2,133.90             & -                         & -                        & -                         & 1                         & $\$$2,133.90             \\
+     & Lanyards                  & I                         & $\$$ 2.54                 &  -                        & -                        &  -                        &  600                      & $\$$1,524.00             \\
+     & Award Certificates        & III                       & $\$$ 2.50                 & -                         &   -                      &   50                      &   -                       & $\$$125.00               \\
+     & Poster Session Prizes     & III                       & $\$$ 100.00               & -                         &    -                     &    3                      &    -                      & $\$$300.00               \\
+     & Swag                      & IV                        & $\$$ 10,000.00            & -                         &     -                    &     -                     &     1                     & $\$$10,000.00            \\
+     & Brewery Tour              & IV                        & $\$$ 5.00                 & 45                        &     -                    &     -                     &     -                     & $\$$275.00               \\
+     & Travel Reimbursements     & I                         & $\$$ 250.00               &  -                        &     -                    &                           &  450                      & $\$$112,500.00           \\ \hline
+     &                           &                           &                           &                           &\multicolumn{3}{r}{Miscellaneous Subtotal:}                                       & $\$$126,857.90           \\ \hline\hline
+     &                           &                           &                           &                           &                          &                           &                           &                          \\
+     &                           &                           &                           &                           &\multicolumn{3}{r}{Grand Total:}                                                  & $\$$230,984.79           \\
+     &                           &                           &                           &                           &                          &                           &                           &                          \\ \hline\hline
+  \end{tabular}
+    \begin{tabular}{lrrr}
+  \hline\hline
+  \multicolumn{1}{l}{Level of Cuts Made} & \multicolumn{1}{c}{Amount Saved} & \multicolumn{1}{c}{Grand Total} & \multicolumn{1}{c}{\% of Max Revenue} \\ \hline\hline 
+  Priority IV Cuts Made & $\$$9,346.00 & $\$$221,638.79 & ********** \\
+  III and IV Cuts Made & $\$$22,987.25 &$\$$207,997.54 & ********* \\
+  II, III, and IV Cuts Made & $\$$49,053.19 & $\$$181,931.60 & ********* \\
 
+  \end{tabular}
 \subsection{Sponsorship Plan}
@@
 We will assume that minimizing cost is a priority for schools, thus number of persons per hotel room is double the number of beds.
+
+% Jeremy's budget plan

### 2019-09-27 budget.tex
worked on budgetz

--- 2019-09-25 budget.tex
@@
 \subsection{Revenue}
+We have compared the predicted and actual revenues from previous reports and used these to estimate our expected revenue.
+To maintain reasonable accuracy in the budget, we were financially conservative in our estimates to account for fluctuating economy and attendance numbers.
+Should our bid be selected, these conservative estimates will result in a smoother planning and execution process.
+We have also accounted an estimated number of waived professional registration based on previous conferences.
+This  correlates to the number of waived fees given in our expected tier sponsorship figures and also factors in discounts to speakers, panelists, and workshop instructors.
+\\
+
+\begin{table}[H]
+\centering
+\caption*{\textbf{Attendance}}
+\begin{tabular}{|c|c|c|c|}
+\hline
+    \textbf{Item} & \textbf{Quantity} & \textbf{Cost} & \textbf{Subtotal}	\\ 
+\hline
+	Student			&	443	&	\$40	&	\$17,720						\\
+	Professional	&	127	& 	\$250	&	\$31,750						\\
+	Waived			&	60	& 	-\$250	&	-\$15,000						\\
+\hline
+	\multicolumn{3}{|r|}{\textbf{Attendance Total:}}	&	\$34,470		\\
+\hline
+\end{tabular}
+\end{table}
+
+\vspace{10mm}
+
+\begin{table}[H]
+\centering
+\caption*{\textbf{Sponsors}}
+\begin{tabular}{|c|c|c|c|}
+\hline
+    \textbf{Package} & \textbf{Quantity} & \textbf{Cost} & \textbf{Subtotal}	\\ 
+\hline
+	World Savior	&	1	&	\$30,000	&	\$30,000						\\
+	National Hero	&	3	& 	\$15,000	&	\$45,000						\\
+	Local Prodigy	&	5	& 	\$10,000	&	\$50,000						\\
+	Lifesaver		&	6	& 	\$5,000		&	\$30,000						\\
+	Exhibitor+		&	3	& 	\$3,500		&	\$10,500						\\
+	Exhibitor		&	5	& 	\$2,500		&	\$12,500						\\
+	Good Samaritan	&	10	& 	\$1,500		&	\$15,000						\\
+	Contributor		&	8	& 	\$1,000		&	\$8,000							\\
+\hline
+	\multicolumn{3}{|r|}{\textbf{Sponsors Total:}}	&	\$201,000				\\
+\hline
+\end{tabular}
+\end{table}
+
+\vspace{10mm}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{|c|}
+\hline
+    \textbf{Total Revenue: \$235,470}\\ 
+\hline
+\end{tabular}
+\end{table}
 
@@
 
-\subsection{Sponsorship Plan}
+\subsection{Sponsorship and Fundraising}
+The sponsorship breakdown for our conference pulls from averages of sponsorship packages in the last several conferences, with for main tiers that tie into the conference theme for the largest representation in the conference and visibility in the career fair, socials, sessions, technical, and meals as well as in conference shirts and attendee bags.
+Using two tiers for an exhibitor package allows for a platform for DOE national laboratories to participate, with the higher tier having logo representation on shirts as well as the opportunity to sponsor a coffee break or lunch \& learn session.
+Lastly, two packages are left to benefactors who are recognized in the conference program and represent the anticipated support from ANS divisions or local industry or University of Illinois contributors (or some generous contributions from out-of-state companies!).
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.75\textwidth]{sponsors1.png}	
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.75\textwidth]{sponsors2.png}	
+\end{figure}
 

### 2019-09-27 theme.tex

@@
 We believe that many solutions will come from the nuclear sciences.
-The ANS student conference is an opportunity for students and professionals to come together and share advances in critical technology and research, dedicated to solving these problems.
+The ANS Student Conference is an opportunity for students and professionals to come together and share advances in critical technology and research, dedicated to solving these problems.
 Nuclear, plasma, and radiological engineering will be central to many endeavors.
@@
 By hosting this conference, we hope to inspire and motivate students in nuclear, plasma, and radiological engineering fields to tackle big problems.
-Saving the world one atom at a time reflects the fact that nuclear science is a powerful force in dealing with grand challenge problems.
+Saving the World One Atom at a Time reflects the fact that nuclear science is a powerful force in dealing with grand challenge problems.
 This theme also honors the individual, atomic, contributions from students, researchers, and professionals that are essential to progress.

### 2019-09-27 uiuc.tex

@@
 \subsubsection{Plasma Physics and Fusion Science}
-\begin{wrapfigure}{r}{0.4\textwidth}
-  \begin{center}
-  \vspace{-\baselineskip}
-    \includegraphics[width=0.38\textwidth]{hidra.png}
-    \caption{HIDRA}
-  \end{center}
-\end{wrapfigure}
 The research theme of Fusion and Plasma Physics in the NPRE department has a long history of work in the area of magnetic and inertial nuclear fusion as well as plasma engineering.

### 2019-09-27 conflog.tex
adds building layouts, hotel images

--- 2019-09-27 conflog.tex
@@
 
-\begin{figure}[h]
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.5\textwidth}
 		\centering
 		\includegraphics[scale=0.2]{illini-union.png}
+	\end{subfigure}%
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{union-inside.jpg}
+	\end{subfigure}
 	\caption{Illini Student Union}		
@@
 
-The Illini Union is capable of hosting the entire technical program.
-Keeping the conference contained in one convenient location while being within easy access of the rest of the campus.
+The Illini Union is capable of hosting the entire technical program of the ANS Student Conference.
+This keeps the conference contained in one convenient location while being within easy access of the rest of the campus.
 Technical sessions will be held in a combination of rooms on the second, third, and fourth floors of The Union.
-Each of these rooms has at least enough capacity for 42 people and A/V capability.
+Each of these rooms have at least enough capacity for 42 people, lecture style, and A/V capability.
 There will also be rooms available to have panels and workshops during the course of the technical program.
-The Illini Rooms A and B will be a combined space for the career fair and Illini Room C will host the poster sessions.
-We will keep the space open to allow the poster sessions and career fairs to share attendance and encourage networking.
+The Illini Rooms A and B will be a combined space for the career fair while Illini Room C and the south lounge will host the poster sessions.
+We will keep the space open to allow the poster sessions and career fair to share attendance and encourage networking.
 A detailed list of room capacities and floor plans are located in Appendix D: Building Layout.
@@
 As these buildings are UIUC property, the cost of renting them are significantly reduced compared to a private facility.
-Additionally, these two buildings are adjacent to one another and are at most a 10 minute walk from either the Union or Marriott TowneSuites.
-See Fig.\ref{fig:conf-map} for a map of the proposed conference facilities.\\
+Additionally, these two buildings are adjacent to one another and are at most a 10 minute walk from the Union.
+See Appendix E for a map marking the locations of the proposed conference facilities.\\
 
@@
 
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\textwidth]{campus_map.png}
-	\caption{Map of conference facilities and hotels}
-	\label{fig:conf-map}
-\end{figure}
-
+\newpage
 \subsection{Hotels and Accommodations}
@@
 This will also be the location of the opening ceremony dinner.\\
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{garden_king.jpg}
+		\subcaption{King Suite}
+	\end{subfigure}%
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{garden_queen.jpg}
+		\subcaption{Queen Double}
+	\end{subfigure}
+	\caption{Garden Urbana Hotel rooms}		
+\end{figure}
 
@@
 Hosting technical sessions, workshops, and plenaries in the Union will help us negotiate a lower room rate.\\
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.5\linewidth]{illini-queen.jpg}
+	\caption{Queen Double}		
+\end{figure}
 
@@
 
+{\centering
 \begin{tabular}{lccccc}
@@
 Marriott TowneSuites &0.25 & 4/8-4/11 & 95 & 189 & \$47.50\\ 
-\end{tabular}
+\end{tabular}}
 \textbf{*}\textit{Price for a queen double}
@@
 
-\newpage
 \subsection{Travel and Transportation}

### 2019-09-27 uiuc.tex
adds building layouts, hotel images

--- 2019-09-27 uiuc.tex
@@
 \subsection{University of Illinois at Urbana-Champaign: Learning \& Labor}
+\begin{wrapfigure}{r}{0.5\textwidth}
+  \begin{center}
+  \vspace{-\baselineskip}
+    \includegraphics[width=0.44\textwidth]{alma.jpg}
+  \end{center}
+\end{wrapfigure}
 Founded in 1867, the University of Illinois at Urbana-Champaign (UIUC) has cultivated a long history of significant scientific discoveries and contributions.
@@
 \subsection{UIUC ANS Student Chapter (ANS-UIUC)}
+
 The ANS-UIUC maintains and develops a cohesive community of students in nuclear engineering.
@@
 One of our most popular outreach programs is Engineering Open House (EOH), during which ANS won best exhibit.
-EOH is an annual event where members of the local community, from young children to senior adults, visit the engineering campus to learn more about STEM research.
-
-\begin{wrapfigure}{l}{0.5\textwidth}
-  \begin{center}
-  \vspace{-\baselineskip}
-    \includegraphics[width=0.48\textwidth]{eoh1.JPG}
-    \caption{Mouse Trap Chain Reaction at EOH 2019}
-  \end{center}
-\end{wrapfigure}
-
-Membership is currently around 70-80 students and has been steadily growing.
+EOH is an annual event where members of the local community, from young children to senior adults, visit the engineering campus to learn more about STEM research.Membership is currently around 70-80 students and has been steadily growing.
 The chapter works to host events catering to nuclear, plasma, and radiological concentrations.
@@
 \clearpage
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[scale=0.15]{eoh1.JPG}
+  \caption{Mouse Trap Chain Reaction at EOH 2019}
+\end{figure}
 
@@
 \subsubsection{Plasma Physics and Fusion Science}
-\begin{wrapfigure}{r}{0.4\textwidth}
+\begin{wrapfigure}{r}{0.5\textwidth}
   \begin{center}
   \vspace{-\baselineskip}
-    \includegraphics[width=0.38\textwidth]{hidra.png}
+    \includegraphics[width=0.48\textwidth]{hidra.png}
     \caption{HIDRA}

### 2019-09-27 budget.tex

--- 2019-09-27 budget.tex
@@
 \subsection{Expenses}
-\hspace{-4cm}
-  \begin{tabular}{clcrccccr}
-    \hline\hline
-     & \multicolumn{1}{c}{Priority} & \multicolumn{1}{c}{Priority} & \multicolumn{1}{c}{Cost Per Unit} & \multicolumn{1}{c}{Thursday} & \multicolumn{1}{c}{Friday} & \multicolumn{1}{c}{Saturday} & \multicolumn{1}{c}{General} & \multicolumn{1}{c}{Total Cost} \\ \hline\hline
+\hspace{-1cm}
+  \begin{tabular}{|clcrccccr|}
+    \hline
+     & \multicolumn{1}{c}{Item} & \multicolumn{1}{c}{Priority} & \multicolumn{1}{c}{Cost Per Unit} & \multicolumn{1}{c}{Thursday} & \multicolumn{1}{c}{Friday} & \multicolumn{1}{c}{Saturday} & \multicolumn{1}{c}{General} & \multicolumn{1}{c}{Total Cost} \\ \hline\hline
      \multirow{10}{*}{\STAB{\rotatebox[origin=c]{90}{Facilities}}}
@@
      &                           &                           &                           &                           &\multicolumn{3}{r}{Grand Total:}                                                  & $\$$230,984.79           \\
-     &                           &                           &                           &                           &                          &                           &                           &                          \\ \hline\hline
+     &                           &                           &                           &                           &                          &                           &                           &                          \\ \hline
   \end{tabular}

### 2019-09-27 conflog.tex

--- 2019-09-27 conflog.tex
@@
 Due to the central location of UIUC, driving might be a good option for some schools and individuals. Below are the approximate driving times from several universities.
+
 \begin{center}
-	\begin{tabular}{l r}
+   \begin{tabular}{lcccc}
    \hline\hline
-	\textbf{School}& \textbf{Drive Time}\\
+   \textbf{School}&\textbf{Estimated Mileage (mi)}&\textbf{Driving Time (hrs)}&\textbf{Fuel Cost}&\textbf{Per Person}\\
    \hline\hline
-	U. Tennessee Knoxville & 7 h 13 min\\
-	University of Michigan & 5 h 24 min\\
-	Clemson University & 10 h 5 min\\
-	U. Missouri-Columbia & 4 h 18 min\\
-	Georgia Tech University & 8 h 54 min \\
-	University of Pittsburgh & 7 h 19 min\\
-	U. Wisconsin-Madison & 3 h 53 min \\
-	Penn State University & 9 h 17 min\\
-	University of South Carolina& 10 h 44 min\\
-	Iowa State University & 5 h 24 min \\
-	University of Iowa & 3 h 34 min\\
-	Vanderbilt University & 5 h 18 min\\
+    Purdue University&90&1h 40m&\$21.86&\$5.47\\
+    University of Cincinnati&233& 3h 40m&\$56.60&\$14.15\\
+    Air Force Tech &250&3h 58m&\$60.73&\$15.18\\
+    University of Wisconsin&253&4h&\$61.46&\$15.36\\
+    Missouri University S \& T &279&4h 21m&\$67.77&\$16.94\\
+    U. Missouri - Columbia&291&4h 28m&\$70.69&\$17.67\\
+    Ohio State University&302&4h 47m&\$73.36&\$18.34\\
+    University of Michigan&345&5h 17m&\$83.81&\$20.95\\
+    Vanderbilt University&373&5h 33m&\$90.61&\$22.65\\
+    Iowa State University&378&5h 44m&\$91.82&\$22.96\\
+    \hline
+    Average&279&4h 22m&\$67.87&\$16.97
+
     \end{tabular} 

### 2019-09-27 budget.tex
adds sponsors, revenue, fixes expenses table

@@
 
+% =======================================================================================
+% =======================================================================================
+% =======================================================================================
+% =======================================================================================
+% Revenue Section
+% =======================================================================================
+% =======================================================================================
+% =======================================================================================
+% =======================================================================================
+
 \subsection{Revenue}
+We have compared the predicted and actual revenues from previous reports and used these to estimate our expected revenue.
+To maintain reasonable accuracy in the budget, we were financially conservative in our estimates to account for fluctuating economy and attendance numbers.
+Should our bid be selected, these conservative estimates will result in a smoother planning and execution process.
+We have also accounted an estimated number of waived professional registration based on previous conferences.
+This  correlates to the number of waived fees given in our expected tier sponsorship figures and also factors in discounts to speakers, panelists, and workshop instructors.
+\\
+
+\begin{table}[H]
+\centering
+\caption*{\textbf{Attendance}}
+\begin{tabular}{|c|c|c|c|}
+\hline
+    \textbf{Item} & \textbf{Quantity} & \textbf{Cost} & \textbf{Subtotal}	\\ 
+\hline
+	Student			&	443	&	\$40	&	\$17,720						\\
+	Professional	&	127	& 	\$250	&	\$31,750						\\
+	Waived			&	60	& 	-\$250	&	-\$15,000						\\
+\hline
+	\multicolumn{3}{|r|}{\textbf{Attendance Total:}}	&	\$34,470		\\
+\hline
+\end{tabular}
+\end{table}
+
+\vspace{10mm}
+
+\begin{table}[H]
+\centering
+\caption*{\textbf{Sponsors}}
+\begin{tabular}{|c|c|c|c|}
+\hline
+    \textbf{Package} & \textbf{Quantity} & \textbf{Cost} & \textbf{Subtotal}	\\ 
+\hline
+	World Savior	&	1	&	\$30,000	&	\$30,000						\\
+	National Hero	&	3	& 	\$15,000	&	\$45,000						\\
+	Local Prodigy	&	5	& 	\$10,000	&	\$50,000						\\
+	Lifesaver		&	6	& 	\$5,000		&	\$30,000						\\
+	Exhibitor+		&	3	& 	\$3,500		&	\$10,500						\\
+	Exhibitor		&	5	& 	\$2,500		&	\$12,500						\\
+	Good Samaritan	&	10	& 	\$1,500		&	\$15,000						\\
+	Contributor		&	8	& 	\$1,000		&	\$8,000							\\
+\hline
+	\multicolumn{3}{|r|}{\textbf{Sponsors Total:}}	&	\$201,000				\\
+\hline
+\end{tabular}
+\end{table}
+
+\vspace{10mm}
+
+\begin{table}[H]
+\centering
+\begin{tabular}{|c|}
+\hline
+    \textbf{Total Revenue: \$235,470}\\ 
+\hline
+\end{tabular}
+\end{table}
+
+% =======================================================================================
+% =======================================================================================
+% =======================================================================================
+% =======================================================================================
+% Expenses Section
+% =======================================================================================
+% =======================================================================================
+% =======================================================================================
+% =======================================================================================
 
 \subsection{Expenses}
-\hspace{-1cm}
+
+\hspace{-1.1cm}
 \begin{tabular}{|clcrccccr|}
+
     \hline
-     & \multicolumn{1}{c}{Item} & \multicolumn{1}{c}{Priority} & \multicolumn{1}{c}{Cost Per Unit} & \multicolumn{1}{c}{Thursday} & \multicolumn{1}{c}{Friday} & \multicolumn{1}{c}{Saturday} & \multicolumn{1}{c}{General} & \multicolumn{1}{c}{Total Cost} \\ \hline\hline
+     & \multicolumn{1}{c}{Item} & \multicolumn{1}{c}{Priority} & \multicolumn{1}{c}{Cost Per Unit} & \multicolumn{1}{c}{Thursday} & \multicolumn{1}{c}{Friday} & \multicolumn{1}{c}{Saturday} & \multicolumn{1}{c}{General} & \multicolumn{1}{c}{Total Cost}\\     \hline\hline
      \multirow{10}{*}{\STAB{\rotatebox[origin=c]{90}{Facilities}}}
@@
 \end{tabular}
+
+\vspace{0.5cm}
+
 \begin{tabular}{lrrr}
@@
 \end{tabular}
-\subsection{Sponsorship Plan}
+
+\subsection{Sponsorship and Fundraising}
+The sponsorship breakdown for our conference pulls from averages of sponsorship packages in the last several conferences, with for main tiers that tie into the conference theme for the largest representation in the conference and visibility in the career fair, socials, sessions, technical, and meals as well as in conference shirts and attendee bags.
+Using two tiers for an exhibitor package allows for a platform for DOE national laboratories to participate, with the higher tier having logo representation on shirts as well as the opportunity to sponsor a coffee break or lunch \& learn session.
+Lastly, two packages are left to benefactors who are recognized in the conference program and represent the anticipated support from ANS divisions or local industry or University of Illinois contributors (or some generous contributions from out-of-state companies!).
+
+\vspace{2cm}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\textwidth]{sponsors1.png}	
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\textwidth]{sponsors2.png}	
+\end{figure}
 

### 2019-09-27 conflog.tex
adds transport during the conference

@@
 \subsubsection{Getting to the Conference}
-The primary location for all conference events is the Illini Union.
-This is also the primary hotel for conference attendees.
-The secondary hotel, Marriott TowneSuites is merely a five minute walk from the Union.
+The primary hotel, Garden Hotel Urbana, is approximately two miles from the Union and outside of reasonable walking distance.
+Thus we have budgeted to include transportation provided by Peoria Charter.
+We intend to have busses shuttling continuously between the Union and the Garden Hotel Urbana.
+For those who desire more flexibility and freedom, there is CU-MTD bus stop adjacent to the hotel that has a bus every 10 minutes.
+This bus route, the 22 Illini, can take attendees directly to the Union from the hotel.
+It is also one of the main campus bus routes and can take travelers almost anywhere on or around campus.
+Lyft and Uber are available as well for attendees that choose to use those services.
+A map of the bus route is in Appendix E: Campus Map of Locations.

### 2019-09-27 proglog.tex
adds letter, moves title text up
updates tours and speakers

@@
 \setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.35\textwidth}
+\begin{wrapfigure}{R}{0.35\textwidth}
 	\begin{center}
@@
 Slaybaugh has much to offer the conference with her vision and leadership.\\
+\clearpage
 
@@
 		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{speaker-1.jpeg}
+		\includegraphics[height=5.5cm]{speaker-1.jpeg}
 	\end{center}
@@
 
-\vspace{0.5cm}
 \subsubsection{Todd Allen, UW Madison}
 \setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.35\textwidth}
+\begin{wrapfigure}{R}{0.35\textwidth}
 	\begin{center}
 		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{speaker-6.jpeg}
+		\includegraphics[height=5.5cm]{speaker-6.jpeg}
 	\end{center}
@@
 		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{speaker-5.jpg}
+		\includegraphics[height=5.5cm]{speaker-5.jpg}
 	\end{center}
@@
 \setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.35\textwidth}
+\begin{wrapfigure}{R}{0.35\textwidth}
 	\begin{center}
 		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{speaker-3.jpeg}
+		\includegraphics[height=5cm]{speaker-3.jpeg}
 	\end{center}
@@
 In addition to his experience and ambition, he is an excellent science communicator to scientists and non-scientists alike.
-Together, these factors make him an ideal speaker at the conference.\\
+Together, these factors make him an ideal speaker at the conference.
+
+\subsubsection{William Magwood}
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{R}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=5cm]{magwoodw.jpeg}
+	\end{center}
+\end{wrapfigure}
+Mr.
+Magwood served seven years as the Director of Nuclear Energy with the U.S.
+Department of Energy (DOE), where he was the senior nuclear technology official in the United States Government.
+He oversaw the restoration of the Federal nuclear technology program and led the creation of ``Nuclear Power 2010,'' ``Generation IV,'' and other innovative initiatives—including successful efforts that helped reverse the decline in American nuclear technology education.
+Since joining the NRC, he has continued his advocacy for both U.S.
+science and technology education and strong international cooperation.
+He has also sought to assure transparency and improve the agency's openness to public participation.
+As an NRC Commissioner, Mr.
+Magwood has been a strong defender of the NRC's regulatory independence and adherence to the principle that regulations should be based firmly on scientific and technical facts.
+From his nomination as a Commissioner, Mr.
+Magwood has remained committed to his promise to carry out his responsibilities ``in a manner that earns the public's trust, and always doing the right thing even when the right thing isn't easy.''
 
@@
 		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{nguyenp.png}
+		\includegraphics[height=5cm]{nguyenp.png}
 	\end{center}
@@
 As the former Director of Engineering at Intel, Phi Nguyen is the perfect person to talk about how this important research helps solve big problems.
-
-\subsubsection{William Magwood?}
-
+\clearpage
 \subsubsection{Ross Radel, CEO Phoenix, LLC}
 \setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.35\textwidth}
+\begin{wrapfigure}{R}{0.35\textwidth}
 	\begin{center}
 		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{radel.png}
+		\includegraphics[height=5.5cm]{radel.png}
 	\end{center}
@@
 		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{piefer.jpg}
+		\includegraphics[height=5.5cm]{piefer.jpg}
 	\end{center}
@@
 
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{L}{0.5\textwidth}
+	\begin{center}
+		% \vspace{-\baselineskip}
+		\includegraphics[width=0.48\textwidth]{argonne.png}
+	\end{center}
+\end{wrapfigure}
 \textbf{Argonne National Laboratory}\\
@@
 
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{L}{0.45\textwidth}
+	\begin{center}
+		% \vspace{-\baselineskip}
+		\includegraphics[height=5.5cm]{clintonpp.jpg}
+	\end{center}
+\end{wrapfigure}
 \textbf{Clinton Power Station}\\
@@
 
+\clearpage
 \textbf{Starfire Industries LLC}\\
@@
 
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{L}{0.48\textwidth}
+	\begin{center}
+		% \vspace{-\baselineskip}
+		\includegraphics[height=5.5cm]{bw_front.png}
+	\end{center}
+\end{wrapfigure}
 \textbf{National Center for Supercomputing Applications (NCSA)}\\
@@
 
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{L}{0.4\textwidth}
+	\begin{center}
+		% \vspace{-\baselineskip}
+		\includegraphics[width=0.38\textwidth]{riggs.jpg}
+		\caption{Riggs Brewery}
+	\end{center}
+\end{wrapfigure}
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{R}{0.43\textwidth}
+	\begin{center}
+		% \vspace{-\baselineskip}
+		\includegraphics[width=0.4\textwidth]{triptych.jpeg}
+		\caption{Triptych Brewery}
+	\end{center}
+\end{wrapfigure}
 \textbf{Riggs Brewery Tour}\\
@@
 Transportation to and from the brewery will be provided.\\
-
+\newline
+\newline
+\newline
+% \vspace{3cm}
+\newline
+\newline
 \textbf{University Tour}\\

### 2019-09-27 proglog.tex
adds technical sessions

@@
 
+\subsection{Technical Sessions}
+
+Technical sessions are an integral part of every student conference.
+This is where students can share their research experiences, new ideas, exchange knowledge, and \textit{atomic contributions} to the big problems of the world.
+There are 6 technical sessions held concurrently each day.
+Each room will be equipped with a projectors, computers, podiums, and other necessary equipment.
+Each presenter is given 15 minutes to present and 5 minutes to answer questions from the audience.
+Presenters will be judged on significance, originality, and overall presentation (Podium Presentation Judging Form can be found in Appendix B).
+The divisions of the technical sessions include, but are not limited to
+\begin{itemize}
+	\item Accelerator Applications
+	\item Aerospace Nuclear Science \& Technology
+	\item Computational Medical Physics
+	\item Decommissioning \& Environmental Sciences
+	\item Education, Training \& Workforce Development
+	\item Fuel Cycle \& Waste Management
+	\item Fusion Energy
+	\item Human Factors, Instrumentation \& Control
+	\item Isotopes \& Radiation
+	\item Materials Science \& Technology
+	\item Mathematics \& Computation for Nuclear Engineering
+	\item Next Generation Reactors \& Advanced Reactors
+	\item Nuclear Criticality Safety
+	\item Nuclear Energy Applied to Biology \& Medicine
+	\item Nuclear Installations Safety
+	\item Nuclear Nonproliferation
+	\item Probabilistic Risk Analysis
+	\item Operations \& Power
+	\item Radiation Protection \& Shielding
+	\item Reactor Physics
+	\item Robotics \& Remote Systems
+	\item Thermal Hydraulics
+\end{itemize}
+Practice rooms will be made available every day of the conference.
+We expect a total of 48 technical sessions each with 4-5 presenters.
+There will be an award for best graduate and best undergraduate presentation for each category.
+
+\subsection{Poster Session}
+There will be a poster session on Saturday in Illini Room C and the South Lounge.
+This offers nearly 1600 square feet of space and allows students an opportunity to share their research in an open environment.
+The poster session will be immediately adjacent to the career fair.
+This encourages students and professionals, that might otherwise go to one or neither, to attend both.
+There will be an award for best graduate and undergraduate poster.
+\subsubsection{Highschool Poster Session}
+We believe that attracting younger students to the field of nuclear engineering will help us grow the nuclear community.
+To that end we will invite high school students to present a poster on a topic of interest in the nuclear sciences.
+This will also add to the diversity of the conference.
+
+\subsection{Career Fair}
+The career will be held all day on Friday, from 8am to 5pm, and on Saturday from 8am to noon.
+It will be held in Illini Rooms A \& B, a large space that will be shared with the poster sessions on saturday to encourage students and professionals to attend both.
+Recruiters may mail bulkier items prior to their arrival in Champaign.\\
+
+All companies that sponsor the conference will be given a table at the career fair.
+Location will be decided in order of sponsorship amount and when the agreement was made.
+Universities may freely request a table at the career fair, while space is available.\\
+
+There will be rooms available at the Illini Union for companies to interview potential candidates.
+
 % =========================================================================================

### 2019-09-27 budget.tex
adds expenses and contingency explanation

@@
 \subsection{Expenses}
+A conservative breakdown of conference expenses is outlined in Table ******* on page *******.
+Emphasizing some of the points shown in the table, all rooms hosted in the Union are provided to registered student organizations (such as ANS) free of charge, which allows us to save significantly on event space.
+Meals catered through the University catering service reflect a 6.25\% sales tax in the total cost which is not represented in the unit cost.
+Gratuity is neglected as it is forbidden under the catering service’s policies, allowing us to save cost on meals.
+Under our most conservative estimates for budget and revenue, the spending margin is found to be 1.9\%.
+While this margin leaves little room for variation, we feel this is justified as several costs in the expenses, such as reimbursements, are left significantly inflated as compared with previous years.
+Adopting previous years’ estimates of \$60,000 for travel reimbursements leaves a spending margin of 24.2\%, matching that of the most austere contingency plans provided in previous years.
+Assuming maximum expenses and an attendance of 450 students, the total cost per student is estimated at \$513.30.
+This number also includes the travel reimbursement, which was intentionally set to be considerably more generous than previous years to make the budget more conservative.
+Neglecting the cost of travel reimbursements, the average cost per student falls to \$263.30, at or below that estimated for previous years.
 
@@
 
-\vspace{0.5cm}
-
-\begin{tabular}{lrrr}
-  \hline\hline
-  \multicolumn{1}{l}{Level of Cuts Made} & \multicolumn{1}{c}{Amount Saved} & \multicolumn{1}{c}{Grand Total} & \multicolumn{1}{c}{\% of Max Revenue} \\ \hline\hline 
-  Priority IV Cuts Made & $\$$9,346.00 & $\$$221,638.79 & ********** \\
-  III and IV Cuts Made & $\$$22,987.25 &$\$$207,997.54 & ********* \\
-  II, III, and IV Cuts Made & $\$$49,053.19 & $\$$181,931.60 & ********* \\
-
-\end{tabular}
-
 \subsection{Sponsorship and Fundraising}
@@
 \subsection{Financial Contingency}
+The budget is structured with priority levels outlining the order of cuts, should they be necessary.
+Priority I expenses are not subject to cuts under any circumstances as they are considered necessities for hosting the conference.
+Cuts will be made first to reduce most priority IV expenses by half, preserving events while still saving money.
+Priority III cuts mean eliminating all priority IV expenses and either elimination of, or reduction of the duration of social events by half.
+Priority II cuts entail complete elimination of social event expenses, along with elimination of tour expenses and reduction of dinner costs through cheaper buffet options and desserts.
+The expenditure savings from these cuts are outlined in Table *******.
+While this contingency plan does not consider cuts to the reimbursement funds, this could be reconsidered if necessary, since reimbursements were set aside at a level nearly double that of previous conferences.
+\\
+
+\begin{tabular}{lrrr}
+  \hline\hline
+  \multicolumn{1}{l}{Level of Cuts Made} & \multicolumn{1}{c}{Amount Saved} & \multicolumn{1}{c}{Grand Total} & \multicolumn{1}{c}{\% of Max Revenue} \\ \hline\hline 
+  Priority IV Cuts Made & $\$$9,346.00 & $\$$221,638.79 & ********** \\
+  III and IV Cuts Made & $\$$22,987.25 &$\$$207,997.54 & ********* \\
+  II, III, and IV Cuts Made & $\$$49,053.19 & $\$$181,931.60 & ********* \\
+
+\end{tabular}
 
@@
 We will assume that minimizing cost is a priority for schools, thus number of persons per hotel room is double the number of beds.
+The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport.
+There is also a small airport located just 20 minutes outside of campus.
+Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus up to 10 times per day.
+Below are the round-trip, non-stop, airfare costs for the first weekend of April.
+Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip.
+While some students may wish to make use of the convenience of the local airport, in general the most economic method of arriving in Champaign is by first flying to O’Hare and then busing.
+The average cost of this trip comes out to be \$293 as shown in Table *******.
+Adding this to the lodging costs for four nights (as students often arrive Wednesday evening) and assuming four students per room, the total cost of attendance for each student comes out to an average of \$412.
 

### 2019-09-27 management.tex
makes updates

@@
 They must communicate with their subcommittees and with other directors to make sure there are no conflicting decisions.
-The coordinators work in an even more specialized area and help the directors by handling a single task.
+The coordinators work in an even more specialized area and help the directors by handling a single task.\\
+
+% \vspace{1cm}
 
@@
 
-$\textbf{Financial Co-Chair}$\\\\
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{L}{0.35\textwidth}
+	\begin{center}
+		\vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{ncreid2.jpg}
+	\end{center}
+\end{wrapfigure}
+$\textbf{Diversity Co-Chair - Nathan Reid}$\\
+Nate graduated with a B.S.
+in Nuclear, Plasma, and Radiological Engineering from UIUC in 2016.
+He is currently attending UIUC as a 4th-year Ph.D.
+student in the field of fusion and plasma science and engineering under Prof.
+Jean Paul Allain.
+Nate is currently conducting his thesis research at Oak Ridge National Laboratory, where he has spent the last three summers working on a multitude of projects in the nuclear structural materials group.
+He focuses on the technological assessment of plasma facing materials such as advanced tungsten alloys and composites under the mentorship of Dr.
+Lauren Garrison.
+Nate has attended four of the last five ANS Student Conferences and was a student paper competition finalist at the TOFE embedded topical of the 2018 ANS Winter Meeting, presenting his work on glow-discharge optical emission spectroscopy of tungsten neutron-transmutation elements.
+Nate is recognized by the ANS section at UIUC for his outstanding graduate service in the last year, and served as the Women in Nuclear UIUC chapter Vice President.
+He was part of the executive team that received the national student chapter excellence award at the 2019 Women in Nuclear national conference, of which he was awarded a student sponsorship to attend.
+Nate is ecstatic about working alongside his ANS student section as Diversity Co-Chair and setting goals to bring inclusion to the conference.\\
+\clearpage
 
@@
 	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{stahlj.jpg}
+		% \vspace{-\baselineskip}
+		\includegraphics[height=5.5cm]{stahlj.jpg}
 	\end{center}
 \end{wrapfigure}
-$\textbf{Account Coordinator - Jack Stahl}$\\
-
+$\textbf{Financial Chair - Jack Stahl}$
+Jack graduated with a B.S.
+in Nuclear, Plasma, and Radiological Engineering from UIUC in 2019, and is now a first-year graduate student studying plasma engineering under Dr.
+David Ruzic.
+He has been involved in the UIUC student chapter of ANS since his sophomore year and has attended two student conferences.
+Previously, Jack has spent a summer as an intern at ASML.
+Jack hopes to help host a student conference that will bolster younger student involvement in ANS.
+\newline
+\vspace{1cm}
+\newline
 \setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
+\begin{wrapfigure}{L}{0.35\textwidth}
 	\begin{center}
 		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{dinarij.jpg}
+		\includegraphics[height=5.5cm]{dinarij.jpg}
 	\end{center}
@@
 $\textbf{Registration Coordinator - Jasmine Dinari}$\\
+Jasmine is a frehsman studying Nuclear, Plasma, and Radiological Engineering at UIUC, as well as minors in French and Physics.
+She is starting research with Dr.
+Andruczyk, who is currently at the head of the HIDRA project.
+Powering the world through nuclear is one of her main interests, and she later hopes to participate in nuclear fusion research.
+The ANS Student Conference is an  amazing opportunity to share her interests in nuclear science.
+She gained organizational and leadership experience through various extracurriculars in high school and currently serves as the Professional Development Chair for the UIUC student chapter of Women in Nuclear.
+She plans on attending the 2020 ANS Student Conference at NC State.\\
+\vspace{1cm}
 
@@
 $\textbf{Sponsorship Coordinator - James Shehee}$\\
+Jimmy is a junior undergraduate student in UIUC's Nuclear, Plasma, and Radiological Engineering department, with a concentration in power, safety, and the environment.
+Jimmy has been an active member of the University's ANS student chapter since his freshman year, has held the positions of Secretary and External Vice President, and was chosen to receive the chapter's Undergraduate Outstanding Service Award in the spring of 2019.
+Jimmy was first introduced to the nuclear industry through the Nuclear Science Merit Badge in Boy Scouts, and he is excited about any opportunity to create similar experiences for students and the public.
+Outside of ANS, Jimmy is also the President of the Illini Venturing Crew.
+In the summer of 2019, Jimmy interned at Exelon's Quad Cities Generating Station, and will be returning for another summer in 2020.
+He is excited to attend his first ANS Student Conference in March 2020 at North Carolina State University.\\
 
-$\textbf{Technical Subcommittee}$\\\\
-
+\clearpage
+\vspace{1cm}
 \setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
+\begin{wrapfigure}{L}{0.35\textwidth}
 	\begin{center}
-		\vspace{-\baselineskip}
+		% \vspace{-\baselineskip}
 		\includegraphics[height=15\baselineskip]{cheeg.jpg}
@@
 \end{wrapfigure}
+$\textbf{Technical Subcommittee}$\\
 $\textbf{Technical Subcommittee Chair- Gwen Chee}$\\
+Gwen is a third year graduate student studying fuel cycles for advanced reactor designs with Dr.
+Kathryn Huff in the ARFC group.
+Last summer she had an internship at Argonne National Laboratory where she worked on (...) .She also serves as the president of the UIUC chapter of Women In Nuclear (WiN).
+Under her leadership, WiN-UIUC was honored with the Best Student Chapter award at the WiN National Meeting in 2019.
+She has also been involved with ANS and attended the 2018 ANS Student Conference in Florida and will be attending the upcoming ANS Student Conference at NC State in 2020.
+\\
+\vspace{1cm}
+\newline
 
@@
 He believes hosting the student conference at UIUC will help the field grow and thrive.
-This is also an opportunity to meet other people working in the field, share life experiences, and develop a stronger network.
+This is also an opportunity to meet other people working in the field, share life experiences, and develop a stronger network.\\
 
-$\textbf{Sessions Coordinator - Zachary Jeckell}$\\
-$\textbf{Career Fair Coordinator - Greg Golba}$\\
-
-$\textbf{Non-Technical Subcommittee}$\\\\
+\vspace{1cm}
 
 \setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
+\begin{wrapfigure}{L}{0.45\textwidth}
 	\begin{center}
 		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{gaughann.JPG}
+		\includegraphics[width=0.43\textwidth]{jeckellz.png}
 	\end{center}
 \end{wrapfigure}
+$\textbf{Sessions Coordinator - Zachary Jeckell}$\\
+Zachary graduated with a B.S.
+in Nuclear, Plasma, and Radiological Engineering from UIUC in 2018 and is now a second year graduate student studying plasma engineering under Dr.
+David Ruzic.
+He has presented his research at two previous student conferences  and realized that he wanted to help bring this prestigious event to the University of Illinois.
+He strongly believes that the group of students at UIUC are capable of such a feat and that the University would make an excellent location for the conference because of its stellar program and wonderful faculty.
+He plans to attend the next ANS student conference at NC State to present research on chemical vapor deposition using atmospheric pressure plasma.
+\clearpage
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{R}{0.25\textwidth}
+	\begin{center}
+		% \vspace{-\baselineskip}
+		\includegraphics[height=5cm]{golbag.jpg}
+	\end{center}
+\end{wrapfigure}
+$\textbf{Career Fair Coordinator - Grzegorz Golba}$\\
+Grzegorz Golba is a sophomore pursuing a B.S.
+in Nuclear Engineering with a physics minor in the plasma and fusion science concentration.
+He is now studying material interactions with plasma under Dr.
+Daniel Andruczyk.
+Grzegorz attended the 2019 ANS Student Conference in Virginia, reaffirmed his desire to study of nuclear science.
+He seeks new opportunities to engage with the nuclear science community and is excited for the possibilities of hosting a student conference at UIUC.
+\\
+\newline
+\vspace{1cm}
+\newline
 
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{L}{0.25\textwidth}
+	\begin{center}
+		% \vspace{-\baselineskip}
+		\includegraphics[height=6cm]{gaughann.JPG}
+	\end{center}
+\end{wrapfigure}
+$\textbf{Non-Technical Subcommittee}$\\
 $\textbf{Logistics Chair - Natalie Gaughan}$\\
@@
 in Nuclear Engineering from the University of Wisconsin-Madison in 2017.
-She has completed internships at Argonne National Laboratory and the International Atomic Energy Agency.
+She has completed two summer internships at Argonne National Laboratory where she worked with various neutronics codes.
+Natalie then spent a year in Vienna as an intern at the International Atomic Energy Agency, where she helped organize and evaluate nuclear data for medical isotope production.
 She is now a graduate student at UIUC intending to research radiological science and nuclear medicine.
-Natalie has attended two ANS student conferences in the past and knows how these conferences can be influential in students’ career development.
-She will be attending the upcoming ANS student conference in 2020 at NC State.
+As an undergraduate, Natalie attended two ANS student conferences which played a huge role in obtaining internships and inspired her decision to attend graduate school.
+Natalie knows firsthand how the ANS student conferences can be influential in students’ education and career development, and would love to help younger students experience the same benefits.
+She will also be attending the upcoming ANS student conference in 2020 at NC State.\\
+
+% \clearpage
+\vspace{0.5cm}
 
 \setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.35\textwidth}
+\begin{wrapfigure}{R}{0.25\textwidth}
 	\begin{center}
-		\vspace{-\baselineskip}
+		% \vspace{-\baselineskip}
 		\includegraphics[height=15\baselineskip]{kdilan.jpg}
@@
 $\textbf{Program Coordinator - Dilan Kurukulasuriya}$\\
-Dilan Kurukulasuriay is a second-year undergraduate student pursuing a B.S.
+Dilan Kurukulasuriay is a sophomore pursuing a B.S.
 in Nuclear, Plasma, and Radiological Engineering, along with a minor in Physics and Mathematics.
@@
 He is interested in fusion science research, specifically the materials interaction aspect.
-He also plans on attending the upcoming student conference at NC State in 2020.
+He also plans on attending the upcoming student conference at NC State in 2020.\\
+
+\clearpage
+\vspace{1cm}
+
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{L}{0.35\textwidth}
+	\begin{center}
+		% \vspace{-\baselineskip}
+		\includegraphics[height=15\baselineskip]{davisg.jpg}
+	\end{center}
+\end{wrapfigure}
+$\textbf{Hotels and Transportation Coordinator - Gavin Davis}$\\
+Gavin is currently pursuing a B.S.
+in Nuclear, Plasma, and Radiological Engineering from UIUC and plans to graduate in 2022.
+He has been involved with the ANS-UIUC since his freshman year and has dedicated his time to outreach events and increasing public awareness of nuclear science and nuclear energy.
+He has accomplished this through events such as UIUC's Engineering Open House.
+It was an event he enjoyed as a kid and hopes to help other children develop an interest in nuclear sciences.
+He also returns to his high school to talk about his experience at UIUC.
+He looks forward to learning more about nuclear fission technology and to make advancements in nuclear science and in the nuclear energy sector as a whole.
+He looks forward to attending the student conference at NC State in 2020.\\
+
+\vspace{1cm}
 
@@
 	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{davisg.jpg}
-	\end{center}
-\end{wrapfigure}
-$\textbf{Hotels and Transportation Coordinator - Gavin Davis}$\\
-
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{moranb.jpg}
+		% \vspace{-\baselineskip}
+		\includegraphics[height=5cm]{moranb.jpg}
 	\end{center}
@@
 He is confident that this experience will help him make the Student Conference a great success.
-He will be attending the 2020 conference at NC State.
+He will be attending the 2020 conference at NC State.\\
+\newline
+\vspace{1cm}
+\newline
+
+\setlength\intextsep{0pt}
+\begin{wrapfigure}{L}{0.35\textwidth}
+	\begin{center}
+		% \vspace{-\baselineskip}
+		\includegraphics[height=5cm]{ballaa.jpg}
+	\end{center}
+\end{wrapfigure}
+$\textbf{Tours Coordinator - Anna Balla}$\\
+Anna is a junior in NPRE with a planned concentration in the power, safety, and the environment.
+She became interested in nuclear engineering after taking a general education class with an NPRE professor and learning about how effective nuclear power is at reducing carbon emissions.
+Anna is a teaching assistant for two classes in the NPRE department and is also very involved with the Women in Nuclear chapter at Illinois.
+In her spare time, she enjoys going to concerts, playing volleyball, and wishing she knew how to juggle.\\
+
+\clearpage\vspace{1cm}
+% \newline
 
@@
 	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{ballaa.jpg}
-	\end{center}
-\end{wrapfigure}
-$\textbf{Tours Coordinator - Anna Balla}$\\
-
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.35\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[width=0.3\textwidth]{ryann.jpg}
+		% \vspace{-\baselineskip}
+		\includegraphics[height=5cm]{ryann.jpg}
 	\end{center}
@@
 He believes that an online presence for this event will supplement the success of an already great set of programs and individuals involved.
-He is excited to attend the upcoming ANS Student Conference at NC State in 2020.
+He is excited to attend the upcoming ANS Student Conference at NC State in 2020.\\
 
-[All committee members must plan on attending the upcoming student conference!]
+\vspace{1cm}
 

### 2019-09-28 conflog.tex
makes updates
adds section about banquet space

@@
 A detailed list of room capacities and floor plans are located in Appendix D: Building Layout.
+\\
+
+\subsection{Banquet Space}
+\subsubsection{Garden Hotel in Urbana}
+The opening ceremony dinner on Thursday night will be hosted at the Garden Hotel in Urbana.
+They have a capacity of 600 people in rounds and offer in house catering as well as AV capabilities.
+This location was chosen for its convenience, as it would be the primary hotel for the conference.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.5\textwidth]{garden_dinner.jpg}
+    \caption{The Garden Hotel Banquet Hall with capacity for 600 people in rounds.}
+\end{figure}
+
+\subsubsection{IHotel}
+Dinner on Friday night will be hosted at the IHotel.
+The IHotel is undergoing an expansion that will increase the capacity of their banquet space to 690 people in rounds.
+This expansion is set to be completed by Fall 2020.
+We will be hosting a social at the 77 Club in Memorial Stadium, just up the street.
+Information about the IHotel expansion is included in Appendix D.
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.75\textwidth]{ihotel-dinner.png}
+    \caption{The current 400-person banquet space at the IHotel.}
+\end{figure}
+
+\subsubsection{Illini Union}
+After the career fair is taken down on Saturday the final dinner will be set up in the combined Illini Rooms, which has a seating capacity of 496 people in rounds.
+Catering will be provided by Universiy Catering which allows us to avoid the 20\% gratuity for services.\\
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=\textwidth]{illinirooms.jpg}
+    \caption{The combined Illini rooms with capacity for 496 in rounds.}
+\end{figure}
 
@@
 Additionally, these two buildings are adjacent to one another and are at most a 10 minute walk from the Union.
+We could also host all technical sessions at the IHotel.
+Hosting at the IHotel is more expensive than hosting in University buildings and would also require additional transportation options.
+We would need to reevaluate some parts of our budget in order to host the technical program at this venue.
 See Appendix E for a map marking the locations of the proposed conference facilities.\\
@@
 
+\subsection{Dining}
+\subsubsection{Breakfast}
+Our primary hotel, the Garden Hotel in Urbana, soon to be the Radisson Hotel, serves complimentary breakfast every morning.
+Due to this, we will not be catering breakfast at the Illini Union during the conference.
+Guests staying at the Illini Union Hotel are provided with vouchers for breakfast at the food court in the basement of the Union.
+The food court offers Einstein Brothers, Starbucks, Garbanzo Mediterranean, and more.
+\subsubsection{Lunch}
+\subsubsection{Dinner}
+
+\textbf{Thursday Night}\\
+\textbf{Friday Night}\\
+\textbf{Saturday Night}\\
+
 \subsection{Travel and Transportation}
@@
    \hline\hline
-   \textbf{School}&\textbf{Estimated Mileage (mi)}&\textbf{Driving Time (hrs)}&\textbf{Fuel Cost}&\textbf{Per Person}\\
+   \textbf{School}&\textbf{Estimated Mileage (mi)}&\textbf{Driving Time (hrs)}&\textbf{Fuel Cost*}&\textbf{Per Person**}\\
    \hline\hline
@@
 \end{center}
+\textbf{*}\textit{Estimated assuming an average 23 MPG}\\
+\textbf{**}\textit{Assumes four people in a car}
 

### 2019-09-28 budget.tex
changes order of information
Doubled Busing

@@
      \multirow{5}{*}{\STAB{\rotatebox[origin=c]{90}{Transport}}}
-     & Shuttles From Hotel       & I                         & $\$$ 1,000.00             & 2                         & 2                        & 2                         & -                         & $\$$6,000.00             \\
+     & Shuttles From Hotel       & I                         & $\$$ 1,000.00             & 4                         & 4                        & 4                         & -                         & $\$$12,000.00            \\
      & Ihotel Dinner             & I                         & $\$$ 875.00               & -                         &  -                       &  4                        &  -                        & $\$$3,500.00             \\
@@
      &                           &                           &                           &                           &                          &                           &                           &                          \\
-     &                           &                           &                           &                           &\multicolumn{3}{r}{Grand Total:}                                                  & $\$$230,984.79           \\
+     &                           &                           &                           &                           &\multicolumn{3}{r}{Grand Total:}                                                  & $\$$236,984.79           \\
      &                           &                           &                           &                           &                          &                           &                           &                          \\ \hline
 \end{tabular}
+
+\subsection{Financial Contingency}
+
+\begin{tabular}{lrrr}
+  \hline\hline
+  \multicolumn{1}{l}{Level of Cuts Made} & \multicolumn{1}{c}{Amount Saved} & \multicolumn{1}{c}{Grand Total} & \multicolumn{1}{c}{\% of Max Revenue} \\ \hline\hline 
+  Priority IV Cuts Made & $\$$9,346.00 & $\$$227,638.79 & ********** \\
+  III and IV Cuts Made & $\$$22,987.25 &$\$$213,997.54 & ********* \\
+  II, III, and IV Cuts Made & $\$$49,053.19 & $\$$187,931.60 & ********* \\
+\end{tabular}
+
+The budget is structured with priority levels outlining the order of cuts, should they be necessary.
+Priority I expenses are not subject to cuts under any circumstances as they are considered necessities for hosting the conference.
+Cuts will be made first to reduce most priority IV expenses by half, preserving events while still saving money.
+Priority III cuts mean eliminating all priority IV expenses and either elimination of, or reduction of the duration of social events by half.
+Priority II cuts entail complete elimination of social event expenses, along with elimination of tour expenses and reduction of dinner costs through cheaper buffet options and desserts.
+The expenditure savings from these cuts are outlined in Table *******.
+While this contingency plan does not consider cuts to the reimbursement funds, this could be reconsidered if necessary, since reimbursements were set aside at a level nearly double that of previous conferences.
+\\
 
@@
 
-\vspace{2cm}
+\vspace{1cm}
 
@@
 \input{banking}
-
-\subsection{Financial Contingency}
-The budget is structured with priority levels outlining the order of cuts, should they be necessary.
-Priority I expenses are not subject to cuts under any circumstances as they are considered necessities for hosting the conference.
-Cuts will be made first to reduce most priority IV expenses by half, preserving events while still saving money.
-Priority III cuts mean eliminating all priority IV expenses and either elimination of, or reduction of the duration of social events by half.
-Priority II cuts entail complete elimination of social event expenses, along with elimination of tour expenses and reduction of dinner costs through cheaper buffet options and desserts.
-The expenditure savings from these cuts are outlined in Table *******.
-While this contingency plan does not consider cuts to the reimbursement funds, this could be reconsidered if necessary, since reimbursements were set aside at a level nearly double that of previous conferences.
-\\
-
-\begin{tabular}{lrrr}
-  \hline\hline
-  \multicolumn{1}{l}{Level of Cuts Made} & \multicolumn{1}{c}{Amount Saved} & \multicolumn{1}{c}{Grand Total} & \multicolumn{1}{c}{\% of Max Revenue} \\ \hline\hline 
-  Priority IV Cuts Made & $\$$9,346.00 & $\$$221,638.79 & ********** \\
-  III and IV Cuts Made & $\$$22,987.25 &$\$$207,997.54 & ********* \\
-  II, III, and IV Cuts Made & $\$$49,053.19 & $\$$181,931.60 & ********* \\
-
-\end{tabular}
 

### 2019-09-28 budget.tex
Budget rework for transport
Reduced reimbursement, updated budget and contingency, added spending margin

@@
 Gratuity is neglected as it is forbidden under the catering service’s policies, allowing us to save cost on meals.
-Under our most conservative estimates for budget and revenue, the spending margin is found to be 1.9\%.
-While this margin leaves little room for variation, we feel this is justified as several costs in the expenses, such as reimbursements, are left significantly inflated as compared with previous years.
-Adopting previous years’ estimates of \$60,000 for travel reimbursements leaves a spending margin of 24.2\%, matching that of the most austere contingency plans provided in previous years.
-Assuming maximum expenses and an attendance of 450 students, the total cost per student is estimated at \$513.30.
+Under our most conservative estimates for budget and revenue, the spending margin is found to be 4.13\%.
+While this margin is tight, we feel this is justified as several costs in the expenses, such as reimbursements, are left significantly inflated as compared with previous years.
+Adopting previous years’ estimates of \$60,000 for travel reimbursements leaves a spending margin of 21.6\%, matching that of the most austere contingency plans provided in previous years.
+Assuming maximum expenses and an attendance of 450 students, the total cost per student is estimated at \$501.63.
 This number also includes the travel reimbursement, which was intentionally set to be considerably more generous than previous years to make the budget more conservative.
-Neglecting the cost of travel reimbursements, the average cost per student falls to \$263.30, at or below that estimated for previous years.
+Neglecting the cost of travel reimbursements, the average cost per student falls to \$276.63, at or below that estimated for previous years.
 
@@
      & Argonne Tour              & II                        & $\$$ 875.00               & 1                         &     -                    &     -                     &     -                     & $\$$875.00               \\ \hline
-     &                           &                           &                           &                           &\multicolumn{3}{r}{Transport Subtotal:}      & $\$$12,125.00            \\ \hline\hline
+     &                           &                           &                           &                           &\multicolumn{3}{r}{Transport Subtotal:}      & $\$$18,125.00            \\ \hline\hline
      \multirow{5}{*}{\STAB{\rotatebox[origin=c]{90}{Food}}}
@@
      & Brewery Tour              & IV                        & $\$$ 5.00                 & 45                        &     -                    &     -                     &     -                     & $\$$275.00               \\
-     & Travel Reimbursements     & I                         & $\$$ 250.00               &  -                        &     -                    &                           &  450                      & $\$$112,500.00           \\ \hline
+     & Travel Reimbursements     & I                         & $\$$ 225.00               &  -                        &     -                    &                           &  450                      & $\$$101,250.00           \\ \hline
      &                           &                           &                           &                           &\multicolumn{3}{r}{Miscellaneous Subtotal:}                                       & $\$$126,857.90           \\ \hline\hline
      &                           &                           &                           &                           &                          &                           &                           &                          \\
-     &                           &                           &                           &                           &\multicolumn{3}{r}{Grand Total:}                                                  & $\$$236,984.79           \\
+     &                           &                           &                           &                           &\multicolumn{3}{r}{Grand Total:}                                                  & $\$$225,734.79           \\
      &                           &                           &                           &                           &                          &                           &                           &                          \\ \hline
@@
   \multicolumn{1}{l}{Level of Cuts Made} & \multicolumn{1}{c}{Amount Saved} & \multicolumn{1}{c}{Grand Total} & \multicolumn{1}{c}{\% of Max Revenue} \\ \hline\hline 
-  Priority IV Cuts Made & $\$$9,346.00 & $\$$227,638.79 & ********** \\
-  III and IV Cuts Made & $\$$22,987.25 &$\$$213,997.54 & ********* \\
-  II, III, and IV Cuts Made & $\$$49,053.19 & $\$$187,931.60 & ********* \\
+  Priority IV Cuts Made & $\$$9,346.00 & $\$$216,388.79 & 8.10\% \\
+  III and IV Cuts Made & $\$$22,987.25 &$\$$198,747.54 & 16.44\% \\
+  II, III, and IV Cuts Made & $\$$49,053.19 & $\$$176,681.60 & 24.97\% \\
 \end{tabular}
@@
 The average cost of this trip comes out to be \$293 as shown in Table *******.
-Adding this to the lodging costs for four nights (as students often arrive Wednesday evening) and assuming four students per room, the total cost of attendance for each student comes out to an average of \$412.
+Adding this to the registration and lodging costs for four nights (as students often arrive Wednesday evening) and assuming four students per room, the total cost of attendance for each student comes out to an average of \$447.
 

### 2019-09-28 management.tex
adds formatted exec board images and updates the bios

@@
 
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.35\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{dotsons2.jpg}
-	\end{center}
-\end{wrapfigure}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-dotson.jpg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
 	$\textbf{General Co-Chair - Sam Dotson}$\\
@@
 He helped set a record amount of donations at the 2016 CLC Foundation Gala, where he was an invited speaker and volunteer.
-He will be attending the ANS National conference in November 2019, as well as the ANS Student Conference 2020 at North Carolina State University.\\
+He will be attending the ANS National conference in November 2019, as well as the ANS Student Conference 2020 at North Carolina State University.
+\end{minipage}
 
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{mettlerj.jpg}
-	\end{center}
-\end{wrapfigure}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-mettler.jpg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
 	$\textbf{Technical Co-Chair - Jeremy Mettler}$\\
@@
 He is dedicated to making sure that future generations of students are able to have the same amazing experiences through ANS as he had, especially at the ANS Student Conference.
-Outside of ANS, he has held a summer internship at Oak Ridge National Lab, and is currently focusing his research towards combined laser-plasma systems for materials processing.\\
+Outside of ANS, he has held a summer internship at Oak Ridge National Lab, and is currently focusing his research towards combined laser-plasma systems for materials processing.
+\end{minipage}
 
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.35\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{ncreid2.jpg}
-	\end{center}
-\end{wrapfigure}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{ncreid2.jpg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
 $\textbf{Diversity Co-Chair - Nathan Reid}$\\
@@
 in Nuclear, Plasma, and Radiological Engineering from UIUC in 2016.
-He is currently attending UIUC as a 4th-year Ph.D.
+He is a 4th-year Ph.D.
 student in the field of fusion and plasma science and engineering under Prof.
 Jean Paul Allain.
-Nate is currently conducting his thesis research at Oak Ridge National Laboratory, where he has spent the last three summers working on a multitude of projects in the nuclear structural materials group.
-He focuses on the technological assessment of plasma facing materials such as advanced tungsten alloys and composites under the mentorship of Dr.
+Nate is currently conducting his thesis research at Oak Ridge National Laboratory, where he has spent the last three summers working in the nuclear structural materials group under the mentorship of Dr.
 Lauren Garrison.
-Nate has attended four of the last five ANS Student Conferences and was a student paper competition finalist at the TOFE embedded topical of the 2018 ANS Winter Meeting, presenting his work on glow-discharge optical emission spectroscopy of tungsten neutron-transmutation elements.
-Nate is recognized by the ANS section at UIUC for his outstanding graduate service in the last year, and served as the Women in Nuclear UIUC chapter Vice President.
+Nate has attended four of the last five ANS Student Conferences and was a student paper competition finalist at the TOFE embedded topical of the 2018 ANS Winter Meeting.
+Nate has been recognized by the ANS-UIUC for his outstanding graduate service in the last year, and served as the Women in Nuclear UIUC chapter Vice President.
 He was part of the executive team that received the national student chapter excellence award at the 2019 Women in Nuclear national conference, of which he was awarded a student sponsorship to attend.
-Nate is ecstatic about working alongside his ANS student section as Diversity Co-Chair and setting goals to bring inclusion to the conference.\\
-\clearpage
+Nate is ecstatic about working alongside his ANS student section as Diversity Co-Chair and setting goals to bring inclusion to the conference.
+\end{minipage}
 
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
-	\begin{center}
-		% \vspace{-\baselineskip}
-		\includegraphics[height=5.5cm]{stahlj.jpg}
-	\end{center}
-\end{wrapfigure}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-chee.jpg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
+$\textbf{Technical Subcommittee Chair - Gwen Chee}$\\
+	Gwen is a third year graduate student studying fuel cycles for advanced reactor designs with Dr.
+Kathryn Huff in the ARFC group.
+Last summer she had an internship at Argonne National Laboratory where she worked on (...) .She also serves as the president of the UIUC chapter of Women In Nuclear (WiN).
+Under her leadership, WiN-UIUC was honored with the Best Student Chapter award at the WiN National Meeting in 2019.
+She has also been involved with ANS and attended the 2018 ANS Student Conference in Florida and will be attending the upcoming ANS Student Conference at NC State in 2020.
+\end{minipage}
+
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-gaughan.JPG}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
+$\textbf{Logistics Chair - Natalie Gaughan}$\\
+	Natalie earned her B.S.
+in Nuclear Engineering from the University of Wisconsin-Madison in 2017.
+She has completed two summer internships at Argonne National Laboratory where she worked with various neutronics codes.
+Natalie then spent a year in Vienna as an intern at the International Atomic Energy Agency, where she helped organize and evaluate nuclear data for medical isotope production.
+She is now a graduate student at UIUC intending to research radiological science and nuclear medicine.
+As an undergraduate, Natalie attended two ANS student conferences which played a huge role in obtaining internships and inspired her decision to attend graduate school.
+Natalie knows firsthand how the ANS student conferences can be influential in students’ education and career development, and would love to help younger students experience the same benefits.
+She will also be attending the upcoming ANS student conference in 2020 at NC State.
+\end{minipage}
+
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-stahl.jpg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
 	$\textbf{Financial Chair - Jack Stahl}$
@@
 Jack hopes to help host a student conference that will bolster younger student involvement in ANS.
-\newline
-\vspace{1cm}
-\newline
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.35\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=5.5cm]{dinarij.jpg}
-	\end{center}
-\end{wrapfigure}
+\end{minipage}
+
+% \vspace{1cm}
+\clearpage
+\textbf{Financial Subcommittee}\\
+
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-shehee.jpg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
+	$\textbf{Sponsorship Coordinator - James Shehee}$\\
+Jimmy is a junior undergraduate student in UIUC's Nuclear, Plasma, and Radiological Engineering department, with a concentration in power, safety, and the environment.
+Jimmy has been an active member of the University's ANS student chapter since his freshman year, has held the positions of Secretary and External Vice President, and was chosen to receive the chapter's Undergraduate Outstanding Service Award in the spring of 2019.
+Jimmy was first introduced to the nuclear industry through the Nuclear Science Merit Badge in Boy Scouts, and he is excited about any opportunity to create similar experiences for students and the public.
+Outside of ANS, Jimmy is also the President of the Illini Venturing Crew.
+In the summer of 2019, Jimmy interned at Exelon's Quad Cities Generating Station, and will be returning for another summer in 2020.
+He is excited to attend his first ANS Student Conference in March 2020 at North Carolina State University.
+\end{minipage}
+
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-dinari.jpg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
 	$\textbf{Registration Coordinator - Jasmine Dinari}$\\
@@
 She gained organizational and leadership experience through various extracurriculars in high school and currently serves as the Professional Development Chair for the UIUC student chapter of Women in Nuclear.
-She plans on attending the 2020 ANS Student Conference at NC State.\\
+She plans on attending the 2020 ANS Student Conference at NC State.
+\end{minipage}
+
 \vspace{1cm}
+\textbf{Technical Subcommittee}\\
 
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{sheheej.jpg}
-	\end{center}
-\end{wrapfigure}
-$\textbf{Sponsorship Coordinator - James Shehee}$\\
-Jimmy is a junior undergraduate student in UIUC's Nuclear, Plasma, and Radiological Engineering department, with a concentration in power, safety, and the environment.
-Jimmy has been an active member of the University's ANS student chapter since his freshman year, has held the positions of Secretary and External Vice President, and was chosen to receive the chapter's Undergraduate Outstanding Service Award in the spring of 2019.
-Jimmy was first introduced to the nuclear industry through the Nuclear Science Merit Badge in Boy Scouts, and he is excited about any opportunity to create similar experiences for students and the public.
-Outside of ANS, Jimmy is also the President of the Illini Venturing Crew.
-In the summer of 2019, Jimmy interned at Exelon's Quad Cities Generating Station, and will be returning for another summer in 2020.
-He is excited to attend his first ANS Student Conference in March 2020 at North Carolina State University.\\
-
-\clearpage
-\vspace{1cm}
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.35\textwidth}
-	\begin{center}
-		% \vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{cheeg.jpg}
-	\end{center}
-\end{wrapfigure}
-$\textbf{Technical Subcommittee}$\\
-$\textbf{Technical Subcommittee Chair- Gwen Chee}$\\
-Gwen is a third year graduate student studying fuel cycles for advanced reactor designs with Dr.
-Kathryn Huff in the ARFC group.
-Last summer she had an internship at Argonne National Laboratory where she worked on (...) .She also serves as the president of the UIUC chapter of Women In Nuclear (WiN).
-Under her leadership, WiN-UIUC was honored with the Best Student Chapter award at the WiN National Meeting in 2019.
-She has also been involved with ANS and attended the 2018 ANS Student Conference in Florida and will be attending the upcoming ANS Student Conference at NC State in 2020.
-\\
-\vspace{1cm}
-\newline
-
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{fairhurstr.jpg}
-	\end{center}
-\end{wrapfigure}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-fairhurst.jpg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
 	$\textbf{Workshops Coordinator - Roberto Fairhurst}$\\
@@
 He believes hosting the student conference at UIUC will help the field grow and thrive.
-This is also an opportunity to meet other people working in the field, share life experiences, and develop a stronger network.\\
+This is also an opportunity to meet other people working in the field, share life experiences, and develop a stronger network.
+\end{minipage}
 
-\vspace{1cm}
-
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.45\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[width=0.43\textwidth]{jeckellz.png}
-	\end{center}
-\end{wrapfigure}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-jeckell.png}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
 $\textbf{Sessions Coordinator - Zachary Jeckell}$\\
@@
 He plans to attend the next ANS student conference at NC State to present research on chemical vapor deposition using atmospheric pressure plasma.
-\clearpage
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.25\textwidth}
-	\begin{center}
-		% \vspace{-\baselineskip}
-		\includegraphics[height=5cm]{golbag.jpg}
-	\end{center}
-\end{wrapfigure}
+\end{minipage}
+
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-golba.jpg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
 $\textbf{Career Fair Coordinator - Grzegorz Golba}$\\
@@
 He seeks new opportunities to engage with the nuclear science community and is excited for the possibilities of hosting a student conference at UIUC.
-\\
-\newline
+\end{minipage}
+
 \vspace{1cm}
-\newline
+\textbf{Non-Technical Subcommittee}\\
 
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.25\textwidth}
-	\begin{center}
-		% \vspace{-\baselineskip}
-		\includegraphics[height=6cm]{gaughann.JPG}
-	\end{center}
-\end{wrapfigure}
-$\textbf{Non-Technical Subcommittee}$\\
-$\textbf{Logistics Chair - Natalie Gaughan}$\\
-Natalie earned her B.S.
-in Nuclear Engineering from the University of Wisconsin-Madison in 2017.
-She has completed two summer internships at Argonne National Laboratory where she worked with various neutronics codes.
-Natalie then spent a year in Vienna as an intern at the International Atomic Energy Agency, where she helped organize and evaluate nuclear data for medical isotope production.
-She is now a graduate student at UIUC intending to research radiological science and nuclear medicine.
-As an undergraduate, Natalie attended two ANS student conferences which played a huge role in obtaining internships and inspired her decision to attend graduate school.
-Natalie knows firsthand how the ANS student conferences can be influential in students’ education and career development, and would love to help younger students experience the same benefits.
-She will also be attending the upcoming ANS student conference in 2020 at NC State.\\
-
-% \clearpage
-\vspace{0.5cm}
-
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.25\textwidth}
-	\begin{center}
-		% \vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{kdilan.jpg}
-	\end{center}
-\end{wrapfigure}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-dilan.jpg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
 	$\textbf{Program Coordinator - Dilan Kurukulasuriya}$\\
@@
 He is interested in fusion science research, specifically the materials interaction aspect.
-He also plans on attending the upcoming student conference at NC State in 2020.\\
+He also plans on attending the upcoming student conference at NC State in 2020.
+\end{minipage}
 
-\clearpage
-\vspace{1cm}
-
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.35\textwidth}
-	\begin{center}
-		% \vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{davisg.jpg}
-	\end{center}
-\end{wrapfigure}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-davis.jpg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
 $\textbf{Hotels and Transportation Coordinator - Gavin Davis}$\\
@@
 He looks forward to learning more about nuclear fission technology and to make advancements in nuclear science and in the nuclear energy sector as a whole.
-He looks forward to attending the student conference at NC State in 2020.\\
+He looks forward to attending the student conference at NC State in 2020.
+\end{minipage}
 
-\vspace{1cm}
-
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
-	\begin{center}
-		% \vspace{-\baselineskip}
-		\includegraphics[height=5cm]{moranb.jpg}
-	\end{center}
-\end{wrapfigure}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-moran.jpg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
 	$\textbf{Hospitality and Catering Coordinator - Brady Moran}$\\
@@
 He is confident that this experience will help him make the Student Conference a great success.
-He will be attending the 2020 conference at NC State.\\
-\newline
-\vspace{1cm}
-\newline
+He will be attending the 2020 conference at NC State.
+\end{minipage}
 
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.35\textwidth}
-	\begin{center}
-		% \vspace{-\baselineskip}
-		\includegraphics[height=5cm]{ballaa.jpg}
-	\end{center}
-\end{wrapfigure}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-balla.jpg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
 	$\textbf{Tours Coordinator - Anna Balla}$\\
@@
 Anna is a teaching assistant for two classes in the NPRE department and is also very involved with the Women in Nuclear chapter at Illinois.
-In her spare time, she enjoys going to concerts, playing volleyball, and wishing she knew how to juggle.\\
+In her spare time, she enjoys going to concerts, playing volleyball, and wishing she knew how to juggle.
+\end{minipage}
 
-\clearpage\vspace{1cm}
-% \newline
-
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
-	\begin{center}
-		% \vspace{-\baselineskip}
-		\includegraphics[height=5cm]{ryann.jpg}
-	\end{center}
-\end{wrapfigure}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-ryan.jpg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
 $\textbf{Media Coordinator - Nathan Ryan}$\\
@@
 He believes that an online presence for this event will supplement the success of an already great set of programs and individuals involved.
-He is excited to attend the upcoming ANS Student Conference at NC State in 2020.\\
-
-\vspace{1cm}
+He is excited to attend the upcoming ANS Student Conference at NC State in 2020.
+\end{minipage}
 

### 2019-09-28 main.tex
updates management
adds letter, moves title text up
adds gavin bio
general updates
New usepackages
updates main
changes the header to block I
changes title
updates org chart

@@
 \usepackage{subcaption}
+\usepackage{lipsum}
 \usepackage{wrapfig}
@@
 \usepackage{fancyhdr}
+\usepackage{pdfpages}
+\usepackage{multirow}
+\usepackage{array}
 % \usepackage{pagecounting}
 % \usepackage[dvips]{color}
-
-\newcommand{\illinoislogo}{\includegraphics[height=0.5in]{images/illinoislogo.png}}
+\newcommand{\STAB}[1]{\begin{tabular}{@{}c@{}}#1\end{tabular}}
+\newcommand{\illinoislogo}{\includegraphics[height=0.5in]{images/block-I.png}}
 \newcommand{\anslogo}{\hspace{-4mm}\includegraphics[height=0.5in]{images/ansuiuc.png}}
@@
 \usepackage{float}
-\usepackage[top=2cm, bottom=2.75cm, outer=2cm, inner=2cm]{geometry}
+\usepackage[top=2cm, bottom=2cm, outer=2cm, inner=2cm]{geometry}
 \setcounter{tocdepth}{3}
@@
 
-\tikzstyle{chair} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,thick, fill=blue!50, execute at begin node={\begin{varwidth}{2.5cm}},execute at end node={\end{varwidth}}]
-\tikzstyle{director} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=orange!70, execute at begin node={\begin{varwidth}{2.5cm}},execute at end node={\end{varwidth}}]
-\tikzstyle{coordinator} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=white!30, execute at begin node={\begin{varwidth}{2.5cm}},execute at end node={\end{varwidth}}]
+\tikzstyle{chair} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black,thick, fill=blue!50, execute at begin node={\begin{varwidth}{3.5cm}},execute at end node={\end{varwidth}}]
+\tikzstyle{director} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=orange!70, execute at begin node={\begin{varwidth}{3.5cm}},execute at end node={\end{varwidth}}]
+\tikzstyle{coordinator} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=white!30, execute at begin node={\begin{varwidth}{3.5cm}},execute at end node={\end{varwidth}}]
 % \tikzstyle{arrow} = [thick,--,>=stealth]
@@
 \begin{titlepage}
-\AddToShipoutPictureBG*{\includegraphics[angle=90, width=\paperwidth,height=\paperheight]{earth1.png}};
+\AddToShipoutPictureBG*{\includegraphics[angle=90,width=\paperwidth,height=\paperheight]{earth1.png}}
 
@@
 
-       \vspace*{0.25cm}
+       % \vspace{0.15cm}
 
@@
 
-       \vspace{0.3cm}
-       Nuclear, Plasma, and Radiological Engineering
+       % \vspace{0.1cm}
+       % Nuclear, Plasma, and Radiological Engineering
+       % \includegraphics[width=0.4\textwidth]{ans_sc_logo3.png}
 
        \vfill
-       \vspace{7.5cm}
+       \vspace{8.5cm}
 
@@
 
+\setlength{\headheight}{25pt}
 \pagestyle{fancy}
@@
 \rhead{\illinoislogo}
+% \renewcommand{\headrulewidth}{0pt} % no line in header area
+% \fancyhead{}
 
-\input{letter}
+\includepdf[pages=-]{./documents/chair_letter.pdf}
 
@@
 \input{conflog}
-\newpage
 \input{proglog}
@@
 \input{budget}
-\newpage
+% \newpage
 \input{liability}

### 2019-09-28 management.tex
updates org chart

@@
 
-		\node (log chair) [director, below of = gen chair, xshift = -2.5cm, yshift = -2cm] {Logistics Chair (Natalie Gaughan)};
-		\node (med coord) [coordinator, below of = gen chair, xshift = 1cm, yshift = -4cm] {Media Coordinator (Nathan Ryan)};
+		\node (log chair) [director, below of = gen chair, xshift = -3.75cm, yshift = -2cm] {Logistics Chair\\ (Natalie Gaughan)};
+		\node (med coord) [coordinator, below of = gen chair, xshift = 0.0cm, yshift = -3cm] {Media Coordinator (Nathan Ryan)};
 		\node (prog coord) [coordinator, below of = log chair, yshift = -2cm] {Program Coordinator (Dilan K.)};
 		\node (hat coord) [coordinator, below of = prog coord, yshift = -2cm] {Hotels and Transport (Gavin Davis)};
-		\node (hoa coord) [coordinator, below of = hat coord, yshift = -2cm] {Hospitality and Accomodations (Brady Moran)};
+		\node (hoa coord) [coordinator, below of = hat coord, yshift = -2cm] {Hospitality and Accomodations\\ (Brady Moran)};
 		\node (tours coord) [coordinator, below of = hoa coord, yshift = -2cm] {Tours Coordinator (Anna Balla)};
@@
 		\node (tsc chair) [director, below of = tech chair, xshift = 2cm, yshift = -2cm] {Technical Sub-Committee Chair (Gwen Chee)};
-		\node (work coord) [coordinator, below of = tsc chair, yshift = -2cm] {Workshops Coordinator (Roberto Fairhurst)};
+		\node (work coord) [coordinator, below of = tsc chair, yshift = -2cm] {Workshops Coordinator\\(Roberto Fairhurst)};
 		\node (sesh coord) [coordinator, below of = work coord, yshift = -2cm] {Sessions Coordinator (Zach Jeckell)};
@@
 
-		\node (fin chair) [director, below of = tech chair, xshift = -2cm, yshift = -2cm] {Financial Chair (Jack Stahl)};
+		\node (fin chair) [director, below of = tech chair, xshift = -2.25cm, yshift = -2cm] {Financial Chair\\(Jack Stahl)};
 		\node (spon coord) [coordinator, below of = fin chair, yshift = -2cm] {Sponsorships Coordinator (Jimmy Shehee)};
-		\node (reg coord) [coordinator, below of = spon coord, yshift = -2cm] {Registration Coordinator (Jasmine Dinari)};
+		\node (reg coord) [coordinator, below of = spon coord, yshift = -2cm] {Registration Coordinator\\(Jasmine Dinari)};
 

### 2019-09-28 conflog.tex
adds section about facility contingency
Dinner Descriptions

@@
 
+\textbf{The I Hotel and Conference Center}\\
+The IHotel offers a unique, flexible, meeting space and a variety of small touches that make any meeting, social gathering or event in Champaign-Urbana a flawless and memorable experience.\\
+
+\begin{figure}[H]
+    \centering
+    \includegraphics[width=0.8\textwidth]{ihotel.jpg}
+    \caption{I Hotel}
+    \label{fig:beckman}
+\end{figure}
+
 \newpage
@@
 \textbf{Thursday Night}\\
+Communicating the science of nuclear energy remains one of the chief challenges of our field, which is why the opening dinner of this conference will focus on science communication and the people behind the science.
+Science communication requires more than the recitation of raw data to be effective.
+By telling our own, diverse backstories, we become more effective science communicators.
+Speakers will be chosen which emphasize this fact and will be asked to speak to their own backstory as a nuclear advocate and how this story makes them a more effective communicator.
 \textbf{Friday Night}\\
+The second dinner will be themed around networking and professional-development, and how these critical tools have value beyond finding jobs.
+Communities like ANS thrive on the exchange of ideas and knowledge, and the student conference serves the vital role of connecting the burgeoning minds of the next generation with the wisdom of established professionals.
+This dinner will consist of tables organized by company/national lab to allow students and professionals to mingle, promoting the exchange of ideas.
 \textbf{Saturday Night}\\
-
+The closing dinner of the conference will be a call to action for student attendees.
+Ours is a generation faced with challenges on a scale never witnessed by humanity, and we will only successfully address these challenges through the engagement of as many bright young minds as possible.
+The speakers for this night will be asked to address ways we all can take individual responsibility for the grand challenges of our age, using our own unique skills to tackle problems like climate change and energy poverty from every angle imaginable.
 \subsection{Travel and Transportation}

### 2019-09-28 proglog.tex
makes updates
adds formatted speaker images and changes bio order
improves image placement and adds captions

@@
 
-\subsubsection{Rachel Slaybaugh, UC Berkeley}
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=15\baselineskip]{speaker-0.jpg}
-	\end{center}
-\end{wrapfigure}
-Prof.
-Slaybaugh's research is based in numerical methods for neutron transport with an emphasis on supercomputing.
-She applies these methods to reactor design, shielding, and nuclear security and nonproliferation.
-Slaybaugh was a key founder of the nuclear innovation bootcamp, which seeks to train students and professionals in skills essential to innovation in nuclear energy while executing team projects.
-Finally, Slaybaugh has served as a Program Director at ARPA-E, developing and running their first fission energy programs.
-Advanced Research Projects Agency-Energy (ARPA-E) invests in research for ways to generate, use, and store energy.
-These projects have the potential to radically improve economic prosperity in the U.S.
-and environmental wellbeing.
-Due to her endeavors in teaching and sharing nuclear innovation, we believe that Slaybaugh's goals are aligned with the goals of this conference and would make her an excellent addition to the program.
-Slaybaugh has much to offer the conference with her vision and leadership.\\
-\clearpage
+\subsubsection{Rita Baranwal, DOE Nuclear Energy}
 
-\subsubsection{Suzanne Hobbs Baker}
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=5.5cm]{speaker-1.jpeg}
-	\end{center}
-\end{wrapfigure}
-Talking about nuclear energy, specifically with the general public, is one of Suzanne Hobbs Baker's key goals.
-Baker has a strong track record as a nuclear science communicator.
-In 2008 she founded a nonprofit organization aimed at reaching women, minorities, and young people with critical information about climate change and nuclear energy.
-She currently works as the creative director for Fast Path to Zero Initiatve at the University of Michigan and as a Nuclear security fellow with Third Way Energy.
-Baker's work in empowering minorities and students to solve the world climate crisis with nuclear energy, as well as her skill in creative science communication, ensures that Baker has a lot to offer the student conference.
-Celebrating the people behind the science is one of the key goals of this conference and an area in which Baker has a lot of experience.\\
-
-\subsubsection{Todd Allen, UW Madison}
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=5.5cm]{speaker-6.jpeg}
-	\end{center}
-\end{wrapfigure}
-His first post-Ph.D.
-position was as a staff scientist at Argonne National Laboratory.
-While at Argonne, he joined the leadership team tasked with developing the Generation IV Roadmap, the document that framed the resurgence of the nuclear research programs early in the 21st Century.Following Argonne, he joined the faculty at the University of Wisconsin.
-While there, he split his time between establishing a premier material science program at the university and supporting the Idaho National Laboratory.
-At INL, he led the transition of the Advanced Test Reactor into a national user facility.
-He also ran a six-institution Energy Frontier Research Center focused on answering fundamental questions about heat transfer in nuclear fuel.
-From 2013-2016, he helped lead the Idaho National Laboratory as the Deputy Laboratory Director for Science $\&$ Technology, including being an important contributor to the development of the Gateway for Accelerated Innovation in Nuclear (GAIN) initiative announced at the White House in November 2015.
-Since 2016 he has been a Visiting Senior Fellow with Clean Energy Program at Third Way, a Washington, DC based think tank.
-His role in formulating the roadmap for Generation IV reactors and his leadership indicate that he would make a great speaker at the conference.\\
-
-\subsubsection{Rita Baranwal, DOE Nuclear Energy}
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=5.5cm]{speaker-5.jpg}
-	\end{center}
-\end{wrapfigure}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-baranwal.jpg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
 	Dr.
@@
 Under her leadership, GAIN positively impacted over 120 companies.
-Baranwal is a clear choice of speaker to discuss the ways to improve nuclear legislation and how companies can rapidly develop new nuclear technology.\\
+Baranwal is a clear choice of speaker to discuss the ways to improve nuclear legislation and how companies can rapidly develop new nuclear technology.
+\end{minipage}
 
-\subsubsection{Jim Conca, Forbes}
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=5cm]{speaker-3.jpeg}
-	\end{center}
-\end{wrapfigure}
-Jim Conca has been a scientist in the field of the earth and environmental sciences for 33 years, specializing in geologic disposal of nuclear waste, energy-related research, planetary surface processes, radiobiology and shielding for space colonies, subsurface transport and environmental clean-up of heavy metals.
-He is a Trustee of the Herbert M.
-Parker Foundation, Adjunct at WSU, an Affiliate Scientist at LANL and consult on strategic planning for the DOE, EPA/State environmental agencies, and industry including companies that own nuclear, hydro, wind farms, large solar arrays, coal and gas plants.
-He also writes for Forbes magazine about nuclear issues, energy, and the environment.
-Conca has a strong vision for the future and is not shy about coming up with ideas to solve grand challenge problems.
-In addition to his experience and ambition, he is an excellent science communicator to scientists and non-scientists alike.
-Together, these factors make him an ideal speaker at the conference.
+\subsubsection{Rachel Slaybaugh, UC Berkeley}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-slaybaugh.jpg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
+	Prof.
+Slaybaugh's research is based in numerical methods for neutron transport with an emphasis on supercomputing.
+She applies these methods to reactor design, shielding, and nuclear security and nonproliferation.
+Slaybaugh was a key founder of the nuclear innovation bootcamp, which seeks to train students and professionals in skills essential to innovation in nuclear energy while executing team projects.
+Finally, Slaybaugh has served as a Program Director at ARPA-E, developing and running their first fission energy programs.
+Advanced Research Projects Agency-Energy (ARPA-E) invests in research for ways to generate, use, and store energy.
+These projects have the potential to radically improve economic prosperity in the U.S.
+and environmental wellbeing.
+Due to her endeavors in teaching and sharing nuclear innovation, we believe that Slaybaugh's goals are aligned with the goals of this conference and would make her an excellent addition to the program.
+Slaybaugh has much to offer the conference with her vision and leadership.
+\end{minipage}
 
 \subsubsection{William Magwood}
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=5cm]{magwoodw.jpeg}
-	\end{center}
-\end{wrapfigure}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-magwood.jpeg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
 	Mr.
@@
 Magwood has remained committed to his promise to carry out his responsibilities ``in a manner that earns the public's trust, and always doing the right thing even when the right thing isn't easy.''
+\end{minipage}
 
 \subsubsection{Phi Nguyen, Former Vice President and Director of Engineering at Intel}
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=5cm]{nguyenp.png}
-	\end{center}
-\end{wrapfigure}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-nguyen.png}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
 Phi Nguyen, is a UIUC alumni from the NPRE department and went on to a major leadership role at the Intel corporation.
@@
 As the former Director of Engineering at Intel, Phi Nguyen is the perfect person to talk about how this important research helps solve big problems.
-\clearpage
+
+\end{minipage}
+
+\subsubsection{Suzanne Hobbs Baker}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-baker.jpeg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
+	Talking about nuclear energy, specifically with the general public, is one of Suzanne Hobbs Baker's key goals.
+Baker has a strong track record as a nuclear science communicator.
+In 2008 she founded a nonprofit organization aimed at reaching women, minorities, and young people with critical information about climate change and nuclear energy.
+She currently works as the creative director for Fast Path to Zero Initiatve at the University of Michigan and as a Nuclear security fellow with Third Way Energy.
+Baker's work in empowering minorities and students to solve the world climate crisis with nuclear energy, as well as her skill in creative science communication, ensures that Baker has a lot to offer the student conference.
+Celebrating the people behind the science is one of the key goals of this conference and an area in which Baker has a lot of experience.
+\end{minipage}
+
+\subsubsection{Todd Allen, UW Madison}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-allen.jpeg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
+	His first post-Ph.D.
+position was as a staff scientist at Argonne National Laboratory.
+While at Argonne, he joined the leadership team tasked with developing the Generation IV Roadmap, the document that framed the resurgence of the nuclear research programs early in the 21st Century.Following Argonne, he joined the faculty at the University of Wisconsin.
+While there, he split his time between establishing a premier material science program at the university and supporting the Idaho National Laboratory.
+At INL, he led the transition of the Advanced Test Reactor into a national user facility.
+He also ran a six-institution Energy Frontier Research Center focused on answering fundamental questions about heat transfer in nuclear fuel.
+From 2013-2016, he helped lead the Idaho National Laboratory as the Deputy Laboratory Director for Science $\&$ Technology, including being an important contributor to the development of the Gateway for Accelerated Innovation in Nuclear (GAIN) initiative announced at the White House in November 2015.
+Since 2016 he has been a Visiting Senior Fellow with Clean Energy Program at Third Way, a Washington, DC based think tank.
+His role in formulating the roadmap for Generation IV reactors and his leadership indicate that he would make a great speaker at the conference.
+\end{minipage}
+
+% \clearpage
+\subsubsection{Jim Conca, Forbes}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-conca.jpeg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
+	Jim Conca has been a scientist in the field of the earth and environmental sciences for 33 years, specializing in geologic disposal of nuclear waste, energy-related research, planetary surface processes, radiobiology and shielding for space colonies, subsurface transport and environmental clean-up of heavy metals.
+He is a Trustee of the Herbert M.
+Parker Foundation, Adjunct at WSU, an Affiliate Scientist at LANL and consult on strategic planning for the DOE, EPA/State environmental agencies, and industry including companies that own nuclear, hydro, wind farms, large solar arrays, coal and gas plants.
+He also writes for Forbes magazine about nuclear issues, energy, and the environment.
+Conca has a strong vision for the future and is not shy about coming up with ideas to solve grand challenge problems.
+In addition to his experience and ambition, he is an excellent science communicator to scientists and non-scientists alike.
+Together, these factors make him an ideal speaker at the conference.
+\end{minipage}
+
+% \clearpage
 \subsubsection{Ross Radel, CEO Phoenix, LLC}
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=5.5cm]{radel.png}
-	\end{center}
-\end{wrapfigure}
-Ross is the CEO and a Board of Directors member of Phoenix.
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-radel.png}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
+	Ross Radel is the CEO and a Board of Directors member of Phoenix.
 He holds a MS and a PhD in Nuclear Engineering from the University of Wisconsin-Madison.
@@
 We believe Dr.
-Radel would be a great speaker for the future of nuclear technology.\\
+Radel would be a great speaker for the future of nuclear technology.
+\end{minipage}
 
 \subsubsection{Greg Piefer, CEO SHINE}
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.35\textwidth}
-	\begin{center}
-		\vspace{-\baselineskip}
-		\includegraphics[height=5.5cm]{piefer.jpg}
-	\end{center}
-\end{wrapfigure}
+\begin{minipage}{0.25\textwidth}
+	\centering
+	\includegraphics[width=\textwidth]{fmt-piefer.jpg}
+\end{minipage}
+\begin{minipage}{0.73\textwidth}
 	Dr.
@@
 His passion is the growth of technology companies that take scientific advancement to commercialization, providing the opportunity to serve and better humanity.
-Piefer's goals are perfectly attuned to the goals of this conference and he would be an excellent speaker on the powerful applications of radiological engineering.\\
+Piefer's goals are perfectly attuned to the goals of this conference and he would be an excellent speaker on the powerful applications of radiological engineering.
+\end{minipage}
 
@@
 It will be held in Illini Rooms A \& B, a large space that will be shared with the poster sessions on saturday to encourage students and professionals to attend both.
-Recruiters may mail bulkier items prior to their arrival in Champaign.\\
-
+Recruiters may mail bulkier items prior to their arrival in Champaign.
 All companies that sponsor the conference will be given a table at the career fair.
 Location will be decided in order of sponsorship amount and when the agreement was made.
-Universities may freely request a table at the career fair, while space is available.\\
-
+Universities may freely request a table at the career fair, while space is available.
 There will be rooms available at the Illini Union for companies to interview potential candidates.
@@
 Out of the 61 commercially operating nuclear power plants and 99 nuclear reactors in the U.S., Illinois is home to six nuclear power stations and eleven active reactors.
-Being located in a state with numerous power plants, as well as being surrounded by locations of interest to a variety of nuclear-related disciplines, the touring opportunities at the University of Illinois mirror the diversity of UIUC’s Nuclear Plasma and Radiological Engineering program.\\
+Being located in a state with numerous power plants, as well as being surrounded by locations of interest to a variety of nuclear-related disciplines, the touring opportunities at the University of Illinois mirror the diversity of UIUC’s Nuclear Plasma and Radiological Engineering program.
 
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.5\textwidth}
-	\begin{center}
-		% \vspace{-\baselineskip}
-		\includegraphics[width=0.48\textwidth]{argonne.png}
-	\end{center}
-\end{wrapfigure}
+\begin{minipage}{0.5\textwidth}
 \textbf{Argonne National Laboratory}\\
@@
 Bus transportation will be provided.
-On the tour, students will be guided around the site’s scientific and engineering facilities.\\
+On the tour, students will be guided around the site’s scientific and engineering facilities.
+\end{minipage}
+\begin{minipage}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{argonne.png}
+	\captionof{figure}{Argonne National Laboratory}
+\end{minipage}
 
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.45\textwidth}
-	\begin{center}
-		% \vspace{-\baselineskip}
-		\includegraphics[height=5.5cm]{clintonpp.jpg}
-	\end{center}
-\end{wrapfigure}
-\textbf{Clinton Power Station}\\
+\begin{minipage}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{clintonpp.jpg}
+	\captionof{figure}{Clinton Powerplant on Clinton Lake}
+\end{minipage}
+\begin{minipage}{0.5\textwidth}
+	\textbf{Clinton Nuclear Power Plant}\\
 Located about 35 miles away from Champaign, the Clinton Power Station is an Exelon owned nuclear power plant that started operating at full power on September 15th, 1987.
@@
 Attendees will be guided by a Clinton employee.
-The tour will include the control-room simulator that operator trainees use, and a chance to learn more about the site’s innovative safety, operation, and engineering practices.\\
+The tour will include the control-room simulator that operator trainees use, and a chance to learn more about the site’s innovative safety, operation, and engineering practices.
+\end{minipage}
 
-\clearpage
+\begin{minipage}{0.5\textwidth}
+	\textbf{National Pentascale Computing Facility (NPCF)}\\
+Also located on campus is NCSA, which houses Blue Waters, one of the most powerful supercomputers in the world.
+The NCSA is within walking distance from all conference hotels.
+During the tour, attendees will tour the machine room and witness some of the beautiful results it produces.
+Supercomputers like Blue Waters are important for solving computationally challenging problems and creating robust simulations for a variety of phenomena.
+\end{minipage}
+\begin{minipage}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{bw_front.png}
+	\captionof{figure}{Blue Waters Supercomputer}
+\end{minipage}
+
 \textbf{Starfire Industries LLC}\\
@@
 Starfire’s collaboration with government agencies and propensity for solving big problems related to plasma engineering make them a great place to learn about plasma processing applications.\\
-
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.48\textwidth}
-	\begin{center}
-		% \vspace{-\baselineskip}
-		\includegraphics[height=5.5cm]{bw_front.png}
-	\end{center}
-\end{wrapfigure}
-\textbf{National Center for Supercomputing Applications (NCSA)}\\
-Also located on campus is NCSA, which houses Blue Waters, one of the most powerful supercomputers in the world.
-The NCSA is within walking distance from all conference hotels.
-During the tour, attendees will tour the machine room and witness some of the beautiful results it produces.
-Supercomputers like Blue Waters are important for solving computationally challenging problems and creating robust simulations for a variety of phenomena.\\
 
@@
 
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{L}{0.4\textwidth}
-	\begin{center}
-		% \vspace{-\baselineskip}
-		\includegraphics[width=0.38\textwidth]{riggs.jpg}
-		\caption{Riggs Brewery}
-	\end{center}
-\end{wrapfigure}
-\setlength\intextsep{0pt}
-\begin{wrapfigure}{R}{0.43\textwidth}
-	\begin{center}
-		% \vspace{-\baselineskip}
-		\includegraphics[width=0.4\textwidth]{triptych.jpeg}
-		\caption{Triptych Brewery}
-	\end{center}
-\end{wrapfigure}
+\begin{minipage}{0.5\textwidth}
+	% \centering
 	\textbf{Riggs Brewery Tour}\\
@@
 Transportation to and from the brewery will be provided.
-\\
+\end{minipage}
+\begin{minipage}{0.55\textwidth}
+	\centering
+	\includegraphics[width=0.75\textwidth]{riggs.jpg}
+	\captionof{figure}{Riggs Brewery}
+\end{minipage}
 
+\begin{minipage}{0.5\textwidth}
+	\centering
+	\includegraphics[width=0.75\textwidth]{triptych.jpeg}
+	\captionof{figure}{Triptych Brewery Vessels -- Not RPVs}
+\end{minipage}
+\begin{minipage}{0.5\textwidth}
+% \centering
 	\textbf{Triptych Brewery Tour}\\
@@
 Triptych is located in Savoy, IL, just 15 minutes from campus.
-Transportation to and from the brewery will be provided.\\
-\newline
-\newline
-\newline
-% \vspace{3cm}
-\newline
-\newline
+Transportation to and from the brewery will be provided.
+\end{minipage}
+
+\begin{minipage}{0.5\textwidth}
 	\textbf{University Tour}\\
@@
 There are also many other historical artifacts on display for participants to see.
-Afterwards, students will be led to various noteworthy locations unique to UIUC.\\
+Afterwards, students will be led to various noteworthy locations unique to UIUC.
+\end{minipage}
+\begin{minipage}{0.5\textwidth}
+	\centering
+	\includegraphics[width=0.75\textwidth]{creek.png}
+	\captionof{figure}{Engineering Hall on the Beautiful Engineering Quad}
+\end{minipage}
+\\
 

### 2019-09-28 management.tex
updates management

@@
 Kathryn Huff in the ARFC group.
-Last summer she had an internship at Argonne National Laboratory where she worked on (...) .She also serves as the president of the UIUC chapter of Women In Nuclear (WiN).
+Last summer she had an internship at Argonne National Laboratory where she worked on sensitivity analysis of the nuclear fuel complex.She also serves as the president of the UIUC chapter of Women In Nuclear (WiN).
 Under her leadership, WiN-UIUC was honored with the Best Student Chapter award at the WiN National Meeting in 2019.
@@
 \begin{minipage}{0.73\textwidth}
-	$\textbf{Financial Chair - Jack Stahl}$
+	$\textbf{Financial Chair - Jack Stahl}$\\
 Jack graduated with a B.S.

### 2019-09-29 conflog.tex

@@
 By telling our own, diverse backstories, we become more effective science communicators.
-Speakers will be chosen which emphasize this fact and will be asked to speak to their own backstory as a nuclear advocate and how this story makes them a more effective communicator.
+Speakers will be chosen which emphasize this fact and will be asked to speak to their own backstory as a nuclear advocate and how this story makes them a more effective communicator.\\
 \textbf{Friday Night}\\
@@
 Communities like ANS thrive on the exchange of ideas and knowledge, and the student conference serves the vital role of connecting the burgeoning minds of the next generation with the wisdom of established professionals.
-This dinner will consist of tables organized by company/national lab to allow students and professionals to mingle, promoting the exchange of ideas.
+This dinner will consist of tables organized by company/national lab to allow students and professionals to mingle, promoting the exchange of ideas.\\
 \textbf{Saturday Night}\\
@@
 Ours is a generation faced with challenges on a scale never witnessed by humanity, and we will only successfully address these challenges through the engagement of as many bright young minds as possible.
-The speakers for this night will be asked to address ways we all can take individual responsibility for the grand challenges of our age, using our own unique skills to tackle problems like climate change and energy poverty from every angle imaginable.
+The speakers for this night will be asked to address ways we all can take individual responsibility for the grand challenges of our age, using our own unique skills to tackle problems like climate change and energy poverty from every angle imaginable.\\
 \subsection{Travel and Transportation}

### 2019-09-29 theme.tex

@@
 Students will hear from visionary speakers and leaders of the nuclear science community and come away with optimism for the future; knowing that they are saving the world one atom at a time.\\
+There are three main goals of our theme and each of these goals will be the focus of a different day of the student conference.
+\begin{enumerate}
+	\item Celebrate the people behind the science\\
+	Everyone that does science has a unique background, skillset, and experiences.
+People are what make science possible.
+Encouraging diversity and inclusivity in these areas, and others, improve creativity, productivity, and insights.
+We showcase this aspect of the conference with panels like \textit{Science is People: How to Conduct Inclusive Research} and \textit{Scientific Storytelling}.
+	\item Help students and professionals develop a strong network of like-minded people.\\
+	This is the networking and professional-development-focused section of the conference.
+Beyond the mere job-seeking aspect, these networks enable the spread of ideas.
+Additionally, this night builds on top of the previous night as we remember that our networks also consist of people.
+Better networks are more diverse.
+This aspect of the conference is captured by workshops like \textit{Developing Your Network}.
+	\item Inspire young students to take on grand challenge problems\\
+	The final day is the culmination of the conference and the single unifying ideal.
+For many students, this conference might be the first time they are presenting research to their peers, mentors, and future employers.
+Everything about this conference should encourage students to take on challenges that seem bigger than they are in order to better the world around them.
+\end{enumerate}
+These goals and our theme motivated every decision in our conference proposal.
 The University of Illinois at Urbana-Champaign chapter of ANS would be honored to host the 2021 student conference.
 We hope to create an atmosphere that will galvanize students and professionals for the exciting future of nuclear engineering.\\
-
-Goals of the conference
-\begin{enumerate}
-	\item Celebrate the people behind the science
-	\item Inspire young students to take on grand challenge problems
-	\item Help students and professionals develop a strong network of like-minded people. 
-\end{enumerate}

### 2019-09-30 socials.tex
adds short barn dance section
adds barn dance desc and pics

@@
 This space can accompany up to 150 people, with extra tables outside of the Rec Room for socializing, playing board games, or having a late night snack or coffee with professionals or students from other universities.
-
+\vspace{0.5cm}\newline
 % Illini Union Rec Room Picture
@@
 	\end{subfigure}	
+	\caption{Illini Union Rec Room}	
 \end{figure}
@@
 This is the perfect event to incorporate a little bit of Illinois history with music, dancing, and socializing!
-
+\vspace{0.5cm}\newline
 % 77 Club Picture
 \begin{figure}[H]
+
 	\centering
@@
 	\end{subfigure}
+	\caption{77 Club at Memorial Stadium}		
 \end{figure}
 
-\subsubsection{Pour Bros. Taproom in Downtown Champaign}
-Welcome to Illinois' first pour-your-own taprooms.
+%%% Reserve for Pour Bros. social %%%
+%\subsubsection{Pour Bros. Taproom in Downtown Champaign}
+%Welcome to Illinois' first pour-your-own taprooms.
 Pour Bros.
@@
 If you are feeling more on the leisurely side, Pour Bros features live music in a spacious and comfortable seating area for you to get your networking on.
+%\vspace{0.5cm}\newline
+%% Pour Bros Picture
+%\begin{figure}[H]
+%
+%	\centering
+%	\begin{subfigure}{0.5\textwidth}
+%		\centering
+%		\includegraphics[width=0.5\linewidth]{pour_bros2.png}
+%	\end{subfigure}%
+%	\begin{subfigure}{0.5\textwidth}
+%		\centering
+%		\includegraphics[width=0.9\linewidth]{pour_bros1.png}
+%	\end{subfigure}	
+%	\caption{Pour Brothers Taproom}	
+%\end{figure}
 
-% Pour Bros Picture
+\subsubsection{Barn Dance: A Proud Midwestern Tradition}
+Barn dances are a staple event at UIUC.
+Socialize in a unique environment with games of corn-hole and other midwestern fun.
+Various barns are used for dancing and mingling by many of the student organizations on UIUC campus, such as Farm Lake barn which hosts dozens of barn dances annually.
+Other barns may be best suited for the student conference social events, such as Hudson Farm, which offers a corporate event or professional social events option which can accommodate up to 300 guests with an alcohol service available and friendly, helpful service.
+Like socials in the past student conferences, the barn may be used and a third party service can be hired to bring the square dance, swing dance, two step and cowboy boogie to the barn dance floor!
+\vspace{0.5cm}\newline
+% Barn Dance Hudson Picture
 \begin{figure}[H]
@@
 		\centering
-		\includegraphics[width=0.5\linewidth]{pour_bros2.png}
+		\includegraphics[width=0.9\linewidth]{barn_dance1.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=0.9\linewidth]{pour_bros1.png}
+		\includegraphics[width=0.9\linewidth]{barn_dance2.png}
 	\end{subfigure}	
+	\caption{Hudson Farm Barn.}	
 \end{figure}
@@
 Snacks and concession items are also available.
-
+\vspace{0.5cm}\newline
 % Ice Arena Picture
@@
 	\includegraphics[width=0.8\textwidth]{ice_arena.png}
+	\caption{The UIUC Ice Arena}
 \end{figure}

### 2019-09-30 conflog.tex
updates from Katy

@@
 
-We propose the conference be held on the following dates: 
+We propose the conference be held on either of the following dates: 
 \begin{enumerate}
@@
 The opening ceremony dinner on Thursday night will be hosted at the Garden Hotel in Urbana.
-They have a capacity of 600 people in rounds and offer in house catering as well as AV capabilities.
+It has a seating capacity of 600 people in rounds and offer in house catering as well as AV capabilities.
 This location was chosen for its convenience, as it would be the primary hotel for the conference.
@@
 
-\subsubsection{IHotel}
-Dinner on Friday night will be hosted at the IHotel.
-The IHotel is undergoing an expansion that will increase the capacity of their banquet space to 690 people in rounds.
+\subsubsection{I Hotel}
+Dinner on Friday night will be hosted at the I Hotel.
+The I Hotel is undergoing an expansion that will increase the capacity of their banquet space to 690 people in rounds.
+Catering is provided by University Catering which avoids a 20\% gratuity charge because of its association with the University of Illinois.
 This expansion is set to be completed by Fall 2020.
 We will be hosting a social at the 77 Club in Memorial Stadium, just up the street.
-Information about the IHotel expansion is included in Appendix D.
+Information about the I Hotel expansion is included in Appendix D.
 
@@
 After the career fair is taken down on Saturday the final dinner will be set up in the combined Illini Rooms, which has a seating capacity of 496 people in rounds.
-Catering will be provided by Universiy Catering which allows us to avoid the 20\% gratuity for services.\\
+Catering will be provided by Universiy Catering which allows us to avoid the 20\% gratuity for services.
+A floorplan for the Illini Rooms in rounds is available in Appendix D.\\
 
@@
 In the event that the Union has reduced availability during the conference we have the ability to host technical sessions and workshops at a combination of buildings: The National Center for Supercomputing Applications (NCSA) and Beckman Institute.
-These two buildings have large capacity rooms and small capacity rooms.
+Rooms in Beckman Institute range from 20 - 60 classroom capacity.
+Most rooms have A/V capabilities.
+NCSA has rooms that can hold 13 - 50 people in lecture style.
 As these buildings are UIUC property, the cost of renting them are significantly reduced compared to a private facility.
 Additionally, these two buildings are adjacent to one another and are at most a 10 minute walk from the Union.
-We could also host all technical sessions at the IHotel.
-Hosting at the IHotel is more expensive than hosting in University buildings and would also require additional transportation options.
+We could also host all technical sessions at the I Hotel.
+Hosting at the I Hotel is more expensive than hosting in University buildings and would also require additional transportation options.
 We would need to reevaluate some parts of our budget in order to host the technical program at this venue.
@@
 
-\textbf{Beckman Institute}
+\textbf{Beckman Institute}\\
 The Beckman Institute for Advanced Science and Technology at the University of Illinois is an interdisciplinary research institute devoted to leading-edge research in the physical sciences, computation, engineering, biology, behavior, cognition, and neuroscience.\\
@@
 Marriott TowneSuites &0.25 & 4/8-4/11 & 95 & 189 & \$47.50\\ 
+\hline
 \end{tabular}}
@@
 Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus several times per day.
-Below are the round-trip, non-stop, airfare costs for the first weekend of April.
+Table \ref{table:airfare} shows the round-trip, non-stop, airfare costs for the first weekend of April.
 Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip.
+Due to the central location of UIUC, driving might be a good option for some schools and individuals.
+Table \ref{table:ground} shows the approximate driving times and costs from several universities.
 
-\begin{center}
+\begin{table}[H]
+\caption{Estimated Costs of Ground Travel}
+\label{table:ground}
+   \begin{tabular}{lcccc}
+   \hline\hline
+   \textbf{School}&\textbf{Estimated Mileage (mi)}&\textbf{Driving Time (hrs)}&\textbf{Fuel Cost*}&\textbf{Per Person**}\\
+   \hline\hline
+    Purdue University&90&1h 40m&\$21.86&\$5.47\\
+    University of Cincinnati&233& 3h 40m&\$56.60&\$14.15\\
+    Air Force Tech &250&3h 58m&\$60.73&\$15.18\\
+    University of Wisconsin&253&4h&\$61.46&\$15.36\\
+    Missouri University S \& T &279&4h 21m&\$67.77&\$16.94\\
+    U. Missouri - Columbia&291&4h 28m&\$70.69&\$17.67\\
+    Ohio State University&302&4h 47m&\$73.36&\$18.34\\
+    University of Michigan&345&5h 17m&\$83.81&\$20.95\\
+    Vanderbilt University&373&5h 33m&\$90.61&\$22.65\\
+    Iowa State University&378&5h 44m&\$91.82&\$22.96\\
+    \hline
+    Average&279&4h 22m&\$67.87&\$16.97
+
+    \end{tabular} 
+\end{table}
+\noindent\textbf{*}\textit{Estimated assuming an average 23 MPG}\\
+\textbf{**}\textit{Assumes four people in a car}
+
+\subsubsection{Getting to the Conference}
+The primary hotel, Garden Hotel Urbana, is approximately two miles from the Union and outside of reasonable walking distance.
+Thus we have budgeted to include transportation provided by Peoria Charter.
+We intend to have busses shuttling continuously between the Union and the Garden Hotel Urbana.
+For those who desire more flexibility and freedom, there is CU-MTD bus stop adjacent to the hotel that has a bus every 10 minutes.
+This bus route, the 22 Illini, can take attendees directly to the Union from the hotel.
+It is also one of the main campus bus routes and can take travelers almost anywhere on or around campus.
+Lyft and Uber are available as well for attendees that choose to use those services.
+A map of the bus route is in Appendix E: Campus Map of Locations.
+
+\begin{table}[H]
+\caption{Airfare to Chicago/Champaign}
+\label{table:airfare}
    \begin{tabular}{lccc}
@@
     \end{tabular} 
-\end{center}
-\textbf{*}\textit{A \$61 round-trip bus ticket through Peoria Charter was added to the cost.}\\
+\end{table}
+
+\noindent\textbf{*}\textit{A \$61 round-trip bus ticket through Peoria Charter was added to the cost.}\\
 \textbf{**}\textit{The average of the lowest price between O'Hare and Willard.}\\
-
-Due to the central location of UIUC, driving might be a good option for some schools and individuals. Below are the approximate driving times from several universities.
-
-\begin{center}
-   \begin{tabular}{lcccc}
-   \hline\hline
-   \textbf{School}&\textbf{Estimated Mileage (mi)}&\textbf{Driving Time (hrs)}&\textbf{Fuel Cost*}&\textbf{Per Person**}\\
-   \hline\hline
-    Purdue University&90&1h 40m&\$21.86&\$5.47\\
-    University of Cincinnati&233& 3h 40m&\$56.60&\$14.15\\
-    Air Force Tech &250&3h 58m&\$60.73&\$15.18\\
-    University of Wisconsin&253&4h&\$61.46&\$15.36\\
-    Missouri University S \& T &279&4h 21m&\$67.77&\$16.94\\
-    U. Missouri - Columbia&291&4h 28m&\$70.69&\$17.67\\
-    Ohio State University&302&4h 47m&\$73.36&\$18.34\\
-    University of Michigan&345&5h 17m&\$83.81&\$20.95\\
-    Vanderbilt University&373&5h 33m&\$90.61&\$22.65\\
-    Iowa State University&378&5h 44m&\$91.82&\$22.96\\
-    \hline
-    Average&279&4h 22m&\$67.87&\$16.97
-
-    \end{tabular} 
-\end{center}
-\textbf{*}\textit{Estimated assuming an average 23 MPG}\\
-\textbf{**}\textit{Assumes four people in a car}
-
-\subsubsection{Getting to the Conference}
-The primary hotel, Garden Hotel Urbana, is approximately two miles from the Union and outside of reasonable walking distance.
-Thus we have budgeted to include transportation provided by Peoria Charter.
-We intend to have busses shuttling continuously between the Union and the Garden Hotel Urbana.
-For those who desire more flexibility and freedom, there is CU-MTD bus stop adjacent to the hotel that has a bus every 10 minutes.
-This bus route, the 22 Illini, can take attendees directly to the Union from the hotel.
-It is also one of the main campus bus routes and can take travelers almost anywhere on or around campus.
-Lyft and Uber are available as well for attendees that choose to use those services.
-A map of the bus route is in Appendix E: Campus Map of Locations.

### 2019-09-30 theme.tex
updates from Katy

@@
 \section{Saving the World One Atom at a Time}
-The future is nuclear.\\
-There are many challenges facing the world today and some have been designated existential threats to humanity.
+The future is nuclear.
+There are many grand challenges facing the world today and some have been designated existential threats to humanity.
 Young people today will witness the growing toll of anthropogenic climate change.
@@
 We believe that many solutions will come from the nuclear sciences.
-The ANS Student Conference is an opportunity for students and professionals to come together and share advances in critical technology and research, dedicated to solving these problems.
-Nuclear, plasma, and radiological engineering will be central to many endeavors.
-Whether the goal is solving the world’s energy needs, developing technology that will take us to the stars, or curing cancer.
-By hosting this conference, we hope to inspire and motivate students in nuclear, plasma, and radiological engineering fields to tackle big problems.
+The ANS Student Conference is an opportunity for students and professionals to come together and share advances in critical technology and research dedicated to solving these problems.
+Nuclear, plasma, and radiological engineering will be central to many endeavors, whether the goal is solving the world’s energy needs, developing technology that will take us to the stars, or curing cancer.
+By hosting this conference, we hope to inspire and motivate students in nuclear, plasma, and radiological engineering to tackle big problems.
 Saving the World One Atom at a Time reflects the fact that nuclear science is a powerful force in dealing with grand challenge problems.
 This theme also honors the individual, atomic, contributions from students, researchers, and professionals that are essential to progress.
-This conference is about science and it is about the people that make science possible.
+This conference is about science and engineering and it is about the people that make science possible.
 Students will hear from visionary speakers and leaders of the nuclear science community and come away with optimism for the future; knowing that they are saving the world one atom at a time.\\
@@
 \begin{enumerate}
-	\item Celebrate the people behind the science\\
+	\item Celebrate the people behind the science and engineering.\\
 	Everyone that does science has a unique background, skillset, and experiences.
@@
 Beyond the mere job-seeking aspect, these networks enable the spread of ideas.
-Additionally, this night builds on top of the previous night as we remember that our networks also consist of people.
-Better networks are more diverse.
+Additionally, this evening builds on top of the previous night as we remember that our networks also consist of people.
+More diverse networks are better networks.
 This aspect of the conference is captured by workshops like \textit{Developing Your Network}.
-	\item Inspire young students to take on grand challenge problems\\
-	The final day is the culmination of the conference and the single unifying ideal.
+	\item Inspire the next generation of nuclear engineers to take on grand challenge problems\\
+	The final day is the culmination of the conference underpins the single unifying ideal.
 For many students, this conference might be the first time they are presenting research to their peers, mentors, and future employers.
-Everything about this conference should encourage students to take on challenges that seem bigger than they are in order to better the world around them.
+Everything about this conference should encourage students to take on challenges that seem bigger than they are in order to improve the world around them.
 \end{enumerate}

### 2019-09-30 uiuc.tex
updates from Katy

@@
 \subsection{Champaign-Urbana in a Nutshell}
-%Champaign-Urbana (CU) is a close-knit community filled with music, culture, and food.
-While Campustown, the neighborhood immediately surrounding campus,  is an important part of the atmosphere, there is plenty to do off campus.
-Relax in one of the outdoor restaurants downtown or walking through the various gardens and parks around town.
-The culture in Champaign is very rich as a result of many annual festivals such as the CU Pride Parade, the Ellnora guitar festival, and the Pygmalion festival.
-The Krannert Center for the Performing Arts is also a world-renowned theater that has hosted groups from all genres like the New York Philharmonic, the Russian National Ballet, and Sonny Rollins.
-
 Champaign-Urbana (CU), colloquially known as Chambana, is home to the state's flagship school, the University of Illinois at Urbana-Champaign (UIUC).
@@
     \includegraphics[width=0.33\textwidth]{chm1.png}
+    \caption{Downtown Champaign}
   \end{center}
@@
 
-Illinois relies heavily on nuclear power to supply its energy needs with 52$\%$ of electricity generated by nuclear plants.
+The state of Illinois relies heavily on nuclear power to supply its energy needs with 52$\%$ of electricity generated by nuclear plants.
 The first human controlled nuclear reaction, Chicago Pile One, happened in Illinois.
@@
 A large number of these hotels are located around downtown Champaign and the Eastern side of campus, making transportation easy.
-Champaign-Urbana Mass Transit (CU-MTD) is a reliable public transportation service that sees millions of rides every year.
+Champaign-Urbana Mass Transit (CU-MTD) is a reliable public transportation service that sees millions of riders every year.
+CU-MTD charges an affordable rate of \$1 per ride.
 All CU-MTD busses are wheelchair accessible.
-There is also a small airport, Willard Airport, just 20 minutes from campus that has regular flights to and from Chicago O’Hare and Dallas Fort Worth airports.
+Rental bikes and rideshare services are also plentiful.
+There is a small airport, Willard Airport, just 20 minutes from campus that has regular flights to and from Chicago O’Hare and Dallas Fort Worth airports.
 Finally, Peoria Charter is a popular bus service with several daily trips between the UIUC campus and the Chicagoland area.
@@
 \subsubsection{Weather}
-With an average high temperature of 65$^{\circ}$ and an average low temperature of 40$^{\circ}$, April in Champaign is a gorgeous month of dwindling winter weather as summer begins to round the corner.
+With an average high temperature of 65$^{\circ}$ and an average low temperature of 40$^{\circ}$, April in Champaign is a gorgeous month of dwindling winter weather and spring coming into bloom.
 Holding a conference during this time would be the perfect way to showcase our beautiful city.
@@
     \includegraphics[width=0.44\textwidth]{alma.jpg}
+    \caption{Alma Mater accompanied by Learning and Labor}
   \end{center}
@@
 Including John Bardeen, the only scientist to ever win the award twice.
-It also offers 15 different majors to more than 9,100 undergraduate and 3,400 graduate students.
+It also offers 15 different majors to almost 6000 undergraduate and 2500 graduate students.
 Of its twelve ranked majors, nine are ranked among the top 10 in the nation, and six of which remain ranked among the top 5 in their degree.
 Overall, the College of Engineering in Urbana-Champaign ranks sixth among the nation’s best undergraduate engineering programs.
-With more than 250 degrees for undergraduates and graduates and a multitude of first-class research facilities and resource, UIUC gives its 45,000 students the ability to succeed.
+With more than 250 degrees for undergraduates and graduates and a multitude of first-class research facilities and resource, UIUC gives its nearly 45,000 students the ability to succeed.
 
@@
 It also engages in education and outreach programs to teach members of the surrounding community about nuclear science.
-One of our most popular outreach programs is Engineering Open House (EOH), during which ANS won best exhibit.
+One of our most popular outreach programs is Engineering Open House (EOH), during which ANS-UIUC repeatedly earns awards for best presentation of a socieyt.
 EOH is an annual event where members of the local community, from young children to senior adults, visit the engineering campus to learn more about STEM research.Membership is currently around 70-80 students and has been steadily growing.
@@
 \subsection{Research at UIUC}
-Faculty in NPRE conduct research in many areas of interest to the nuclear science community.
-Students are highly encouraged to participate and make their own atomic contributions that will someday save the world.
+Faculty and students in NPRE conduct research in many areas of interest to the nuclear science community.
+Both graduate and undergraduate  students actively participate and make their own atomic contributions that will someday save the world.
 
@@
 Safety starndards and maintenance for existing reactors and new reactor designs are also explored by faculty in the department.
-Cross-cutting areas of research include multi-physics and multi-scale modeling and simulation, high performance computing, reliability and risk, validation and verification, and uncertainty analysis.
+Crosscutting areas of research include multi-physics and multi-scale modeling and simulation, high performance computing, reliability and risk, validation and verification, and uncertainty analysis.
 Recently, the University of Illinois declared a plan to be completely carbon-neutral by 2050.
-Nuclear power is the perfect candidate to help UIUC attain its energy goals.
+Nuclear power is the perfect candidate to help UIUC attain its carbon reduction and energy goals.
 Together, the University and the NPRE department are saving the world one atom at at time.
@@
     \includegraphics[width=0.48\textwidth]{hidra.png}
-    \caption{HIDRA}
+    \caption{The Hybrid Illinois Device for Research and Application (HIDRA)}
   \end{center}
 \end{wrapfigure}
-The research theme of Fusion and Plasma Physics in the NPRE department has a long history of work in the area of magnetic and inertial nuclear fusion as well as plasma engineering.
+The Fusion and Plasma Physics research theme in the NPRE department has a long history of work in the area of magnetic and inertial nuclear fusion as well as plasma engineering.
 NPRE is now one of the leading departments in plasma-material interactions with its Center for Plasma-Materials Interactions established by Prof.
@@
 There are five research themes that spans the work in fusion and plasma physics: fusion materials, plasma-material interface (PMI) diagnostics, plasma-edge and PMI modeling, plasma nanosynthesis, and plasma sources and processing.
-The Hybrid Illinois Device for Research and Application (right) marks the newest addition to the team at CPMI.
+The Hybrid Illinois Device for Research and Application (HIDRA) marks the newest addition to the team at CPMI.
 This device finished construction and achieved first plasma during the spring of 2016.
@@
 \subsubsection{Materials Science}
+Materials science research includes investigations of the mechanical properties of cladding and other structural components, and heat exchanger materials.
+Advanced microanalysis techniques are often employed to perform nano-scale interrogation of deformation, precipitation, and chemical segregation studies, for example.
+Ion beam bombardment of materials often runs concurrent with these techniques to simulate fast neutron displacement cascade damage.
+Fuel performance modeling, molecular dynamics, and kinetic Monte Carlo simulations complement these experimental activities.
+The Department also has strong efforts related to the study of nuclear fuel such as urania, including mass transport and mechanical property studies.
+The Department also studies hydrogen in metals, including hydride phase formation and solute dislocation pipe diffusion.
 
@@
 \begin{itemize}
-  \item \textbf{Advanced Reactors and Fuel Cycles (ARFC)} - \textit{Dr. Katy Huff}\\
+  \item \textbf{Advanced Reactors and Fuel Cycles (ARFC)} - \textit{Dr. Kathryn Huff}\\
   The ARFC group seeks to advance the safety and sustainability of nuclear energy production through improved reactor designs, fuel cycle strategies, and waste management techniques.
@@
 Our work in SPECT has also challenged the limits of aperture sensitivity through the engineering of the compound-eye aperture.
+
+  \item \textbf{Laboratory: Multiphase Thermo-fluid Dynamics Lab} - \textit{Dr. Caleb Brooks}\\
+  This group performs experiments related to thermal hydraulics and multiphase flow.
+Phenomena studied include boiling, condensation, critical heat flux, natural circulation, two-phase flow instabilities, bubble dynamics, and two-phase transport.
+Utilizing advanced instrumentation, data from these experiments are used in model development and validation of computational tools.
 \end{itemize}

### 2019-09-30 proglog.tex
adds mccarthy

@@
 
-\subsubsection{Todd Allen, UW Madison}
+\subsubsection{Cathy McCarthy, Canadian Nuclear Laboratories}
 \begin{minipage}{0.25\textwidth}
 	\centering
-	\includegraphics[width=\textwidth]{fmt-allen.jpeg}
+	\includegraphics[width=\textwidth]{fmt-mccarthy.jpg}
 \end{minipage}
 \begin{minipage}{0.73\textwidth}
-	His first post-Ph.D.
-position was as a staff scientist at Argonne National Laboratory.
-While at Argonne, he joined the leadership team tasked with developing the Generation IV Roadmap, the document that framed the resurgence of the nuclear research programs early in the 21st Century.Following Argonne, he joined the faculty at the University of Wisconsin.
-While there, he split his time between establishing a premier material science program at the university and supporting the Idaho National Laboratory.
-At INL, he led the transition of the Advanced Test Reactor into a national user facility.
-He also ran a six-institution Energy Frontier Research Center focused on answering fundamental questions about heat transfer in nuclear fuel.
-From 2013-2016, he helped lead the Idaho National Laboratory as the Deputy Laboratory Director for Science $\&$ Technology, including being an important contributor to the development of the Gateway for Accelerated Innovation in Nuclear (GAIN) initiative announced at the White House in November 2015.
-Since 2016 he has been a Visiting Senior Fellow with Clean Energy Program at Third Way, a Washington, DC based think tank.
-His role in formulating the roadmap for Generation IV reactors and his leadership indicate that he would make a great speaker at the conference.
+	Dr.
+Kathy McCarthy joined CNL as the Vice-President of Research and Development in 2017.
+Kathy has also held the position of Director of the US Department of Energy Light Water Reactor Sustainability Program Technical Integration Office.
+Her team, made up of scientists and engineers from across the US, conducted and guided important research that enabled power companies to be able to make informed decisions regarding long-term operation broadly, and second licence renewal specifically, for their operating nuclear units.
+Her expertise, leadership and contributions to the nuclear science and technology community are globally recognized, having received the American Nuclear Society Presidential Citation (2015, 2007), and the Partnership for Science \& Technology Nuclear Energy Advocate of the Year Award (2011), among many others.
+Her many contributions to the nuclear industry indicate that she would make a great speaker at this confrence.
 \end{minipage}
@@
 
-% \clearpage
-\subsubsection{Ross Radel, CEO Phoenix, LLC}
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-radel.png}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-	Ross Radel is the CEO and a Board of Directors member of Phoenix.
+% % \clearpage
+% \subsubsection{Ross Radel, CEO Phoenix, LLC}
+% \begin{minipage}{0.25\textwidth}
+% 	\centering
+% 	\includegraphics[width=\textwidth]{fmt-radel.png}
+% \end{minipage}
+% \begin{minipage}{0.73\textwidth}
+% 	Ross Radel is the CEO and a Board of Directors member of Phoenix.
 He holds a MS and a PhD in Nuclear Engineering from the University of Wisconsin-Madison.
@@
 Radel would be a great speaker for the future of nuclear technology.
-\end{minipage}
+% \end{minipage}
 
@@
 
-\subsubsection{Applications for Plasma Processing}
+\subsubsection{Plasma Processing in Your Pocket}
 Plasma processing has become a staple in many fields of advanced manufacturing.

### 2019-09-30 proglog.tex
updates program logistics

@@
 We have a several groups on campus researching, simulating, and modelling microreactors.
-Faculty leading these groups would be excellent speakers on this panel.
+Faculty leading these groups such as Dr.
+Caleb Brooks and Dr.
+Kathryn Huff would be excellent speakers on this panel.
 
@@
 In this panel, representatives from companies at the cutting-edge of plasma processing research will discuss how plasmas continue to revolutionize contemporary industry.
-Potential panelists include Brian Jurczyk, CEO of Starfire Industries, and Phi Nguyen, former Vice President and Director of Engineering at Intel Corp.
+Potential panelists include Brian Jurczyk, CEO of Starfire Industries, and David Ruzic, Professor of NPRE and Principle Investigator of CPMI.
 
@@
 One of the largest remaining obstacles to fusion energy is the unprecedented strain placed on the materials from which fusion reactors are built.
-This panel will focus on the latest advancements in plasma facing components research and could feature panelists such as Professor David Ruzic, director of the UIUC Center for Plasma-Material Interactions, and Dr.
+This panel will focus on the latest advancements in plasma facing components research and could feature panelists such as Professor Dan Andruczyk, director of the UIUC Center for Plasma-Material Interactions, and Dr.
 Lauren Garrison, Weinberg Fellow at ORNL.
@@
 This panel will allow attendees to learn who is working in this area and develop a network of people devoted to issues of nuclear policy.
-Rita Baranwal would be an excellent speaker on this panel because of her work for the DOE.
+Leadership of the GAIN program would make excellent panelists to discuss policy.
 
@@
 This panel will illuminate some of those applications and show attendees what could be possible with radiological technology.
-Speakers may include Greg Piefer from SHINE and Ross Radel from Phoenix.\\
+Speakers may include and Ross Radel from Phoenix and Professor DiFulvio from UIUC.\\
 
@@
 This panel works toward the goal of celebrating the people behind the science.
-It also serves to inspire students and
+It also serves to inspire students and professionals to consider how diversity plays a role in their research.
 
-\subsubsection{Talking To Non-Scientists}
+\subsubsection{Effective and Unorthodox Science Communication}
 It has been shown that when members of the general public are given more scientific evidence they are less likely to shift their beliefs.
 While this finding is surprising to members of the scientific community, people who value data and evidence, it can be difficult to find ways to effectively communicate your research to the public.
-Attendees will learn how other scientists effectively communicate their results.
-No longer discouraged by potential resistance from the public, students will steel their resolve for working on ambitious projects that can save the world.
-Suzanne Hobbs Baker would be a great choice for this panel, as well as members of The Story Collider; a non-profit organization devoted to helping scientists tell stories that
+Professor Paul Kwiat of the Physics Department at UIUC has taken science communication in an entirely new direction.
+He owns and operates Lab Escape, a popular escape room in Urbana.
+Kwiat along with members of the Story Collider, non-profit organization devoted to helping scientists tell stories that will resonate with their audiences, would make an excellent panel on unusual methods of science communication.
 
@@
 This panel is for students by students.
-We will discuss our process from writing a successful proposal to executing a successful conference.
+Students from other schools will be able to ask questions and gain insights for their own conference hosting process.
 
@@
 The Advanced Reactors and Fuel Cycles (ARFC) research group at UIUC and its collaborators will provide instructors.
-This workshop, alpha-tested at the University of Wisconsin will be aimed at students who can provid their own laptops and have a desire to improve their nuclear computational skills.
+This workshop, alpha-tested at the University of Wisconsin will be aimed at students who can provide their own laptops and have a desire to improve their nuclear computational skills.
 The workshop will be approximately two hours of instruction at NCSA room 1030.
@@
 We expect a total of 48 technical sessions each with 4-5 presenters.
-There will be an award for best graduate and best undergraduate presentation for each category.
+Where possible, students will be awarded with funds donated by the technical divisions of ANS.
 
@@
 There will be an award for best graduate and undergraduate poster.
+A layout of the rooms are available in Appendix D: Building Layout.
+
 \subsubsection{Highschool Poster Session}
@@
 The career will be held all day on Friday, from 8am to 5pm, and on Saturday from 8am to noon.
-It will be held in Illini Rooms A \& B, a large space that will be shared with the poster sessions on saturday to encourage students and professionals to attend both.
-Recruiters may mail bulkier items prior to their arrival in Champaign.
+It will be held in Illini Rooms A \& B, a large space capable of holding 600 people.
+This space will be immediately adjacent to the poster sessions on saturday to encourage students and professionals to attend both.
+Together, the Illini Rooms can hold up to 900 people.
+Recruiters can mail bulkier items prior to their arrival in Champaign.
 All companies that sponsor the conference will be given a table at the career fair.
@@
 
+\noindent{
+\begin{minipage}{0.5\textwidth}
+	\textbf{National Pentascale Computing Facility (NPCF)}\\
+Also located on campus is NCSA, which houses Blue Waters, one of the most powerful supercomputers in the world.
+The NCSA is within walking distance from all conference hotels.
+During the tour, attendees will tour the machine room and witness some of the beautiful results it produces.
+Supercomputers like Blue Waters are important for solving computationally challenging problems and creating robust simulations for a variety of phenomena.
+\end{minipage}
+\begin{minipage}{0.5\textwidth}
+	\includegraphics[width=\textwidth]{bw_front.png}
+	\captionof{figure}{Blue Waters Supercomputer}
+\end{minipage}
+}
+
+\textbf{Starfire Industries LLC}\\
+Starfire Industries is located at the south end of campus and works with federal organizations such as DARPA, Homeland Security, NASA, and others.
+They offer services in areas like neutron radiography, fabrication, and prototyping.
+Students will be able to get to the site by using the MTD busses that run continuously throughout the day and will be free to all conference attendees.
+Here, students will be able to learn more about Starfire products such as the IMPULSE pulsed power module, plasma sources, thin film systems, nGen neutron generators, neutron detectors, and the PICTORIS neutron radiography system.
+Starfire’s collaboration with government agencies and propensity for solving big problems related to plasma engineering make them a great place to learn about plasma processing applications.\\
+
+\noindent{
 \begin{minipage}{0.5\textwidth}
@@
 	\captionof{figure}{Argonne National Laboratory}
-\end{minipage}
+\end{minipage}}
 
+\noindent{
 \begin{minipage}{0.5\textwidth}
@@
 The tour will include the control-room simulator that operator trainees use, and a chance to learn more about the site’s innovative safety, operation, and engineering practices.
-\end{minipage}
-
-\begin{minipage}{0.5\textwidth}
-	\textbf{National Pentascale Computing Facility (NPCF)}\\
-Also located on campus is NCSA, which houses Blue Waters, one of the most powerful supercomputers in the world.
-The NCSA is within walking distance from all conference hotels.
-During the tour, attendees will tour the machine room and witness some of the beautiful results it produces.
-Supercomputers like Blue Waters are important for solving computationally challenging problems and creating robust simulations for a variety of phenomena.
-\end{minipage}
-\begin{minipage}{0.5\textwidth}
-	\includegraphics[width=\textwidth]{bw_front.png}
-	\captionof{figure}{Blue Waters Supercomputer}
-\end{minipage}
-
-\textbf{Starfire Industries LLC}\\
-Starfire Industries is located at the south end of campus and works with federal organizations such as DARPA, Homeland Security, NASA, and others.
-They offer services in areas like neutron radiography, fabrication, and prototyping.
-Students will be able to get to the site by using the MTD busses that run continuously throughout the day and will be free to all conference attendees.
-Here, students will be able to learn more about Starfire products such as the IMPULSE pulsed power module, plasma sources, thin film systems, nGen neutron generators, neutron detectors, and the PICTORIS neutron radiography system.
-Starfire’s collaboration with government agencies and propensity for solving big problems related to plasma engineering make them a great place to learn about plasma processing applications.\\
+\end{minipage}}
 
@@
 
-\begin{minipage}{0.5\textwidth}
+\noindent{\begin{minipage}{0.5\textwidth}
 	% \centering
@@
 	\captionof{figure}{Riggs Brewery}
-\end{minipage}
+\end{minipage}}
 
+\noindent{
 \begin{minipage}{0.5\textwidth}
@@
 Transportation to and from the brewery will be provided.
-\end{minipage}
+\end{minipage}}
 
-\begin{minipage}{0.5\textwidth}
+\noindent{\begin{minipage}{0.5\textwidth}
 	\textbf{University Tour}\\
@@
 	\captionof{figure}{Engineering Hall on the Beautiful Engineering Quad}
-\end{minipage}
+\end{minipage}}
 \\

### 2019-09-30 conflog.tex
adds quotes, and general updates

@@
 In this case we found that holding the conference at the end of April would conflict with finals for students and holding it earlier in March would conflict with several spring breaks as well as having potentially poorer weather.
-A detailed conflict schedule is listed in Appendix A.
+A detailed conflict schedule is listed in Appendix A on page \pageref{appendix:schedule}.
 
@@
 We will keep the space open to allow the poster sessions and career fair to share attendance and encourage networking.
-A detailed list of room capacities and floor plans are located in Appendix D: Building Layout.
+A detailed list of room capacities and floor plans are located in Appendix D: Building Layout on page \pageref{appendix:building}.
 \\
@@
 We would need to reevaluate some parts of our budget in order to host the technical program at this venue.
-See Appendix E for a map marking the locations of the proposed conference facilities.\\
+See Appendix E on page \pageref{appendix:map} for a map marking the locations of the proposed conference facilities.\\
 
@@
 The Garden Hotel Urbana (soon to be the Radisson) will be the primary hotel for all attendees.
-Since this hotel is just beyond walking distance from the main conference activities, regular transportation to and from the Union will be provided during peak commuting hours (8am-10am $\&$ 3pm-5pm).
+This will also be the location of the opening ceremony dinner.
+Since this hotel is just beyond walking distance from the main conference activities, we will hire four Peoria Charter busses to shuttle attendees to and from the Union every 10 minutes.
 Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 8am to 6pm.
-This will also be the location of the opening ceremony dinner.\\
+\\
 \begin{figure}[H]
@@
 
-{\centering
-\begin{tabular}{lccccc}
+\begin{table}
+\caption{Cost of Hotels}
+\label{table:hotels}
+	\centering
+	\makebox[0.6\linewidth]{\begin{tabular}{lccccc}
 	\hline\hline
@@
 	\end{tabular}}
+\end{table}
 \textbf{*}\textit{Price for a queen double}
@@
 \subsubsection{Lunch}
+Conference attendees are encouraged to explore the University’s campus and surroundings, including getting lunch on the main street of campus, Green street.
+Due to this, lunch will not be provided for the conference.
+However, box lunches will be provided for the Student Sections Committee meeting from 11:30pm to 1:30pm on Friday as well as any lunch and learns hosted by sponsors on Friday and Saturday.
+The Illini Union’s catering service, University Catering, will be used.
+Sponsors can also choose to sponsor and host a lunch in one of the technical session rooms on Friday or Saturday.
+If more rooms are required, there are available rooms on the first and second floor of the Union.
+Sponsors will be able to use University Catering, or cater from one of the food vendors in the Illini Union.
 \subsubsection{Dinner}
@@
 Lyft and Uber are available as well for attendees that choose to use those services.
-A map of the bus route is in Appendix E: Campus Map of Locations.
+A map of the bus route is in Appendix E: Campus Map of Locations on page \pageref{appendix:map}.
 
@@
     Kansas State University & Manhattan (MHK) & $\$$336 & $\$$406 \\ 
-    Louisiana State University & Baton Roughe (BTR) & $\$$380 & $\$$329 \\
+    Louisiana State University & Baton Rouge (BTR) & $\$$380 & $\$$329 \\
     United States Naval Academy & Hanover (BWI) & $\$$210 & $\$$321 \\  
@@
     University of New Mexico &Albuquerque (ABQ) &$\$$439 &$\$$358 \\ 
-    City College of New York &$\$$New York (JFK) &$\$$245 &$\$$325 \\
+    City College of New York &\$New York (JFK) &$\$$245 &$\$$325 \\
     Excelsior College & Albany (ALB) &$\$$444 &$\$$327 \\ 

### 2019-09-30 proglog.tex
adds quotes, and general updates

@@
 \begin{minipage}{0.5\textwidth}
-	\textbf{National Pentascale Computing Facility (NPCF)}\\
+	\textbf{National Petascale Computing Facility (NPCF)}\\
 Also located on campus is NCSA, which houses Blue Waters, one of the most powerful supercomputers in the world.

### 2019-09-30 uiuc.tex
adds quotes, and general updates

@@
 UIUC also bears a long tradition of nuclear power research and was home to the TRIGA nuclear reactor for almost 40 years.
-During this time researchers at UIUC made contributed to the knowledge store of nuclear reactor kinetics, isotope production, fission fragment physics, and much more.
+During this time researchers at UIUC contributed to the knowledge store of nuclear reactor kinetics, isotope production, fission fragment physics, and much more.
 Now, UIUC is exploring ways to use nuclear power to accelerate its decarbonization efforts.
@@
 \subsubsection{Accessibility and Accomodation}
-Myriad festivals and sporting events on campus draw many people to Champaign-Urbana at various of the year, which means hotels are not hard to find.
-A large number of these hotels are located around downtown Champaign and the Eastern side of campus, making transportation easy.
+ A large number of hotels are located around downtown Champaign and the Eastern side of campus, making transportation easy.
 Champaign-Urbana Mass Transit (CU-MTD) is a reliable public transportation service that sees millions of riders every year.

### 2019-09-30 uiuc.tex
adds advisor letter, fixes headheight which was squashing the page numbers, and adds some more text for a couple of missing labs. Finally, adds faculty photos

--- 2019-09-30 uiuc.tex
@@
 Both graduate and undergraduate  students actively participate and make their own atomic contributions that will someday save the world.
+Research programs in Nuclear, Plasma, and Radiological Engineering at the University of Illinois at Urbana-Champaign can be
+broadly classified into five areas:
+\begin{itemize}
+        \item \textbf{Nuclear Power} (reactor physics, thermalhydraulics, fuel cycle, radiation transport, I\&C)
+        \item \textbf{Plasma and Fusion} (modeling, plasma-material interactions)
+        \item \textbf{Radiological Sciences} (detectors, imaging, health physics, medical applications)
+        \item \textbf{Material Science} (nuclear fuels, structural materials)
+        \item \textbf{Risk and Policy} (PRA, safety, energy, arms controls, disarmament, security)
+\end{itemize}
+
+These research areas are supported by a stellar faculty and world-class facilities, which 
+will be briefly described below.
 
@@
 \subsubsection{NPRE Research Groups and Laboratories}
+The faculty, pictured in Figure \ref{fig:faculty} support the above areas of 
+expertise in the collaborations and facilites discussed below.
+
+\begin{figure}[htbp]
+        \begin{center}
+                \includegraphics[width=0.75\textwidth]{./images/full.png}
+                \includegraphics[width=0.6\textwidth]{./images/associate.png}
+                \includegraphics[width=0.6\textwidth]{./images/assistant.png}
+                \includegraphics[width=0.3\textwidth]{./images/research.png}
+        \end{center}
+        \caption{Faculty in Nuclear, Plasma, and Radiological Engineering  at 
+        the University of Illinois at Urbana-Champaign.}
+        \label{fig:faculty}
+\end{figure}
+
 \begin{itemize}
@@
 Utilizing advanced instrumentation, data from these experiments are used in model development and validation of computational tools.
+  \item \textbf{Laboratory: Nuclear Measurements Laboratory} - \textit{Dr.
+Angela DiFulvio}\\ The lab is equipped with a Cf-252 source and a D-T neutron generator with an emission rate of ~1E7 and ~1E8 neutrons/s, respectively.
+The neutron flux density is well-characterized in energy and intensity employing various instruments, including multisphere spectrometers, ionization chambers, long counters, and scintillators, calibrated to primary reference standards, which enable the detection of neutrons via scattering of protons or via fission of uranium nuclei.
 \end{itemize}

### 2019-09-30 budget.tex
general updates

@@
 \subsection{Expenses}
-A conservative breakdown of conference expenses is outlined in Table ******* on page *******.
-Emphasizing some of the points shown in the table, all rooms hosted in the Union are provided to registered student organizations (such as ANS) free of charge, which allows us to save significantly on event space.
+A conservative breakdown of conference expenses is outlined in Table \ref{table:budget} on page \pageref{table:budget}.
+All rooms hosted in the Union are provided to registered student organizations (such as ANS-UIUC) free of charge.
+This allows us to save significantly on event space.
 Meals catered through the University catering service reflect a 6.25\% sales tax in the total cost which is not represented in the unit cost.
-Gratuity is neglected as it is forbidden under the catering service’s policies, allowing us to save cost on meals.
+Gratuity is neglected because it is forbidden under the catering service’s policies, allowing us to save 20\% gratuity on meals.
 Under our most conservative estimates for budget and revenue, the spending margin is found to be 4.13\%.
@@
 Neglecting the cost of travel reimbursements, the average cost per student falls to \$276.63, at or below that estimated for previous years.
+In Appendix \ref{appendix:quotes} on page \pageref{appendix:quotes} there are quotes from Peria Charter and the Union to give some sense of costs.
 
-\hspace{-1.1cm}
+% \hspace{-1.1cm}
+\begin{table}[H]
+    \caption{Budget Expenses}
+    \label{table:budget}
+    \makebox[\linewidth]{
         \begin{tabular}{|clcrccccr|}
@@
         \hline
-     & \multicolumn{1}{c}{Item} & \multicolumn{1}{c}{Priority} & \multicolumn{1}{c}{Cost Per Unit} & \multicolumn{1}{c}{Thursday} & \multicolumn{1}{c}{Friday} & \multicolumn{1}{c}{Saturday} & \multicolumn{1}{c}{General} & \multicolumn{1}{c}{Total Cost}\\     \hline\hline
-     \multirow{10}{*}{\STAB{\rotatebox[origin=c]{90}{Facilities}}}
+         & \multicolumn{1}{c}{\textbf{Item}} & \multicolumn{1}{c}{\textbf{Priority}} & \multicolumn{1}{c}{\textbf{Cost Per Unit}} & \multicolumn{1}{c}{\textbf{Thursday}} & \multicolumn{1}{c}{\textbf{Friday}} & \multicolumn{1}{c}{\textbf{Saturday}} & \multicolumn{1}{c}{\textbf{General}} & \multicolumn{1}{c}{\textbf{Total Cost}}\\     \hline\hline
+         \multirow{10}{*}{\STAB{\rotatebox[origin=c]{90}{\textbf{Facilities}}}}
          & Technical Session AV      & I                         & $\$$ 13.80                & 1                         & 6                        & 6                         & -                         & $\$$179.40               \\
@@
          &                           &                           &                           &                           &\multicolumn{3}{r}{Facilities Subtotal:}     & $\$$12,286.20            \\ \hline\hline
-     \multirow{5}{*}{\STAB{\rotatebox[origin=c]{90}{Transport}}}
+         \multirow{5}{*}{\STAB{\rotatebox[origin=c]{90}{\textbf{Transport}}}}
          & Shuttles From Hotel       & I                         & $\$$ 1,000.00             & 4                         & 4                        & 4                         & -                         & $\$$12,000.00            \\
@@
          &                           &                           &                           &                           &\multicolumn{3}{r}{Transport Subtotal:}      & $\$$18,125.00            \\ \hline\hline
-     \multirow{5}{*}{\STAB{\rotatebox[origin=c]{90}{Food}}}
+         \multirow{5}{*}{\STAB{\rotatebox[origin=c]{90}{\textbf{Food}}}}
          & Coffee/Tea                & III                       & $\$$ 1.95                 & -                         & 600                      & 600                       & -                         & $\$$2,486.25             \\
@@
          &                           &                           &                           &                           &\multicolumn{3}{r}{Food Subtotal:}           & $\$$70,255.69            \\ \hline\hline
-     \multirow{5}{*}{\STAB{\rotatebox[origin=c]{90}{Socials}}}
+         \multirow{5}{*}{\STAB{\rotatebox[origin=c]{90}{\textbf{Socials}}}}
          & Ice Skating               & III                       & $\$$ 240.00               & 2                         & -                        & -                         & -                         & $\$$480.00               \\
@@
          &                           &                           &                           &                           &\multicolumn{3}{r}{Socials Subtotal:}        & $\$$9,462.00             \\ \hline\hline
-     \multirow{7}{*}{\STAB{\rotatebox[origin=c]{90}{Miscellaneous}}}
+         \multirow{7}{*}{\STAB{\rotatebox[origin=c]{90}{\textbf{Miscellaneous}}}}
          & Conference Programs       & I                         & $\$$ 2,133.90             & -                         & -                        & -                         & 1                         & $\$$2,133.90             \\
@@
          &                           &                           &                           &                           &                          &                           &                           &                          \\ \hline
-\end{tabular}
+    \end{tabular}}
+\end{table}
 
@@
 
-\begin{tabular}{lrrr}
+\begin{table}
+    \caption{Budget Cuts}
+    \label{table:cuts}
+    \centering
+    \makebox[0.65\linewidth]{\begin{tabular}{lrrr}
       \hline\hline
@@
       II, III, and IV Cuts Made & $\$$49,053.19 & $\$$176,681.60 & 24.97\% \\
-\end{tabular}
+      \hline
+    \end{tabular}}
+\end{table}
 
@@
 Priority II cuts entail complete elimination of social event expenses, along with elimination of tour expenses and reduction of dinner costs through cheaper buffet options and desserts.
-The expenditure savings from these cuts are outlined in Table *******.
+The expenditure savings from these cuts are outlined in Table \ref{table:cuts}.
 While this contingency plan does not consider cuts to the reimbursement funds, this could be reconsidered if necessary, since reimbursements were set aside at a level nearly double that of previous conferences.
-\\
 
@@
 
-\vspace{1cm}
+% \vspace{1cm}
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{sponsors1.png}	
+	\includegraphics[width=0.85\textwidth]{sponsors1.png}	
 \end{figure}
@@
 	\centering
-	\includegraphics[width=\textwidth]{sponsors2.png}	
+	\includegraphics[width=0.85\textwidth]{sponsors2.png}	
 \end{figure}
@@
 The cost of attending the student conference, per student, varies among schools and is highly dependent on distance from UIUC and the preferred mode of travel.
-We will assume that minimizing cost is a priority for schools, thus number of persons per hotel room is double the number of beds.
+We will assume that minimizing cost is a priority for schools, thus number of persons per hotel room is assumed to be double the number of beds.
 The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport.
 There is also a small airport located just 20 minutes outside of campus.
-Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus up to 10 times per day.
-Below are the round-trip, non-stop, airfare costs for the first weekend of April.
-Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip.
 While some students may wish to make use of the convenience of the local airport, in general the most economic method of arriving in Champaign is by first flying to O’Hare and then busing.
-The average cost of this trip comes out to be \$293 as shown in Table *******.
-Adding this to the registration and lodging costs for four nights (as students often arrive Wednesday evening) and assuming four students per room, the total cost of attendance for each student comes out to an average of \$447.
+The average cost of this trip comes out to be \$293 as shown in Table  \ref{table:airfare}.
+Adding this to the registration and lodging costs (see Table \ref{table:hotels}) for four nights (as students often arrive Wednesday evening) and assuming four students per room, the total cost of attendance for each student comes out to an average of \$447.
+The travel reimbursement is meant to help mitigate some or most of the costs for students coming to this conference to encourage future attendance at other conferences.
 
 % Jeremy's budget plan
+
+\subsection{Student Travel Reimbursement Procedure}
+The procedure for student travel reimbursement will require each section send via email all acquired expenses in their travels and lodging for this conference.
+Each chapter will be required to send us:
+\begin{enumerate}
+    \item The number of students that attended.
+    \item The number of hotel rooms reserved.
+    \item The location of the hotel rooms.
+    \item Modes of transportation
+    \item Parking costs (excluding airport reserved parking).
+    \item Receipts for all purchases will be required for all submitted purchases.
+\end{enumerate}
+A form will be emailed to each of the chapter presidents for their section to fill out and attach the appropriate receipts.
+We will require that the form along with the necessary receipts be submitted via email to the Finance Director in one PDF, two weeks after the Sunday following the conference.
+The Finance Chair will review all of the submitted documents for any corrections that need to be made.
+Any section that needs to make corrections to their reimbursement form will be emailed the following Tuesday.
+The reimbursement form must be re-submitted to us by that Friday.
+Once all the sections have their forms submitted to us we will turn in our master list to ANS National for reimbursement distributions.
+Checks will be mailed to each of the chapter presidents or a selected representative for the chapter.

### 2019-09-30 management.tex
adds barn dance desc and pics

@@
 
+\newpage
 \subsection{Position Responsibilities}
@@
 & Launch social media plan& Communications\\
-& Finalize list of potential speakers& Non-Technical\\
+&Finalize list of potential speakers& Non-Technical\\
 & Finalize technical topics& Technical\\

### 2019-09-30 staffreq.tex
adds staff requirements

\section{Appendix: Staffing Requirements}
\label{appendix:staff}

\begin{table}[H]
	\caption{Staffing Requirements by Day}
	\label{table:staff}
	\centering
	\begin{tabular}{ccc}
	\hline\hline
	\textbf{Event} & \textbf{Description} & \textbf{Volunteers} \\
	\hline\hline
	& \textbf{Thursday} & \\
	\hline
	Registration & 3/shift, 5 2-hr shifts & 15\\
	Student HQ & 2/shift, 5 2-hr shifts & 10\\
	Professional's Lounge & 1/shift, 5 2-hr shifts & 5\\
	Workshops & 1/workshop for technical assistance & 4\\
	Bussed Tours & 1/tour for logistic assistance & 4\\
	Campus Tours & 4 tour groups, 2 per group & 8\\
	Dinner & 4 all purpose & 4\\
	Social & 2 all purpose & 2\\
	Career Fair Setup & 2 to assist recruiters & 2 \\
	\hline	
	& Total & 54\\
	\hline
	& \textbf{Friday} & \\
	\hline
	Registration & 2/shift, 5 2-hr shifts & 10\\
	Student HQ & 2/shift, 5 2-hr shifts & 10\\
	Professional's Lounge & 1/shift, 5 2-hr shifts & 5\\
	Technical Sessions & Session MCs & 24\\
	Panels & 1/panel for technical assistance & 4\\
	Dinner & 4 all purpose & 4\\
	Social & 2 all purpose & 2\\
	\hline
	& Total & 59\\
	\hline
	& \textbf{Saturday} & \\
	\hline
	Registration & 2/shift, 5 2-hr shifts & 10\\
	Student HQ & 2/shift, 5 2-hr shifts & 10\\
	Professional's Lounge & 1/shift, 5 2-hr shifts & 5\\
	Technical Sessions & Session MCs & 24\\
	Panels & 1/panel for technical assistance & 4\\
 	Poster Session & 2 all purpose & 2\\
	Dinner & 4 all purpose & 4\\
	Social & 2 all purpose & 2\\
	\hline
	 & Total & 61\\
	\hline
	\end{tabular}
\end{table}

### 2019-09-30 website.tex
adds a short section about social media

@@
 \subsection{Social Media} 
+Two accounts will be used to monitor and promote social media at the event.
+The first will be a Twitter account, created specifically for the conference.
+This account will send out schedules and updates, as well as neat facts about events at the conference.
+The second account will be a Facebook page which will serve a similar function to the Twitter account.
+The Facebook page has the added benefit of being able to create events.
+This ability would be used to provide another source of schedule information to conference attendees.

### 2019-09-30 budget.tex
minor updates to budget, theme, and logistics

@@
 
+\subsection{Projected Attendance}
+We project to have 450 student attendees and 150 professional attendees.
+We have based these projections on the attendance from previous years and on our central midwestern location.
+Additionally, this estimate allows us to create the most conservative budget possible and be prepared in the event that attendance is unusually high.
+A summary of the previous attendance is shown in Table \ref{table:attendance}.
+
+\begin{table}[H]
+\caption{Summary of Previous Attendance}
+\label{table:attendance}
+    \centering
+    \begin{tabular}{cccccccccccc}
+    \textbf{Host}& VCU & UF & UPitt & UWM & T. A\&M & Penn & MIT & UNLV & GIT & Mean ($\mu$) & Margin ($\frac{\sigma}{\sqrt{N}}$) \\
+    \hline
+    Students & 450 & 430 & 500 & 438 & 375 & 388 & 536 & 400 & 425 & 438 & $\approx$16 \\
+    Professionals & 100 & 120 & 75 & 130 & 137 & 134 & 101 & 200 & 150 & 127 & $\approx$11\\
+    \hline
+    \end{tabular}
+\end{table}
 % =======================================================================================
@@
 Should our bid be selected, these conservative estimates will result in a smoother planning and execution process.
-We have also accounted an estimated number of waived professional registration based on previous conferences.
+We have also accounted for an estimated number of waived professional registration based on previous conferences.
 This  correlates to the number of waived fees given in our expected tier sponsorship figures and also factors in discounts to speakers, panelists, and workshop instructors.
@@
 
+\clearpage
 \begin{table}[H]
@@
 \hline
-	Student			&	443	&	\$40	&	\$17,720						\\
-	Professional	&	127	& 	\$250	&	\$31,750						\\
+	Student			&	450	&	\$40	&	\$18,000						\\
+	Professional	&	150	& 	\$250	&	\$37,500						\\
 	Waived			&	60	& 	-\$250	&	-\$15,000						\\
 \hline
-	\multicolumn{3}{|r|}{\textbf{Attendance Total:}}	&	\$34,470		\\
+	\multicolumn{3}{|r|}{\textbf{Attendance Total:}}	&	\$40,500		\\
 \hline
@@
 
-\vspace{10mm}
+% \vspace{10mm}
 
@@
 \hline
-    \textbf{Total Revenue: \$235,470}\\ 
+    \textbf{Total Revenue: \$241,500}\\ 
 \hline
@@
 Gratuity is neglected because it is forbidden under the catering service’s policies, allowing us to save 20\% gratuity on meals.
-Under our most conservative estimates for budget and revenue, the spending margin is found to be 4.13\%.
+Under our most conservative estimates for budget and revenue, the spending margin is found to be 6.8\%.
 While this margin is tight, we feel this is justified as several costs in the expenses, such as reimbursements, are left significantly inflated as compared with previous years.
@@
 This number also includes the travel reimbursement, which was intentionally set to be considerably more generous than previous years to make the budget more conservative.
+Assuming every student traveled here with the avereage cost of flights from Table \ref{table:airfare}, our current travel reimbursement package would cover 76.8\% of the accumulated costs.
 Neglecting the cost of travel reimbursements, the average cost per student falls to \$276.63, at or below that estimated for previous years.
-In Appendix \ref{appendix:quotes} on page \pageref{appendix:quotes} there are quotes from Peria Charter and the Union to give some sense of costs.
+In Appendix \ref{appendix:quotes} on page \pageref{appendix:quotes} we included quotes where possible.
 
@@
 
-\begin{table}
+\begin{table}[H]
     \caption{Budget Cuts}
@@
       \multicolumn{1}{l}{Level of Cuts Made} & \multicolumn{1}{c}{Amount Saved} & \multicolumn{1}{c}{Grand Total} & \multicolumn{1}{c}{\% of Max Revenue} \\ \hline\hline 
-      Priority IV Cuts Made & $\$$9,346.00 & $\$$216,388.79 & 8.10\% \\
-      III and IV Cuts Made & $\$$22,987.25 &$\$$198,747.54 & 16.44\% \\
-      II, III, and IV Cuts Made & $\$$49,053.19 & $\$$176,681.60 & 24.97\% \\
+      Priority IV Cuts Made & $\$$9,346.00 & $\$$216,388.79 & 10.4\% \\
+      III and IV Cuts Made & $\$$22,987.25 &$\$$198,747.54 & 17.4\% \\
+      II, III, and IV Cuts Made & $\$$49,053.19 & $\$$176,681.60 & 26.56\% \\
       \hline

### 2019-09-30 conflog.tex
minor updates to budget, theme, and logistics

@@
 \textbf{Thursday Night}\\
-Communicating the science of nuclear energy remains one of the chief challenges of our field, which is why the opening dinner of this conference will focus on science communication and the people behind the science.
+Communicating the science of nuclear energy remains one of the chief challenges of our field.
+The opening dinner of this conference will focus on science communication and the people behind the science.
 Science communication requires more than the recitation of raw data to be effective.
 By telling our own, diverse backstories, we become more effective science communicators.
-Speakers will be chosen which emphasize this fact and will be asked to speak to their own backstory as a nuclear advocate and how this story makes them a more effective communicator.\\
-\textbf{Friday Night}\\
-The second dinner will be themed around networking and professional-development, and how these critical tools have value beyond finding jobs.
-Communities like ANS thrive on the exchange of ideas and knowledge, and the student conference serves the vital role of connecting the burgeoning minds of the next generation with the wisdom of established professionals.
-This dinner will consist of tables organized by company/national lab to allow students and professionals to mingle, promoting the exchange of ideas.\\
-\textbf{Saturday Night}\\
+Speakers will be asked to speak to their own backstory as a nuclear advocate and how their story makes them a more effective communicator.\\\\
+\indent\textbf{Friday Night}\\
+The second dinner will be themed around networking and professional-development and how these critical tools have value beyond finding jobs.
+Communities like ANS thrive on the exchange of ideas and knowledge.
+The student conference serves plays an essential role by connecting the burgeoning minds of the next generation with the wisdom of established professionals.
+This dinner will consist of tables organized by company/national lab to allow students and professionals to mingle, promoting the exchange of ideas.\\\\
+\indent\textbf{Saturday Night}\\
 The closing dinner of the conference will be a call to action for student attendees.
 Ours is a generation faced with challenges on a scale never witnessed by humanity, and we will only successfully address these challenges through the engagement of as many bright young minds as possible.
-The speakers for this night will be asked to address ways we all can take individual responsibility for the grand challenges of our age, using our own unique skills to tackle problems like climate change and energy poverty from every angle imaginable.\\
+The speakers for this night will be asked to address ways we all can take individual responsibility for the grand challenges of our age by using our own unique skills to tackle problems like climate change and energy poverty from every angle imaginable.\\
 \subsection{Travel and Transportation}

### 2019-09-30 theme.tex
minor updates to budget, theme, and logistics

@@
 Nuclear, plasma, and radiological engineering will be central to many endeavors, whether the goal is solving the world’s energy needs, developing technology that will take us to the stars, or curing cancer.
-By hosting this conference, we hope to inspire and motivate students in nuclear, plasma, and radiological engineering to tackle big problems.
+By hosting this conference, we hope to inspire and motivate students in these engineering fields to tackle big problems.
 Saving the World One Atom at a Time reflects the fact that nuclear science is a powerful force in dealing with grand challenge problems.
 This theme also honors the individual, atomic, contributions from students, researchers, and professionals that are essential to progress.
-This conference is about science and engineering and it is about the people that make science possible.
+This conference is about science and engineering and it is about the people that make science and engineering possible.
 Students will hear from visionary speakers and leaders of the nuclear science community and come away with optimism for the future; knowing that they are saving the world one atom at a time.\\
@@
 We showcase this aspect of the conference with panels like \textit{Science is People: How to Conduct Inclusive Research} and \textit{Scientific Storytelling}.
-	\item Help students and professionals develop a strong network of like-minded people.\\
+	\item Connect students and professionals to develop strong networks.\\
 	This is the networking and professional-development-focused section of the conference.
@@
 	\item Inspire the next generation of nuclear engineers to take on grand challenge problems\\
-	The final day is the culmination of the conference underpins the single unifying ideal.
+	The final day is the culmination of the conference and underpins the single unifying ideal.
 For many students, this conference might be the first time they are presenting research to their peers, mentors, and future employers.

### 2019-09-30 management.tex
adds dates to milestones

@@
 % 	      child[grandchild,third] {node[coordinator] {Hospitality and Catering}}}
-% 	    child {node[committee] {Communications Subcommittee}
+% 	    child {node[committee] {Media Subcommittee}
 % 	      child[grandchild, first] {node[chair] {Publications Chair}}
@@
 Thus, it will be an overall positive experience for the volunteers.
-Quantitative needs are outlined in Appendix G.
+Quantitative needs are outlined in Appendix G on page \pageref{appendix:staff}.
 
@@
 % ===============================================
+\newpage
 \subsection{Milestones}
@@
 \hline\hline
-Deadline & Task & Responsibility\\
+\textbf{Deadline} & \textbf{Task} & \textbf{Responsible Committee}\\
 \hline\hline
 
-&November&\\
+&\textbf{November}&\\
 \hline\hline
-& Announcement of 2021 Conference & \\
-& Update milestones with lessons learned &\\
-& Notify department of selection & Co-Chairs\\
-& Confirm Conference Committee & Co-Chairs\\
-& Finalize Conference Date & Co-Chairs\\
-& Confirm Conference Reservations & Non-Technical\\
-& Contact ANS National for support with hotel negotiations& Co-Chairs and Non-Technical\\
-& Set up banking through Busey Bank and ANS National& Financial\\
+11/21/19 & Announcement of 2021 Conference & \\
+11/21/19 & Update milestones with lessons learned &\\
+11/21/19 & Notify department of selection & Co-Chairs\\
+11/22/19 & Confirm Conference Committee & Co-Chairs\\
+11/29/19 & Finalize Conference Date & Co-Chairs\\
 \hline\hline
-&December&\\
+&\textbf{December}&\\
 \hline\hline
-&Finalize Facilities Reservations& Non-Technical\\
-&Finalize Logo Design& Communications\\
-&Begin Designing Website and Social Media& Communications\\
+12/1/19 & Contact ANS National for support with hotel negotiations& Co-Chairs and Non-Technical\\
+12/1/19 & Set up banking through Busey Bank and ANS National& Financial\\
+12/3/19 & Confirm Conference Reservations & Non-Technical\\
+12/3/19 & Finalize Facilities Reservations& Non-Technical\\
+12/20/19 & Finalize Logo Design& Media\\
+12/20/19 & Begin Designing Website and Social Media& Media\\
 \hline\hline
@@
 \hline\hline
-&January&\\
+&\textbf{January}&\\
 \hline\hline
-& Finalize meeting schedule& Co-Chairs\\
-&&\\
+1/13/20 & Finalize meeting schedule& Co-Chairs\\
 \hline\hline
-&February&\\
+&\textbf{February}&\\
 \hline\hline
-& Launch social media plan& Communications\\
-&Finalize list of potential speakers& Non-Technical\\
-& Finalize technical topics& Technical\\
+2/3/20 & Launch social media plan& Media\\
+2/17/20 & Finalize list of potential speakers& Non-Technical\\
+2/17/20 & Finalize technical topics& Technical\\
 \hline\hline
-&March&\\
+&\textbf{March}&\\
 \hline\hline
-& Contact Speakers and Presenters& Non-Technical and Technical\\
+3/9/20 & Contact Speakers and Presenters& Non-Technical and Technical\\
+3/26-28/20 & Attend Student Conference at NC State& All\\
+3/28/20 & Request lessons learned from NC State& Co-Chairs\\
 \hline\hline
-&April&\\
+&\textbf{April}&\\
 \hline\hline
-& Attend Student Conference at NC State& All\\
-& Request lessons learned from NC State& Co-Chairs\\
-& Create sponsor letters and contact & General Co-Chair\\
-& Prepare tour opportunities& Non-Technical\\
+4/6/20 & Create sponsor letters and contact & General Co-Chair\\
+4/13/20 & Prepare tour opportunities& Non-Technical\\
 \hline\hline
-&May&\\
+&\textbf{May}&\\
 \hline\hline
-& Confirm tours and costs& Non-Technical\\
-& Submit Progress Report to SSC& \\
-& Create a Call for Papers & Technical and Communications\\
+5/4/20 & Confirm tours and costs& Non-Technical\\
+5/18/20 & Submit Progress Report to SSC& Co-Chairs\\
+5/18/20 & Create a Call for Papers & Technical and Media\\
 \hline\hline
-&June&\\
+&\textbf{June}&\\
 \hline\hline
-& Send Delegates to National Conference& Co-Chairs, All\\
+6/7-11/20 & Send Delegates to Annual Meeting in Arizona& Co-Chairs, All\\
 \hline\hline
-&July&\\
+&\textbf{July}&\\
 \hline\hline
-& Confirm with all speakers and presenters& \\
-& Report on sponsorship& Financial\\
-& Reassess budget& Financial\\
+7/6/20 & Confirm with all speakers and presenters& Technical\\
+7/20/20 & Report on sponsorship& Financial\\
+7/27/20 & Reassess budget& Financial\\
 \hline\hline
-&August&\\
+&\textbf{August}&\\
 \hline\hline
-& Update with sponsors& Financial\\
-& Submit second progress to SSC& Co-Chairs\\
+8/10/20 & Update with sponsors& Financial\\
+8/24/20 & Submit second progress to SSC& Co-Chairs\\
 \hline\hline
-&September&\\
+&\textbf{September}&\\
 \hline\hline
-& Updates on conference deadlines& Financial\\
-& Order gift bags& Non-Technical\\
+9/14/20 & Updates on conference deadlines& Financial\\
+9/21/20 & Finalize gift bag order& Non-Technical\\
 \hline\hline
-&October&\\
+&\textbf{October}&\\
 \hline\hline
-& Confirm hotel blocks and contracts& Non-Technical\\
-& Registration Opens& Financial\\
-& Create and test online paper submission& Technical\\
+10/12/20 & Confirm hotel blocks and contracts& Non-Technical\\
+10/26/20 & Registration Opens& Financial\\
+10/26/20 & Create and test online paper submission& Technical\\
 \hline\hline
-&November&\\
+&\textbf{November}&\\
 \hline\hline
-& Attend Winter Conference 2020& Co-Chairs, All\\
-& Finalize marketing material& Communications\\
-& Report from winter conference & Co-Chairs\\
+11/15-19/20 & Attend Winter Conference 2020 in Chicago& Co-Chairs, All\\
+11/24/20 & Finalize marketing material& Media\\
+11/24/20 & Report from winter conference & Co-Chairs\\
 \hline\hline
-&December&\\
+&\textbf{December}&\\
 \hline\hline
-& Update website & Communications \\
-& Third progress report to SSC& Co-Chairs\\
-& Send out call for papers& Communications\\
+12/4/20 & Reassess Budget & Financial \\
+12/4/20 & Update website & Media \\
+12/18/20 & Third progress report to SSC& Co-Chairs\\
+12/18/20 & Send out call for papers& Media\\
 \hline\hline
@@
 \hline\hline
-&January&\\
+&\textbf{January}&\\
 \hline\hline
-& Confirm all judges, panelists, and speakers& Technical\\
-& First paper deadline -- send to reviewers & Technical\\
-& Recruit student volunteers& All\\
-& Finalize tours& Non-Technical\\
-& Finalize conference transportation& Non-Technical\\
+1/4/20 & Confirm all judges, panelists, and speakers& Technical\\
+1/18/20 & First paper deadline -- send to reviewers & Technical\\
+1/22/20 & Recruit student volunteers& All\\
+1/29/21 & Finalize tours& Non-Technical\\
+1/29/21& Finalize conference transportation& Non-Technical\\
 \hline\hline
-&February&\\
+&\textbf{February}&\\
 \hline\hline
-& Finalize program& Communications\\
-& Order gift bag items & Financial and Non-Technical\\
-& Final Paper Deadline& Technical\\
-& Finalize App& Communications\\
-& Finalize budget& Financial\\
-& Extended Paper Deadline& \\
+2/1/21 & Finalize program& Media\\
+2/1/21 & Order gift bag items & Financial and Non-Technical\\
+2/5/21 & Final Paper Deadline& Technical\\
+2/9/21 & Extended Paper Deadline& \\
+2/15/21 & Finalize Website& Media\\
+2/19/21 & Finalize budget& Financial\\
 \hline\hline
-&March&\\
+&\textbf{March}&\\
 \hline\hline
-& Print Programs& Communications\\
-& Finalize Awards& Technical\\
-& Finalize Staff Schedule& Non-Technical\\
-& Prepare gift bags, print tags, and banners& Non-Technical\\
-& Final progress report to SSC& Co-Chairs\\
+3/22/21 & Print Programs& Media\\
+3/26/21 & Finalize Awards& Technical\\
+3/26/21 & Finalize Staff Schedule& Non-Technical\\
+3/29/21 & Final progress report to SSC& Co-Chairs\\
 \hline\hline
-&April&\\
+&\textbf{April}&\\
 \hline\hline
-& Host ANS Student Conference 2021 & \\
-& Return seed money& Financial\\
-& Process Student Reimbursements& Financial\\
-& Finalize financial report& Financial\\
-& Submit conference report& Co-Chairs\\
+4/1/21 & Prepare gift bags, print tags, and banners& Non-Technical\\
+4/8-11/21 & Host ANS Student Conference 2021 & \\
+4/22/21 & Return seed money& Financial\\
+4/29/21 & Process Student Reimbursements& Financial\\
+4/29/21 & Finalize financial report& Financial\\
+4/29/21 & Submit conference report& Co-Chairs\\
 \hline\hline

### 2019-09-30 management.tex
bachman edits

@@
 Lauren Garrison.
+He will return the UIUC in December 2019.
 Nate has attended four of the last five ANS Student Conferences and was a student paper competition finalist at the TOFE embedded topical of the 2018 ANS Winter Meeting.
@@
 Kathryn Huff in the ARFC group.
-Last summer she had an internship at Argonne National Laboratory where she worked on sensitivity analysis of the nuclear fuel complex.She also serves as the president of the UIUC chapter of Women In Nuclear (WiN).
-Under her leadership, WiN-UIUC was honored with the Best Student Chapter award at the WiN National Meeting in 2019.
+Last summer she had an internship at Argonne National Laboratory where she worked on sensitivity analysis of the nuclear fuel complex.
+She also serves as the president of the UIUC chapter of Women In Nuclear (WIN).
+Under her leadership, WIN-UIUC was honored with the Best Student Chapter award at the WIN National Meeting in 2019.
 She has also been involved with ANS and attended the 2018 ANS Student Conference in Florida and will be attending the upcoming ANS Student Conference at NC State in 2020.
@@
 While it is likely that members of our student chapter will voluntarily fill all the staffing requirements of conference hosted events.
-If not, we will rely on other student organizations for support including, but not limited to: ACDIS and WIE.
+If not, we will rely on other student organizations for support including, but not limited to: Arms Control and Domestic and International Security (ACDIS) and Women in Engineering (WIE).
 Participating in conference events on a staff level is a beneficial experience for any undergraduate who wants to become more familiar with ANS or support their ANS Chapter.

### 2019-09-30 proglog.tex
bachman edits

@@
 Baranwal is a clear choice of speaker to discuss the ways to improve nuclear legislation and how companies can rapidly develop new nuclear technology.
+We would ask her to give a call to action for students on the final night of the conference.
 \end{minipage}
@@
 Celebrating the people behind the science is one of the key goals of this conference and an area in which Baker has a lot of experience.
+Thus she would be a great speaker on the opening night.
 \end{minipage}
@@
 In addition to his experience and ambition, he is an excellent science communicator to scientists and non-scientists alike.
-Together, these factors make him an ideal speaker at the conference.
+His diverse background makes him an ideal speaker to discuss the importance of developing a diverse network on the second night of the conference.
 \end{minipage}
@@
 \subsubsection{Building Your Network}
-The AAAS conducts workshops that teach early career scientists and students how to develop a professional network that will benefit them in the future.
+The American Association for the Advancement of Science (AAAS) conducts workshops that teach early career scientists and students how to develop a professional network that will benefit them in the future.
 They hold regular workshops about strategic networking, making new contacts, and getting the most out of a conference.
@@
 The Advanced Reactors and Fuel Cycles (ARFC) research group at UIUC and its collaborators will provide instructors.
-This workshop, alpha-tested at the University of Wisconsin will be aimed at students who can provide their own laptops and have a desire to improve their nuclear computational skills.
+This workshop, tested at the University of Wisconsin will be aimed at students who can provide their own laptops and have a desire to improve their nuclear computational skills.
 The workshop will be approximately two hours of instruction at NCSA room 1030.

### 2019-09-30 socials.tex
adds farm lake pics
bachman edits

--- 2019-09-25 socials.tex
@@
 	\end{subfigure}
+	\caption{77 Club at Memorial Stadium}		
 \end{figure}
 
+%% Reserve for Pour Bros. social %%%
 \subsubsection{Pour Bros. Taproom in Downtown Champaign}
@@
 If you are feeling more on the leisurely side, Pour Bros features live music in a spacious and comfortable seating area for you to get your networking on.
-
+\vspace{0.5cm}\newline
 % Pour Bros Picture
 \begin{figure}[H]
+
 	\centering
@@
 		\centering
-		\includegraphics[width=0.5\linewidth]{pour_bros2.png}
+		\includegraphics[width=0.4\linewidth]{pour_bros2.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=0.9\linewidth]{pour_bros1.png}
+		\includegraphics[width=0.7\linewidth]{pour_bros1.png}
 	\end{subfigure}	
+	\caption{Pour Brothers Taproom}	
+\end{figure}
+
+\subsubsection{Barn Dance: A Proud Midwestern Tradition}
+Barn dances are a staple event at UIUC.
+Socialize in a unique environment with games of corn-hole and other midwestern fun.
+Various barns are used for dancing and mingling by many of the student organizations on UIUC campus, such as Farm Lake barn which hosts dozens of barn dances annually.
+Other barns may be best suited for the student conference social events, such as Hudson Farm, which offers a corporate event or professional social events option which can accommodate up to 300 guests with an alcohol service available and friendly, helpful service.
+Like socials in the past student conferences, the barn may be used and a third party service can be hired to bring the square dance, swing dance, two step and cowboy boogie to the barn dance floor!
+\vspace{0.5cm}\newline
+% Barn Dance Hudson Picture
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.4\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{barn_dance1.png}
+	\end{subfigure}%
+	\begin{subfigure}{0.4\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{barn_dance2.png}
+	\end{subfigure}	
+	\caption{Hudson Farm Barn.}	
+\end{figure} 
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.4\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{farmlake1.jpg}
+	\end{subfigure}%
+	\begin{subfigure}{0.4\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{farmlake2.jpg}
+	\end{subfigure}	
+	\caption{Farm Lake Barn}	
 \end{figure}

### 2019-09-30 uiuc.tex
bachman edits
Nate-Bachmann edits to uiuc.tex

@@
 Champaign-Urbana Mass Transit (CU-MTD) is a reliable public transportation service that sees millions of riders every year.
-CU-MTD charges an affordable rate of \$1 per ride.
+CU-MTD charges an affordable rate of \$1 per ride, which can be paid in cash or using the Token Transit app.
+Additionally, an all-day pass can be bought on Saturdays and Sundays for \$2 from any bus operator or from the app.
 All CU-MTD busses are wheelchair accessible.
@@
 The UIUC Grainger College of Engineering has had sixteen Nobel Laureates in physics.
-Including John Bardeen, the only scientist to ever win the award twice.
+Including John Bardeen, the only scientist to ever win the award in physics twice.
 It also offers 15 different majors to almost 6000 undergraduate and 2500 graduate students.
 Of its twelve ranked majors, nine are ranked among the top 10 in the nation, and six of which remain ranked among the top 5 in their degree.
-Overall, the College of Engineering in Urbana-Champaign ranks sixth among the nation’s best undergraduate engineering programs.
+Overall, the Grainger College of Engineering in Urbana-Champaign ranks sixth among the nation’s best undergraduate engineering programs.
 With more than 250 degrees for undergraduates and graduates and a multitude of first-class research facilities and resource, UIUC gives its nearly 45,000 students the ability to succeed.
@@
 It also engages in education and outreach programs to teach members of the surrounding community about nuclear science.
-One of our most popular outreach programs is Engineering Open House (EOH), during which ANS-UIUC repeatedly earns awards for best presentation of a socieyt.
-EOH is an annual event where members of the local community, from young children to senior adults, visit the engineering campus to learn more about STEM research.Membership is currently around 70-80 students and has been steadily growing.
+One of our most popular outreach programs is Engineering Open House (EOH), during which ANS-UIUC repeatedly earns awards for best presentation of a society.
+EOH is an annual event where members of the local community, from young children to senior adults, visit the engineering campus to learn more about STEM research.
+Membership is currently around 70-80 students and has been steadily growing.
 The chapter works to host events catering to nuclear, plasma, and radiological concentrations.
 Professional development plays a crucial role in student development, and it is the biggest part of member involvement at UIUC.
-Events range from tours of various facilities to pizza with campus visitors.
-Some of the past tours have included Clinton Power Station, Oak Ridge National Laboratory, Analysis System (ANSYS) Inc, and Argonne National Laboratory.
+Professional development activities range from tours of various facilities to pizza with campus visitors.
+Some of the past tours have included Clinton Power Station, Curium Pharma through UIUC Women In Nuclear, Oak Ridge National Laboratory, Analysis System (ANSYS) Inc, and Argonne National Laboratory.
 ANS-UIUC has historically been one of the best represented institutions at the annual student conference and is a tradition this chapter is eager to uphold.
-
-\clearpage
 
@@
 
+\clearpage
+
 \subsection{Research at UIUC}
-Faculty and students in NPRE conduct research in many areas of interest to the nuclear science community.
+Faculty and students in the Department of Nuclear, Plasma, and Radiological Engineering (NPRE) at Illinois conduct research in many areas of interest to the nuclear science community.
 Both graduate and undergraduate  students actively participate and make their own atomic contributions that will someday save the world.
@@
 \subsubsection{Nuclear Power}
-The Department of Nuclear, Plasma, and Radiological Engineering at Illinois is well known for its pioneering research in the area of reactor power engineering.
+NPRE is well known for its pioneering research in the area of reactor power engineering.
 Graduates have gone on to leadership positions in industry, national laboratories, and academia.
@@
 This device finished construction and achieved first plasma during the spring of 2016.
+\\
 

### 2019-09-30 conflog.tex
bachman edits
edits to satisfy SSC requirements and feedback - Nate

@@
 This expansion is set to be completed by Fall 2020.
-We will be hosting a social at the 77 Club in Memorial Stadium, just up the street.
+We will be hosting a social at the 77 Club in Memorial Stadium, which is just a brief walk up the street.
 Information about the I Hotel expansion is included in Appendix D.
+Cost of transportation to and from the I Hotel and 77 Club are discussed in the budget section.
 
@@
 The Garden Hotel Urbana (soon to be the Radisson) will be the primary hotel for all attendees.
+It features complimentary breakfast for its guests every morning.
 This will also be the location of the opening ceremony dinner.
-Since this hotel is just beyond walking distance from the main conference activities, we will hire four Peoria Charter busses to shuttle attendees to and from the Union every 10 minutes.
-Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 8am to 6pm.
+Since this hotel is just beyond walking distance from the main conference activities (2.2 miles), we will hire four Peoria Charter busses to shuttle attendees to and from the Union every 10 minutes.
+Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 7am to 5am the following day for weekdays, and every 30 minutes on weekends.
 \\
@@
 $\textbf{Marriott TowneSuites}$\\
-In the event that attendance exceeds 600 people, we will have overflow rooms in the Marriott TowneSuites.
+The Marriott TowneSuites is the professional's designated hotel; and, in the event that attendance exceeds 600 people, we will have overflow rooms in the Marriott TowneSuites.
 Rooms at the Marriott resemble a studio apartment with an open floor plan, refrigerator, stove, microwave,dishes, and dining area.
@@
 Students from UIUC will be able to stay in their respective dorms and apartments to maximize the number of hotel rooms available to out of town guests.
+Sections seeking travel assistance are required to use the room blocks described above to prevent extra costs.
+Another proposed method to alleviate costs is to allow an option for students from smaller sections to be housed at an ANS-UIUC section member's apartment.
+The Diversity co-chair will assume responsibilities of reaching out to members-at-large and other minority serving institutions.
 
@@
 	\end{tabular}}
+\subcaption*{\textbf{*}\textit{Price for a queen double} \textbf{**}\textit{Assumes 4 people per room}}
 \end{table}
-\textbf{*}\textit{Price for a queen double}
-\textbf{**}\textit{Assumes 4 people per room}
 
@@
 The student conference serves plays an essential role by connecting the burgeoning minds of the next generation with the wisdom of established professionals.
-This dinner will consist of tables organized by company/national lab to allow students and professionals to mingle, promoting the exchange of ideas.\\\\
+This dinner will consist of tables organized by company/national laboratory or by topic/discipline area to allow students and professionals to mingle, promoting the exchange of ideas.\\\\
 \indent\textbf{Saturday Night}\\
@@
 Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip.
+While travel from airport to hotel can be managed by train (Amtrak/Metra), the conference planning committee excluded this option due to the added complexities of getting from the airport to train station, and train station to hotel with the associated costs of doing so.
+We believe the charter bus to be the best route of action as it picks up travelers directly at the arrivals gate and brings them to the Illini Union.
 Due to the central location of UIUC, driving might be a good option for some schools and individuals.

### 2019-09-30 socials.tex
updates socials reflecting feedback

@@
 The Illini Union Rec Room is located in the basement of the Union building.
-A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at the Krannert Center for Performing Arts, only a short walk away through the University of Illinois main quad!
-This space can accompany up to 150 people, with extra tables outside of the Rec Room for socializing, playing board games, or having a late night snack or coffee with professionals or students from other universities.
+A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at The Garden Hotel.
+This space can accompany up to 150 people, with extra overflow space with tables outside of the Rec Room for socializing, playing board games, or having a late night snack or coffee with professionals or students from other universities.
+This will be an alcohol free social option for Thursday night, and a bar social will be reserved as well for this night.
 \vspace{0.5cm}\newline
@@
 
-\subsubsection{77 Club at Memorial Stadium}
-Memorial Stadium is not only home to the Fighting Illini football team, but also to exquisite event space overlooking Zuppke Field.
-The sixth level of Memorial Stadium is home of the magnificent 77 Club, which honors Illini great, the ``Galloping Ghost'' Red Grange.
-This 5,020 square foot space is located midfield and features an outdoor patio area overlooking the city of Champaign, for a combined total space of 9,740 square feet.
-This event will take place following dinner at I Hotel Conference Center, and is just a short and scenic walk away past the State Farm Center (formerly the historic Assembly Hall).
-Tables will be set up around a stage featuring live music and a dance floor and drinks will be served.
-This is the perfect event to incorporate a little bit of Illinois history with music, dancing, and socializing!
-\vspace{0.5cm}\newline
-% 77 Club Picture
-\begin{figure}[H]
-
-	\centering
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.7\linewidth]{77club1.png}
-	\end{subfigure}%
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.9\linewidth]{77club2.png}
-	\end{subfigure}
-	\caption{77 Club at Memorial Stadium}		
-\end{figure}
-
-%% Reserve for Pour Bros. social %%%
 \subsubsection{Pour Bros. Taproom in Downtown Champaign}
@@
 
+\subsubsection{77 Club at Memorial Stadium}
+Memorial Stadium is not only home to the Fighting Illini football team, but also to exquisite event space overlooking Zuppke Field.
+The sixth level of Memorial Stadium is home of the magnificent 77 Club, which honors Illini great, the ``Galloping Ghost'' Red Grange.
+This 5,020 square foot space is located midfield and features an outdoor patio area overlooking the city of Champaign, for a combined total space of 9,740 square feet.
+This event will take place following dinner at I Hotel Conference Center, and is just a short and scenic walk away past the State Farm Center (formerly the historic Assembly Hall).
+Tables will be set up around a stage featuring live music and a dance floor and drinks will be served, along with hosting raffles with nuclear and Illinois trivia.
+This is the perfect event to incorporate a little bit of Illinois history with music, dancing, and socializing!
+\vspace{0.5cm}\newline
+% 77 Club Picture
+\begin{figure}[H]
+
+	\centering
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.7\linewidth]{77club1.png}
+	\end{subfigure}%
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{77club2.png}
+	\end{subfigure}
+	\caption{77 Club at Memorial Stadium}		
+\end{figure}
+
 \subsubsection{Barn Dance: A Proud Midwestern Tradition}
@@
 Other barns may be best suited for the student conference social events, such as Hudson Farm, which offers a corporate event or professional social events option which can accommodate up to 300 guests with an alcohol service available and friendly, helpful service.
+Conference attendees will be encouraged to dress up in country-style attire or costume for this event.
 Like socials in the past student conferences, the barn may be used and a third party service can be hired to bring the square dance, swing dance, two step and cowboy boogie to the barn dance floor!
@@
 
-\subsubsection{Under 21 Social: University of Illinois Ice Arena}
-For students under the drinking age that cannot attend the Pour Bros.
+%\subsubsection{Under 21 Social: University of Illinois Ice Arena}
+%For students under the drinking age that cannot attend the Pour Bros.
 Taproom social event, the University of Illinois Ice Arena is another option that is only a brief walking distance from the Union.
@@
 Snacks and concession items are also available.
-\vspace{0.5cm}\newline
-% Ice Arena Picture
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.8\textwidth]{ice_arena.png}
-	\caption{The UIUC Ice Arena}
-\end{figure}
+%\vspace{0.5cm}\newline
+%% Ice Arena Picture
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.8\textwidth]{ice_arena.png}
+%	\caption{The UIUC Ice Arena}
+%\end{figure}

### 2019-10-01 budget.tex
bachman edits
minor edits

@@
 \centering
-\caption*{\textbf{Attendance}}
+\caption*{\textbf{Attendance Revenue}}
 \begin{tabular}{|c|c|c|c|}
@@
 \centering
-\caption*{\textbf{Sponsors}}
+\caption*{\textbf{Sponsorship Revenue}}
 \begin{tabular}{|c|c|c|c|}
@@
 \subsection{Sponsorship and Fundraising}
-The sponsorship breakdown for our conference pulls from averages of sponsorship packages in the last several conferences, with for main tiers that tie into the conference theme for the largest representation in the conference and visibility in the career fair, socials, sessions, technical, and meals as well as in conference shirts and attendee bags.
+The sponsorship breakdown for our conference pulls from averages of sponsorship 
+packages in the last several conferences, with four main tiers that tie into the conference theme for the largest representation in the conference and visibility in the career fair, socials, sessions, technical, and meals as well as in conference shirts and attendee bags.
 Using two tiers for an exhibitor package allows for a platform for DOE national laboratories to participate, with the higher tier having logo representation on shirts as well as the opportunity to sponsor a coffee break or lunch \& learn session.

### 2019-10-01 uiuc.tex
airports and typos

@@
 \subsubsection{Accessibility and Accomodation}
- A large number of hotels are located around downtown Champaign and the Eastern side of campus, making transportation easy.
-Champaign-Urbana Mass Transit (CU-MTD) is a reliable public transportation service that sees millions of riders every year.
-CU-MTD charges an affordable rate of \$1 per ride, which can be paid in cash or using the Token Transit app.
-Additionally, an all-day pass can be bought on Saturdays and Sundays for \$2 from any bus operator or from the app.
-All CU-MTD busses are wheelchair accessible.
-Rental bikes and rideshare services are also plentiful.
-There is a small airport, Willard Airport, just 20 minutes from campus that has regular flights to and from Chicago O’Hare and Dallas Fort Worth airports.
-Finally, Peoria Charter is a popular bus service with several daily trips between the UIUC campus and the Chicagoland area.
+ Many hotels are located around downtown Champaign and the Eastern 
+ side of campus, making transportation easy. Champaign-Urbana Mass Transit 
+ (CU-MTD) is a reliable public transportation service that sees millions of 
+ riders every year. CU-MTD charges an affordable rate of \$1 per ride, which 
+ can be paid in cash or using the Token Transit app. Additionally, an all-day 
+ pass can be bought on Saturdays and Sundays for \$2 from any bus operator or 
+ from the app. All CU-MTD busses are wheelchair accessible. Rental bikes and 
+ rideshare services are also plentiful.
+ Champaign's Willard Airport (CMI) is just 15 minutes from campus and has 
+regular flights to and from Chicago O’Hare (ORD), Dallas/Fort Worth (DFW), and 
+Charlotte (CLT). Finally, Peoria Charter is a popular bus service with several 
+daily trips between the UIUC campus and the Chicagoland area.
 
 \subsubsection{Weather}
-With an average high temperature of 65$^{\circ}$ and an average low temperature of 40$^{\circ}$, April in Champaign is a gorgeous month of dwindling winter weather and spring coming into bloom.
-Holding a conference during this time would be the perfect way to showcase our beautiful city.
+With an average high temperature of 65$^{\circ}$ and an average low temperature 
+of 40$^{\circ}$, April in Champaign is a gorgeous month of dwindling winter 
+weather and spring coming into bloom. Holding a conference during this time 
+will be the perfect way to showcase our beautiful city.
 

### 2019-10-01 uiuc.tex
airports and typos

@@
 regular flights to and from Chicago O’Hare (ORD), Dallas/Fort Worth (DFW), and 
-Charlotte (CLT). Finally, Peoria Charter is a popular bus service with several 
+Charlotte (CLT).  Other nearby airports include Chicago (ORD and MDW),
+Indianapolis (IND), and Bloomington (BMI). If attendees fly into these
+airports, ground transportation to the Champaign area will be required. To this
+end, Peoria Charter is a popular bus service with several 
 daily trips between the UIUC campus and the Chicagoland area.

### 2019-10-01 staffreq.tex
adds reporting relationship to staffreq

@@
 	\centering
-	\begin{tabular}{ccc}
+	\begin{tabular}{ccc|c}
 	\hline\hline
-	\textbf{Event} & \textbf{Description} & \textbf{Volunteers} \\
+	\textbf{Event} & \textbf{Description} & \textbf{Volunteers}& \textbf{Reports To} \\
 	\hline\hline
-	& \textbf{Thursday} & \\
+	& \textbf{Thursday} & &\\
 	\hline
-	Registration & 3/shift, 5 2-hr shifts & 15\\
-	Student HQ & 2/shift, 5 2-hr shifts & 10\\
-	Professional's Lounge & 1/shift, 5 2-hr shifts & 5\\
-	Workshops & 1/workshop for technical assistance & 4\\
-	Bussed Tours & 1/tour for logistic assistance & 4\\
-	Campus Tours & 4 tour groups, 2 per group & 8\\
-	Dinner & 4 all purpose & 4\\
-	Social & 2 all purpose & 2\\
-	Career Fair Setup & 2 to assist recruiters & 2 \\
+	Registration & 3/shift, 5 2-hr shifts & 15& Registration Coordinator\\
+	Student HQ & 2/shift, 5 2-hr shifts & 10& Program Coordinator\\
+	Professional's Lounge & 1/shift, 5 2-hr shifts & 5& Program Coordinator\\
+	Workshops & 1/workshop for technical assistance & 4& Workshops Coordinator\\
+	Bussed Tours & 1/tour for logistic assistance & 4& Tours Coordinator\\
+	Campus Tours & 4 tour groups, 2 per group & 8& Tours Coordinator\\
+	Dinner & 4 all purpose & 4& Hospitality Coordinator\\
+	Social & 2 all purpose & 2& Hospitality Coordinator\\
+	Career Fair Setup & 2 to assist recruiters & 2 & Career Fair Coordinator\\
 	\hline	
-	& Total & 54\\
+	& Total & 54&\\
 	\hline
-	& \textbf{Friday} & \\
+	& \textbf{Friday} & &\\
 	\hline
-	Registration & 2/shift, 5 2-hr shifts & 10\\
-	Student HQ & 2/shift, 5 2-hr shifts & 10\\
-	Professional's Lounge & 1/shift, 5 2-hr shifts & 5\\
-	Technical Sessions & Session MCs & 24\\
-	Panels & 1/panel for technical assistance & 4\\
-	Dinner & 4 all purpose & 4\\
-	Social & 2 all purpose & 2\\
+	Registration & 2/shift, 5 2-hr shifts & 10& Registration Coordinator\\
+	Student HQ & 2/shift, 5 2-hr shifts & 10& Program Coordinator\\
+	Professional's Lounge & 1/shift, 5 2-hr shifts & 5& Program Coordinator\\
+	Technical Sessions & Session MCs & 24& Sessions Coordinator\\
+	Panels & 1/panel for technical assistance & 4& Workshops Coordinator\\
+	Dinner & 4 all purpose & 4& Hospitality Coordinator\\
+	Social & 2 all purpose & 2& Hospitality Coordinator\\
 	\hline
-	& Total & 59\\
+	& Total & 59&\\
 	\hline
-	& \textbf{Saturday} & \\
+	& \textbf{Saturday} & &\\
 	\hline
-	Registration & 2/shift, 5 2-hr shifts & 10\\
-	Student HQ & 2/shift, 5 2-hr shifts & 10\\
-	Professional's Lounge & 1/shift, 5 2-hr shifts & 5\\
-	Technical Sessions & Session MCs & 24\\
-	Panels & 1/panel for technical assistance & 4\\
- 	Poster Session & 2 all purpose & 2\\
-	Dinner & 4 all purpose & 4\\
-	Social & 2 all purpose & 2\\
+	Registration & 2/shift, 5 2-hr shifts & 10& Registration Coordinator\\
+	Student HQ & 2/shift, 5 2-hr shifts & 10& Program Coordinator\\
+	Professional's Lounge & 1/shift, 5 2-hr shifts & 5& Program Coordinator\\
+	Technical Sessions & Session MCs & 24& Sessions Coordinator\\
+	Panels & 1/panel for technical assistance & 4& Workshops Coordinator\\
+ 	Poster Session & 2 all purpose & 2& Sessions Coordinator\\
+	Dinner & 4 all purpose & 4& Hospitality Coordinator\\
+	Social & 2 all purpose & 2& Hospitality Coordinator\\
 	\hline
-	 & Total & 61\\
+	 & Total & 61&\\
 	\hline

### 2019-10-01 uiuc.tex
adds mohaghegh image

@@
 Indianapolis (IND), and Bloomington (BMI). If attendees fly into these
-airports, ground transportation to the Champaign area will be required. To this
-end, Peoria Charter is a popular bus service with several 
-daily trips between the UIUC campus and the Chicagoland area.
+airports, ground transportation to the Champaign area will be required. 
+If flying into Chicago (ORD or MDW), attendees may choose to rent a car or take a bus to 
+Champaign. The organizers recommend Peoria Charter in this case. Peoria Charter 
+is a reliable bus company that offers several shuttles throughout the day from 
+Chicago to the university. The Altgeld Hall Peoria bus stop is less than one block 
+from the Illini Union and the TownePlace Suites.
 
@@
 
-The ANS-UIUC maintains and develops a cohesive community of students in nuclear engineering.
-It also engages in education and outreach programs to teach members of the surrounding community about nuclear science.
-One of our most popular outreach programs is Engineering Open House (EOH), during which ANS-UIUC repeatedly earns awards for best presentation of a society.
-EOH is an annual event where members of the local community, from young children to senior adults, visit the engineering campus to learn more about STEM research.
+The ANS-UIUC maintains and develops a cohesive community of students in nuclear 
+engineering. It also engages in education and outreach programs to teach 
+members of the surrounding community about nuclear science. One of our most 
+popular outreach programs is Engineering Open House (EOH), during which 
+ANS-UIUC repeatedly earns awards for best presentation of a society. EOH is an 
+annual event where members of the local community, from young children to 
+senior adults, visit the engineering campus to learn more about STEM research. 
 Membership is currently around 70-80 students and has been steadily growing. 
-The chapter works to host events catering to nuclear, plasma, and radiological concentrations.
-Professional development plays a crucial role in student development, and it is the biggest part of member involvement at UIUC.
-Professional development activities range from tours of various facilities to pizza with campus visitors.
-Some of the past tours have included Clinton Power Station, Curium Pharma through UIUC Women In Nuclear, Oak Ridge National Laboratory, Analysis System (ANSYS) Inc, and Argonne National Laboratory.
-ANS-UIUC has historically been one of the best represented institutions at the annual student conference and is a tradition this chapter is eager to uphold.
+The chapter works to host events catering to nuclear, plasma, and radiological 
+concentrations. Professional development plays a crucial role in student 
+development, and it is the biggest part of member involvement at UIUC. 
+Professional development activities range from tours of various facilities to 
+pizza with campus visitors. Some of the past tours have included Clinton Power 
+Station, Curium Pharma through UIUC Women In Nuclear, Oak Ridge National 
+Laboratory, Analysis System (ANSYS) Inc, and Argonne National Laboratory. 
+ANS-UIUC has historically been one of the best represented institutions at the 
+annual student conference and hosting it is a tradition this chapter is eager 
+to uphold.
 
@@
 \subsubsection{Reliability and Risk Analysis}
+\begin{wrapfigure}{r}{0.5\textwidth}
+  \begin{center}
+  \vspace{-\baselineskip}
+    \includegraphics[width=0.48\textwidth]{mohaghegh.jpg}
+    \caption{Prof. Zahra Mohaghegh is an Assistant Professor in Nuclear, 
+          Plasma, and Radiological Engineering and director of the 
+          Socio-Technical Risk Analysis (SoTeRiA) Research Laboratory.}
+  \end{center}
+\end{wrapfigure}
 Risk analysis represents the pinnacle of interdisciplinary research and education.

### 2019-10-01 conflog.tex
15 minutes

--- 2019-09-30 conflog.tex
@@
 \end{itemize}
-This is a backup date because Easter falls on that Sunday.
-In general, this should be avoided.
-In this case we found that holding the conference at the end of April would conflict with finals for students and holding it earlier in March would conflict with several spring breaks as well as having potentially poorer weather.
-A detailed conflict schedule is listed in Appendix A on page \pageref{appendix:schedule}.
+This is a backup date because Easter falls on that Sunday. In general, this 
+should be avoided. In this case we found that holding the conference at the end 
+of April would conflict with finals for students and holding it earlier in 
+March would conflict with several spring breaks as well as having potentially 
+poorer weather. \textbf{A detailed graphical conflict schedule can be found in Appendix 
+\ref{appendix:schedule} on page \pageref{appendix:schedule}.}
 
@@
 
-The Illini Union is capable of hosting the entire technical program of the ANS Student Conference.
-This keeps the conference contained in one convenient location while being within easy access of the rest of the campus.
-Technical sessions will be held in a combination of rooms on the second, third, and fourth floors of The Union.
-Each of these rooms have at least enough capacity for 42 people, lecture style, and A/V capability.
-There will also be rooms available to have panels and workshops during the course of the technical program.
-The Illini Rooms A and B will be a combined space for the career fair while Illini Room C and the south lounge will host the poster sessions.
-We will keep the space open to allow the poster sessions and career fair to share attendance and encourage networking.
-A detailed list of room capacities and floor plans are located in Appendix D: Building Layout on page \pageref{appendix:building}.
-\\
+The Illini Union is capable of hosting the entire technical program of the ANS 
+Student Conference. This keeps the conference contained in one convenient 
+location while being within easy access of the rest of the campus. Technical 
+sessions will be held in a combination of rooms on the second, third, and 
+fourth floors of The Union. Each of these rooms have at least enough capacity 
+for 42 people, lecture style, and A/V capability. There will also be rooms 
+available to have panels and workshops during the course of the technical 
+program. The Illini Rooms A and B will be a combined space for the career fair 
+while Illini Room C and the south lounge will host the poster sessions. We will 
+keep the space open to allow the poster sessions and career fair to share 
+attendance and encourage networking. A detailed list of room capacities and 
+floor plans are located in Appendix \ref{appendix:building}: Building Layout on 
+page \pageref{appendix:building}. \\
 
@@
     \includegraphics[width=0.75\textwidth]{ihotel-dinner.png}
-    \caption{The current 400-person banquet space at the IHotel.}
+    \caption{The current 400-person banquet space at the IHotel is pictured 
+        above. A new, 690-person ballroom will be available in 2020.}
 \end{figure}
@@
 	\hline\hline
-	\textbf{Hotel} & \textbf{Distance from the Union (mi)} & \textbf{Dates} & \textbf{Number of Rooms} & \textbf{Rates*} & \textbf{Per Person**}\\
+	\textbf{Hotel} & \textbf{Distance from} & \textbf{Dates} & \textbf{Number of Rooms} & \textbf{Rates*} & \textbf{Per Person**}\\
+                & \textbf{the Union (mi)} & & & & \\
 	\hline\hline
@@
 	\end{tabular}}
+\subcaption*{\textbf{*}\textit{Price for a queen double}\\ \textbf{**}\textit{Assumes 4 people per room}}
 \end{table}
-\textbf{*}\textit{Price for a queen double}
-\textbf{**}\textit{Assumes 4 people per room}
 

### 2019-10-01 conflog.tex
grammar things + table

--- 2019-09-30 conflog.tex
@@
 The opening ceremony dinner on Thursday night will be hosted at the Garden Hotel in Urbana.
-It has a seating capacity of 600 people in rounds and offer in house catering as well as AV capabilities.
+It has a seating capacity of 600 people in round tables, offers in-house catering, and AV capabilities.
 This location was chosen for its convenience, as it would be the primary hotel for the conference.
@@
     \includegraphics[width=0.5\textwidth]{garden_dinner.jpg}
-    \caption{The Garden Hotel Banquet Hall with capacity for 600 people in rounds.}
+    \caption{The Garden Hotel Banquet Hall with capacity for 600 people in round tables.}
 \end{figure}
@@
 Dinner on Friday night will be hosted at the I Hotel.
-The I Hotel is undergoing an expansion that will increase the capacity of their banquet space to 690 people in rounds.
+The I Hotel is undergoing an expansion that will increase the capacity of their banquet space to 690 people in round tables.
 Catering is provided by University Catering which avoids a 20\% gratuity charge because of its association with the University of Illinois.
@@
 \subsubsection{Illini Union}
-After the career fair is taken down on Saturday the final dinner will be set up in the combined Illini Rooms, which has a seating capacity of 496 people in rounds.
-Catering will be provided by Universiy Catering which allows us to avoid the 20\% gratuity for services.
-A floorplan for the Illini Rooms in rounds is available in Appendix D.\\
+After the career fair is taken down on Saturday, the final dinner will be set up in the combined Illini Rooms, which has a seating capacity of 496 people in round tables.
+Catering will be provided by University Catering which allows us to avoid the 20\% gratuity for services.
+A floorplan for the Illini Rooms in round tables is available in Appendix D.\\
 
@@
     \includegraphics[width=\textwidth]{illinirooms.jpg}
-    \caption{The combined Illini rooms with capacity for 496 in rounds.}
+    \caption{The combined Illini rooms with capacity for 496 in round tables.}
 \end{figure}
@@
 Guests staying at the Illini Union Hotel are provided with vouchers for breakfast at the food court in the basement of the Union.
-The food court offers Einstein Brothers, Starbucks, Garbanzo Mediterranean, and more.
+The food court offers Einstein Bros, Starbucks, Garbanzo Mediterranean, and more.
 \subsubsection{Lunch}

### 2019-10-01 theme.tex
grammar things + table

@@
 As students, obstacles at the scale of the world climate crisis appear daunting and overwhelming.
-We believe that many solutions will come from the nuclear sciences.
+We believe that many solutions will come from nuclear science.
 The ANS Student Conference is an opportunity for students and professionals to come together and share advances in critical technology and research dedicated to solving these problems.
@@
 This theme also honors the individual, atomic, contributions from students, researchers, and professionals that are essential to progress.
-This conference is about science and engineering and it is about the people that make science and engineering possible.
+This conference is as much about science and engineering and it is about the people that make science and engineering possible.
 Students will hear from visionary speakers and leaders of the nuclear science community and come away with optimism for the future; knowing that they are saving the world one atom at a time.\\
@@
 	This is the networking and professional-development-focused section of the conference.
-Beyond the mere job-seeking aspect, these networks enable the spread of ideas.
+Beyond job-seeking aspects, these networks enable the spread of ideas.
 Additionally, this evening builds on top of the previous night as we remember that our networks also consist of people.
@@
 This aspect of the conference is captured by workshops like \textit{Developing Your Network}.
-	\item Inspire the next generation of nuclear engineers to take on grand challenge problems\\
+	\item Inspire the next generation of nuclear engineers to take on grand challenge problems. \\
 	The final day is the culmination of the conference and underpins the single unifying ideal.

### 2019-10-01 uiuc.tex
grammar things + table

--- 2019-10-01 uiuc.tex
@@
 Since its founding in the mid 19th century CU has grown into the flourishing cultural hub of the midwest it is today.
-CU houses many landmarks and districts and showcases both local and national events annually.
+CU houses many landmarks and districts, and showcases both local and national events annually.
 It is home to the Historic Virginia Theater that hosts Ebertfest in honor of the late film critic and UIUC alumnus Roger Ebert.
@@
 \subsubsection{Accessibility and Accomodation}
- Many hotels are located around downtown Champaign and the Eastern 
- side of campus, making transportation easy. Champaign-Urbana Mass Transit 
- (CU-MTD) is a reliable public transportation service that sees millions of 
- riders every year. CU-MTD charges an affordable rate of \$1 per ride, which 
- can be paid in cash or using the Token Transit app. Additionally, an all-day 
- pass can be bought on Saturdays and Sundays for \$2 from any bus operator or 
- from the app. All CU-MTD busses are wheelchair accessible. Rental bikes and 
- rideshare services are also plentiful.
- Champaign's Willard Airport (CMI) is just 15 minutes from campus and has 
-regular flights to and from Chicago O’Hare (ORD), Dallas/Fort Worth (DFW), and 
-Charlotte (CLT). Finally, Peoria Charter is a popular bus service with several 
-daily trips between the UIUC campus and the Chicagoland area.
+ A large number of hotels are located around downtown Champaign and the Eastern side of campus, making transportation easy.
+Champaign-Urbana Mass Transit (CU-MTD) is a reliable public transportation service that sees millions of riders every year.
+CU-MTD charges an affordable rate of \$1 per ride, which can be paid in cash or using the Token Transit app.
+Additionally, an all-day pass can be bought on Saturdays and Sundays for \$2 from any bus operator or from the app.
+All CU-MTD busses are wheelchair accessible.
+Rental bikes and rideshare services are also plentiful.
+There is a small airport, Willard Airport, just 20 minutes from campus that has regular flights to and from Chicago O’Hare and Dallas Fort Worth airports.
+Finally, Peoria Charter is a popular bus service with several daily trips between the UIUC campus and the Chicagoland area.
 
 \subsubsection{Weather}
-With an average high temperature of 65$^{\circ}$ and an average low temperature 
-of 40$^{\circ}$, April in Champaign is a gorgeous month of dwindling winter 
-weather and spring coming into bloom. Holding a conference during this time 
-will be the perfect way to showcase our beautiful city.
+With an average high temperature of 65$^{\circ}$ and an average low temperature of 40$^{\circ}$, April in Champaign is a gorgeous month of dwindling winter weather and spring coming into bloom.
+Holding a conference during this time would be the perfect way to showcase our beautiful city.
 
@@
 These include aspects of reactor physics, reactor thermal-hydraulics, reactor safety, reliability and risk, instrumentation and control, training and education, human factors engineering, reactor materials, nonproliferation, and more.
-Safety starndards and maintenance for existing reactors and new reactor designs are also explored by faculty in the department.
+Safety standards and maintenance for existing reactors and new reactor designs are also explored by faculty in the department.
 Crosscutting areas of research include multi-physics and multi-scale modeling and simulation, high performance computing, reliability and risk, validation and verification, and uncertainty analysis.
@@
 David Ruzic.
-Furthermore, in the past few years, three new faculty members have been added to this area including: Prof.
+Furthermore, in the past few years, two new faculty members have been added to this area including: Prof.
 Davide Curelli and Prof.
@@
 These algorithms range from the use of so-called "big data" techniques applied to large sensor networks to advanced radiological imaging methods and image processing techniques for biomedical research.
-We work with physicists, biologist, chemists, material scientists, statisticians, and physicians around the world, to develop advanced diagnostic imaging and radiation-induced therapeutic approaches to address some of the most critical health care-related issues, such as cancer, cardiac diseases, diabetes and neurodegenerative disorders.
+We work with physicists, biologists, chemists, material scientists, statisticians, and physicians around the world, to develop advanced diagnostic imaging and radiation-induced therapeutic approaches to address some of the most critical health care-related issues, such as cancer, cardiac diseases, diabetes and neurodegenerative disorders.
 We also work with organizations like the Departments of Defense, Energy, and Homeland Security and the International Atomic Energy Agency to deploy our research around the world to detect and identify the illicit movement of nuclear and radiological materials.
@@
 Enhancing the prevention of catastrophic technological accidents and the protection of the environment requires advancement in multidisciplinary PRA.
-It demands the development of a common vocabulary within diverse engineering and social science domains in order to address risks emerging from the interface of social and technical systems.
+It demands the development of a common vocabulary within diverse engineering and social science domains in order to address risks that emerge from the interface of social and technical systems.
 
@@
 Materials science research includes investigations of the mechanical properties of cladding and other structural components, and heat exchanger materials.
-Advanced microanalysis techniques are often employed to perform nano-scale interrogation of deformation, precipitation, and chemical segregation studies, for example.
-Ion beam bombardment of materials often runs concurrent with these techniques to simulate fast neutron displacement cascade damage.
+Advanced microanalysis techniques are often employed to perform nano-scale interrogation of deformation, precipitation, and chemical segregation studies, etc.
+Ion beam bombardment of materials is often used with these techniques to simulate fast neutron displacement cascade damage.
 Fuel performance modeling, molecular dynamics, and kinetic Monte Carlo simulations complement these experimental activities.
-The Department also has strong efforts related to the study of nuclear fuel such as urania, including mass transport and mechanical property studies.
-The Department also studies hydrogen in metals, including hydride phase formation and solute dislocation pipe diffusion.
+The department also has strong efforts related to the study of nuclear fuel such as urania, including mass transport and mechanical property studies.
+The department also studies hydrogen in metals, including hydride phase formation and solute dislocation pipe diffusion.
 

### 2019-10-01 conflog.tex
Grammatical edits suggested by smpark7, Roberto, and Jack

--- 2019-10-01 conflog.tex
@@
 We believe either of these dates would serve as an appropriate first choice because they avoid major conflict dates like finals and spring break for most schools.
-Additionally, mid-April offers pleasant, mild, weather in Champaign.
+Additionally, mid-April offers pleasant, mild weather in Champaign.
 The reason for proposing two weekends to host the conference is due to the UIUC tradition of hosting Mom's Weekend on or near the first weekend in April.
@@
 \end{itemize}
-This is a backup date because Easter falls on that Sunday. In general, this 
-should be avoided. In this case we found that holding the conference at the end 
-of April would conflict with finals for students and holding it earlier in 
-March would conflict with several spring breaks as well as having potentially 
-poorer weather. \textbf{A detailed graphical conflict schedule can be found in Appendix 
-\ref{appendix:schedule} on page \pageref{appendix:schedule}.}
+This is a backup date because Easter falls on that Sunday.
+In general, this should be avoided.
+In this case we found that holding the conference at the end of April would conflict with finals for students and holding it earlier in March would conflict with several spring breaks as well as having potentially poorer weather.
+A detailed conflict schedule is listed in Appendix A on page \pageref{appendix:schedule}.
 
@@
 
-The Illini Union is capable of hosting the entire technical program of the ANS 
-Student Conference. This keeps the conference contained in one convenient 
-location while being within easy access of the rest of the campus. Technical 
-sessions will be held in a combination of rooms on the second, third, and 
-fourth floors of The Union. Each of these rooms have at least enough capacity 
-for 42 people, lecture style, and A/V capability. There will also be rooms 
-available to have panels and workshops during the course of the technical 
-program. The Illini Rooms A and B will be a combined space for the career fair 
-while Illini Room C and the south lounge will host the poster sessions. We will 
-keep the space open to allow the poster sessions and career fair to share 
-attendance and encourage networking. A detailed list of room capacities and 
-floor plans are located in Appendix \ref{appendix:building}: Building Layout on 
-page \pageref{appendix:building}. \\
+The Illini Union is capable of hosting the entire technical program of the ANS Student Conference.
+This keeps the conference contained in one convenient location while being within easy access of the rest of the campus.
+Technical sessions will be held in a combination of rooms on the second, third, and fourth floors of The Union.
+Each of these rooms have at least enough capacity for 42 people, lecture style, and A/V capability.
+There will also be rooms available to have panels and workshops during the course of the technical program.
+The Illini Rooms A and B will be a combined space for the career fair while Illini Room C and the south lounge will host the poster sessions.
+We will keep the space open to allow the poster sessions and career fair to share attendance and encourage networking.
+A detailed list of room capacities and floor plans are located in Appendix D: Building Layout on page \pageref{appendix:building}.
+\\
 
@@
     \includegraphics[width=0.75\textwidth]{ihotel-dinner.png}
-    \caption{The current 400-person banquet space at the IHotel is pictured 
-        above. A new, 690-person ballroom will be available in 2020.}
+    \caption{The current 400-person banquet space at the IHotel.}
 \end{figure}
@@
 \subsubsection{Illini Union}
-After the career fair is taken down on Saturday the final dinner will be set up in the combined Illini Rooms, which has a seating capacity of 496 people in rounds.
+The final dinner will be set up in the combined Illini Rooms, which has a seating capacity of 496 people in rounds.
 Catering will be provided by Universiy Catering which allows us to avoid the 20\% gratuity for services.
@@
 \textbf{The I Hotel and Conference Center}\\
-The IHotel offers a unique, flexible, meeting space and a variety of small touches that make any meeting, social gathering or event in Champaign-Urbana a flawless and memorable experience.\\
+The I Hotel offers a unique, flexible, meeting space and a variety of small touches that make any meeting, social gathering or event in Champaign-Urbana a flawless and memorable experience.\\
 
@@
 Guests have access to Wi-Fi and, upon request, guest passes to the university recreational facilities.
-Breakfast is provided in the form vouchers for any of the hotel restaurant options inside the Union.
+Breakfast is provided in the form of vouchers for any of the hotel restaurant options inside the Union.
 Hosting technical sessions, workshops, and plenaries in the Union will help us negotiate a lower room rate.\\
@@
 
-$\textbf{Marriott TowneSuites}$\\
-In the event that attendance exceeds 600 people, we will have overflow rooms in the Marriott TowneSuites.
-Rooms at the Marriott resemble a studio apartment with an open floor plan, refrigerator, stove, microwave,dishes, and dining area.
+$\textbf{Marriott TownePlace Suites}$\\
+In the event that attendance exceeds 600 people, we will have overflow rooms in the Marriott TownePlace Suites.
+Rooms at the Marriott resemble a studio apartment with an open floor plan, refrigerator, stove, microwave, dishes, and dining area.
 Many rooms are equipped with pull-out couches, allowing 5 students to share a queen double room if desired.
@@
 	\hline\hline
-	\textbf{Hotel} & \textbf{Distance from} & \textbf{Dates} & \textbf{Number of Rooms} & \textbf{Rates*} & \textbf{Per Person**}\\
-                & \textbf{the Union (mi)} & & & & \\
+	\textbf{Hotel} & \textbf{Distance from the Union (mi)} & \textbf{Dates} & \textbf{Number of Rooms} & \textbf{Rates*} & \textbf{Per Person**}\\
 	\hline\hline
@@
 	\end{tabular}}
-\subcaption*{\textbf{*}\textit{Price for a queen double}\\ \textbf{**}\textit{Assumes 4 people per room}}
+\subcaption*{\textbf{*}\textit{Price for a queen double} \textbf{**}\textit{Assumes 4 people per room}}
 \end{table}
@@
 Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip.
-Due to the central location of UIUC, driving might be a good option for some schools and individuals.
+Due to the central location of Champaign-Urbana, driving might be a good option for some schools and individuals.
 Table \ref{table:ground} shows the approximate driving times and costs from several universities.

### 2019-10-01 socials.tex
Grammatical edits suggested by smpark7, Roberto, and Jack

--- 2019-09-30 socials.tex
@@
 The Illini Union Rec Room is located in the basement of the Union building.
-A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at the Krannert Center for Performing Arts, only a short walk away through the University of Illinois main quad!
+A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at the Illini Union!
 This space can accompany up to 150 people, with extra tables outside of the Rec Room for socializing, playing board games, or having a late night snack or coffee with professionals or students from other universities.

### 2019-10-01 theme.tex
Grammatical edits suggested by smpark7, Roberto, and Jack

--- 2019-09-30 theme.tex
@@
 This aspect of the conference is captured by workshops like \textit{Developing Your Network}.
-	\item Inspire the next generation of nuclear engineers to take on grand challenge problems\\
+	\item Inspire the next generation of nuclear engineers to take on grand challenge problems.\\
 	The final day is the culmination of the conference and underpins the single unifying ideal.

### 2019-10-01 uiuc.tex
Grammatical edits suggested by smpark7, Roberto, and Jack

--- 2019-10-01 uiuc.tex
@@
 \subsubsection{Accessibility and Accomodation}
- Many hotels are located around downtown Champaign and the Eastern 
- side of campus, making transportation easy. Champaign-Urbana Mass Transit 
- (CU-MTD) is a reliable public transportation service that sees millions of 
- riders every year. CU-MTD charges an affordable rate of \$1 per ride, which 
- can be paid in cash or using the Token Transit app. Additionally, an all-day 
- pass can be bought on Saturdays and Sundays for \$2 from any bus operator or 
- from the app. All CU-MTD busses are wheelchair accessible. Rental bikes and 
- rideshare services are also plentiful.
- Champaign's Willard Airport (CMI) is just 15 minutes from campus and has 
-regular flights to and from Chicago O’Hare (ORD), Dallas/Fort Worth (DFW), and 
-Charlotte (CLT).  Other nearby airports include Chicago (ORD and MDW),
-Indianapolis (IND), and Bloomington (BMI). If attendees fly into these
-airports, ground transportation to the Champaign area will be required. To this
-end, Peoria Charter is a popular bus service with several 
-daily trips between the UIUC campus and the Chicagoland area.
+ A large number of hotels are located around downtown Champaign and the Eastern side of campus, making transportation easy.
+Champaign-Urbana Mass Transit (CU-MTD) is a reliable public transportation service that sees millions of riders every year.
+CU-MTD charges an affordable rate of \$1 per ride, which can be paid in cash or using the Token Transit app.
+Additionally, an all-day pass can be bought on Saturdays and Sundays for \$2 from any bus operator or from the app.
+All CU-MTD busses are wheelchair accessible.
+Rental bikes and rideshare services are also plentiful.
+There is a small airport, Willard Airport, just 20 minutes from campus that has regular flights to and from Chicago O’Hare and Dallas Fort Worth airports.
+Finally, Peoria Charter is a popular bus service with several daily trips between the UIUC campus and the Chicagoland area.
 
 \subsubsection{Weather}
-With an average high temperature of 65$^{\circ}$ and an average low temperature 
-of 40$^{\circ}$, April in Champaign is a gorgeous month of dwindling winter 
-weather and spring coming into bloom. Holding a conference during this time 
-will be the perfect way to showcase our beautiful city.
+With an average high temperature of 65$^{\circ}$ and an average low temperature of 40$^{\circ}$, April in Champaign is a gorgeous month of dwindling winter weather and spring coming into bloom.
+Holding a conference during this time would be the perfect way to showcase our beautiful city.
 
@@
 Attendees might also be familiar with Blue Waters, one of the world’s fastest supercomputers.
-The UIUC Grainger College of Engineering has had sixteen Nobel Laureates in physics.
-Including John Bardeen, the only scientist to ever win the award in physics twice.
+The UIUC Grainger College of Engineering has had sixteen Nobel Laureates in physics, including John Bardeen, the only scientist to ever win the award in physics twice.
 It also offers 15 different majors to almost 6000 undergraduate and 2500 graduate students.
@@
 It also engages in education and outreach programs to teach members of the surrounding community about nuclear science.
-One of our most popular outreach programs is Engineering Open House (EOH), during which ANS-UIUC repeatedly earns awards for best presentation of a society.
-EOH is an annual event where members of the local community, from young children to senior adults, visit the engineering campus to learn more about STEM research.
+One of our most popular outreach programs is Engineering Open House (EOH), an annual event where members of the local community, from young children to senior adults, visit the engineering campus to learn more about STEM research; ANS-UIUC has repeatedly earned awards for best presentation of a society at EOH.
 Membership is currently around 70-80 students and has been steadily growing.
@@
   \end{subfigure}   
+  \caption{ANS Activities}
 \end{figure}
@@
 \begin{itemize}
-        \item \textbf{Nuclear Power} (reactor physics, thermalhydraulics, fuel cycle, radiation transport, I\&C)
+        \item \textbf{Nuclear Power} (reactor physics, thermal hydraulics, fuel cycle, radiation transport, I\&C)
         \item \textbf{Plasma and Fusion} (modeling, plasma-material interactions)
@@
 \end{wrapfigure}
-The Fusion and Plasma Physics research theme in the NPRE department has a long history of work in the area of magnetic and inertial nuclear fusion as well as plasma engineering.
+The Fusion and Plasma Physics research concentration in the NPRE department has a long history of work in the area of magnetic and inertial nuclear fusion as well as plasma engineering.
 NPRE is now one of the leading departments in plasma-material interactions with its Center for Plasma-Materials Interactions established by Prof.
 David Ruzic.
-Furthermore, in the past few years, three new faculty members have been added to this area including: Prof.
+Furthermore, in the past few years, two new faculty members have been added to this area: Prof.
 Davide Curelli and Prof.
@@
   The ARFC group seeks to advance the safety and sustainability of nuclear energy production through improved reactor designs, fuel cycle strategies, and waste management techniques.
-In the area of advanced reactors, our work focuses on extending current simulation tools with features essential to advanced reactor multiphysics.
+In the area of advanced reactors, their work focuses on extending current simulation tools with features essential to advanced reactor multiphysics.
 In the context of the broader nuclear fuel cycle, the ARFC group emphasizes modeling, simulation, and analysis of the global nuclear fuel cycle, with an emphasis on sustainability.
@@
   The ARTS group performs deterministic safety analysis by developing and validating advanced methods to accurately determine reactor safety margins and reactor behavior.
-By performing high-fidelity numerical predictions of the reactor behavior in abnormal transient scenarios of safety significance, our work supports the nuclear reactor safety analysis, and increases the fidelity of primary system simulation.
+By performing high-fidelity numerical predictions of the reactor behavior in abnormal transient scenarios of safety significance, their work supports the nuclear reactor safety analysis, and increases the fidelity of primary system simulation.
 This approach is at the heart of nuclear power’s excellent safety record – always striving to improve current tools and methods.
@@
 The structure and dynamics of these systems are either inherently complex or driven away from equilibrium by extreme conditions.
-In particular, our current interests include a range of fundamental and technical problems involving slow phenomena and rare events, such as: materials far from equilibrium and in extreme environments; extreme properties of liquids; and glassy or jammed soft matters.
+In particular, their current interests include a range of fundamental and technical problems involving slow phenomena and rare events, such as: materials far from equilibrium and in extreme environments; extreme properties of liquids; and glassy or jammed soft matters.
 
@@
   The Radiation Detection and Imaging Lab focuses on developing non-invasive imaging technology for use in preclinical medical research.
-Many of our current endeavors focus on developing semiconductor Single Photon Emission Computed Tomography (SPECT) and Positron Emission Tomography (PET).
+Many of their current endeavors focus on developing semiconductor Single Photon Emission Computed Tomography (SPECT) and Positron Emission Tomography (PET).
 These works challenge the current state of the art for spatial resolution and system sensitivity.
-The use of highly pixelated CdTe detectors has driven our work to break into a spatial resolution on the order of 300 microns for both PET and SPECT.
-Our work in SPECT has also challenged the limits of aperture sensitivity through the engineering of the compound-eye aperture.
+The use of highly pixelated CdTe detectors has driven their work to break into a spatial resolution on the order of 300 microns for both PET and SPECT.
+Their work in SPECT has also challenged the limits of aperture sensitivity through the engineering of the compound-eye aperture.
 

### 2019-10-01 banking.tex

@@
 
+\paragraph{Tax Exemption} will be discussed with meeting planning staff at
+ANS Headquarters. The University of Illinois is tax exempt in the state of Illinois. 
+Additionally, we will work driectly with ANS Headquarters to ensure tax 
+exemption. Since ANS is incorporated under the General Not for Profit 
+Corporation Act of Illinois, we expect this will be straightforward. We 
+additionally expect such discussions will be facilitated by the physical 
+proximity of ANS Headquarters and the University of Illinois (a 2 hour drive).
+
 \subsubsection{Financial Oversight}

### 2019-10-01 budget.tex

@@
 \subsection{Cost of Attendance and Student Reimbursement}
-The cost of attending the student conference, per student, varies among schools and is highly dependent on distance from UIUC and the preferred mode of travel.
-We will assume that minimizing cost is a priority for schools, thus number of persons per hotel room is assumed to be double the number of beds.
-The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport.
-There is also a small airport located just 20 minutes outside of campus.
-While some students may wish to make use of the convenience of the local airport, in general the most economic method of arriving in Champaign is by first flying to O’Hare and then busing.
-The average cost of this trip comes out to be \$293 as shown in Table  \ref{table:airfare}.
-Adding this to the registration and lodging costs (see Table \ref{table:hotels}) for four nights (as students often arrive Wednesday evening) and assuming four students per room, the total cost of attendance for each student comes out to an average of \$447.
-The travel reimbursement is meant to help mitigate some or most of the costs for students coming to this conference to encourage future attendance at other conferences.
+The cost of attending the student conference, per student, varies among schools 
+and is highly dependent on distance from UIUC and the preferred mode of travel. 
+We will assume that minimizing cost is a priority for schools, thus number of 
+persons per hotel room is assumed to be double the number of beds. The 
+University of Illinois is a 2.5 hour drive from one of the largest airports in 
+the world, O'Hare International Airport. There is also a small airport located 
+just 15 minutes outside of campus which has regular flights to Chicago O'Hare 
+(ORD), Dallas/Fort Worth (DFW), and Charlotte (CLT). While some students may 
+wish to make use of the convenience of the local airport, in general the most 
+economic method of arriving in Champaign is by first flying to O’Hare and then 
+busing. The average cost of this trip comes out to be \$293 as shown in Table  
+\ref{table:airfare}. Adding this to the registration and lodging costs (see 
+Table \ref{table:hotels}) for four nights (as students often arrive Wednesday 
+evening) and assuming four students per room, \textbf{the total cost of attendance for 
+each student comes out to an average of \$447.} The travel reimbursement is 
+meant to help mitigate some or most of the costs for students coming to this 
+conference to encourage future attendance at other conferences.
 

### 2019-10-01 uiuc.tex
grammar fixes

--- 2019-10-01 uiuc.tex
@@
 \subsubsection{Accessibility and Accomodation}
- A large number of hotels are located around downtown Champaign and the Eastern side of campus, making transportation easy.
-Champaign-Urbana Mass Transit (CU-MTD) is a reliable public transportation service that sees millions of riders every year.
-CU-MTD charges an affordable rate of \$1 per ride, which can be paid in cash or using the Token Transit app.
-Additionally, an all-day pass can be bought on Saturdays and Sundays for \$2 from any bus operator or from the app.
-All CU-MTD busses are wheelchair accessible.
-Rental bikes and rideshare services are also plentiful.
-There is a small airport, Willard Airport, just 20 minutes from campus that has regular flights to and from Chicago O’Hare and Dallas Fort Worth airports.
-Finally, Peoria Charter is a popular bus service with several daily trips between the UIUC campus and the Chicagoland area.
+ Many hotels are located around downtown Champaign and the Eastern 
+ side of campus, making transportation easy. Champaign-Urbana Mass Transit 
+ (CU-MTD) is a reliable public transportation service that sees millions of 
+ riders every year. CU-MTD charges an affordable rate of \$1 per ride, which 
+ can be paid in cash or using the Token Transit app. Additionally, an all-day 
+ pass can be bought on Saturdays and Sundays for \$2 from any bus operator or 
+ from the app. All CU-MTD busses are wheelchair accessible. Rental bikes and 
+ rideshare services are also plentiful.
+ Champaign's Willard Airport (CMI) is just 15 minutes from campus and has 
+regular flights to and from Chicago O’Hare (ORD), Dallas/Fort Worth (DFW), and 
+Charlotte (CLT).  Other nearby airports include Chicago (ORD and MDW),
+Indianapolis (IND), and Bloomington (BMI). If attendees fly into these
+airports, ground transportation to the Champaign area will be required. 
+If flying into Chicago (ORD or MDW), attendees may choose to rent a car or take a bus to 
+Champaign. The organizers recommend Peoria Charter in this case. Peoria Charter 
+is a reliable bus company that offers several shuttles throughout the day from 
+Chicago to the university. The Altgeld Hall Peoria bus stop is less than one block 
+from the Illini Union and the TownePlace Suites.
 
 \subsubsection{Weather}
-With an average high temperature of 65$^{\circ}$ and an average low temperature of 40$^{\circ}$, April in Champaign is a gorgeous month of dwindling winter weather and spring coming into bloom.
-Holding a conference during this time would be the perfect way to showcase our beautiful city.
+With an average high temperature of 65$^{\circ}$ and an average low temperature 
+of 40$^{\circ}$, April in Champaign is a gorgeous month of dwindling winter 
+weather and spring coming into bloom. Holding a conference during this time 
+will be the perfect way to showcase our beautiful city.
 
@@
 
-\clearpage
+% \clearpage
 
@@
 
+\subsubsection{Reliability and Risk Analysis}
+\begin{wrapfigure}{r}{0.5\textwidth}
+  \begin{center}
+  \vspace{-\baselineskip}
+    \includegraphics[width=0.48\textwidth]{mohaghegh.jpg}
+    \caption{Prof. Zahra Mohaghegh is an Assistant Professor in Nuclear, 
+          Plasma, and Radiological Engineering and director of the 
+          Socio-Technical Risk Analysis (SoTeRiA) Research Laboratory.}
+  \end{center}
+\end{wrapfigure}
+Risk analysis represents the pinnacle of interdisciplinary research and education.
+Following the Three Mile Island disaster in 1979, Probabilistic Risk Assessment (PRA) has become a key pillar of the risk-informed nuclear regulatory framework, and is now a requirement for every nuclear power plant in the United States.
+Enhancing the prevention of catastrophic technological accidents and the protection of the environment requires advancement in multidisciplinary PRA.
+It demands the development of a common vocabulary within diverse engineering and social science domains in order to address risks emerging from the interface of social and technical systems.
 \subsubsection{NPRE Research Groups and Laboratories}

### 2019-10-01 theme.tex
nuclear science(s)
grammar

--- 2019-10-01 theme.tex
@@
 As students, obstacles at the scale of the world climate crisis appear daunting and overwhelming.
-We believe that many solutions will come from nuclear science.
+We believe that many solutions will come from the nuclear sciences.
 The ANS Student Conference is an opportunity for students and professionals to come together and share advances in critical technology and research dedicated to solving these problems.
@@
 This theme also honors the individual, atomic, contributions from students, researchers, and professionals that are essential to progress.
-This conference is as much about science and engineering and it is about the people that make science and engineering possible.
+This conference is about science and engineering and it is about the people that make science and engineering possible.
 Students will hear from visionary speakers and leaders of the nuclear science community and come away with optimism for the future; knowing that they are saving the world one atom at a time.\\

### 2019-10-01 conflog.tex

--- 2019-10-01 conflog.tex
@@
 	\end{tabular}}
-\subcaption*{\textbf{*}\textit{Price for a queen double} \textbf{**}\textit{Assumes 4 people per room}}
+\subcaption*{\textbf{*}\textit{Price for a queen double}\\ \textbf{**}\textit{Assumes 4 people per room}}
 \end{table}

### 2019-10-01 conflog.tex
minor changes

@@
 The opening ceremony dinner on Thursday night will be hosted at the Garden Hotel in Urbana.
-It has a seating capacity of 600 people in round tables, offers in-house catering, and AV capabilities.
+It has a seating capacity of 600 people in rounds and offer in house catering as well as AV capabilities.
 This location was chosen for its convenience, as it would be the primary hotel for the conference.
@@
     \includegraphics[width=0.5\textwidth]{garden_dinner.jpg}
-    \caption{The Garden Hotel Banquet Hall with capacity for 600 people in round tables.}
+    \caption{The Garden Hotel Banquet Hall with capacity for 600 people in rounds.}
 \end{figure}
@@
 Dinner on Friday night will be hosted at the I Hotel.
-The I Hotel is undergoing an expansion that will increase the capacity of their banquet space to 690 people in round tables.
+The I Hotel is undergoing an expansion that will increase the capacity of their banquet space to 690 people in rounds.
 Catering is provided by University Catering which avoids a 20\% gratuity charge because of its association with the University of Illinois.
 This expansion is set to be completed by Fall 2020.
-We will be hosting a social at the 77 Club in Memorial Stadium, just up the street.
+We will be hosting a social at the 77 Club in Memorial Stadium, which is just a brief walk up the street.
 Information about the I Hotel expansion is included in Appendix D.
+Cost of transportation to and from the I Hotel and 77 Club are discussed in the budget section..
 
@@
 \subsubsection{Illini Union}
-After the career fair is taken down on Saturday, the final dinner will be set up in the combined Illini Rooms, which has a seating capacity of 496 people in round tables.
-Catering will be provided by University Catering which allows us to avoid the 20\% gratuity for services.
-A floorplan for the Illini Rooms in round tables is available in Appendix D.\\
+After the career fair is taken down on Saturday the final dinner will be set up in the combined Illini Rooms, which has a seating capacity of 496 people in rounds.
+Catering will be provided by Universiy Catering which allows us to avoid the 20\% gratuity for services.
+A floorplan for the Illini Rooms in rounds is available in Appendix D.\\
 
@@
     \includegraphics[width=\textwidth]{illinirooms.jpg}
-    \caption{The combined Illini rooms with capacity for 496 in round tables.}
+    \caption{The combined Illini rooms with capacity for 496 in rounds.}
 \end{figure}
@@
 The Garden Hotel Urbana (soon to be the Radisson) will be the primary hotel for all attendees.
+It features complimentary breakfast for its guests every morning.
 This will also be the location of the opening ceremony dinner.
-Since this hotel is just beyond walking distance from the main conference activities, we will hire four Peoria Charter busses to shuttle attendees to and from the Union every 10 minutes.
-Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 8am to 6pm.
-\\
+Since this hotel is just beyond walking distance from the main conference activities (2.2 miles), we will hire four Peoria Charter busses to shuttle attendees to and from the Union every 10 minutes.
+Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 7am to 5am the following day for weekdays, and every 30 minutes on weekends.\\
 \begin{figure}[H]
@@
 Guests staying at the Illini Union Hotel are provided with vouchers for breakfast at the food court in the basement of the Union.
-The food court offers Einstein Bros, Starbucks, Garbanzo Mediterranean, and more.
+The food court offers Einstein Brothers, Starbucks, Garbanzo Mediterranean, and more.
 \subsubsection{Lunch}
@@
 Communities like ANS thrive on the exchange of ideas and knowledge.
-The student conference serves plays an essential role by connecting the burgeoning minds of the next generation with the wisdom of established professionals.
-This dinner will consist of tables organized by company/national lab to allow students and professionals to mingle, promoting the exchange of ideas.\\\\
+The student conference plays an essential role by connecting the burgeoning minds of the next generation with the wisdom of established professionals.
+This dinner will consist of tables organized by company/national lab, or by topic/discipline area, to allow students and professionals to mingle, promoting the exchange of ideas.\\\\
 \indent\textbf{Saturday Night}\\
@@
 Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip.
+While travel from airport to hotel can be managed by train (Amtrak/Metra), the conference planning committee excluded this option due to the added complexities of getting from the airport to train station, and train station to hotel with the associated costs of doing so.
+We recommend Peoria Charter because it is the most direct option for travel from O'Hare Aiport to the Illini Union.
 Due to the central location of UIUC, driving might be a good option for some schools and individuals.

### 2019-10-01 socials.tex
minor changes

--- 2019-09-30 socials.tex
@@
 %% Reserve for Pour Bros. social %%%
-\subsubsection{Pour Bros. Taproom in Downtown Champaign}
-Welcome to Illinois' first pour-your-own taprooms.
+% \subsubsection{Pour Bros. Taproom in Downtown Champaign}
+% Welcome to Illinois' first pour-your-own taprooms.
 Pour Bros.
@@
 If you are feeling more on the leisurely side, Pour Bros features live music in a spacious and comfortable seating area for you to get your networking on.
-\vspace{0.5cm}\newline
-% Pour Bros Picture
-\begin{figure}[H]
+% \vspace{0.5cm}\newline
+% % Pour Bros Picture
+% \begin{figure}[H]
 
-	\centering
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.4\linewidth]{pour_bros2.png}
-	\end{subfigure}%
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.7\linewidth]{pour_bros1.png}
-	\end{subfigure}	
-	\caption{Pour Brothers Taproom}	
-\end{figure}
+% 	\centering
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=0.4\linewidth]{pour_bros2.png}
+% 	\end{subfigure}%
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=0.7\linewidth]{pour_bros1.png}
+% 	\end{subfigure}	
+% 	\caption{Pour Brothers Taproom}	
+% \end{figure}
 
@@
 
-\subsubsection{Under 21 Social: University of Illinois Ice Arena}
-For students under the drinking age that cannot attend the Pour Bros.
+% \subsubsection{Under 21 Social: University of Illinois Ice Arena}
+% For students under the drinking age that cannot attend the Pour Bros.
 Taproom social event, the University of Illinois Ice Arena is another option that is only a brief walking distance from the Union.
@@
 Snacks and concession items are also available.
-\vspace{0.5cm}\newline
-% Ice Arena Picture
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.8\textwidth]{ice_arena.png}
-	\caption{The UIUC Ice Arena}
-\end{figure}
+% \vspace{0.5cm}\newline
+% % Ice Arena Picture
+% \begin{figure}[H]
+% 	\centering
+% 	\includegraphics[width=0.8\textwidth]{ice_arena.png}
+% 	\caption{The UIUC Ice Arena}
+% \end{figure}

### 2019-10-01 conflog.tex

@@
 \subsubsection{I Hotel}
+
 Dinner on Friday night will be hosted at the I Hotel.
@@
 Information about the I Hotel expansion is included in Appendix D.
-Cost of transportation to and from the I Hotel and 77 Club are discussed in the budget section..
+Cost of transportation to and from the I Hotel and 77 Club are discussed in the budget section.
 

### 2019-10-01 conflog.tex

@@
 Catering will be provided by University Catering which allows us to avoid the 20\% gratuity for services.
-A floorplan for the Illini Rooms in round tables is available in Appendix D.\\
+A floorplan for the Illini Rooms in round tables is available in \textbf{Appendix D}.\\
 

### 2019-10-01 management.tex
grammar things + table

@@
 
-		\node (tsc chair) [director, below of = tech chair, xshift = 2cm, yshift = -2cm] {Technical Sub-Committee Chair (Gwen Chee)};
+		\node (tsc chair) [director, below of = tech chair, xshift = 2cm, yshift = -2cm] {Technical Sub-Committee Chair (Gwendolyn Chee)};
 		\node (work coord) [coordinator, below of = tsc chair, yshift = -2cm] {Workshops Coordinator\\(Roberto Fairhurst)};
@@
 \subsection{Staffing Requirements}
-Staffing for room breakdowns and setups, registration, socials, workshops, tours, etc.
-will be supplied by either UIUC ANS members or students of the NPRE department.
-While it is likely that members of our student chapter will voluntarily fill all the staffing requirements of conference hosted events.
-If not, we will rely on other student organizations for support including, but not limited to: Arms Control and Domestic and International Security (ACDIS) and Women in Engineering (WIE).
-Participating in conference events on a staff level is a beneficial experience for any undergraduate who wants to become more familiar with ANS or support their ANS Chapter.
-Throughout the conference, interacting with registering students, driving groups to tour a scientific facility, and turning rooms for technical sessions provide plentiful opportunities for volunteers to interact with myriad members on a number of levels.
-Thus, it will be an overall positive experience for the volunteers.
-Quantitative needs are outlined in Appendix G on page \pageref{appendix:staff}.
+Staffing for room breakdowns and setups, registration, socials, workshops, 
+tours, etc.  will be supplied by either UIUC ANS members or students of the 
+NPRE department. While it is likely that members of our student chapter will 
+voluntarily fill all the staffing requirements of conference hosted events. If 
+not, we will rely on other student organizations for support including, but not 
+limited to: Arms Control and Domestic and International Security (ACDIS) and 
+Women in Engineering (WIE). Participating in conference events on a staff level 
+is a beneficial experience for any undergraduate who wants to become more 
+familiar with ANS or support their ANS Chapter. Throughout the conference, 
+interacting with registering students, driving groups to tour a scientific 
+facility, and turning rooms for technical sessions provide plentiful 
+opportunities for volunteers to interact with myriad members on a number of 
+levels. Thus, it will be an overall positive experience for the volunteers. 
+Quantitative needs are outlined in Appendix \ref{appendix:staff} on page 
+\pageref{appendix:staff}.
 

### 2019-10-01 uiuc.tex

@@
 \subsection{UIUC ANS Student Chapter (ANS-UIUC)}
-
 The ANS-UIUC maintains and develops a cohesive community of students in nuclear 
@@
 \end{wrapfigure}
-The Fusion and Plasma Physics research theme in the NPRE department has a long history of work in the area of magnetic and inertial nuclear fusion as well as plasma engineering.
+The Fusion and Plasma Physics research concentration in the NPRE department has a long history of work in the area of magnetic and inertial nuclear fusion as well as plasma engineering.
 NPRE is now one of the leading departments in plasma-material interactions with its Center for Plasma-Materials Interactions established by Prof.
 David Ruzic.
-Furthermore, in the past few years, two new faculty members have been added to this area including: Prof.
+Furthermore, in the past few years, two new faculty members have been added to this area: Prof.
 Davide Curelli and Prof.

### 2019-10-01 proglog.tex

@@
 In 2008 she founded a nonprofit organization aimed at reaching women, minorities, and young people with critical information about climate change and nuclear energy.
-She currently works as the creative director for Fast Path to Zero Initiatve at the University of Michigan and as a Nuclear security fellow with Third Way Energy.
+She currently works as the creative director for Fast Path to Zero Initiative at the University of Michigan and as a Nuclear security fellow with Third Way Energy.
 Baker's work in empowering minorities and students to solve the world climate crisis with nuclear energy, as well as her skill in creative science communication, ensures that Baker has a lot to offer the student conference.
@@
 Her team, made up of scientists and engineers from across the US, conducted and guided important research that enabled power companies to be able to make informed decisions regarding long-term operation broadly, and second licence renewal specifically, for their operating nuclear units.
-Her expertise, leadership and contributions to the nuclear science and technology community are globally recognized, having received the American Nuclear Society Presidential Citation (2015, 2007), and the Partnership for Science \& Technology Nuclear Energy Advocate of the Year Award (2011), among many others.
-Her many contributions to the nuclear industry indicate that she would make a great speaker at this confrence.
+Her expertise, leadership and contributions to the nuclear science and technology community are globally recognized, having received the American Nuclear Society Presidential Citation (2007, 2015), and the Partnership for Science \& Technology Nuclear Energy Advocate of the Year Award (2011), among many others.
+Her many contributions to the nuclear industry indicate that she would make a great speaker at this conference.
 \end{minipage}

### 2019-10-01 theme.tex

@@
 	This is the networking and professional-development-focused section of the conference.
-Beyond job-seeking aspects, these networks enable the spread of ideas.
+Beyond the job-seeking aspects, these networks enable the spread of ideas.
 Additionally, this evening builds on top of the previous night as we remember that our networks also consist of people.
@@
 	\item Inspire the next generation of nuclear engineers to take on grand challenge problems. \\
+
 	The final day is the culmination of the conference and underpins the single unifying ideal.

### 2019-10-01 proglog.tex
fixes tour info

@@
 
+The tours of Blue Waters and Starfire Industries will be a combined tour. Visitors will spend approximately 1.5 hours at each location. These tours will depart from the hotel. 
 \noindent{
 \begin{minipage}{0.5\textwidth}
-	\textbf{National Petascale Computing Facility (NPCF)}\\
+	\textbf{National Petascale Computing Facility (NPCF) - Blue Waters}\\
 Also located on campus is NCSA, which houses Blue Waters, one of the most powerful supercomputers in the world.
@@
 \noindent{\begin{minipage}{0.5\textwidth}
-	\textbf{University Tour}\\
-Attendees will be able to take a tour of the UIUC campus.
+	\textbf{NPRE Lab Tours}\\
+Attendees will be able to take a tour of the various NPRE labs on campus.
 They will start at the Talbot Laboratory where the department of Nuclear Plasma and Radiological Engineering is located.
 Here, students will get to see the Virtual Education and Research Laboratory to see how virtual reality technology can be adapted and applied to educational methods.
+After, they will walk across the Engineering Quad to the Center for Plasma-Material Interactions (CPMI) where students conduct experiments on the stellerator-tokamak, HIDRA.
 There are also many other historical artifacts on display for participants to see.
-Afterwards, students will be led to various noteworthy locations unique to UIUC.
+This tour will depart from the front entrance of the Illini Union.
 \end{minipage}

### 2019-10-01 conflog.tex
makes various updates

@@
 
-\subsubsection{Getting to the Conference}
-The primary hotel, Garden Hotel Urbana, is approximately two miles from the Union and outside of reasonable walking distance.
-Thus we have budgeted to include transportation provided by Peoria Charter.
-We intend to have busses shuttling continuously between the Union and the Garden Hotel Urbana.
-For those who desire more flexibility and freedom, there is CU-MTD bus stop adjacent to the hotel that has a bus every 10 minutes.
-This bus route, the 22 Illini, can take attendees directly to the Union from the hotel.
-It is also one of the main campus bus routes and can take travelers almost anywhere on or around campus.
-Lyft and Uber are available as well for attendees that choose to use those services.
-A map of the bus route is in Appendix E: Campus Map of Locations on page \pageref{appendix:map}.
+\input{conftrans}
 

### 2019-10-01 conftrans.tex
makes various updates

\subsubsection{Getting to the Conference}
% The primary hotel, Garden Hotel Urbana, is approximately two miles from the Union and outside of reasonable walking distance. Thus we have budgeted to include transportation provided by Peoria Charter. We intend to have busses shuttling continuously between the Union and the Garden Hotel Urbana. For those who desire more flexibility and freedom, there is CU-MTD bus stop adjacent to the hotel that has a bus every 10 minutes. This bus route, the 22 Illini, can take attendees directly to the Union from the hotel. It is also one of the main campus bus routes and can take travelers almost anywhere on or around campus. Lyft and Uber are available as well for attendees that choose to use those services. A map of the bus route is in Appendix E: Campus Map of Locations on page \pageref{appendix:map}.
Each day of the conference, there will be four, 55 passenger, busses from Peoria Charter outside the hotel by 7:00 AM. They will leave as they fill up and be staggered such that there will be two busses arriving at either the Union or the hotel every ten minutes. These busses will run throughout the day from 7:00 AM to 5:00 PM. At 5:00 PM the busses will begin transporting attendees to the dinner venue (except on Thursday night when the dinner is located at the Garden Hotel) until 6:00 PM. Busses will be available at 8:00 PM until 9:00 PM to transport attendees either back to the hotel or to the evening social. The final rounds of busses will be optionally available to take attendees from the social to the hotel at 10pm. For those who desire more flexibility and freedom, there is CU-MTD bus stop adjacent to the hotel that has a bus every 10 minutes. This bus route, the 22 Illini, can take attendees directly to the Union from the hotel. It is also one of the main campus bus routes and can take travelers almost anywhere on or around campus. Lyft and Uber are available as well for attendees that choose to use those services. A map of the bus route is in Appendix E: Campus Map of Locations on page \pageref{appendix:map}.
\begin{figure}[H]
	\centering
	\label{figure:busses}
	\includegraphics[width=\textwidth]{transportation.png}
	\caption{Summary of Bus Transportation}
	\subcaption*{Same color refers to same set of busses.}
\end{figure}

### 2019-10-01 management.tex
makes various updates

@@
 \begin{minipage}{0.73\textwidth}
-$\textbf{Technical Subcommittee Chair - Gwen Chee}$\\
+$\textbf{Technical Subcommittee Chair - Gwendolyn Chee}$\\
 	Gwen is a third year graduate student studying fuel cycles for advanced reactor designs with Dr.

### 2019-10-01 proglog.tex
makes various updates

@@
 Due to this, we will be able to expand the number of attendees that can go on these tours over previous conferences.
-These will require sign up before the conference and we expect spots to fill up quickly.\\
+These will require sign up before the conference and we expect spots to fill up quickly.
+Attendees will have the option of choosing one brewery tour.\\
 
@@
 	\textbf{Riggs Brewery Tour}\\
-For 21+ attendees, two tours of a local brewery will be included in our tours list Thursday afternoon from 3-5pm.
+For 21+ attendees, two tours of a local brewery will be included in our tours list Thursday afternoon from 11-1pm.
 Find out how Riggs makes their beer and taste test it along the way.
 Each tour will last approximately one hour and accommodates up to 20 people per tour.
+There will be a variety of food trucks at the brewery to purchase lunch.
 Riggs is located in east Urbana.
@@
 
+\vspace{0.5cm}
 \noindent{\begin{minipage}{0.5\textwidth}

### 2019-10-01 conflog.tex

@@
 \subsubsection{I Hotel}
-
 Dinner on Friday night will be hosted at the I Hotel.
@@
 This will also be the location of the opening ceremony dinner.
-Since this hotel is just beyond walking distance from the main conference activities (2.2 miles), we will hire four Peoria Charter busses to shuttle attendees to and from the Union every 10 minutes.
+Since this hotel is just beyond walking distance from the main conference activities (2.2 miles), we will hire four Peoria Charter buses to shuttle attendees to and from the Union every 10 minutes.
 Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 7am to 5am the following day for weekdays, and every 30 minutes on weekends.\\
+>>>>>>> upstream/master
 \begin{figure}[H]
@@
 
-$\textbf{Marriott TownePlace Suites}$\\
-In the event that attendance exceeds 600 people, we will have overflow rooms in the Marriott TownePlace Suites.
-Rooms at the Marriott resemble a studio apartment with an open floor plan, refrigerator, stove, microwave, dishes, and dining area.
+$\textbf{Marriott TowneSuites}$\\
+The Marriott TowneSuites is the professional's designated hotel; and, in the event that attendance exceeds 600 people, we will have overflow rooms in the Marriott TowneSuites.
+Rooms at the Marriott resemble a studio apartment with an open floor plan, refrigerator, stove, microwave,dishes, and dining area.
 Many rooms are equipped with pull-out couches, allowing 5 students to share a queen double room if desired.
@@
 For $\$7$ a day, guests may park in a parking garage with 8ft clearance.\\
+
 \begin{figure}[H]
@@
 Communities like ANS thrive on the exchange of ideas and knowledge.
-The student conference plays an essential role by connecting the burgeoning minds of the next generation with the wisdom of established professionals.
-This dinner will consist of tables organized by company/national lab, or by topic/discipline area, to allow students and professionals to mingle, promoting the exchange of ideas.\\\\
+The student conference serves plays an essential role by connecting the burgeoning minds of the next generation with the wisdom of established professionals.
+This dinner will consist of tables organized by company/national laboratory or by topic/discipline area to allow students and professionals to mingle, promoting the exchange of ideas.\\\\
 \indent\textbf{Saturday Night}\\
@@
 While travel from airport to hotel can be managed by train (Amtrak/Metra), the conference planning committee excluded this option due to the added complexities of getting from the airport to train station, and train station to hotel with the associated costs of doing so.
-We recommend Peoria Charter because it is the most direct option for travel from O'Hare Aiport to the Illini Union.
+We believe the charter bus to be the best route of action as it picks up travelers directly at the arrivals gate and brings them to the Illini Union.
 Due to the central location of UIUC, driving might be a good option for some schools and individuals.

### 2019-10-01 socials.tex

--- 2019-10-01 socials.tex
@@
 
-\subsubsection{Illini Union Rec Room Lockout}
-The Illini Union Rec Room is located in the basement of the Union building.
-A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at the Illini Union!
-This space can accompany up to 150 people, with extra tables outside of the Rec Room for socializing, playing board games, or having a late night snack or coffee with professionals or students from other universities.
+\subsubsection{Barn Dance: A Proud Midwestern Tradition}
+Barn dances are a staple event at UIUC.
+Socialize in a unique environment with games of corn-hole and other midwestern fun.
+Various barns are used for dancing and mingling by many of the student organizations on UIUC campus, such as Farm Lake barn which hosts dozens of barn dances annually.
+Conference attendees will be encouraged to dress up in country-style attire or costume for this Thursday evening event.
+Like socials in the past student conferences, the barn may be used and a third party service can be hired to bring the square dance, swing dance, two step and cowboy boogie to the barn dance floor!
 \vspace{0.5cm}\newline
-% Illini Union Rec Room Picture
+% Barn Dance Hudson Picture
+%\begin{figure}[H]
+%	\centering
+%	\begin{subfigure}{0.4\textwidth}
+%		\centering
+%		\includegraphics[width=0.9\linewidth]{barn_dance1.png}
+%	\end{subfigure}%
+%	\begin{subfigure}{0.4\textwidth}
+%		\centering
+%		\includegraphics[width=0.9\linewidth]{barn_dance2.png}
+%	\end{subfigure}	
+%	\caption{Hudson Farm Barn.}	
+%\end{figure} 
 \begin{figure}[H]
 	\centering
-	\begin{subfigure}{0.5\textwidth}
+	\begin{subfigure}{0.4\textwidth}
 		\centering
-		\includegraphics[width=0.9\linewidth]{union_recroom1.png}
+		\includegraphics[width=0.9\linewidth]{farmlake1.jpg}
 	\end{subfigure}%
-	\begin{subfigure}{0.5\textwidth}
+	\begin{subfigure}{0.4\textwidth}
 		\centering
-		\includegraphics[width=0.9\linewidth]{union_recroom2.png}
+		\includegraphics[width=0.9\linewidth]{farmlake2.jpg}
 	\end{subfigure}	
-	\caption{Illini Union Rec Room}	
+	\caption{Farm Lake Barn}	
 \end{figure}
@@
 This event will take place following dinner at I Hotel Conference Center, and is just a short and scenic walk away past the State Farm Center (formerly the historic Assembly Hall).
-Tables will be set up around a stage featuring live music and a dance floor and drinks will be served.
+Tables will be set up around a stage featuring live music and a dance floor and drinks will be served, along with hosting raffles with nuclear and Illinois trivia.
 This is the perfect event to incorporate a little bit of Illinois history with music, dancing, and socializing!
@@
 
-%% Reserve for Pour Bros. social %%%
-\subsubsection{Pour Bros. Taproom in Downtown Champaign}
-Welcome to Illinois' first pour-your-own taprooms.
+\subsubsection{Illini Union Rec Room Lockout}
+The Illini Union Rec Room is located in the basement of the Union building.
+A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at The Garden Hotel.
+This space can accompany up to 150 people, with extra overflow space with tables outside of the Rec Room for socializing, playing board games, or having a late night snack or coffee with professionals or students from other universities.
+This will be an alcohol free social option for Thursday night, and a bar social will be reserved as well for this night.
+\vspace{0.5cm}\newline
+% Illini Union Rec Room Picture
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{union_recroom1.png}
+	\end{subfigure}%
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{union_recroom2.png}
+	\end{subfigure}	
+	\caption{Illini Union Rec Room}	
+\end{figure}
+
+\subsubsection{Bars in the Downtown Champaign District} 
+The downtown Champaign area on the north-east block of University Ave.
+and Neil St.
+offers a selection of casual, approachable, and fun bars for 21+ guests of Illinois who wish to spend the night out rather than attend the Illini Union Rec Room.
+Reservations will be made in advance and several bars can accompany up to 100 patrons or more in the area.
+Some of the recommended bars that the conference planning committee recommend that would be great sponsorship opportunities are Pour Bros.
+Taproom (up to 100 guest reservation), Guido's Bar and Grill (private lower level space that seats up to 100 with a capacity of 230), and Barrelhouse 34 (has a cozy rooftop lounge if weather permits).
+Conveniently, the recommended bars are just a couple of blocks from each other, and transportation will be available to get people to and from the downtown Champaign area to the Illini Union.
+\vspace{0.5cm}\newline
+% Pour Bros Picture
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.5\linewidth]{pour_bros2.png}
+	\end{subfigure}%
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{pour_bros1.png}
+	\end{subfigure}	
+	\caption{Pour Brothers Taproom}	
+\end{figure}
+
+% Guido's and Barrelhouse Picture
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{guidos.png}
+	\end{subfigure}%
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{barrelhouse.png}
+	\end{subfigure}	
+	\caption{Guido's (left) and Barrelhouse (right)}	
+\end{figure}
+
+%\subsubsection{Pour Bros. Taproom in Downtown Champaign}
+%Welcome to Illinois' first pour-your-own taprooms.
 Pour Bros.
@@
 If you are feeling more on the leisurely side, Pour Bros features live music in a spacious and comfortable seating area for you to get your networking on.
-\vspace{0.5cm}\newline
-% Pour Bros Picture
-\begin{figure}[H]
 
-	\centering
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.4\linewidth]{pour_bros2.png}
-	\end{subfigure}%
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.7\linewidth]{pour_bros1.png}
-	\end{subfigure}	
-	\caption{Pour Brothers Taproom}	
-\end{figure}
-
-\subsubsection{Barn Dance: A Proud Midwestern Tradition}
-Barn dances are a staple event at UIUC.
-Socialize in a unique environment with games of corn-hole and other midwestern fun.
-Various barns are used for dancing and mingling by many of the student organizations on UIUC campus, such as Farm Lake barn which hosts dozens of barn dances annually.
-Other barns may be best suited for the student conference social events, such as Hudson Farm, which offers a corporate event or professional social events option which can accommodate up to 300 guests with an alcohol service available and friendly, helpful service.
-Like socials in the past student conferences, the barn may be used and a third party service can be hired to bring the square dance, swing dance, two step and cowboy boogie to the barn dance floor!
-\vspace{0.5cm}\newline
-% Barn Dance Hudson Picture
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}{0.4\textwidth}
-		\centering
-		\includegraphics[width=0.9\linewidth]{barn_dance1.png}
-	\end{subfigure}%
-	\begin{subfigure}{0.4\textwidth}
-		\centering
-		\includegraphics[width=0.9\linewidth]{barn_dance2.png}
-	\end{subfigure}	
-	\caption{Hudson Farm Barn.}	
-\end{figure} 
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}{0.4\textwidth}
-		\centering
-		\includegraphics[width=0.9\linewidth]{farmlake1.jpg}
-	\end{subfigure}%
-	\begin{subfigure}{0.4\textwidth}
-		\centering
-		\includegraphics[width=0.9\linewidth]{farmlake2.jpg}
-	\end{subfigure}	
-	\caption{Farm Lake Barn}	
-\end{figure}
-
-\subsubsection{Under 21 Social: University of Illinois Ice Arena}
-For students under the drinking age that cannot attend the Pour Bros.
+%\subsubsection{Under 21 Social: University of Illinois Ice Arena}
+%For students under the drinking age that cannot attend the Pour Bros.
 Taproom social event, the University of Illinois Ice Arena is another option that is only a brief walking distance from the Union.

### 2019-10-01 conflog.tex
fixes positions

@@
 
+\clearpage
 \subsection{Conference Facilities}
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{garden_dinner.jpg}
+    \includegraphics[width=0.4\textwidth]{garden_dinner.jpg}
     \caption{The Garden Hotel Banquet Hall with capacity for 600 people in round tables.}
@@
     \centering
-    \includegraphics[width=0.75\textwidth]{ihotel-dinner.png}
-    \caption{The current 400-person banquet space at the IHotel is pictured 
+    \includegraphics[width=0.65\textwidth]{ihotel-dinner.png}
+    \caption{The current 400-person banquet space at the I Hotel is pictured 
         above. A new, 690-person ballroom will be available in 2020.}
@@
     \centering
-    \includegraphics[width=\textwidth]{illinirooms.jpg}
+    \includegraphics[width=0.75\textwidth]{illinirooms.jpg}
     \caption{The combined Illini rooms with capacity for 496 in round tables.}
@@
 Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 7am to 5am the following day for weekdays, and every 30 minutes on weekends.\\
->>>>>>> upstream/master
 \begin{figure}[H]
@@
     \end{tabular}
+\subcaption*{\textbf{*}\textit{Estimated assuming an average 23 MPG} \textbf{**}\textit{Assumes four people in a car}} 
 \end{table}
-\noindent\textbf{*}\textit{Estimated assuming an average 23 MPG}\\
-\textbf{**}\textit{Assumes four people in a car}
 

### 2019-10-01 website.tex
fixes positions

@@
 Since there is no cost, the website can be hosted indefinitely.
-This webhost was selected because several members of the chapter possess knowledge and experience in using it for serving collaborative, Jekyll-based, and static HTML websites.
+This webhost was selected because several members of the chapter possess knowledge and experience in using it for serving collaborative, Jekyll-based, and static websites.
 The domain name can be purchased for as little as one dollar for the first year, and a little less than $\$20$ to maintain annually.

### 2019-10-01 proglog.tex

@@
 Out of the 61 commercially operating nuclear power plants and 99 nuclear reactors in the U.S., Illinois is home to six nuclear power stations and eleven active reactors.
-Being located in a state with numerous power plants, as well as being surrounded by locations of interest to a variety of nuclear-related disciplines, the touring opportunities at the University of Illinois mirror the diversity of UIUC’s Nuclear Plasma and Radiological Engineering program.
+Being located in a state with numerous power plants, as well as being surrounded by locations of interest to a variety of nuclear-related disciplines, the touring opportunities at the University of Illinois mirror the diversity of UIUC’s Nuclear Plasma and Radiological Engineering program.\\
 
-The tours of Blue Waters and Starfire Industries will be a combined tour. Visitors will spend approximately 1.5 hours at each location. These tours will depart from the hotel. 
+The tours of Blue Waters and Starfire Industries will be a combined tour. Visitors will spend approximately 1.5 hours at each location. These tours will depart from the hotel. \\
+
 \noindent{
@@
 \begin{minipage}{0.5\textwidth}
-	\includegraphics[width=\textwidth]{bw_front.png}
+	\centering
+	\includegraphics[width=0.9\textwidth]{bw_front.png}
 	\captionof{figure}{Blue Waters Supercomputer}
@@
 \begin{minipage}{0.5\textwidth}
-	\includegraphics[width=\textwidth]{argonne.png}
+	\centering
+	\includegraphics[width=0.9\textwidth]{argonne.png}
 	\captionof{figure}{Argonne National Laboratory}
@@
 
+\vspace{0.5cm}
 \noindent{
 \begin{minipage}{0.5\textwidth}
-	\includegraphics[width=\textwidth]{clintonpp.jpg}
+	\centering
+	\includegraphics[width=0.9\textwidth]{clintonpp.jpg}
 	\captionof{figure}{Clinton Powerplant on Clinton Lake}
@@
 \end{minipage}
-\begin{minipage}{0.5\textwidth}
+\hspace{0.5cm}
+\begin{minipage}{0.45\textwidth}
 	\centering
-	\includegraphics[width=0.75\textwidth]{creek.png}
+	\includegraphics[width=0.85\textwidth]{creek.png}
 	\captionof{figure}{Engineering Hall on the Beautiful Engineering Quad}

### 2019-10-01 socials.tex

@@
 		\centering
-		\includegraphics[width=0.7\linewidth]{77club1.png}
+		\includegraphics[width=0.6\linewidth]{77club1.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=0.9\linewidth]{77club2.png}
+		\includegraphics[width=0.75\linewidth]{77club2.png}
 	\end{subfigure}
@@
 
-\subsubsection{Illini Union Rec Room Lockout}
-The Illini Union Rec Room is located in the basement of the Union building.
+% \subsubsection{Illini Union Rec Room Lockout}
+% The Illini Union Rec Room is located in the basement of the Union building.
 A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at The Garden Hotel.
@@
 This will be an alcohol free social option for Thursday night, and a bar social will be reserved as well for this night.
-\vspace{0.5cm}\newline
-% Illini Union Rec Room Picture
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.9\linewidth]{union_recroom1.png}
-	\end{subfigure}%
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.9\linewidth]{union_recroom2.png}
-	\end{subfigure}	
-	\caption{Illini Union Rec Room}	
-\end{figure}
+% \vspace{0.5cm}\newline
+% % Illini Union Rec Room Picture
+% \begin{figure}[H]
+% 	\centering
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=0.75\linewidth]{union_recroom1.png}
+% 	\end{subfigure}%
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=0.75\linewidth]{union_recroom2.png}
+% 	\end{subfigure}	
+% 	\caption{Illini Union Rec Room}	
+% \end{figure}
 
@@
 and Neil St.
-offers a selection of casual, approachable, and fun bars for 21+ guests of Illinois who wish to spend the night out rather than attend the Illini Union Rec Room.
+offers a selection of casual, approachable, and fun bars for 21+ guests of Illinois who wish to spend the night out rather than go Ice Skating at the Ice Arena.
 Reservations will be made in advance and several bars can accompany up to 100 patrons or more in the area.
-Some of the recommended bars that the conference planning committee recommend that would be great sponsorship opportunities are Pour Bros.
-Taproom (up to 100 guest reservation), Guido's Bar and Grill (private lower level space that seats up to 100 with a capacity of 230), and Barrelhouse 34 (has a cozy rooftop lounge if weather permits).
-Conveniently, the recommended bars are just a couple of blocks from each other, and transportation will be available to get people to and from the downtown Champaign area to the Illini Union.
+A couple of bars that the conference planning committee recommends are Guido's Bar and Grill (private lower level space that seats up to 100 with a capacity of 230), and Barrelhouse 34 (has a cozy rooftop lounge if weather permits).
+Conveniently, these bars are just a couple of blocks from each other with several more in between.
+Transportation will be available to get people to and from the downtown Champaign area to the Illini Union.
 \vspace{0.5cm}\newline
-% Pour Bros Picture
-\begin{figure}[H]
-	\centering
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.5\linewidth]{pour_bros2.png}
-	\end{subfigure}%
-	\begin{subfigure}{0.5\textwidth}
-		\centering
-		\includegraphics[width=0.9\linewidth]{pour_bros1.png}
-	\end{subfigure}	
-	\caption{Pour Brothers Taproom}	
-\end{figure}
+% % Pour Bros Picture
+% \begin{figure}[H]
+% 	\centering
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=0.5\linewidth]{pour_bros2.png}
+% 	\end{subfigure}%
+% 	\begin{subfigure}{0.5\textwidth}
+% 		\centering
+% 		\includegraphics[width=0.9\linewidth]{pour_bros1.png}
+% 	\end{subfigure}	
+% 	\caption{Pour Brothers Taproom}	
+% \end{figure}
 
@@
 		\centering
-		\includegraphics[width=0.9\linewidth]{guidos.png}
+		\includegraphics[width=0.65\linewidth]{guidos.png}
 	\end{subfigure}%
@@
 		\centering
-		\includegraphics[width=0.9\linewidth]{barrelhouse.png}
+		\includegraphics[width=0.65\linewidth]{barrelhouse.png}
 	\end{subfigure}	
@@
 
-%\subsubsection{Under 21 Social: University of Illinois Ice Arena}
-%For students under the drinking age that cannot attend the Pour Bros.
-Taproom social event, the University of Illinois Ice Arena is another option that is only a brief walking distance from the Union.
+\subsubsection{Under 21 Social: University of Illinois Ice Arena}
+For students under the drinking age that cannot attend the Champaign Bars social event, the University of Illinois Ice Arena is another option that is only a brief walking distance from the Union.
 It was built in 1931 and offers a unique option for skating get-togethers from broomball and hockey to group skating parties.
@@
 The dimensions of the rink are 192' by 115' with a 1,200 seat arena surrounding.
-There are four public locker rooms, four party areas, and two Zambonis in the facility.
+There are four public locker rooms, four party areas and two Zambonis in the facility.
 The Center Ice Cafe offers hot chocolate, coffee, smoothies, fountain drinks, and more to quench your thirst.
 Snacks and concession items are also available.
-%\vspace{0.5cm}\newline
-%% Ice Arena Picture
-%\begin{figure}[H]
-%	\centering
-%	\includegraphics[width=0.8\textwidth]{ice_arena.png}
-%	\caption{The UIUC Ice Arena}
-%\end{figure}
+\vspace{0.5cm}\newline
+% Ice Arena Picture
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.8\textwidth]{ice_arena.png}
+	\caption{The UIUC Ice Arena}
+\end{figure}

### 2019-10-01 socials.tex
adds alternative socials

@@
 \end{figure}
+
+\subsubsection{Alternative Options}
+
+Listed above are just a few of the many ideas for socials we've had. Here are some alternative social options that we can explore when we have more information.
+
+\begin{itemize}
+	\item Cocktail Hour at Krannert Center for the Performing Arts\\
+	Krannert is UIUC's world famous performance center with a beautiful lobby area capable of holding up to 2000 people. They have a cocktail bar on site as well as a stage in the lobby.
+\end{itemize}

### 2019-10-01 uiuc.tex
most spelling handled
whoops, included risk section twice

@@
  pass can be bought on Saturdays and Sundays for \$2 from any bus operator or 
- from the app. All CU-MTD busses are wheelchair accessible. Rental bikes and 
+ from the app. All CU-MTD buses are wheelchair accessible. Rental bikes and 
  rideshare services are also plentiful.
@@
 
-\subsubsection{Reliability and Risk Analysis}
-Risk analysis represents the pinnacle of interdisciplinary research and education.
-Following the Three Mile Island disaster in 1979, Probabilistic Risk Assessment (PRA) has become a key pillar of the risk-informed nuclear regulatory framework, and is now a requirement for every nuclear power plant in the United States.
-Enhancing the prevention of catastrophic technological accidents and the protection of the environment requires advancement in multidisciplinary PRA.
-It demands the development of a common vocabulary within diverse engineering and social science domains in order to address risks that emerge from the interface of social and technical systems.
-
 \subsubsection{Materials Science}

### 2019-10-01 banking.tex

@@
 ANS Headquarters. The University of Illinois is tax exempt in the state of Illinois. 
-Additionally, we will work driectly with ANS Headquarters to ensure tax 
+Additionally, we will work directly with ANS Headquarters to ensure tax 
 exemption. Since ANS is incorporated under the General Not for Profit 
@@
 These requests must carefully outline the reason for the purchase and the total cost.
-If the purchase is reoccuring, automation will be required at the time of request.
+If the purchase is reoccurring, automation will be required at the time of request.
 These requests will require the approval of both conference chairs in addition to the financial director.

### 2019-10-01 management.tex

@@
 	\item $\large\textbf{\textit{Diversity Co-Chair}}$\\
-	In addition to the responsibilities outlined above, the Diversity Co-Chair is responsible for making sure the conference is as inclusive, diverse, and accessible as possible.
-This includes: contacting minority serving institutions to encourage their students to attend the conference, ensuring socials and dinners are accessible, verifies that the final list of speakers has adequate representation, and more.
-We believe the example set by UIUC will make this role a staple of future conferences.
+	In addition to the responsibilities outlined above, the Diversity 
+                Co-Chair is responsible for making sure the conference is as 
+                inclusive, diverse, and accessible as possible. This includes: 
+                contacting minority serving institutions to encourage their 
+                students to attend the conference, ensuring socials and dinners 
+                are accessible, verifying that the final list of speakers has 
+                adequate representation, engaging with the national Diversity and 
+                Inclusion in ANS Committee, and more. We believe the example set 
+                by UIUC will make this role a staple of future conferences.
 
@@
 		\item[$\circ$] $\textbf{Hotels and Transportation Coordinator}$\\
-		Coordinates with ANS National to negotiate room rates and room blocks for hotels. Reserves busses for the 
+		Coordinates with ANS National to negotiate room rates and room blocks for hotels. Reserves buses for the 
 		necessary times and events. Works with the Hospitality and Catering Coordinator and the Logistics Chair.
 		\item[$\circ$] $\textbf{Hospitality and Catering Coordinator}$\\
-		Responsible for planning and organizing all catered meals for the conference.
-that includes contacting the catering services, reserving the venues where meals are held, and making sure the venues are staffed.
+		Responsible for planning and organizing all catered meals for 
+                        the conference. That includes contacting the catering services, reserving the venues where meals are held, and making sure the venues are staffed.
 		\item[$\circ$]$\textbf{Tours Coordinator}$\\
@@
 	\item $\textbf{Media Coordinator}$\\
-		The Media Coordinator is reponsible for designing the conference website, constantly updating social media presence,
+		The Media Coordinator is responsible for designing the conference website, constantly updating social media presence,
 		and obtains information from other members of the planning committee for the website.
@@
 	$\textbf{Registration Coordinator - Jasmine Dinari}$\\
-Jasmine is a frehsman studying Nuclear, Plasma, and Radiological Engineering at UIUC, as well as minors in French and Physics.
+Jasmine is a freshman studying Nuclear, Plasma, and Radiological Engineering at UIUC, as well as minors in French and Physics.
 She is starting research with Dr.

### 2019-10-01 proglog.tex

@@
 \begin{minipage}{0.73\textwidth}
-	Prof.
-Slaybaugh's research is based in numerical methods for neutron transport with an emphasis on supercomputing.
-She applies these methods to reactor design, shielding, and nuclear security and nonproliferation.
-Slaybaugh was a key founder of the nuclear innovation bootcamp, which seeks to train students and professionals in skills essential to innovation in nuclear energy while executing team projects.
-Finally, Slaybaugh has served as a Program Director at ARPA-E, developing and running their first fission energy programs.
-Advanced Research Projects Agency-Energy (ARPA-E) invests in research for ways to generate, use, and store energy.
-These projects have the potential to radically improve economic prosperity in the U.S.
-and environmental wellbeing.
+	Prof. Slaybaugh's research is based in numerical methods for neutron 
+        transport with an emphasis on supercomputing. She applies these methods 
+        to reactor design, shielding, and nuclear security and 
+        nonproliferation. Slaybaugh was a key founder of the nuclear innovation 
+        bootcamp, which seeks to train students and professionals in skills 
+        essential to innovation in nuclear energy while executing team 
+        projects. Finally, Slaybaugh has served as a Program Director at 
+        ARPA-E, developing and running their first fission energy programs. 
+        Advanced Research Projects Agency-Energy (ARPA-E) invests in research 
+        for ways to generate, use, and store energy. These projects have the 
+        potential to radically improve economic prosperity in the U.S. and 
+        environmental well-being.
 Due to her endeavors in teaching and sharing nuclear innovation, we believe that Slaybaugh's goals are aligned with the goals of this conference and would make her an excellent addition to the program.
@@
 \begin{minipage}{0.73\textwidth}
-	Mr.
-Magwood served seven years as the Director of Nuclear Energy with the U.S.
-Department of Energy (DOE), where he was the senior nuclear technology official in the United States Government.
-He oversaw the restoration of the Federal nuclear technology program and led the creation of ``Nuclear Power 2010,'' ``Generation IV,'' and other innovative initiatives—including successful efforts that helped reverse the decline in American nuclear technology education.
-Since joining the NRC, he has continued his advocacy for both U.S.
+	Mr. Magwood served seven years as the Director of Nuclear Energy with 
+        the U.S. Department of Energy (DOE), where he was the senior nuclear 
+        technology official in the United States Government. He oversaw the 
+        restoration of the Federal nuclear technology program and led the 
+        creation of ``Nuclear Power 2010,'' ``Generation IV,'' and other 
+        innovative initiatives—including successful efforts that helped reverse 
+        the decline in American nuclear technology education. Since joining the 
+        NRC, he has continued his advocacy for both U.S.
 science and technology education and strong international cooperation.
@@
 \subsection{Career Fair}
-The career will be held all day on Friday, from 8am to 5pm, and on Saturday from 8am to noon.
-It will be held in Illini Rooms A \& B, a large space capable of holding 600 people.
-This space will be immediately adjacent to the poster sessions on saturday to encourage students and professionals to attend both.
+The career will be held all day on Friday, from 8am to 5pm, and on Saturday 
+from 8am to noon. It will be held in Illini Rooms A \& B, a large space capable 
+of holding 600 people. This space will be immediately adjacent to the poster 
+sessions on Saturday to encourage students and professionals to attend both.
 Together, the Illini Rooms can hold up to 900 people.
@@
 	\includegraphics[width=0.9\textwidth]{clintonpp.jpg}
-	\captionof{figure}{Clinton Powerplant on Clinton Lake}
+        \captionof{figure}{Clinton Power Plant on Clinton Lake}
 \end{minipage}

### 2019-10-01 socials.tex
adds alt. socials

@@
 \begin{itemize}
-	\item Cocktail Hour at Krannert Center for the Performing Arts\\
+	\item \textbf{Cocktail Hour at Krannert Center for the Performing Arts}\\
 	Krannert is UIUC's world famous performance center with a beautiful lobby area capable of holding up to 2000 people. They have a cocktail bar on site as well as a stage in the lobby.
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=0.5\textwidth]{krannert.jpg}
+	\end{figure}
+	\item \textbf{Illini Union Rec Room Lockout}\\
+	The Illini Union Rec Room is located in the basement of the Union building.
+A Rec Room lockout gives ANS exclusive access to 14 bowling lanes, 12 billiard tables, and coin-operated arcade games following dinner at The Garden Hotel.
+This space can accompany up to 150 people, with extra overflow space with tables outside of the Rec Room for socializing, playing board games, or having a late night snack or coffee with professionals or students from other universities.
+This will be an alcohol free social option.
+	\begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.75\linewidth]{union_recroom1.png}
+	\end{subfigure}%
+	\begin{subfigure}{0.5\textwidth}
+		\centering
+		\includegraphics[width=0.75\linewidth]{union_recroom2.png}
+	\end{subfigure}	
+	\caption{Illini Union Rec Room}	
+\end{figure}
+	\item \textbf{The Illini Bar-nana Crawl}\\
+	ANS-UIUC hosts an annual Bar-nana Crawl that combines social and public outreach aspects.
+This fun and hilarious (21+) social event includes a public outreach spin.
+Everyone will don a marvelous banana-suit costume and enjoy the great nightlife of downtown champaign.
+Discussing radiation dosage in terms of Banana Equivalent Dose (BED) is a popular way to demystify the risks of radiation.
+Banana suits would be included in the registration gift bag and potentially sponsored by an interested company.
 \end{itemize}

### 2019-10-01 budget.tex
Budget Tables Updated

--- 2019-09-30 budget.tex
@@
 
-\subsection{Projected Attendance}
-We project to have 450 student attendees and 150 professional attendees.
-We have based these projections on the attendance from previous years and on our central midwestern location.
-Additionally, this estimate allows us to create the most conservative budget possible and be prepared in the event that attendance is unusually high.
-A summary of the previous attendance is shown in Table \ref{table:attendance}.
-
-\begin{table}[H]
-\caption{Summary of Previous Attendance}
-\label{table:attendance}
-    \centering
-    \begin{tabular}{cccccccccccc}
-    \textbf{Host}& VCU & UF & UPitt & UWM & T. A\&M & Penn & MIT & UNLV & GIT & Mean ($\mu$) & Margin ($\frac{\sigma}{\sqrt{N}}$) \\
-    \hline
-    Students & 450 & 430 & 500 & 438 & 375 & 388 & 536 & 400 & 425 & 438 & $\approx$16 \\
-    Professionals & 100 & 120 & 75 & 130 & 137 & 134 & 101 & 200 & 150 & 127 & $\approx$11\\
-    \hline
-    \end{tabular}
-\end{table}
 % =======================================================================================
@@
 Should our bid be selected, these conservative estimates will result in a smoother planning and execution process.
-We have also accounted for an estimated number of waived professional registration based on previous conferences.
+We have also accounted an estimated number of waived professional registration based on previous conferences.
 This  correlates to the number of waived fees given in our expected tier sponsorship figures and also factors in discounts to speakers, panelists, and workshop instructors.
@@
 
-\clearpage
 \begin{table}[H]
@@
 \hline
-	Student			&	450	&	\$40	&	\$18,000						\\
-	Professional	&	150	& 	\$250	&	\$37,500						\\
+	Student			&	443	&	\$40	&	\$17,720						\\
+	Professional	&	127	& 	\$250	&	\$31,750						\\
 	Waived			&	60	& 	-\$250	&	-\$15,000						\\
 \hline
-	\multicolumn{3}{|r|}{\textbf{Attendance Total:}}	&	\$40,500		\\
+	\multicolumn{3}{|r|}{\textbf{Attendance Total:}}	&	\$34,470		\\
 \hline
@@
 
-% \vspace{10mm}
+\vspace{10mm}
 
@@
 \hline
-    \textbf{Total Revenue: \$241,500}\\ 
+    \textbf{Total Revenue: \$235,470}\\ 
 \hline
@@
 \subsection{Expenses}
-A conservative breakdown of conference expenses is outlined in Table \ref{table:budget} on page \pageref{table:budget}.
-All rooms hosted in the Union are provided to registered student organizations (such as ANS-UIUC) free of charge.
-This allows us to save significantly on event space.
+A conservative breakdown of conference expenses is outlined in Table ******* on page *******.
+Emphasizing some of the points shown in the table, all rooms hosted in the Union are provided to registered student organizations (such as ANS) free of charge, which allows us to save significantly on event space.
 Meals catered through the University catering service reflect a 6.25\% sales tax in the total cost which is not represented in the unit cost.
-Gratuity is neglected because it is forbidden under the catering service’s policies, allowing us to save 20\% gratuity on meals.
-Under our most conservative estimates for budget and revenue, the spending margin is found to be 6.8\%.
+Gratuity is neglected as it is forbidden under the catering service’s policies, allowing us to save cost on meals.
+Under our most conservative estimates for budget and revenue, the spending margin is found to be 4.13\%.
 While this margin is tight, we feel this is justified as several costs in the expenses, such as reimbursements, are left significantly inflated as compared with previous years.
@@
 This number also includes the travel reimbursement, which was intentionally set to be considerably more generous than previous years to make the budget more conservative.
-Assuming every student traveled here with the avereage cost of flights from Table \ref{table:airfare}, our current travel reimbursement package would cover 76.8\% of the accumulated costs.
 Neglecting the cost of travel reimbursements, the average cost per student falls to \$276.63, at or below that estimated for previous years.
-In Appendix \ref{appendix:quotes} on page \pageref{appendix:quotes} we included quotes where possible.
 
-% \hspace{-1.1cm}
-\begin{table}[H]
-    \caption{Budget Expenses}
-    \label{table:budget}
-    \makebox[\linewidth]{
+\hspace{-1.1cm}
 \begin{tabular}{|clcrccccr|}
@@
     \hline
-         & \multicolumn{1}{c}{\textbf{Item}} & \multicolumn{1}{c}{\textbf{Priority}} & \multicolumn{1}{c}{\textbf{Cost Per Unit}} & \multicolumn{1}{c}{\textbf{Thursday}} & \multicolumn{1}{c}{\textbf{Friday}} & \multicolumn{1}{c}{\textbf{Saturday}} & \multicolumn{1}{c}{\textbf{General}} & \multicolumn{1}{c}{\textbf{Total Cost}}\\     \hline\hline
-         \multirow{10}{*}{\STAB{\rotatebox[origin=c]{90}{\textbf{Facilities}}}}
-         & Technical Session AV      & I                         & $\$$ 13.80                & 1                         & 6                        & 6                         & -                         & $\$$179.40               \\
-         & Technical Session Rooms   & I                         & $\$$ 0.00                 & -                         &  -                       &  -                        &  1                        & $\$$0.00                 \\
-         & Panel AV                  & I                         & $\$$ 17.80                & -                         &   2                      &   2                       &   -                       & $\$$71.20                \\
-         & Panel Rooms               & I                         & $\$$ 0.00                 & -                         &    -                     &    -                      &    1                      & $\$$0.00                 \\
-         & Workshop AV               & I                         & $\$$ 17.80                & 2                         &     -                    &     -                     &     -                     & $\$$35.60                \\
-         & Workshop Rooms            & I                         & $\$$ 0.00                 &  -                        &      -                   &      -                    &      1                    & $\$$0.00                 \\
-         & Dinner Room (Ihotel)      & I                         & $\$$ 4,000.00             &   -                       &       -                  &       1                   &       -                   & $\$$4,000.00             \\
-         & Dinner AV (Ihotel)        & I                         & $\$$ 0.00                 &    -                      &        -                 &        1                  &        -                  & $\$$0.00                 \\
-         & Dinner Room (Garden Hotel)& I                         & $\$$ 4,000.00             &     1                     &         1                &         -                 &         -                 & $\$$8,000.00             \\
-         & Dinner AV (Garden Hotel)  & I                         & $\$$ 0.00                 &      1                    &          1               &          -                &          -                & $\$$0.00                 \\ \hline
-         &                           &                           &                           &                           &\multicolumn{3}{r}{Facilities Subtotal:}     & $\$$12,286.20            \\ \hline\hline
-         \multirow{5}{*}{\STAB{\rotatebox[origin=c]{90}{\textbf{Transport}}}}
-         & Shuttles From Hotel       & I                         & $\$$ 1,000.00             & 4                         & 4                        & 4                         & -                         & $\$$12,000.00            \\
-         & Ihotel Dinner             & I                         & $\$$ 875.00               & -                         &  -                       &  4                        &  -                        & $\$$3,500.00             \\
-         & Brewery/Starfire Tours    & II                        & $\$$ 875.00               & 1                         &   -                      &   -                       &   -                       & $\$$875.00               \\
-         & Clinton Tour              & II                        & $\$$ 875.00               & 1                         &    -                     &    -                      &    -                      & $\$$875.00               \\
-         & Argonne Tour              & II                        & $\$$ 875.00               & 1                         &     -                    &     -                     &     -                     & $\$$875.00               \\ \hline
-         &                           &                           &                           &                           &\multicolumn{3}{r}{Transport Subtotal:}      & $\$$18,125.00            \\ \hline\hline
-         \multirow{5}{*}{\STAB{\rotatebox[origin=c]{90}{\textbf{Food}}}}
-         & Coffee/Tea                & III                       & $\$$ 1.95                 & -                         & 600                      & 600                       & -                         & $\$$2,486.25             \\
-         & Garden Hotel Dinners*     & II                        & $\$$ 36.50                & 600                       & 600                      &  -                        &  -                        & $\$$46,537.50            \\
-         & Ihotel Dinner             & II                        & $\$$ 27.50                & -                         &   -                      &   600                     &   -                       & $\$$17,531.25            \\
-         & Dinner Cash Bars          & III                       & $\$$ 336.00               & 1                         &    1                     &    1                      &    -                      & $\$$1,071.00             \\
-         & SSC Lunches               & II                        & $\$$ 16.50                & -                         &     -                    &     150                   &     -                     & $\$$2,629.69             \\ \hline
-         &                           &                           &                           &                           &\multicolumn{3}{r}{Food Subtotal:}           & $\$$70,255.69            \\ \hline\hline
-         \multirow{5}{*}{\STAB{\rotatebox[origin=c]{90}{\textbf{Socials}}}}
-         & Ice Skating               & III                       & $\$$ 240.00               & 2                         & -                        & -                         & -                         & $\$$480.00               \\
-         & Illini Rec Room           & III                       & $\$$ 490.00               &  -                        & 2                        &  -                        &  -                        & $\$$982.00               \\
-         & Memorial Stadium Club 77  & III                       & $\$$ 2,000.00             & -                         &   -                      &   1                       &   -                       & $\$$2,000.00             \\
-         & Club 77 Tab               & IV                        & $\$$ 3,000.00             & -                         &    -                     &    1                      &    -                      & $\$$3,000.00             \\
-         & Guido's Tab               & IV                        & $\$$ 3,000.00             & -                         &     1                    &     -                     &     -                     & $\$$3,000.00             \\ \hline
-         &                           &                           &                           &                           &\multicolumn{3}{r}{Socials Subtotal:}        & $\$$9,462.00             \\ \hline\hline
-         \multirow{7}{*}{\STAB{\rotatebox[origin=c]{90}{\textbf{Miscellaneous}}}}
-         & Conference Programs       & I                         & $\$$ 2,133.90             & -                         & -                        & -                         & 1                         & $\$$2,133.90             \\
-         & Lanyards                  & I                         & $\$$ 2.54                 &  -                        & -                        &  -                        &  600                      & $\$$1,524.00             \\
-         & Award Certificates        & III                       & $\$$ 2.50                 & -                         &   -                      &   50                      &   -                       & $\$$125.00               \\
-         & Poster Session Prizes     & III                       & $\$$ 100.00               & -                         &    -                     &    3                      &    -                      & $\$$300.00               \\
-         & Swag                      & IV                        & $\$$ 10,000.00            & -                         &     -                    &     -                     &     1                     & $\$$10,000.00            \\
-         & Brewery Tour              & IV                        & $\$$ 5.00                 & 45                        &     -                    &     -                     &     -                     & $\$$275.00               \\
-         & Travel Reimbursements     & I                         & $\$$ 225.00               &  -                        &     -                    &                           &  450                      & $\$$101,250.00           \\ \hline
-         &                           &                           &                           &                           &\multicolumn{3}{r}{Miscellaneous Subtotal:}                                       & $\$$126,857.90           \\ \hline\hline
+     & \multicolumn{1}{c}{Item} & \multicolumn{1}{c}{Priority} & \multicolumn{1}{c}{Cost Per Unit} & \multicolumn{1}{c}{Thursday} & \multicolumn{1}{c}{Friday} & \multicolumn{1}{c}{Saturday} & \multicolumn{1}{c}{General} & \multicolumn{1}{c}{Total Cost}\\     \hline\hline
+     \multirow{12}{*}{\STAB{\rotatebox[origin=c]{90}{Facilities}}}
+     & Technical Session AV      & I                         & $\$$ 13.80                & 1                         & 7                        & 7                         & -                         & $\$$ 207.00               \\
+     & Technical Session Rooms   & I                         & $\$$ 0.00                 & -                         &  -                       &  -                        &  1                        & $\$$ 0.00                 \\
+     & Panel AV                  & I                         & $\$$ 17.80                & -                         &   2                      &   2                       &   -                       & $\$$ 71.20                \\
+     & Panel Rooms               & I                         & $\$$ 0.00                 & -                         &    -                     &    -                      &    1                      & $\$$ 0.00                 \\
+     & Workshop AV               & I                         & $\$$ 17.80                & 2                         &     -                    &     -                     &     -                     & $\$$ 35.60                \\
+     & Workshop Rooms            & I                         & $\$$ 0.00                 &  -                        &      -                   &      -                    &      1                    & $\$$ 0.00                 \\
+     & Dinner Room (Garden)      & I                         & $\$$ 4,000.00             &   1                       &       -                  &       -                   &       -                   & $\$$ 4,000.00             \\
+     & Dinner AV (Garden)        & I                         & $\$$ 0.00                 &    1                      &        -                 &        -                  &        -                  & $\$$ 0.00                 \\
+     & Dinner Room (I-Hotel)     & I                         & $\$$ 4,000.00             &     -                     &         1                &         -                 &         -                 & $\$$ 4,000.00             \\
+     & Dinner AV (I-Hotel)       & I                         & $\$$ 0.00                 &      -                    &          1               &          -                &          -                & $\$$ 0.00                 \\
+     & Dinner Room (Union)       & I                         & $\$$ 0.00                 &     -                     &         -                &         1                 &         -                 & $\$$ 0.00                 \\
+     & Dinner AV (Union)         & I                         & $\$$ 17.80                &      -                    &          -               &        1                  &          -                & $\$$ 17.80                \\ \hline
+
+     &                           &                           &                           &                           &\multicolumn{3}{r}{Facilities Subtotal:}     & $\$$ 8,331.60            \\ \hline\hline
+     \multirow{10}{*}{\STAB{\rotatebox[origin=c]{90}{Transport}}}
+     & Shuttles From Hotel       & I                         & $\$$ 1,000.00             & 4                         & 4                        & 4                         & -                         & $\$$ 12,000.00            \\
+     & Ihotel Dinner             & I                         & $\$$ 100.00               & -                         &  4                       &  -                        &  -                        & $\$$ 400.00               \\
+     & Union Dinner              & I                         & $\$$ 100.00               & -                         &   -                      &   4                       &   -                       & $\$$ 400.00               \\
+     & Barn Dance/Ice Skating    & III                       & $\$$ 300.00               & 4                         & -                        & -                         & -                         & $\$$ 1,200.00             \\
+     & Memorial Stadium Social   & III                       & $\$$ 300.00               & -                         &  4                       &  -                        &  -                        & $\$$ 1,200.00             \\
+     & Downtown Champaign Social & III                       & $\$$ 300.00               & -                         &   -                      &   4                       &   -                       & $\$$ 1,200.00             \\
+     & Triptych/Blue Waters Tour & II                        & $\$$ 875.00               & 1                         &   -                      &   -                       &   -                       & $\$$ 875.00               \\
+     & Riggs Tour                & III                       & $\$$ 875.00               & 1                         &    -                     &    -                      &    -                      & $\$$ 875.00               \\
+     & Clinton Tour              & II                        & $\$$ 900.00               & 1                         &    -                     &    -                      &    -                      & $\$$ 900.00               \\
+     & Argonne Tour              & II                        & $\$$ 900.00               & 1                         &     -                    &     -                     &     -                     & $\$$ 900.00               \\ \hline
+     &                           &                           &                           &                           &\multicolumn{3}{r}{Transport Subtotal:}      & $\$$ 19,950.00            \\ \hline\hline
+     \multirow{6}{*}{\STAB{\rotatebox[origin=c]{90}{Food}}}
+     & Coffee/Tea                & II                        & $\$$ 1.95                 & -                         & 600                      & 600                       & -                         & $\$$ 2,340.00             \\
+     & Garden Hotel Dinner       & II                        & $\$$ 36.50                & 600                       & -                        &  -                        &  -                        & $\$$ 26,280.00            \\
+     & Ihotel Dinner             & II                        & $\$$ 27.50                & -                         &   600                    &   -                       &   -                       & $\$$ 16,500.00            \\
+     & Union Dinner              & II                        & $\$$ 27.50                & -                         &   -                      &   600                     &   -                       & $\$$ 16,500.00            \\
+     & Dinner Cash Bars          & III                       & $\$$ 336.00               & 1                         &    1                     &    1                      &    -                      & $\$$ 1,008.00             \\
+     & SSC Lunches               & II                        & $\$$ 16.50                & -                         &     -                    &     150                   &     -                     & $\$$ 2,475.00             \\ \hline
+     &                           &                           &                           &                           &\multicolumn{3}{r}{Food Subtotal:}           & $\$$ 65,103.00            \\ \hline\hline
+     \multirow{5}{*}{\STAB{\rotatebox[origin=c]{90}{Socials}}}
+     & Ice Skating               & III                       & $\$$ 240.00               & 2                         & -                        & -                         & -                         & $\$$ 480.00               \\
+     & Barn Dance                & IV                        & $\$$ 2,800.00             &  1                        & -                        &  -                        &  -                        & $\$$ 2,800.00             \\
+     & Memorial Stadium Club 77  & III                       & $\$$ 2,000.00             & -                         &   1                      &   -                       &   -                       & $\$$ 2,000.00             \\
+     & Club 77 Tab               & IV                        & $\$$ 2,000.00             & -                         &    1                     &    -                      &    -                      & $\$$ 2,000.00             \\
+     & Guido's Tab               & IV                        & $\$$ 2,000.00             & -                         &     -                    &     1                     &     -                     & $\$$ 2,000.00             \\ \hline
+     &                           &                           &                           &                           &\multicolumn{3}{r}{Socials Subtotal:}        & $\$$ 9,280.00             \\ \hline\hline
+     \multirow{8}{*}{\STAB{\rotatebox[origin=c]{90}{Miscellaneous}}}
+     & Conference Programs       & I                         & $\$$ 2,133.90             & -                         & -                        & -                         & 1                         & $\$$ 2,133.90             \\
+     & Lanyards                  & I                         & $\$$ 2.54                 &  -                        & -                        &  -                        &  600                      & $\$$ 1,524.00             \\
+     & Award Certificates        & II                        & $\$$ 2.50                 & -                         &   -                      &   50                      &   -                       & $\$$ 125.00               \\
+     & Poster Session Prizes     & II                        & $\$$ 100.00               & -                         &    -                     &    3                      &    -                      & $\$$ 300.00               \\
+     & Swag                      & IV                        & $\$$ 10,000.00            & -                         &     -                    &     -                     &     1                     & $\$$ 10,000.00            \\
+     & Triptych Tour             & III                       & $\$$ 5.00                 & 55                        &     -                    &     -                     &     -                     & $\$$ 275.00               \\
+     & Riggs Tour                & III                       & $\$$ 0.00                 & 55                        &     -                    &     -                     &     -                     & $\$$ 0.00                 \\
+     & Travel Reimbursements     & I                         & $\$$ 225.00               &  -                        &     -                    &                           &  450                      & $\$$ 101,250.00           \\ \hline
+     &                           &                           &                           &                           &\multicolumn{3}{r}{Miscellaneous Subtotal:}                                       & $\$$ 115,607.90           \\ \hline\hline
      &                           &                           &                           &                           &                          &                           &                           &                           \\
-         &                           &                           &                           &                           &\multicolumn{3}{r}{Grand Total:}                                                  & $\$$225,734.79           \\
+     &                           &                           &                           &                           &\multicolumn{3}{r}{Grand Total:}                                                  & $\$$218,272.50            \\
      &                           &                           &                           &                           &                          &                           &                           &                           \\ \hline
-    \end{tabular}}
-\end{table}
+\end{tabular}
 
@@
 
-\begin{table}[H]
-    \caption{Budget Cuts}
-    \label{table:cuts}
-    \centering
-    \makebox[0.65\linewidth]{\begin{tabular}{lrrr}
+\begin{tabular}{lrrr}
   \hline\hline
-      \multicolumn{1}{l}{Level of Cuts Made} & \multicolumn{1}{c}{Amount Saved} & \multicolumn{1}{c}{Grand Total} & \multicolumn{1}{c}{\% of Max Revenue} \\ \hline\hline 
-      Priority IV Cuts Made & $\$$9,346.00 & $\$$216,388.79 & 10.4\% \\
-      III and IV Cuts Made & $\$$22,987.25 &$\$$198,747.54 & 17.4\% \\
-      II, III, and IV Cuts Made & $\$$49,053.19 & $\$$176,681.60 & 26.56\% \\
-      \hline
-    \end{tabular}}
-\end{table}
+  \multicolumn{1}{l}{Level of Cuts Made} & \multicolumn{1}{c}{Amount Saved} & \multicolumn{1}{c}{Grand Total} & \multicolumn{1}{c}{\% Margin} \\ \hline\hline 
+  Priority IV Cuts Made & $\$$ 9,800.00 & $\$$ 208,472.50 & 13.68 \% \\
+  III and IV Cuts Made & $\$$ 23,648.00 &$\$$ 194,624.50 & 19.41 \% \\
+  II, III, and IV Cuts Made & $\$$ 40,393.00 & $\$$ 177,879.50 & 26.34 \% \\
+
+  \end{tabular}
 
@@
 Priority II cuts entail complete elimination of social event expenses, along with elimination of tour expenses and reduction of dinner costs through cheaper buffet options and desserts.
-The expenditure savings from these cuts are outlined in Table \ref{table:cuts}.
+The expenditure savings from these cuts are outlined in Table *******.
 While this contingency plan does not consider cuts to the reimbursement funds, this could be reconsidered if necessary, since reimbursements were set aside at a level nearly double that of previous conferences.
+\\
 
@@
 
-% \vspace{1cm}
+\vspace{1cm}
 
@@
 	\centering
-	\includegraphics[width=0.85\textwidth]{sponsors1.png}	
+	\includegraphics[width=\textwidth]{sponsors1.png}	
 \end{figure}
@@
 	\centering
-	\includegraphics[width=0.85\textwidth]{sponsors2.png}	
+	\includegraphics[width=\textwidth]{sponsors2.png}	
 \end{figure}
@@
 The cost of attending the student conference, per student, varies among schools and is highly dependent on distance from UIUC and the preferred mode of travel.
-We will assume that minimizing cost is a priority for schools, thus number of persons per hotel room is assumed to be double the number of beds.
+We will assume that minimizing cost is a priority for schools, thus number of persons per hotel room is double the number of beds.
 The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport.
 There is also a small airport located just 20 minutes outside of campus.
+Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus up to 10 times per day.
+Below are the round-trip, non-stop, airfare costs for the first weekend of April.
+Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip.
 While some students may wish to make use of the convenience of the local airport, in general the most economic method of arriving in Champaign is by first flying to O’Hare and then busing.
-The average cost of this trip comes out to be \$293 as shown in Table  \ref{table:airfare}.
-Adding this to the registration and lodging costs (see Table \ref{table:hotels}) for four nights (as students often arrive Wednesday evening) and assuming four students per room, the total cost of attendance for each student comes out to an average of \$447.
-The travel reimbursement is meant to help mitigate some or most of the costs for students coming to this conference to encourage future attendance at other conferences.
+The average cost of this trip comes out to be \$293 as shown in Table *******.
+Adding this to the registration and lodging costs for four nights (as students often arrive Wednesday evening) and assuming four students per room, the total cost of attendance for each student comes out to an average of \$447.
 
 % Jeremy's budget plan
-
-\subsection{Student Travel Reimbursement Procedure}
-The procedure for student travel reimbursement will require each section send via email all acquired expenses in their travels and lodging for this conference.
-Each chapter will be required to send us:
-\begin{enumerate}
-    \item The number of students that attended.
-    \item The number of hotel rooms reserved.
-    \item The location of the hotel rooms.
-    \item Modes of transportation
-    \item Parking costs (excluding airport reserved parking).
-    \item Receipts for all purchases will be required for all submitted purchases.
-\end{enumerate}
-A form will be emailed to each of the chapter presidents for their section to fill out and attach the appropriate receipts.
-We will require that the form along with the necessary receipts be submitted via email to the Finance Director in one PDF, two weeks after the Sunday following the conference.
-The Finance Chair will review all of the submitted documents for any corrections that need to be made.
-Any section that needs to make corrections to their reimbursement form will be emailed the following Tuesday.
-The reimbursement form must be re-submitted to us by that Friday.
-Once all the sections have their forms submitted to us we will turn in our master list to ANS National for reimbursement distributions.
-Checks will be mailed to each of the chapter presidents or a selected representative for the chapter.

### 2019-10-01 budget.tex
Edits to budget text

@@
 Emphasizing some of the points shown in the table, all rooms hosted in the Union are provided to registered student organizations (such as ANS) free of charge, which allows us to save significantly on event space.
-Meals catered through the University catering service reflect a 6.25\% sales tax in the total cost which is not represented in the unit cost.
-Gratuity is neglected as it is forbidden under the catering service’s policies, allowing us to save cost on meals.
-Under our most conservative estimates for budget and revenue, the spending margin is found to be 4.13\%.
-While this margin is tight, we feel this is justified as several costs in the expenses, such as reimbursements, are left significantly inflated as compared with previous years.
-Adopting previous years’ estimates of \$60,000 for travel reimbursements leaves a spending margin of 21.6\%, matching that of the most austere contingency plans provided in previous years.
-Assuming maximum expenses and an attendance of 450 students, the total cost per student is estimated at \$501.63.
+Gratuity is omitted for all catering provided by the University Catering service, as the University is unable to accept gratuity on purchases.
+Under our most conservative estimates for budget and revenue, the spending margin is found to be 9.62\%.
+This margin is generous and in line with that allotted in previous years.
+Additionally, our budget calls for significantly higher student travel reimbursements than what where accounted for in previously proposed budgets.
+Reducing to levels proposed in recent years would free an additional $\$$ 40,000, if absolutely necessary.
+Assuming maximum expenses and an attendance of 450 students, the total cost per student is estimated at \$ 485.05.
 This number also includes the travel reimbursement, which was intentionally set to be considerably more generous than previous years to make the budget more conservative.
-Neglecting the cost of travel reimbursements, the average cost per student falls to \$276.63, at or below that estimated for previous years.
+Neglecting the cost of travel reimbursements, the average cost per student falls to \$260.05, at or below that estimated for previous years.
 

### 2019-10-01 budget.tex
final changes made

@@
 
+% \clearpage
 \begin{table}[H]
 \centering
-\caption*{\textbf{Attendance}}
+\caption*{\textbf{Attendance Revenue}}
 \begin{tabular}{|c|c|c|c|}
@@
 \subsection{Expenses}
-A conservative breakdown of conference expenses is outlined in Table ******* on page *******.
+A conservative breakdown of conference expenses is outlined in Table \ref{table:budget} on page \pageref{table:budget}.
 Emphasizing some of the points shown in the table, all rooms hosted in the Union are provided to registered student organizations (such as ANS) free of charge, which allows us to save significantly on event space.
@@
 This number also includes the travel reimbursement, which was intentionally set to be considerably more generous than previous years to make the budget more conservative.
-Neglecting the cost of travel reimbursements, the average cost per student falls to \$260.05, at or below that estimated for previous years.
+Assuming every student traveled here with the average cost of flights from Table \ref{table:airfare}, our current travel reimbursement package would cover 76.8\% of the accumulated costs.
+Neglecting the cost of travel reimbursements, the average cost per student falls to \$260.05 at or below that estimated for previous years.
+In Appendix \ref{appendix:quotes} on page \pageref{appendix:quotes} we included quotes where possible.
 
-\hspace{-1.1cm}
+% \hspace{-1.1cm}
+\begin{table}[h]
+    \caption{Budget Expenses}
+    \label{table:budget}
+    \makebox[\linewidth]{
         \begin{tabular}{|clcrccccr|}
@@
      &                           &                           &                           &                           &                          &                           &                           &                           \\ \hline
-\end{tabular}
+\end{tabular}}
+\end{table}
 
@@
 
-\begin{tabular}{lrrr}
+\begin{table}[H]
+    \caption{Budget Cuts}
+    \label{table:cuts}
+    \centering
+    \makebox[0.65\linewidth]{\begin{tabular}{lrrr}
   \hline\hline
@@
   II, III, and IV Cuts Made & $\$$ 40,393.00 & $\$$ 177,879.50 & 26.34 \% \\
-
-  \end{tabular}
+  \hline
+  \end{tabular}}
+\end{table}
 
@@
 Priority II cuts entail complete elimination of social event expenses, along with elimination of tour expenses and reduction of dinner costs through cheaper buffet options and desserts.
-The expenditure savings from these cuts are outlined in Table *******.
+The expenditure savings from these cuts are outlined in Table \ref{table:cuts}.
 While this contingency plan does not consider cuts to the reimbursement funds, this could be reconsidered if necessary, since reimbursements were set aside at a level nearly double that of previous conferences.
-\\
 
 \subsection{Sponsorship and Fundraising}
-The sponsorship breakdown for our conference pulls from averages of sponsorship packages in the last several conferences, with for main tiers that tie into the conference theme for the largest representation in the conference and visibility in the career fair, socials, sessions, technical, and meals as well as in conference shirts and attendee bags.
+The sponsorship breakdown for our conference pulls from averages of sponsorship 
+packages in the last several conferences, with four main tiers that tie into the conference theme for the largest representation in the conference and visibility in the career fair, socials, sessions, technical, and meals as well as in conference shirts and attendee bags.
 Using two tiers for an exhibitor package allows for a platform for DOE national laboratories to participate, with the higher tier having logo representation on shirts as well as the opportunity to sponsor a coffee break or lunch \& learn session.
@@
 	\centering
-	\includegraphics[width=\textwidth]{sponsors1.png}	
+	\includegraphics[width=0.75\textwidth]{sponsors1.png}	
 \end{figure} 
-
+\vspace{-1cm}
 \begin{figure}[H]
 	\centering
-	\includegraphics[width=\textwidth]{sponsors2.png}	
+	\includegraphics[width=0.75\textwidth]{sponsors2.png}	
 \end{figure}
@@
 \subsection{Cost of Attendance and Student Reimbursement}
-The cost of attending the student conference, per student, varies among schools and is highly dependent on distance from UIUC and the preferred mode of travel.
-We will assume that minimizing cost is a priority for schools, thus number of persons per hotel room is double the number of beds.
-The University of Illinois is a 2.5 hour drive from one of the largest airports in the world, O'Hare International Airport.
-There is also a small airport located just 20 minutes outside of campus.
-Additionally, there is a reliable bus service, Peoria Charter, that runs between O'Hare and the UIUC campus up to 10 times per day.
-Below are the round-trip, non-stop, airfare costs for the first weekend of April.
-Peoria Charter fare from O'Hare to UIUC is currently $\$61$ round-trip.
-While some students may wish to make use of the convenience of the local airport, in general the most economic method of arriving in Champaign is by first flying to O’Hare and then busing.
-The average cost of this trip comes out to be \$293 as shown in Table *******.
-Adding this to the registration and lodging costs for four nights (as students often arrive Wednesday evening) and assuming four students per room, the total cost of attendance for each student comes out to an average of \$447.
+The cost of attending the student conference, per student, varies among schools 
+and is highly dependent on distance from UIUC and the preferred mode of travel. 
+We will assume that minimizing cost is a priority for schools, thus number of 
+persons per hotel room is assumed to be double the number of beds. The 
+University of Illinois is a 2.5 hour drive from one of the largest airports in 
+the world, O'Hare International Airport. There is also a small airport located 
+just 15 minutes outside of campus which has regular flights to Chicago O'Hare 
+(ORD), Dallas/Fort Worth (DFW), and Charlotte (CLT). While some students may 
+wish to make use of the convenience of the local airport, in general the most 
+economic method of arriving in Champaign is by first flying to O’Hare and then 
+busing. The average cost of this trip comes out to be \$293 as shown in Table  
+\ref{table:airfare}. Adding this to the registration and lodging costs (see 
+Table \ref{table:hotels}) for four nights (as students often arrive Wednesday 
+evening) and assuming four students per room, \textbf{the total cost of attendance for 
+each student comes out to an average of \$447.} The travel reimbursement is 
+meant to help mitigate some or most of the costs for students coming to this 
+conference to encourage future attendance at other conferences.
 
 % Jeremy's budget plan
+
+\subsection{Student Travel Reimbursement Procedure}
+The procedure for student travel reimbursement will require each section send via email all acquired expenses in their travels and lodging for this conference.
+Each chapter will be required to send us:
+\begin{enumerate}
+    \item The number of students that attended.
+    \item The number of hotel rooms reserved.
+    \item The location of the hotel rooms.
+    \item Modes of transportation
+    \item Parking costs (excluding airport reserved parking).
+    \item Receipts for all purchases will be required for all submitted purchases.
+\end{enumerate}
+A form will be emailed to each of the chapter presidents for their section to fill out and attach the appropriate receipts.
+We will require that the form along with the necessary receipts be submitted via email to the Finance Director in one PDF, two weeks after the Sunday following the conference.
+The Finance Chair will review all of the submitted documents for any corrections that need to be made.
+Any section that needs to make corrections to their reimbursement form will be emailed the following Tuesday.
+The reimbursement form must be re-submitted to us by that Friday.
+Once all the sections have their forms submitted to us we will turn in our master list to ANS National for reimbursement distributions.
+Checks will be mailed to each of the chapter presidents or a selected representative for the chapter.

### 2020-11-19 addendum.tex
adds biographies and formatted images

\section*{Proposal Updates for 2020}

A few changes to the original ANS-UIUC proposal in response to the new conference date in 2022. Most of the changes involve updates to conference management structure, other changes are minimal but will be noted here.

\subsection*{Planning Committee Changes}

An overview of the changes to the planning committee are shown in Figure \ref{fig:newmgmt}. Notably, the roles of \textit{Technical Subcommittee Chair} and \textit{Logistics Subcommittee Chair} have been absorbed by the Technical Chair and the General Chair, respectively. The responsibilities of the  \textit{Sponsorship Coordinator} have been absorbed by the Financial Chair.

\begin{figure}[H]
\begin{center}
	\begin{tikzpicture}
		\node (gen chair) [chair] {General Co-Chair (Sam Dotson)};
		\node (tech chair) [chair, right of = gen chair, xshift = 5cm] {Technical Co-Chair (Jeremy Mettler)};
		\node (div chair) [chair, left of = gen chair, xshift = -5cm] {Diversity Co-Chair (Amanda Bachmann)};

		\node (prog coord) [coordinator, below of = gen chair, xshift=-1.75cm, yshift = -2cm] {Program Coordinator (Dilan K.)};
    \node (med coord) [coordinator, below of = div chair, xshift = -0.5cm, yshift = -2.0cm] {Media Coordinator (Nathan Ryan)};
		\node (hat coord) [coordinator, below of = prog coord, yshift = -2cm] {Hotels and Transport (Gavin Davis)};
		\node (hoa coord) [coordinator, below of = hat coord, yshift = -2cm] {Hospitality and Accomodations\\ (Nataly Panczyk)};
		\node (tours coord) [coordinator, below of = hoa coord, yshift = -2cm] {Tours Coordinator (Jake Mitstifer)};

		\node (work coord) [coordinator, below of = tech chair, xshift=0.5cm, yshift = -2cm] {Workshops Coordinator\\(Roberto Fairhurst)};
		\node (sesh coord) [coordinator, below of = work coord, yshift = -2cm] {Sessions Coordinator (Joshua Hoffman)};
		\node (cf coord) [coordinator, below of = sesh coord, yshift = -2cm] {Career Fair Coordinator (Greg Golba)};

		\node (fin chair) [director, below of = tech chair, xshift = -3.75cm, yshift = -2cm] {Financial Chair\\(Stephen Armstrong)};
		\node (reg coord) [coordinator, below of = fin chair, yshift = -2cm] {Registration Coordinator\\(Jasmine Dinari)};

		\draw  (gen chair) -- (tech chair);
		\draw  (gen chair) -- (div chair);

		\draw  (gen chair) -- (prog coord);
		\draw  (prog coord) -- (hat coord);
		\draw  (hat coord) -- (hoa coord);
		\draw  (hoa coord) -- (tours coord);
		\draw  (gen chair) -- (med coord);
		\draw  (tech chair) -- (fin chair);
		\draw  (gen chair) -- (fin chair);
		\draw  (fin chair) -- (reg coord);
		\draw  (tech chair) -- (work coord);
		\draw  (work coord) -- (sesh coord);
		\draw  (sesh coord) -- (cf coord);

	\end{tikzpicture}
  \caption{Note: The hierarchy of responsibility is denoted by color, not necessarily by the position on the chart.}
  \label{fig:newmgmt}
\end{center}
\end{figure}

% ===========================================================================
\subsection{Updated Biographies}
\input{new_biographies}

### 2020-11-19 biographies.tex
adds biographies and formatted images

--- 2019-10-01 management.tex
@@
-\section{Conference Management}
-
-The Conference Planning Committee is separated into three categories: Co-Chairs, Directors, Coordinators.
-The three co-chairs are responsible for setting up major milestones and ensuring that those milestones are met.
-Together they oversee all three subcommittees.
-They will serve as the primary contacts between subcommittee chairs and the faculty as well as professionals.
-The co-chairs have the final word on all conference decisions.
-They serve as the faces of the conference.
-In this proposal we have decided to add a novel Co-Chair position: Diversity Co-Chair.
-This addition reflects our goal of celebrating the people behind the science and make this conference experience accessible to as many people as possible.
-The Directors are in charge of specialized subcommittees and are responsible for making decisions in those areas.
-They must communicate with their subcommittees and with other directors to make sure there are no conflicting decisions.
-The coordinators work in an even more specialized area and help the directors by handling a single task.\\
-
-% \vspace{1cm}
-
-% ===============================================
-% This is the hierarchy breakdown
-% ===============================================
-% \begin{center}
-% 	\begin{tikzpicture}[
-% 		chair/.style={rectangle, text centered, draw,fill=blue!20, execute at begin node={\begin{varwidth}{9em}},
-%    		execute at end node={\end{varwidth}}},
-%    		committee/.style={rectangle,draw,fill=green!40, text centered, execute at begin node={\begin{varwidth}{7em}},
-%    		execute at end node={\end{varwidth}}},
-%    		coordinator/.style={rectangle,draw,fill=red!30, text centered, execute at begin node={\begin{varwidth}{7em}},
-%    		execute at end node={\end{varwidth}}},
-% 		grandchild/.style={grow=down,xshift=1em,anchor=west,
-% 		edge from parent path={(\tikzparentnode.south) |- (\tikzchildnode.west)}, execute at begin node={\begin{varwidth}{8em}},
-%    		execute at end node={\end{varwidth}}},
-% 		first/.style={level distance=12ex},
-% 		second/.style={level distance=24ex},
-% 		third/.style={level distance=36ex},
-% 		level 1/.style={sibling distance=11em}]
-% 	    % Parents
-% 	    \coordinate
-% 	      child[grow=left] {node[chair,anchor=east]{General Co-Chair \\ (Sam Dotson)}}
-% 	      child[grow=right] {node[chair,anchor=west]{Technical Co-Chair\\ (Jeremy Mettler)}}
-% 	      child[grow=down,level distance=3ex]
-% 	    [edge from parent fork down]
-% 	    % Children and grandchildren
-% 	    child{node[committee] {Non-Technical Subcommittee}
-% 	      child[grandchild,first] {node[chair]{Logistics Chair}}
-% 	      child[grandchild,second] {node[coordinator]{Hotels and Transportation}}
-% 	      child[grandchild,third] {node[coordinator] {Hospitality and Catering}}}
-% 	    child {node[committee] {Media Subcommittee}
-% 	      child[grandchild, first] {node[chair] {Publications Chair}}
-% 	      child[grandchild, second] {node[coordinator]{Media}}
-% 	      child[grandchild, third] {node[coordinator] {Program}}}
-% 	    child{node[committee] {Financial Subcommittee}
-% 	      child[grandchild,first] {node[chair]{Financial Chair}}
-% 	      child[grandchild,second] {node[coordinator]{Registration}}
-% 	      child[grandchild,third] {node[coordinator]{Sponsorship}}}
-% 	    child {node[committee]{Technical Subcommittee}
-% 	      child[grandchild,first] {node[chair]{Sessions Chair}}
-% 	      child[grandchild,second] {node[coordinator]{Workshops}}
-% 	      child[grandchild,third] {node[coordinator]{Career Fair}}};
-% 	\end{tikzpicture}
-% \end{center}
-\begin{center}
-	\begin{tikzpicture}
-		\node (gen chair) [chair] {General Co-Chair (Sam Dotson)};
-		\node (tech chair) [chair, right of = gen chair, xshift = 5cm] {Technical Co-Chair (Jeremy Mettler)};
-		\node (div chair) [chair, left of = gen chair, xshift = -5cm] {Diversity Co-Chair (Nate Reid)};
-
-		\node (log chair) [director, below of = gen chair, xshift = -3.75cm, yshift = -2cm] {Logistics Chair\\ (Natalie Gaughan)};
-		\node (med coord) [coordinator, below of = gen chair, xshift = 0.0cm, yshift = -3cm] {Media Coordinator (Nathan Ryan)};
-		\node (prog coord) [coordinator, below of = log chair, yshift = -2cm] {Program Coordinator (Dilan K.)};
-		\node (hat coord) [coordinator, below of = prog coord, yshift = -2cm] {Hotels and Transport (Gavin Davis)};
-		\node (hoa coord) [coordinator, below of = hat coord, yshift = -2cm] {Hospitality and Accomodations\\ (Brady Moran)};
-		\node (tours coord) [coordinator, below of = hoa coord, yshift = -2cm] {Tours Coordinator (Anna Balla)};
-
-		\node (tsc chair) [director, below of = tech chair, xshift = 2cm, yshift = -2cm] {Technical Sub-Committee Chair (Gwendolyn Chee)};
-		\node (work coord) [coordinator, below of = tsc chair, yshift = -2cm] {Workshops Coordinator\\(Roberto Fairhurst)};
-		\node (sesh coord) [coordinator, below of = work coord, yshift = -2cm] {Sessions Coordinator (Zach Jeckell)};
-		\node (cf coord) [coordinator, below of = sesh coord, yshift = -2cm] {Career Fair Coordinator (Greg Golba)};
-
-		\node (fin chair) [director, below of = tech chair, xshift = -2.25cm, yshift = -2cm] {Financial Chair\\(Jack Stahl)};
-		\node (spon coord) [coordinator, below of = fin chair, yshift = -2cm] {Sponsorships Coordinator (Jimmy Shehee)};
-		\node (reg coord) [coordinator, below of = spon coord, yshift = -2cm] {Registration Coordinator\\(Jasmine Dinari)};
-
-		\draw  (gen chair) -- (tech chair);
-		\draw  (gen chair) -- (div chair);
-		\draw  (gen chair) -- (log chair);
-		\draw  (log chair) -- (prog coord);
-		\draw  (prog coord) -- (hat coord);
-		\draw  (hat coord) -- (hoa coord);
-		\draw  (hoa coord) -- (tours coord);
-		\draw  (gen chair) -- (med coord);
-		\draw  (tech chair) -- (fin chair);
-		\draw  (gen chair) -- (fin chair);
-		\draw  (tech chair) -- (tsc chair);
-		\draw  (fin chair) -- (spon coord);
-		\draw  (spon coord) -- (reg coord);
-		\draw  (tsc chair) -- (work coord);
-		\draw  (work coord) -- (sesh coord);
-		\draw  (sesh coord) -- (cf coord);
-		\draw  (div chair) -- (log chair);
-
-	\end{tikzpicture}
-\end{center}
-
-% ===============================================
-% ===============================================
-% ===============================================
-
-\newpage
-\subsection{Position Responsibilities}
-
-\begin{itemize}
-	\item $\large\textbf{\textit{General Co-Chair}}$\\
-	In addition to the responsibilities outlined above, the General Co-Chair oversees the
-	Non-technical Subcommittee, the Media Coordinator, and the Financial Subcommittee. He works with the Technical Co-Chair in talking to sponsors, companies, and planning full committee meetings. 
-	\item $\large\textbf{\textit{Technical Co-Chair}}$\\
-	In addition to the responsibilities outlined above, the Technical Co-Chair primarily oversees the
-	Technical Subcommittee. Works with the General Co-Chair to plan full committee meetings and completes any remaining tasks to ensure that milestones are met.
-	\item $\large\textbf{\textit{Diversity Co-Chair}}$\\
-	In addition to the responsibilities outlined above, the Diversity 
-                Co-Chair is responsible for making sure the conference is as 
-                inclusive, diverse, and accessible as possible. This includes: 
-                contacting minority serving institutions to encourage their 
-                students to attend the conference, ensuring socials and dinners 
-                are accessible, verifying that the final list of speakers has 
-                adequate representation, engaging with the national Diversity and 
-                Inclusion in ANS Committee, and more. We believe the example set 
-                by UIUC will make this role a staple of future conferences.
-
-	\item $\textbf{Non-Technical Subcommittee}$\\
-	The Non-Technical Subcommittee oversees, arranges, and executes all actions related to hospitality, transportation, special events, and non-technical workshops and panels.
-This committee keeps the theme of the conference in mind when organizing all events.
-They ensure that the conference runs smoothly.
-	\begin{itemize}
-		\item[$\circ$] $\textbf{Logistics Chair}$\\
-		The Logistics Chair is in charge of planning all tours and non-technical workshops and panels.
-Organizes speakers during dinners.
-Recruits student volunteers to staff events and sessions during the conference.
-		Also responsible for keeping track of the subcommittee and reporting to the Co-Chairs.
-		\item[$\circ$] $\textbf{Hotels and Transportation Coordinator}$\\
-		Coordinates with ANS National to negotiate room rates and room blocks for hotels. Reserves buses for the 
-		necessary times and events. Works with the Hospitality and Catering Coordinator and the Logistics Chair.
-		\item[$\circ$] $\textbf{Hospitality and Catering Coordinator}$\\
-		Responsible for planning and organizing all catered meals for 
-                        the conference. That includes contacting the catering services, reserving the venues where meals are held, and making sure the venues are staffed.
-		\item[$\circ$]$\textbf{Tours Coordinator}$\\
-		The tours coordinator organizes tours and works with the transportation coordinator to ensure that transportation is available during the conference for these tours.
-		\item[$\circ$]$\textbf{Program Coordinator}$\\
-		The program coordinator creates programs for the conference, sets the conference schedule to minimize overlap between events and increase student involvement.
-Communicates with other coordinators and subcommittees about the schedule of events.
-Designs and purchases T-shirts for attendees.
-Arranges gift bags for attendees.
-Works with sponsorship coordinator to create gift bags.
-	\end{itemize}
-	\item $\textbf{Financial Subcommittee}$\\
-	The Financial Subcommittee oversees, arranges, and executes all actions related to banking, sponsorship, registration, reimbursement, budgeting, and monetary exchanges.
-This committee works closely with the General and Technical Co-Chairs.
-	\begin{itemize}
-		\item[$\circ$] $\textbf{Financial Chair}$\\
-		Manages the ANS Planning Committee account with Busey Bank and ANS National.
-The account coordinator is also responsible for keeping track of receipts, setting a budget for the committee, keeps track of all transactions,
-		\item[$\circ$] $\textbf{Registration Coordinator }$
-		Handles the registration for professional and student attendees. Communicates the number of attendees to the Program Coordinator. 
-		\item[$\circ$] $\textbf{Sponsorship Coordinator}$\\
-		Assists the Financial Co-Chair with matters involving sponsorship as well as working closely with the Registration and Account Coordinators and the General and Technical Co-Chairs.
-Works with the Program Coordinator on gift bag items and works with the Career Fair Coordinator.
-	\end{itemize}
-	\item $\textbf{Technical Subcommittee}$\\
-	The Technical Subcommittee works with the Technical Co-Chair to process student abstracts and set up 
-	technical workshops, panels and sessions. 
-	\begin{itemize}
-		\item[$\circ$] $\textbf{Technical Subcommittee Chair}$\\
-		 Also responsible for ensuring that judges understand the judging criteria, and organizes the award ceremony.
-		Keeps track of subcommittee progress and reports to the General and Technical Co-chairs.
-		\item[$\circ$] $\textbf{Sessions Coordinator}$\\
-		Responsible for organizing presentation, poster sessions, and technical
-		panels. Makes sure that all rooms are properly set up with equipment to ensure smooth technical sessions.
-		\item[$\circ$] $\textbf{Workshops Coordinator}$\\
-		Organizes workshops locations, times, staffing, costs, supplies, student enrollment
-		and any other tasks required to have successful workshops. Also assists the Sessions Chair when needed.
-		\item[$\circ$] $\textbf{Career Fair Coordinator}$\\
-		Oversees staffing and support for the career fair as well as working with the Sponsorship
-		Coordinator to ensure a successful career fair. Also assists the Sessions Chair when needed.
-	\end{itemize}
-	\item $\textbf{Media Coordinator}$\\
-		The Media Coordinator is responsible for designing the conference website, constantly updating social media presence,
-		and obtains information from other members of the planning committee for the website.
-\end{itemize}
-
-\newpage
-\subsection{Planning Committee Biographies}
-
 \begin{minipage}{0.25\textwidth}
@@
 \end{minipage}
-
-\subsection{Conflict Resolution}
-
-Committee members should hold professionalism at the forefront of their composure in order to avoid and resolve issues amicably without the involvement of higher powers.
-As such, members are encouraged to settle conflicts without invoking this protocol.
-If an issue arises that immediately presents itself as overwhelming, the scope of the issue exceeds an individual’s ability to handle it, or the issue imposes certain implications that jeopardizes the mission of the planning committee, members should not hesitate to refer to this section.
-In the event of a conflict between members of the planning committee, a document for decision-making and
-conflict resolution has been drafted and approved by the general committee. All General Committee members
-are expected to abide by the resolution. Key points of the resolution are as follows:
-\begin{enumerate}
-	\item Subcommittees are encouraged to resolve conflicts internally and as democratically as possible.
-If an independent resolution cannot be reached, the Co-Chairs should be involved.
-The Co-Chairs have the final word on all decisions.
-If the Co-Chairs are unable to agree on a solution, the faculty advisor will be involved.
-	\item Conflicts between individual committee members are to be resolved outside of the committee. Should such a conflict jeopradize the mission of the conference the Co-Chairs will be involved. 
-	\item Any cases of misconduct or negligence will be handled appropriately by the Co-Chairs.
-	\item For extreme cases of misconduct or negligence, separate steps for the removal and replacement of a
-	member are outlined for general members, Subcommittee Chairs, and Co-Chairs. These include
-	a discussion with the offending member, consultation of the Faculty Advisor, and a hearing with the
-	General Committee to decide if removal is necessary.
-\end{enumerate}
-
-\subsection{Staffing Requirements}
-Staffing for room breakdowns and setups, registration, socials, workshops, 
-tours, etc.  will be supplied by either UIUC ANS members or students of the 
-NPRE department. While it is likely that members of our student chapter will 
-voluntarily fill all the staffing requirements of conference hosted events. If 
-not, we will rely on other student organizations for support including, but not 
-limited to: Arms Control and Domestic and International Security (ACDIS) and 
-Women in Engineering (WIE). Participating in conference events on a staff level 
-is a beneficial experience for any undergraduate who wants to become more 
-familiar with ANS or support their ANS Chapter. Throughout the conference, 
-interacting with registering students, driving groups to tour a scientific 
-facility, and turning rooms for technical sessions provide plentiful 
-opportunities for volunteers to interact with myriad members on a number of 
-levels. Thus, it will be an overall positive experience for the volunteers. 
-Quantitative needs are outlined in Appendix \ref{appendix:staff} on page 
-\pageref{appendix:staff}.
-
-% ===============================================
-% Milestones
-% ===============================================
-\newpage
-\subsection{Milestones}
-
-\begin{center}
-\begin{longtable}{c |  c  c}
-\hline\hline
-\textbf{Deadline} & \textbf{Task} & \textbf{Responsible Committee}\\
-\hline\hline
-
-&\textbf{November}&\\
-\hline\hline
-11/21/19 & Announcement of 2021 Conference & \\
-11/21/19 & Update milestones with lessons learned &\\
-11/21/19 & Notify department of selection & Co-Chairs\\
-11/22/19 & Confirm Conference Committee & Co-Chairs\\
-11/29/19 & Finalize Conference Date & Co-Chairs\\
-\hline\hline
-&\textbf{December}&\\
-\hline\hline
-12/1/19 & Contact ANS National for support with hotel negotiations& Co-Chairs and Non-Technical\\
-12/1/19 & Set up banking through Busey Bank and ANS National& Financial\\
-12/3/19 & Confirm Conference Reservations & Non-Technical\\
-12/3/19 & Finalize Facilities Reservations& Non-Technical\\
-12/20/19 & Finalize Logo Design& Media\\
-12/20/19 & Begin Designing Website and Social Media& Media\\
-\hline\hline
-&$\textbf{2020}$&\\
-\hline\hline
-&\textbf{January}&\\
-\hline\hline
-1/13/20 & Finalize meeting schedule& Co-Chairs\\
-\hline\hline
-&\textbf{February}&\\
-\hline\hline
-2/3/20 & Launch social media plan& Media\\
-2/17/20 & Finalize list of potential speakers& Non-Technical\\
-2/17/20 & Finalize technical topics& Technical\\
-\hline\hline
-&\textbf{March}&\\
-\hline\hline
-3/9/20 & Contact Speakers and Presenters& Non-Technical and Technical\\
-3/26-28/20 & Attend Student Conference at NC State& All\\
-3/28/20 & Request lessons learned from NC State& Co-Chairs\\
-\hline\hline
-&\textbf{April}&\\
-\hline\hline
-4/6/20 & Create sponsor letters and contact & General Co-Chair\\
-4/13/20 & Prepare tour opportunities& Non-Technical\\
-\hline\hline
-&\textbf{May}&\\
-\hline\hline
-5/4/20 & Confirm tours and costs& Non-Technical\\
-5/18/20 & Submit Progress Report to SSC& Co-Chairs\\
-5/18/20 & Create a Call for Papers & Technical and Media\\
-\hline\hline
-&\textbf{June}&\\
-\hline\hline
-6/7-11/20 & Send Delegates to Annual Meeting in Arizona& Co-Chairs, All\\
-\hline\hline
-&\textbf{July}&\\
-\hline\hline
-7/6/20 & Confirm with all speakers and presenters& Technical\\
-7/20/20 & Report on sponsorship& Financial\\
-7/27/20 & Reassess budget& Financial\\
-\hline\hline
-&\textbf{August}&\\
-\hline\hline
-8/10/20 & Update with sponsors& Financial\\
-8/24/20 & Submit second progress to SSC& Co-Chairs\\
-\hline\hline
-&\textbf{September}&\\
-\hline\hline
-9/14/20 & Updates on conference deadlines& Financial\\
-9/21/20 & Finalize gift bag order& Non-Technical\\
-\hline\hline
-&\textbf{October}&\\
-\hline\hline
-10/12/20 & Confirm hotel blocks and contracts& Non-Technical\\
-10/26/20 & Registration Opens& Financial\\
-10/26/20 & Create and test online paper submission& Technical\\
-\hline\hline
-&\textbf{November}&\\
-\hline\hline
-11/15-19/20 & Attend Winter Conference 2020 in Chicago& Co-Chairs, All\\
-11/24/20 & Finalize marketing material& Media\\
-11/24/20 & Report from winter conference & Co-Chairs\\
-\hline\hline
-&\textbf{December}&\\
-\hline\hline
-12/4/20 & Reassess Budget & Financial \\
-12/4/20 & Update website & Media \\
-12/18/20 & Third progress report to SSC& Co-Chairs\\
-12/18/20 & Send out call for papers& Media\\
-\hline\hline
-&$\textbf{2021}$&\\
-\hline\hline
-&\textbf{January}&\\
-\hline\hline
-1/4/20 & Confirm all judges, panelists, and speakers& Technical\\
-1/18/20 & First paper deadline -- send to reviewers & Technical\\
-1/22/20 & Recruit student volunteers& All\\
-1/29/21 & Finalize tours& Non-Technical\\
-1/29/21& Finalize conference transportation& Non-Technical\\
-\hline\hline
-&\textbf{February}&\\
-\hline\hline
-2/1/21 & Finalize program& Media\\
-2/1/21 & Order gift bag items & Financial and Non-Technical\\
-2/5/21 & Final Paper Deadline& Technical\\
-2/9/21 & Extended Paper Deadline& \\
-2/15/21 & Finalize Website& Media\\
-2/19/21 & Finalize budget& Financial\\
-\hline\hline
-&\textbf{March}&\\
-\hline\hline
-3/22/21 & Print Programs& Media\\
-3/26/21 & Finalize Awards& Technical\\
-3/26/21 & Finalize Staff Schedule& Non-Technical\\
-3/29/21 & Final progress report to SSC& Co-Chairs\\
-\hline\hline
-&\textbf{April}&\\
-\hline\hline
-4/1/21 & Prepare gift bags, print tags, and banners& Non-Technical\\
-4/8-11/21 & Host ANS Student Conference 2021 & \\
-4/22/21 & Return seed money& Financial\\
-4/29/21 & Process Student Reimbursements& Financial\\
-4/29/21 & Finalize financial report& Financial\\
-4/29/21 & Submit conference report& Co-Chairs\\
-\hline\hline
-\end{longtable}
-\end{center}

### 2020-11-19 management.tex
adds biographies and formatted images

@@
 \subsection{Planning Committee Biographies}
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-dotson.jpg}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-	$\textbf{General Co-Chair - Sam Dotson}$\\
-Sam graduated with a B.S.
-in Physics from UIUC in 2019.
-He attended his first ANS student conference in April 2019 and was so inspired by his experience that he decided to pursue graduate work in nuclear engineering rather than physics.
-Now he does research on machine learning applications and computational reactor physics with Dr.
-Kathryn Huff in the ARFC group.
-Hosting a student conference that will inspire others the way he was inspired is one of his top priorities this year.
-He has experience planning activities for student organizations such as Guidance for Physics Students (GPS) and has experience fundraising for the College of Lake County (CLC).
-He helped set a record amount of donations at the 2016 CLC Foundation Gala, where he was an invited speaker and volunteer.
-He will be attending the ANS National conference in November 2019, as well as the ANS Student Conference 2020 at North Carolina State University.
-\end{minipage}
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-mettler.jpg}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-	$\textbf{Technical Co-Chair - Jeremy Mettler}$\\
-Jeremy graduated with a B.S.
-in Nuclear, Plasma, and Radiological Engineering from UIUC in 2018, and is now attending as a 2nd-year graduate student studying plasma science under Dr.
-David Ruzic.
-He has been heavily involved in the UIUC student chapter of ANS since his freshman year, serving on the executive board for three years as External Vice President and President.
-Jeremy has attended the past five ANS Student Conferences, which serve as an inspiration for his involvement in this proposal process.
-He is dedicated to making sure that future generations of students are able to have the same amazing experiences through ANS as he had, especially at the ANS Student Conference.
-Outside of ANS, he has held a summer internship at Oak Ridge National Lab, and is currently focusing his research towards combined laser-plasma systems for materials processing.
-\end{minipage}
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{ncreid2.jpg}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-$\textbf{Diversity Co-Chair - Nathan Reid}$\\
-	Nate graduated with a B.S.
-in Nuclear, Plasma, and Radiological Engineering from UIUC in 2016.
-He is a 4th-year Ph.D.
-student in the field of fusion and plasma science and engineering under Prof.
-Jean Paul Allain.
-Nate is currently conducting his thesis research at Oak Ridge National Laboratory, where he has spent the last three summers working in the nuclear structural materials group under the mentorship of Dr.
-Lauren Garrison.
-He will return the UIUC in December 2019.
-Nate has attended four of the last five ANS Student Conferences and was a student paper competition finalist at the TOFE embedded topical of the 2018 ANS Winter Meeting.
-Nate has been recognized by the ANS-UIUC for his outstanding graduate service in the last year, and served as the Women in Nuclear UIUC chapter Vice President.
-He was part of the executive team that received the national student chapter excellence award at the 2019 Women in Nuclear national conference, of which he was awarded a student sponsorship to attend.
-Nate is ecstatic about working alongside his ANS student section as Diversity Co-Chair and setting goals to bring inclusion to the conference.
-\end{minipage}
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-chee.jpg}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-$\textbf{Technical Subcommittee Chair - Gwendolyn Chee}$\\
-	Gwen is a third year graduate student studying fuel cycles for advanced reactor designs with Dr.
-Kathryn Huff in the ARFC group.
-Last summer she had an internship at Argonne National Laboratory where she worked on sensitivity analysis of the nuclear fuel complex.
-She also serves as the president of the UIUC chapter of Women In Nuclear (WIN).
-Under her leadership, WIN-UIUC was honored with the Best Student Chapter award at the WIN National Meeting in 2019.
-She has also been involved with ANS and attended the 2018 ANS Student Conference in Florida and will be attending the upcoming ANS Student Conference at NC State in 2020.
-\end{minipage}
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-gaughan.JPG}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-$\textbf{Logistics Chair - Natalie Gaughan}$\\
-	Natalie earned her B.S.
-in Nuclear Engineering from the University of Wisconsin-Madison in 2017.
-She has completed two summer internships at Argonne National Laboratory where she worked with various neutronics codes.
-Natalie then spent a year in Vienna as an intern at the International Atomic Energy Agency, where she helped organize and evaluate nuclear data for medical isotope production.
-She is now a graduate student at UIUC intending to research radiological science and nuclear medicine.
-As an undergraduate, Natalie attended two ANS student conferences which played a huge role in obtaining internships and inspired her decision to attend graduate school.
-Natalie knows firsthand how the ANS student conferences can be influential in students’ education and career development, and would love to help younger students experience the same benefits.
-She will also be attending the upcoming ANS student conference in 2020 at NC State.
-\end{minipage}
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-stahl.jpg}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-	$\textbf{Financial Chair - Jack Stahl}$\\
-Jack graduated with a B.S.
-in Nuclear, Plasma, and Radiological Engineering from UIUC in 2019, and is now a first-year graduate student studying plasma engineering under Dr.
-David Ruzic.
-He has been involved in the UIUC student chapter of ANS since his sophomore year and has attended two student conferences.
-Previously, Jack has spent a summer as an intern at ASML.
-Jack hopes to help host a student conference that will bolster younger student involvement in ANS.
-\end{minipage}
-
-% \vspace{1cm}
-\clearpage
-\textbf{Financial Subcommittee}\\
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-shehee.jpg}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-	$\textbf{Sponsorship Coordinator - James Shehee}$\\
-Jimmy is a junior undergraduate student in UIUC's Nuclear, Plasma, and Radiological Engineering department, with a concentration in power, safety, and the environment.
-Jimmy has been an active member of the University's ANS student chapter since his freshman year, has held the positions of Secretary and External Vice President, and was chosen to receive the chapter's Undergraduate Outstanding Service Award in the spring of 2019.
-Jimmy was first introduced to the nuclear industry through the Nuclear Science Merit Badge in Boy Scouts, and he is excited about any opportunity to create similar experiences for students and the public.
-Outside of ANS, Jimmy is also the President of the Illini Venturing Crew.
-In the summer of 2019, Jimmy interned at Exelon's Quad Cities Generating Station, and will be returning for another summer in 2020.
-He is excited to attend his first ANS Student Conference in March 2020 at North Carolina State University.
-\end{minipage}
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-dinari.jpg}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-	$\textbf{Registration Coordinator - Jasmine Dinari}$\\
-Jasmine is a freshman studying Nuclear, Plasma, and Radiological Engineering at UIUC, as well as minors in French and Physics.
-She is starting research with Dr.
-Andruczyk, who is currently at the head of the HIDRA project.
-Powering the world through nuclear is one of her main interests, and she later hopes to participate in nuclear fusion research.
-The ANS Student Conference is an  amazing opportunity to share her interests in nuclear science.
-She gained organizational and leadership experience through various extracurriculars in high school and currently serves as the Professional Development Chair for the UIUC student chapter of Women in Nuclear.
-She plans on attending the 2020 ANS Student Conference at NC State.
-\end{minipage}
-
-\vspace{1cm}
-\textbf{Technical Subcommittee}\\
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-fairhurst.jpg}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-	$\textbf{Workshops Coordinator - Roberto Fairhurst}$\\
-Roberto graduated with a B.S.
-in Nuclear Engineering from Instituto Balseiro (Argentina) April 2018.
-He is now a 2nd-year graduate student at UIUC.
-He does research on computational multi-physics solvers applied to advanced reactors as part of the Advanced Reactors and Fuel Cycle group under the supervision of Dr.
-Kathryn Huff.
-He got experience in the organization of conferences during the planning and development of a technical workshop (TWOFCS19) that took place at UIUC in June 2019.
-His motivation for hosting a student conference is his passion for Nuclear Energy and his desire to transmit this passion to other students.
-He believes hosting the student conference at UIUC will help the field grow and thrive.
-This is also an opportunity to meet other people working in the field, share life experiences, and develop a stronger network.
-\end{minipage}
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-jeckell.png}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-$\textbf{Sessions Coordinator - Zachary Jeckell}$\\
-	Zachary graduated with a B.S.
-in Nuclear, Plasma, and Radiological Engineering from UIUC in 2018 and is now a second year graduate student studying plasma engineering under Dr.
-David Ruzic.
-He has presented his research at two previous student conferences  and realized that he wanted to help bring this prestigious event to the University of Illinois.
-He strongly believes that the group of students at UIUC are capable of such a feat and that the University would make an excellent location for the conference because of its stellar program and wonderful faculty.
-He plans to attend the next ANS student conference at NC State to present research on chemical vapor deposition using atmospheric pressure plasma.
-\end{minipage}
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-golba.jpg}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-$\textbf{Career Fair Coordinator - Grzegorz Golba}$\\
-	Grzegorz Golba is a sophomore pursuing a B.S.
-in Nuclear Engineering with a physics minor in the plasma and fusion science concentration.
-He is now studying material interactions with plasma under Dr.
-Daniel Andruczyk.
-Grzegorz attended the 2019 ANS Student Conference in Virginia, reaffirmed his desire to study of nuclear science.
-He seeks new opportunities to engage with the nuclear science community and is excited for the possibilities of hosting a student conference at UIUC.
-\end{minipage}
-
-\vspace{1cm}
-\textbf{Non-Technical Subcommittee}\\
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-dilan.jpg}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-	$\textbf{Program Coordinator - Dilan Kurukulasuriya}$\\
-Dilan Kurukulasuriay is a sophomore pursuing a B.S.
-in Nuclear, Plasma, and Radiological Engineering, along with a minor in Physics and Mathematics.
-He has been active in ANS at UIUC since the start of his freshman year, and he currently serves as the Outreach Chair on the Executive Board.
-Dilan has worked at the Center for Plasma-Material Interactions lab since the start of his freshman year on HIDRA, and he stayed on campus over the summer to continue to do so.
-Dilan attended the 2019 ANS Student Conference and it was the highlight of his freshman year of college.
-He is interested in fusion science research, specifically the materials interaction aspect.
-He also plans on attending the upcoming student conference at NC State in 2020.
-\end{minipage}
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-davis.jpg}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-$\textbf{Hotels and Transportation Coordinator - Gavin Davis}$\\
-	Gavin is currently pursuing a B.S.
-in Nuclear, Plasma, and Radiological Engineering from UIUC and plans to graduate in 2022.
-He has been involved with the ANS-UIUC since his freshman year and has dedicated his time to outreach events and increasing public awareness of nuclear science and nuclear energy.
-He has accomplished this through events such as UIUC's Engineering Open House.
-It was an event he enjoyed as a kid and hopes to help other children develop an interest in nuclear sciences.
-He also returns to his high school to talk about his experience at UIUC.
-He looks forward to learning more about nuclear fission technology and to make advancements in nuclear science and in the nuclear energy sector as a whole.
-He looks forward to attending the student conference at NC State in 2020.
-\end{minipage}
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-moran.jpg}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-	$\textbf{Hospitality and Catering Coordinator - Brady Moran}$\\
-Brady a freshman in the Nuclear, Plasma, and Radiological Engineering program in the Plasma concentration.
-He is looking forward to putting his time and efforts toward ANS events throughout his years at UIUC.
-Last year, Brady planned a large tasting event, the Taste of Sauk Valley, which boasted 550 attendees, $\$$15,000 in revenue, and required him to coordinate 12 restaurants and various subcommittees.
-He is confident that this experience will help him make the Student Conference a great success.
-He will be attending the 2020 conference at NC State.
-\end{minipage}
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-balla.jpg}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-	$\textbf{Tours Coordinator - Anna Balla}$\\
-Anna is a junior in NPRE with a planned concentration in the power, safety, and the environment.
-She became interested in nuclear engineering after taking a general education class with an NPRE professor and learning about how effective nuclear power is at reducing carbon emissions.
-Anna is a teaching assistant for two classes in the NPRE department and is also very involved with the Women in Nuclear chapter at Illinois.
-In her spare time, she enjoys going to concerts, playing volleyball, and wishing she knew how to juggle.
-\end{minipage}
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-ryan.jpg}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-$\textbf{Media Coordinator - Nathan Ryan}$\\
-	Nathan is pursuing a B.S.
-in Physics from UIUC.
-He graduated in the top five of his high school class, while holding down a part time managerial position and running a research project at Argonne National Laboratory concurrent with his Sophomore through Senior years of Secondary Education.
-His first experience with Nuclear Physics was at the National Superconducting Cyclotron Laboratory where he worked with grad students on rare Cadmium isotopes.
-He has experience with building appealing website pages, as well as social media communications.
-He believes that an online presence for this event will supplement the success of an already great set of programs and individuals involved.
-He is excited to attend the upcoming ANS Student Conference at NC State in 2020.
-\end{minipage}
+\input{biographies}
 

### 2020-11-19 new_biographies.tex
adds biographies and formatted images

--- 2020-11-19 biographies.tex
@@
 He has experience planning activities for student organizations such as Guidance for Physics Students (GPS) and has experience fundraising for the College of Lake County (CLC).
-He helped set a record amount of donations at the 2016 CLC Foundation Gala, where he was an invited speaker and volunteer.
-He will be attending the ANS National conference in November 2019, as well as the ANS Student Conference 2020 at North Carolina State University.
 \end{minipage}
@@
 Jeremy graduated with a B.S.
-in Nuclear, Plasma, and Radiological Engineering from UIUC in 2018, and is now attending as a 2nd-year graduate student studying plasma science under Dr.
+in Nuclear, Plasma, and Radiological Engineering from UIUC in 2018, and is now attending as a 3rd-year graduate student studying plasma science under Dr.
 David Ruzic.
@@
 	\centering
-	\includegraphics[width=\textwidth]{ncreid2.jpg}
+	\includegraphics[width=\textwidth]{fmt-bachmanna.jpg}
 \end{minipage}
 \begin{minipage}{0.73\textwidth}
-$\textbf{Diversity Co-Chair - Nathan Reid}$\\
-	Nate graduated with a B.S.
-in Nuclear, Plasma, and Radiological Engineering from UIUC in 2016.
-He is a 4th-year Ph.D.
-student in the field of fusion and plasma science and engineering under Prof.
-Jean Paul Allain.
-Nate is currently conducting his thesis research at Oak Ridge National Laboratory, where he has spent the last three summers working in the nuclear structural materials group under the mentorship of Dr.
-Lauren Garrison.
-He will return the UIUC in December 2019.
-Nate has attended four of the last five ANS Student Conferences and was a student paper competition finalist at the TOFE embedded topical of the 2018 ANS Winter Meeting.
-Nate has been recognized by the ANS-UIUC for his outstanding graduate service in the last year, and served as the Women in Nuclear UIUC chapter Vice President.
-He was part of the executive team that received the national student chapter excellence award at the 2019 Women in Nuclear national conference, of which he was awarded a student sponsorship to attend.
-Nate is ecstatic about working alongside his ANS student section as Diversity Co-Chair and setting goals to bring inclusion to the conference.
+$\textbf{\textit{Diversity Co-Chair - Amanda Bachmann}}$\\
+Amanda has B.S.
+and M.S.
+degrees in Nuclear Engineering from the University of Tennessee at Knoxville under Professor Jamie Coble.
+Now she is a first year PhD student at the University of Illinois where she develops open-source software for nuclear fuel cycle applications with Professor Kathryn Huff.
+Amanda has served on the ANS Student Sections Committee, the Diversity and Inclusion in ANS Committee, and was recently nominated to be the Student Director on the ANS Board of Directors.
 \end{minipage}
@@
 	\centering
-	\includegraphics[width=\textwidth]{fmt-chee.jpg}
+	\includegraphics[width=\textwidth]{fmt-armstrongs.png}
 \end{minipage}
 \begin{minipage}{0.73\textwidth}
-$\textbf{Technical Subcommittee Chair - Gwendolyn Chee}$\\
-	Gwen is a third year graduate student studying fuel cycles for advanced reactor designs with Dr.
-Kathryn Huff in the ARFC group.
-Last summer she had an internship at Argonne National Laboratory where she worked on sensitivity analysis of the nuclear fuel complex.
-She also serves as the president of the UIUC chapter of Women In Nuclear (WIN).
-Under her leadership, WIN-UIUC was honored with the Best Student Chapter award at the WIN National Meeting in 2019.
-She has also been involved with ANS and attended the 2018 ANS Student Conference in Florida and will be attending the upcoming ANS Student Conference at NC State in 2020.
-\end{minipage}
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-gaughan.JPG}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-$\textbf{Logistics Chair - Natalie Gaughan}$\\
-	Natalie earned her B.S.
-in Nuclear Engineering from the University of Wisconsin-Madison in 2017.
-She has completed two summer internships at Argonne National Laboratory where she worked with various neutronics codes.
-Natalie then spent a year in Vienna as an intern at the International Atomic Energy Agency, where she helped organize and evaluate nuclear data for medical isotope production.
-She is now a graduate student at UIUC intending to research radiological science and nuclear medicine.
-As an undergraduate, Natalie attended two ANS student conferences which played a huge role in obtaining internships and inspired her decision to attend graduate school.
-Natalie knows firsthand how the ANS student conferences can be influential in students’ education and career development, and would love to help younger students experience the same benefits.
-She will also be attending the upcoming ANS student conference in 2020 at NC State.
-\end{minipage}
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-stahl.jpg}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-	$\textbf{Financial Chair - Jack Stahl}$\\
-Jack graduated with a B.S.
-in Nuclear, Plasma, and Radiological Engineering from UIUC in 2019, and is now a first-year graduate student studying plasma engineering under Dr.
-David Ruzic.
-He has been involved in the UIUC student chapter of ANS since his sophomore year and has attended two student conferences.
-Previously, Jack has spent a summer as an intern at ASML.
-Jack hopes to help host a student conference that will bolster younger student involvement in ANS.
-\end{minipage}
-
-% \vspace{1cm}
-\clearpage
-\textbf{Financial Subcommittee}\\
-
-\begin{minipage}{0.25\textwidth}
-	\centering
-	\includegraphics[width=\textwidth]{fmt-shehee.jpg}
-\end{minipage}
-\begin{minipage}{0.73\textwidth}
-	$\textbf{Sponsorship Coordinator - James Shehee}$\\
-Jimmy is a junior undergraduate student in UIUC's Nuclear, Plasma, and Radiological Engineering department, with a concentration in power, safety, and the environment.
-Jimmy has been an active member of the University's ANS student chapter since his freshman year, has held the positions of Secretary and External Vice President, and was chosen to receive the chapter's Undergraduate Outstanding Service Award in the spring of 2019.
-Jimmy was first introduced to the nuclear industry through the Nuclear Science Merit Badge in Boy Scouts, and he is excited about any opportunity to create similar experiences for students and the public.
-Outside of ANS, Jimmy is also the President of the Illini Venturing Crew.
-In the summer of 2019, Jimmy interned at Exelon's Quad Cities Generating Station, and will be returning for another summer in 2020.
-He is excited to attend his first ANS Student Conference in March 2020 at North Carolina State University.
+	$\textbf{\textit{Financial Chair - Stephen Armstrong}}$\\
+Stephen is a junior undergraduate student in UIUC's Nuclear, Plasma, and Radiological Engineering department, with a concentration in Plasma. He serves as the current Finance Chair for ANS-UIUC
 \end{minipage}
@@
 	$\textbf{Registration Coordinator - Jasmine Dinari}$\\
-Jasmine is a freshman studying Nuclear, Plasma, and Radiological Engineering at UIUC, as well as minors in French and Physics.
+Jasmine is a sophomore studying Nuclear, Plasma, and Radiological Engineering at UIUC, as well as minors in French and Physics.
 She is starting research with Dr.
@@
 She gained organizational and leadership experience through various extracurriculars in high school and currently serves as the Professional Development Chair for the UIUC student chapter of Women in Nuclear.
-She plans on attending the 2020 ANS Student Conference at NC State.
 \end{minipage}
-
-\vspace{1cm}
-\textbf{Technical Subcommittee}\\
 
@@
 in Nuclear Engineering from Instituto Balseiro (Argentina) April 2018.
-He is now a 2nd-year graduate student at UIUC.
+He is now a 3rd-year graduate student at UIUC.
 He does research on computational multi-physics solvers applied to advanced reactors as part of the Advanced Reactors and Fuel Cycle group under the supervision of Dr.
@@
 	\centering
-	\includegraphics[width=\textwidth]{fmt-jeckell.png}
+	\includegraphics[width=\textwidth]{fmt-hoffmanj.png}
 \end{minipage}
 \begin{minipage}{0.73\textwidth}
-$\textbf{Sessions Coordinator - Zachary Jeckell}$\\
-	Zachary graduated with a B.S.
-in Nuclear, Plasma, and Radiological Engineering from UIUC in 2018 and is now a second year graduate student studying plasma engineering under Dr.
-David Ruzic.
-He has presented his research at two previous student conferences  and realized that he wanted to help bring this prestigious event to the University of Illinois.
-He strongly believes that the group of students at UIUC are capable of such a feat and that the University would make an excellent location for the conference because of its stellar program and wonderful faculty.
-He plans to attend the next ANS student conference at NC State to present research on chemical vapor deposition using atmospheric pressure plasma.
+$\textbf{\textit{Sessions Coordinator - Joshua Hoffman}}$\\
+
 \end{minipage}
@@
 \end{minipage}
-
-\vspace{1cm}
-\textbf{Non-Technical Subcommittee}\\
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{fmt-moran.jpg}
+	\includegraphics[width=\textwidth]{fmt-panczykn.png}
 \end{minipage}
 \begin{minipage}{0.73\textwidth}
-	$\textbf{Hospitality and Catering Coordinator - Brady Moran}$\\
-Brady a freshman in the Nuclear, Plasma, and Radiological Engineering program in the Plasma concentration.
-He is looking forward to putting his time and efforts toward ANS events throughout his years at UIUC.
-Last year, Brady planned a large tasting event, the Taste of Sauk Valley, which boasted 550 attendees, $\$$15,000 in revenue, and required him to coordinate 12 restaurants and various subcommittees.
-He is confident that this experience will help him make the Student Conference a great success.
-He will be attending the 2020 conference at NC State.
+	$\textbf{\textit{Hospitality and Catering Coordinator - Nataly Panczyk}}$\\
+	Nataly is a freshman in Nuclear, Plasma, and Radiological Engineering at UIUC.
 \end{minipage}
@@
 	\centering
-	\includegraphics[width=\textwidth]{fmt-balla.jpg}
+	\includegraphics[width=\textwidth]{fmt-mitstiferj.png}
 \end{minipage}
 \begin{minipage}{0.73\textwidth}
-	$\textbf{Tours Coordinator - Anna Balla}$\\
-Anna is a junior in NPRE with a planned concentration in the power, safety, and the environment.
-She became interested in nuclear engineering after taking a general education class with an NPRE professor and learning about how effective nuclear power is at reducing carbon emissions.
-Anna is a teaching assistant for two classes in the NPRE department and is also very involved with the Women in Nuclear chapter at Illinois.
-In her spare time, she enjoys going to concerts, playing volleyball, and wishing she knew how to juggle.
+	$\textbf{\textit{Tours Coordinator - Jake Mitstifer}}$\\
+
 \end{minipage}
